### 2013-07-30 ceph-eval.tex
ceph report init

\documentclass{article}

\usepackage{fontspec}
\usepackage{mathptm}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{fancyvrb}
\usepackage{float}

\defaultfontfeatures{Mapping=tex-text}
\setmainfont{Times}
%\setmonofont{Consolas}
\setmonofont{Inconsolata}

\title{Ceph Parallel File System Evaluation Report}
\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
Brad Settlemyer, Scotty Atchley, Jason Hill, Mark Nelson}

%% adjust float figure placement
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{1.00}
\renewcommand{\bottomfraction}{0.70}
\renewcommand{\floatpagefraction}{0.85}

\begin{document}

\maketitle
%\authorrunning{}
%\titlerunning{}

\section{Introduction}

NCCS contracted Inktank, the major developer behind the open-sourced parallel
file system, Ceph, for a deep-dive study. It covers a wide range of technical
topics, ranging from system setup, deployment, administration to internal
mechanism. As part of this effort, we have set up a Ceph testbed within NCCS
for performance evaluation. The goal is to examine the suitability of Ceph
system as a potential candidate for our next-generation HPC storage solution.
This report presents our experience, results, and observations.

\section{Evaluation Environment Description}

The backend storage we use for this evaluation is DDN's SFA10K. It consists of
200 SAS drives and 280 SATA drives, driven by 4 hosts. Each host has
2 IB QDR connections to the storage backend. We configure and use 4 IB as
primary connections, which can saturate the maximum theoretical throughput,
around 11 - 12 GB/s. The connection diagram is illustrated as the following:

\begin{figure}[htb]
\centering
\includegraphics[width=4in]{figs/sfa10k}
\caption{DDN SFA10K Hardware Diagram}
\end{figure}

The supporting infrastructure nodes are summarized in the following table:

\begin{table}[htb]
\centering
    \begin{tabular}{ll}
    \toprule
    Node & Role \\
    \midrule
    tick-mds1 & Ceph monitor node \\
    spoon46 & Ceph MDS node \\
    tick-oss[1-4] & Ceph OSD servers \\
    spoon28-31, spoon37-41 & Ceph client nodes \\
    \bottomrule

    \end{tabular}

\end{table}

The hosts are running Redhat 6.3 with 3.5.1 kernel (rhl-ceph image), Glibc 2.12
with syncfs support, locally patched. The Ceph version is 0.55 release. For a
complete a list of hosts that are running ceph images, you can do:

\begin{Verbatim}
grep "rhel6-ceph" /etc/gedi/MAC.info
\end{Verbatim}

\section{Baseline Performance}

Before we dive into specific Ceph performance measurement, we need to establish
the baseline performance. At the block level, assuming each LUN is RAID6 8+2,
we have the following results:

\begin{table}[htb]
\centering
\begin{tabular}{ll}
    \toprule
    SAS single LUN sequential read & ~1.4 GB/s \\
    SATA single LUN sequential read & ~955 MB/s \\
    Single host with 4 SAS LUNs & ~ 2.8 GB/s \\
    Single host with 7 SATA LUNs & ~ 2.6 GB/s \\
    \bottomrule
\end{tabular}

\end{table}

Single host refers to one of tick-oss node. Overall, the entire SSU
performance has been measured to perform at 11GB/s, compare to advertised
12GB/s. Also note that we performed IP over IB test as Ceph doesn't have
native IB support. The single host performance is about 2.7 GB per second.
Later, we will see RADOS is performing a maximum of 5 to 6 GB per seconds with
4 hosts.  So, this test shows that we have enough network bandwidth.

\section{Ceph Evaluation}

In this section, we will discuss the setup and results of a series of Ceph
specific benchmark results.

\subsection{System Tuning}

After experimentation, this is a set of tuning parameters we apply:

\begin{table}[htb]
\centering
\begin{tabular}{ll}
    \toprule
    \verb!nr_requests! & 2048 \\
    \verb!read_ahead_kb! & 4096 \\
    \verb!scheduler! & deadline \\
    \verb!/proc/sys/net/ipv4/tcp_moderate_rcvbuf! & 0 \\
    \bottomrule
\end{tabular}

\end{table}

The last tuning in the table is to disable TCP auto tuning. We have observed
this will make a notable improvement on Ceph read performance.

\subsection{XFS Performance}

As we are going to make use of production ready XFS file system as the backend
local file system for Ceph, we want to see the level of performance of XFS on
SFA10K and acquire a set of sensible configuration parameters.
It is not meant to be exhaustive and full sweep of the performance
spectrum. Rather, we sample a selected set of parameters (block size, queue
depth, request size, sequential read and write), and this is the configurations
we selected: mount with \verb!nobarrier,noatim,inode64! options. The
\verb!inode64! option had a notable improvement on sequential write (around
20\%).

\begin{figure}[htb]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/xdd-read}
\caption{XFS read scaling on \# of devices}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/xdd-write}
\caption{XFS write scaling on \# of devices}
\end{minipage}%
\end{figure}

The above scaling test on the number of devices indicates that XFS can get to
peak read performance with 5 SATA LUNs, then there is a bit of degradation from
there. The parameter space explored regarding to the queue depth doesn't seem
to make any obvious difference on performance though.

\subsection{Ceph RADOS Performance}

RADOS is Ceph object store, a foundational storage component for CephFS file
system. There are three types of scaling tests we are interested at RADOS layer:

\begin{itemize}
  \item scaling on the number of servers
  \item scaling on the number of clients
  \item scaling on the number of OSDs
\end{itemize}

Our system setup poses some limitation on the scalability test we want to
perform. In particular, we currently have 4 OSS server, 8 clients, and 11 OSD
per clients. So the scaling test will be within these constraints. However, we
can do larger scale test should the interest arise.

\subsubsection{Scaling on number of OSDs}

In the following test, a single Ceph host drives $n$ number of OSDs. We
want to observe performance scaling properties when $n$ increases from 1 to
11.

\begin{figure}[htb]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/rados_osd}
\caption{RADOS scaling on \# of OSDs}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/rados_server}
\caption{RADOS scaling on \# of OSDs}
\end{minipage}%
\end{figure}

We observe that Ceph OSS exhibits near linear scalability up to 9 OSDs, and
still have room to grow at 11 OSDs. This suggests that we have not reached the
saturation point yet. The provisioning of more OSDs requires a SFA10K
reconfiguration, we will revisit this when time and resource permit.

\subsubsection{Scaling on number of servers}

In this test, we exercise OSS number from 1 to 4, driven by another 4 clients.
Each addition of OSS adds 11 more OSDs into the play. We observe that Ceph
exhibits linear scaling property with regard to number of servers as well, at
least in the given set of servers. However, the peak performance we are seeing
is about the half of what are expecting from SFA10K. The reasoning behind write
is attributed to the way Ceph perform journaling: Ceph doesn't support the
meta-data only journaling, therefore every write is equivalent of a
double-write: once to the data device, once to the journaling device. It
effectively cut the system bandwidth in half. That said, it doesn't explain the
read performance - though it is better than write, but is still far from the
theoretical maximum.

\subsection{Ceph File System Performance}

We use synthetic IOR benchmark suite for file system level test. The particular
parameter setup is show in Table \ref{tbl:ior}.

\begin{table}[tb]
\centering
\begin{tabular}{p{1.5in} | p{3in}}
    \toprule
    IOR parameter & Note \\ \midrule
    \verb!-F! & file per process \\ \midrule
    \verb!-a POSIX! & use POSIX API \\ \midrule
    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
    	ordering for read back so it won't read from the write cache. \\ \midrule
    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
    \midrule  
    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
    \verb!-b 8g or 16g! & the block size \\ \midrule
    \verb!-t 4k to 4m! & the transfer size \\ \midrule
    \verb!-o file! & mandatory test file  \\   	
    \bottomrule
\end{tabular}
\caption{IOR parameter setup}
\label{tbl:ior}
\end{table}

\begin{figure}[h]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/ior_4k}
\caption{IOR tests: 4k transfer size}
\label{fig:ior4k}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/ior_4m}
\caption{IOR tests: 4m transfer size}
\label{fig:ior4m}
\end{minipage}%
\end{figure}

Each client node has 6 GB physical memory, the block size is set so as to
mitigate the cache effect. In addition, the test harness program will issue the
following command at the beginning of each test: 
\begin{Verbatim}
# sync
# echo 3 | tee /proc/sys/vm/drop_caches
\end{Verbatim}

Here, 0 is the default value of \verb!drop_cahces!; 1 is to free pagecaches, 2
is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.

The full permutation of IOR parameters are not explored due to IO errors we ran
into (that is to be further investigated by the InkTank team). For the two
extreme cases we were to able to record, see Figure \ref{fig:ior4k} and
\ref{fig:ior4m}, we make the following observations:

\begin{itemize}
  \item The small read performance is almost an anomaly - we need to
  investigate why it is so low compare to write.
  \item The large read performance is almost half of the write performance,
  which is the opposite of RADOS level. 
  \item The write performance is cut in half compare to what we can obtain from
  RADOS benchmark. And number of clients reaches 8, there is a significant
  performance drop as well. 
\end{itemize}

\begin{figure}[htb]
\centering
\includegraphics[width=5in]{data/mdtest}
\caption{mdtest of single MDS}
\label{fig:mdtest1c}
\end{figure}

\section{Metadata Performance}

In our particular setup, we have only one metadata server (MDS)
configured. Therefore, this is not a scalability test on the performance of
clustered MDS, which would be very interesting and might as well come later.
Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
scales. The particular parameters we use for testing are:

\begin{itemize}
\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
perform sync after it. This is a more realistic use case scenario than just
open, close and removal.

\item \verb!-n 1000!: this is per client file \textit{and} directories. For 8
clients, the number of files and directories is 8,000. Since we didn't specify
either \verb!-D! or \verb!-F!, so this is a mixture of both.

\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
Lustre file system, where you can have single client multiple mounts (for
increasing workload per client), here we just give the test an explicit home.

\item \verb!-u!: without this option, we are exercising shared directory; with
this option, we are exercising unique directories.

\end{itemize}

Each test iterates 5 times and we are showing the max. Figure
\ref{fig:mdtest1c} is meant to give an overview on the trending of each
directory (prefixed with d) and file (prefixed with f) operations, against the
number of clients. Due to the scale difference, it doesn't convey the
magnitude of lower numbers. We summarize the results as follows:

\begin{itemize}

\item Within a single sharing mode (either shared or unique directory), the
directory stat and file stat, as well as file read exhibit strong linear
scaling property.

\item While the other operations seems unaffected or flat by the number of
clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
contention for shared directory. The performance degradation amount to 50\% or
more.

\item Though the same saturation or degradation trend is not observed for file
creation, it is likely due to we have not put enough of workload stress on MDS.

\end{itemize}

\begin{figure}[htb]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/mdtest-fcreate}
\caption{file creation vs.  \# of clients}
\label{fig:mdtest-fcreate}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/mdtest-dcreate}
\caption{directory creation vs. \# of clients}
\label{fig:mdtest-dcreate}
\end{minipage}%
\end{figure}

\section{Observations and Conclusions}

This is preliminary observations from mostly performance perspective:

\begin{itemize}

  \item Ceph is built on the assumption that the underlying hardware components
  is unreliable, with little or no redundancy and failure detection capability.
  This is not the case in this leadership computing facilities. We have disabled
  replication for pools, but this will take a toll somewhere in the processing
  and we don't know if this is significant.

  \item Ceph do \textbf{metadata + data} journaling, which is fine for host
  system that has locally attached disk. However, this presents a problem in DDN
  SFA10-like hardware, where the backend LUNs are exposed as block device
  through SRP over IB. The journaling write would requires double bandwidth
  compare to Lustre-like metadata only journaling mechanism. For Ceph to anything
  viable in this facility, there has to be a solution for this.

  \item Ceph is observed to have consist results and linear scalability at the
  RADOS level. However, it broke down at the file system level with synthetic
  benchmark suite such as IOR. We have experience large performance swings
  during different runs, very low read performance when transfer size is small,
  and IO errors tend to happen when system is under stress (more clients and
  large transfer size). These are not particularly reproducible results, but it
  suggests the level of maturity still have a long way to go.

\end{itemize}

\section*{Appendix: CRUSH Map}

This crush map is just an example of full OSD mapping. As we create and
re-create different testbed with different OSD configurations, the map will
change accordingly.

\input{crush.txt}

\end{document}

### 2013-07-30 data/gen.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+Rscript plotxfs.R xfs.csv
+Rscript plot_rados_osd.R rados_osd.csv
+Rscript plot_rados_client.R rados_client.csv
+Rscript plot_rados_server.R rados_server.csv
+Rscript plot_ior.R ior-8c-4k-scaling.dat
+Rscript plot_ior.R ior-8c-4m-scaling.dat
+Rscript plotxdd.R xdd-read.csv read
+Rscript plotxdd.R xdd-write.csv write
+

### 2013-07-30 data/plot_ior.R

@@ -1,0 +1,48 @@
+
+plot_xfs <- function(file) {
+    cat("Processing: ", file, "\n")
+    df=read.csv(file, strip.white=TRUE)
+
+    # compute min and max 
+    ymin=as.integer(min(df$bw))
+    ymax=as.integer(max(df$bw))
+
+    tsize=df$tsize[1]
+    np = ymax
+
+    xmin=as.integer(min(df$np))
+    xmax=as.integer(max(df$np))
+
+    quartz(type="pdf", file=paste("ior_", tsize, ".pdf", sep =""))
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    g = qplot(np, bw,
+            data=df,
+            shape=factor(df$mode),
+            color=factor(df$mode),
+            method=loess,
+            # geom=c("point", "smooth"),
+            ylab="Max (MB/s)\n",
+            xlab="\nNum of clients",
+            main=paste("4 OSS servers, blocksize=8GB, transfer size=", tsize,sep=""))
+    g = g + scale_shape_discrete(name="IO mode")
+    g = g + scale_color_discrete(name="IO mode")
+    g = g + geom_point(size=3)
+    g = g + geom_line(size=1.5)
+    g = g + opts(legend.position="top")
+    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+                    as.integer((ymax-ymin)/5)))
+    g = g + scale_x_continuous(breaks=seq(xmin, xmax))
+
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+    print(g)
+    dev.off()
+            
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+options(warn=-1)
+plot_xfs(args[1])
+
+

### 2013-07-30 data/plot_mdtest.R

@@ -1,0 +1,76 @@
+
+plot_mdtest <- function(file) {
+    cat("Processing: ", file, "\n")
+    df=read.csv(file, strip.white=TRUE, skip=1)
+
+    quartz(type="pdf", file="mdtest.pdf")
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    
+    df2 = melt(df, id.vars=c("client.num", "mode"))
+    names(df2)[3] = "ops"
+    names(df2)[4] = "max"
+    g = qplot(client.num, max, data=df2,
+              ylab = "Max (ops/second)",
+              xlab = "Number of clients",
+              main = "-n 1000 [-u] -y -w 1048576 -i 5")
+    g = g + geom_point(size=3.5)
+    g = g + geom_line(size=1.5)
+    g = g + facet_grid(mode ~ ops)
+    # g = g + opts(aspect.ratio = 2)
+    # g = g + opts(plot.margin = unit(c(1,1,2,2), 'lines'))
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+    
+    print(g)
+    
+      
+    quartz(type="pdf", file="mdtest-fcreate.pdf")
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    df2 = subset(df, , c("client.num", "mode", "fcreate"))
+    df2 = melt(df2, id.vars=c("client.num", "mode"))
+    names(df2)[3] = "ops"
+    names(df2)[4] = "max"
+    g = qplot(client.num, max, data=df2,
+              ylab = "Max (ops/second)",
+              xlab = "Number of clients")
+    g = g + geom_point(size=3.5)
+    g = g + geom_line(size=1.5)
+    g = g + facet_grid(mode ~ ops)
+    # g = g + opts(aspect.ratio = 2)
+    # g = g + opts(plot.margin = unit(c(1,1,2,2), 'lines'))
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+
+    print(g)
+
+    quartz(type="pdf", file="mdtest-dcreate.pdf")
+    theme_set(theme_bw(base_family="Lucida Grande"))
[…]

### 2013-07-30 data/plot_rados_client.R

@@ -1,0 +1,46 @@
+
+plot_xfs <- function(file) {
+    cat("Processing: ", file, "\n")
+    df=read.csv(file, strip.white=TRUE)
+
+    # compute min and max 
+    ymin=as.integer(min(df$bw))
+    ymax=as.integer(max(df$bw))
+
+
+    xmin=as.integer(min(df$client.num))
+    xmax=as.integer(max(df$client.num))
+
+    quartz(type="pdf", file="rados_client.pdf")
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    g = qplot(client.num, bw,
+            data=df,
+            shape=factor(df$mode),
+            color=factor(df$mode),
+            ylab="Max (MB/s)\n",
+            xlab="\nNum of clients",
+            main="Scaling client number on 4 node server system")
+    g = g + scale_shape_discrete(name="IO mode")
+    g = g + scale_color_discrete(name="IO mode")
+    g = g + geom_point(size=3.5)
+    #g = g + geom_smooth(method=loess, se=FALSE)
+    g = g + geom_line(size=1.5)
+    g = g + opts(legend.position="top")
+    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+                    as.integer((ymax-ymin)/5)))
+    g = g + scale_x_continuous(breaks=seq(xmin, xmax))
+
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+ 
+    print(g)
+    dev.off()
+            
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+options(warn=-1)
+plot_xfs(args[1])
+
+

### 2013-07-30 data/plot_rados_osd.R

@@ -1,0 +1,47 @@
+
+plot_xfs <- function(file) {
+    cat("Processing: ", file, "\n")
+    df=read.csv(file, strip.white=TRUE)
+
+    # compute min and max 
+    ymin=as.integer(min(df$bw))
+    ymax=as.integer(max(df$bw))
+
+
+    xmin=as.integer(min(df$osd.num))
+    xmax=as.integer(max(df$osd.num))
+
+    quartz(type="pdf", file="rados_osd.pdf")
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    g = qplot(osd.num, bw,
+            data=df,
+            shape=factor(df$mode),
+            color=factor(df$mode),
+            method=loess,
+            # geom=c("point", "smooth"),
+            ylab="Max (MB/s)\n",
+            xlab="\nNum of OSDs",
+            main="Scaling OSD on a single server single client")
+    g = g + scale_shape_discrete(name="IO mode")
+    g = g + scale_color_discrete(name="IO mode")
+    g = g + geom_point(size=3.5)
+    g = g + geom_line(size=1.5)
+    g = g + opts(legend.position="top")
+    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+                    as.integer((ymax-ymin)/5)))
+    g = g + scale_x_continuous(breaks=seq(xmin, xmax))
+
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+ 
+    print(g)
+    dev.off()
+            
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+options(warn=-1)
+plot_xfs(args[1])
+
+

### 2013-07-30 data/plot_rados_server.R

@@ -1,0 +1,46 @@
+
+plot_xfs <- function(file) {
+    cat("Processing: ", file, "\n")
+    df=read.csv(file, strip.white=TRUE)
+
+    # compute min and max 
+    ymin=as.integer(min(df$bw))
+    ymax=as.integer(max(df$bw))
+
+
+    xmin=as.integer(min(df$node.num))
+    xmax=as.integer(max(df$node.num))
+
+    quartz(type="pdf", file="rados_server.pdf")
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    g = qplot(node.num, bw,
+            data=df,
+            shape=factor(df$mode),
+            color=factor(df$mode),
+            ylab="Max (MB/s)\n",
+            xlab="\nNum of servers",
+            main="Scaling server numbers: 4 clients, 4 processes on each")
+    g = g + scale_shape_discrete(name="IO mode")
+    g = g + scale_color_discrete(name="IO mode")
+    g = g + geom_point(size=3.5)
+    #g = g + geom_smooth(method=loess, se=FALSE)
+    g = g + geom_line(size=1.5)
+    g = g + opts(legend.position="top")
+    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+                    as.integer((ymax-ymin)/5)))
+    g = g + scale_x_continuous(breaks=seq(xmin, xmax))
+
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+ 
+    print(g)
+    dev.off()
+            
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+options(warn=-1)
+plot_xfs(args[1])
+
+

### 2013-07-30 data/plotxdd.R

@@ -1,0 +1,46 @@
+
+plot_xdd <- function(f, m) {
+    cat("Processing: ", f, m , "\n")
+    df=read.csv(f, strip.white=TRUE)
+
+    # compute min and max 
+    ymin=as.integer(min(df$bw))
+    ymax=as.integer(max(df$bw))
+
+
+    xmin=as.integer(min(df$dev.num))
+    xmax=as.integer(max(df$dev.num))
+
+    quartz(type="pdf", file=paste("xdd-", m, ".pdf", sep=""))
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    g = qplot(dev.num, bw,
+            data=df,
+            shape=factor(df$qd),
+            color=factor(df$qd),
+            method=loess,
+            #geom=c("point", "smooth"),
+            ylab="Max (MB/s)\n",
+            xlab="\nNum of Devices",
+            main=paste("XFS ", m, " xdd -dio, req.size=32768", sep=""))
+    g = g + scale_shape_discrete(name="queue depth")
+    g = g + scale_color_discrete(name="queue depth")
+    g = g + geom_point(size=3.5)
+    g = g + geom_line(size=1.5)
+    g = g + opts(legend.position="top")
+    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+                    as.integer((ymax-ymin)/5)))
+    g = g + scale_x_continuous(breaks=seq(xmin, xmax))
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+ 
+    print(g)
+    dev.off()
+            
+}
+
+args = commandArgs(trailingOnly = TRUE)
+print(args)
+options(warn=-1)
+plot_xdd(args[1], args[2])
+
+

### 2013-07-30 data/plotxfs.R

@@ -1,0 +1,46 @@
+
+plot_xfs <- function(file) {
+    cat("Processing: ", file, "\n")
+    df=read.csv(file, strip.white=TRUE)
+
+    # compute min and max 
+    ymin=as.integer(min(df$bw.max))
+    ymax=as.integer(max(df$bw.max))
+
+
+    xmin=as.integer(min(df$num.dev))
+    xmax=as.integer(max(df$num.dev))
+
+    quartz(type="pdf", file="xfs.pdf")
+    theme_set(theme_bw(base_family="Lucida Grande"))
+    g = qplot(num.dev, bw.max,
+            data=df,
+            shape=factor(df$mode),
+            color=factor(df$mode),
+            method=loess,
+            geom=c("point", "smooth"),
+            ylab="Max (MB/s)\n",
+            xlab="\nNum of Devices",
+            main="XFS, xdd -dio qd=4, req.size=32768")
+    g = g + scale_shape_discrete(name="IO mode")
+    g = g + scale_color_discrete(name="IO mode")
+    g = g + geom_point(size=3.5)
+    g = g + geom_smooth(size=1.5)
+    g = g + opts(legend.position="top")
+    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+                    as.integer((ymax-ymin)/5)))
+    g = g + scale_x_continuous(breaks=seq(xmin, xmax))
+    g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
+    g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))
+ 
+    print(g)
+    dev.off()
+            
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+options(warn=-1)
+plot_xfs(args[1])
+
+

### 2013-07-30 data/test.R

@@ -1,0 +1,8 @@
+xdd = function(file, mode) {
+    print(file)
+    print(mode)
+    }
+
+args = commandArgs(trailingOnly=TRUE)
+print(args)
+xdd (args[1],args[2])

### 2013-08-15 ceph-eval.tex
update with mark's input

@@
 \usepackage{microtype}
-\usepackage{hyperref}
 \usepackage{fancyvrb}
 \usepackage{float}
+\usepackage{setspace}
+
+\usepackage[colorlinks = true,%
+            linkcolor = blue,%
+            urlcolor  = blue,%
+            citecolor = blue,%
+            anchorcolor = blue]{hyperref}
+
+\onehalfspacing
 
 \defaultfontfeatures{Mapping=tex-text}
-\setmainfont{Times}
-%\setmonofont{Consolas}
-\setmonofont{Inconsolata}
+
+\setmainfont{rosario}
+\setmonofont{Consolas}
+%\setmainfont{Times}
+%\setmonofont{Inconsolata}
+%\setmonofont[Scale=0.8]{Monaco}
+%\setmonofont[Scale=0.8]{Courier}
 
@@
 
+\graphicspath{{./figs/}}
+\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+
 \begin{document}
 
-\maketitle
+\input{cover}
+
+%\maketitle
 %\authorrunning{}
@@
 file system, Ceph, for a deep-dive study. It covers a wide range of technical
-topics, ranging from system setup, deployment, administration to internal
-mechanism. As part of this effort, we have set up a Ceph testbed within NCCS
-for performance evaluation. The goal is to examine the suitability of Ceph
-system as a potential candidate for our next-generation HPC storage solution.
-This report presents our experience, results, and observations.
+topics: from system setup, deployment, administration to internal mechanism. In
+comparison to other parallel file systems, Ceph has a number of distinctive
+features:
 
-\section{Evaluation Environment Description}
+\begin{itemize}
+  \item Ceph has an intelligent and powerful data placement mechanism, known as
+  CRUSH. CRUSH algorithm allows the client side to pre-calculate the layout
+  info, and take failure domain, hierarchical storage tiers into placement
+  consideration.
 
-The backend storage we use for this evaluation is DDN's SFA10K. It consists of
-200 SAS drives and 280 SATA drives, driven by 4 hosts. Each host has
-2 IB QDR connections to the storage backend. We configure and use 4 IB as
-primary connections, which can saturate the maximum theoretical throughput,
-around 11 - 12 GB/s. The connection diagram is illustrated as the following:
+  \item From the on start, Ceph is designed to manage metadata and name space
+  with a cluster of metadata servers.
+
+\item Ceph is designed with the assumption that system is composed with
+unreliable components, so replication and failure detection and tolerance are
+the norm rather than the exception. This is in line with the expectation of
+exascale computing.
+
+\item Ceph is built on top of a unified object management layer,
+\texttt{RADOS}. Both metadata and the actual data can take advantage of this
+uniformity.
+
+\item Most of Ceph code base are in user-space. Generally speaking, it makes the
+system easier to debug and maintain. The client side support has long been
+integrated into Linux mainline kernel, which make the deployment and out-of-box
+experience easier.
+
+\end{itemize}
+
+As part of this effort, we set up a dedicated testbed within NCCS for Ceph
+system evaluation. The goal is to investigate the feasibility of Ceph system as
+a potential candidate for our next-generation HPC storage solution.
+This report presents our experience, results, and observations. While evaluating
+our results, please keep in mind that Ceph is such a moving target that its
+code base is changing rapidly. In between releases, we often see different
+outcomes. We will try to make clear when such change happens in the report.
+
+\section{Testbed Environment Description}
+
+The storage backend we have for this evaluation is DDN's SFA10K. It consists of
+200 SAS drives and 280 SATA drives, driven by 4 hosts. Each host has 2 IB QDR
+connections to the storage backend. We configure and use 4 Mellanox IB cards as
+primary connections, which by calculation can saturate the maximum theoretical
+throughput, around 11 - 12 GB/s. The connection diagram is illustrated as the
+following:
 
@@
 
-\begin{table}[htb]
+\begin{table}[H]
 \centering
@@
 The hosts are running Redhat 6.3 with 3.5.1 kernel (rhl-ceph image), Glibc 2.12
-with syncfs support, locally patched. The Ceph version is 0.55 release. For a
+with syncfs support, locally patched. The Ceph version is 0.55 release in the
+initial test, then upgraded to 0.64 and 0.67RC for second round of test. For a
 complete a list of hosts that are running ceph images, you can do:
@@
 
-Before we dive into specific Ceph performance measurement, we need to establish
-the baseline performance. At the block level, assuming each LUN is RAID6 8+2,
-we have the following results:
+\subsection*{Block I/O}
+We first establish the baseline performance by measuring block I/O performance.
+At the block level, with LUN configured as RAID6 8+2, we have the following
+results:
 
@@
     SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\
+    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
     Single host with 4 SAS LUNs & ~ 2.8 GB/s \\
@@
 
-Single host refers to one of tick-oss node. Overall, the entire SSU
-performance has been measured to perform at 11GB/s, compare to advertised
-12GB/s. Also note that we performed IP over IB test as Ceph doesn't have
-native IB support. The single host performance is about 2.7 GB per second.
-Later, we will see RADOS is performing a maximum of 5 to 6 GB per seconds with
-4 hosts.  So, this test shows that we have enough network bandwidth.
+Single host refers to one of 4 tick-oss nodes, which drives the entire SSU.
+Overall, the entire SSU performance can perform at 11GB/s, comparing to
+theoretical maximum of 12GB/s.
 
-\section{Ceph Evaluation}
+\subsection*{IP over IB}
 
-In this section, we will discuss the setup and results of a series of Ceph
-specific benchmark results.
+Note that we are using IP over IB for networking, since Ceph doesn't have
+native IB support\footnote{Inktank is developing rsocket alternative to better take
+advantage of IB fabric}.
+A single host with IP over IB (QDR) can perform at 2.7 GB per second with
+Mellanox recommended tuning applied. With all 4 hosts (OSD servers), we expect
+the aggregate throughput is in the neighborhood of 10GB/s.
 
-\subsection{System Tuning}
+Unfortunately there was not enough time to do more detailed analysis of network
+bisection bandwidth. Later, we will see RADOS is performing a
+maximum of 5 to 6 GB per seconds driven by 4 hosts.  So, this test shows that we
+have enough network bandwidth, i.e., IP over IB is not a bottleneck in this
+case.
 
-After experimentation, this is a set of tuning parameters we apply:
+\section{The Starting Point of System Tuning}
+
+Base upon past experience and further experimentation, we started out on the
+following set of tuning parameters:
 
@@
     \verb!scheduler! & deadline \\
-    \verb!/proc/sys/net/ipv4/tcp_moderate_rcvbuf! & 0 \\
     \bottomrule
@@
 
-The last tuning in the table is to disable TCP auto tuning. We have observed
-this will make a notable improvement on Ceph read performance.
+\section{XFS Performance}
 
-\subsection{XFS Performance}
-
-As we are going to make use of production ready XFS file system as the backend
-local file system for Ceph, we want to see the level of performance of XFS on
-SFA10K and acquire a set of sensible configuration parameters.
-It is not meant to be exhaustive and full sweep of the performance
-spectrum. Rather, we sample a selected set of parameters (block size, queue
-depth, request size, sequential read and write), and this is the configurations
-we selected: mount with \verb!nobarrier,noatim,inode64! options. The
-\verb!inode64! option had a notable improvement on sequential write (around
+As we plan to use XFS file system as the backend local file system for Ceph, we
+examine XFS against SFA10K to acquire a set of sensible configuration parameters
+for optimized performance. We sampled a selected set of parameters (block size,
+queue depth, request size, sequential read and write), and this is the
+configurations we selected: mount with \verb!nobarrier,noatim,inode64! options.
+The \verb!inode64! option had a notable improvement on sequential write (around
 20\%).
@@
 \caption{XFS read scaling on \# of devices}
+\label{fig:xfs-read}
 \end{minipage}%
@@
 \caption{XFS write scaling on \# of devices}
+\label{fig:xfs-write}
 \end{minipage}%
@@
 
-The above scaling test on the number of devices indicates that XFS can get to
-peak read performance with 5 SATA LUNs, then there is a bit of degradation from
-there. The parameter space explored regarding to the queue depth doesn't seem
-to make any obvious difference on performance though.
+The read and write result are summarized in Figure~\ref{fig:xfs-read}
+and Figure~\ref{fig:xfs-write}. These scaling test on the number of devices
+indicates that XFS can get to peak read performance with 5 SATA LUNs, then there
+is a bit of degradation from there. The parameter space explored regarding to
+the queue depth doesn't seem to make any obvious difference on the performance
+though.
 
-\subsection{Ceph RADOS Performance}
+\section{Ceph RADOS Scaling: Initial Test}
 
-RADOS is Ceph object store, a foundational storage component for CephFS file
+RADOS is Ceph object store, a foundational component for CephFS file
 system. There are three types of scaling tests we are interested at RADOS layer:
@@
 perform. In particular, we currently have 4 OSS server, 8 clients, and 11 OSD
-per clients. So the scaling test will be within these constraints. However, we
-can do larger scale test should the interest arise.
+per clients. So the scaling test will be within these constraints.
 
-\subsubsection{Scaling on number of OSDs}
+An open source tool developed by Inktank called RADOS bench was do perform
+initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
+writes out objects to the underlying object storage as fast as possible, and
+then later reads those objects in the same order as they were written.
 
-In the following test, a single Ceph host drives $n$ number of OSDs. We
-want to observe performance scaling properties when $n$ increases from 1 to
-11.
+We've observed that using more than one client processes and lots of concurrent
+operations is important when performing these tests.  8 Client processes are
+used with 32 concurrent 4MB Objects in flight each, and a pool is created for
+each RADOS bench process to ensure that object reads come from independent pools
+(RADOS bench is not smart enough to ensure that objects are not read by multiple
+processes and thus possibly cached).  A sync and flush is performed on every
+node before every test to ensure no data or metadata is in cache.  All tests
+were run with 1X replication.  Unfortunately at this time only XFS was present
+and usable for the underlying OSDs so BTRFS and EXT4 file systems were not
+tested at this time.
 
-\begin{figure}[htb]
+\subsection{Scaling on number of OSDs}
+
+In the following test, a single Ceph host drives $n$ number of OSDs, where $n$
+increases from 1 to 11. The result is illustrated in Figure~\ref{fig:osd-scale}.
+We ran the test against a single client with 4 concurrent process. In this test
+case, we observe that Ceph OSS exhibits near linear scalability up to 9
+OSDs, and still have room to grow at 11 OSDs. This suggests that we have not reached the
+saturation point yet. It requires provisioning of more OSDs at SFA10K backend.
+
+\begin{figure}[H]
 \centering
@@
 \caption{RADOS scaling on \# of OSDs}
+\label{fig:osd-scale}
 \end{minipage}%
@@
 \includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on \# of OSDs}
+\caption{RADOS scaling on \# of servers}
+\label{fig:oss-scale}
 \end{minipage}%
@@
 
-We observe that Ceph OSS exhibits near linear scalability up to 9 OSDs, and
-still have room to grow at 11 OSDs. This suggests that we have not reached the
-saturation point yet. The provisioning of more OSDs requires a SFA10K
-reconfiguration, we will revisit this when time and resource permit.
+\subsection{Scaling on number of servers}
 
-\subsubsection{Scaling on number of servers}
+In this test, we exercise OSS number from 1 to 4, driven by 4 clients with 4
+concurrent process for each client. Each addition of OSS adds 11 more OSDs into
+the play. We observe that Ceph exhibits linear scaling property with regard to
+number of servers as well, at least in the given set of servers. However, the peak
+performance we are seeing is about the half of what are expecting from SFA10K.
+For the write, the reason behind it is attributed to the way Ceph perform
+journaling: Ceph doesn't support the meta-data only journaling, therefore every
+write is equivalent of a double-write: once to the data device, once to the
+journaling device. It effectively cut the system bandwidth in half. That said,
+it doesn't explain the read performance - though it is better than write, but is
+still far from the theoretical maximum.
 
-In this test, we exercise OSS number from 1 to 4, driven by another 4 clients.
-Each addition of OSS adds 11 more OSDs into the play. We observe that Ceph
-exhibits linear scaling property with regard to number of servers as well, at
-least in the given set of servers. However, the peak performance we are seeing
-is about the half of what are expecting from SFA10K. The reasoning behind write
-is attributed to the way Ceph perform journaling: Ceph doesn't support the
-meta-data only journaling, therefore every write is equivalent of a
-double-write: once to the data device, once to the journaling device. It
-effectively cut the system bandwidth in half. That said, it doesn't explain the
-read performance - though it is better than write, but is still far from the
-theoretical maximum.
-
-\subsection{Ceph File System Performance}
+\section{Ceph File System Performance: Initial Test}
 
 We use synthetic IOR benchmark suite for file system level test. The particular
-parameter setup is show in Table \ref{tbl:ior}.
+parameter setup is show in Table \ref{tbl:ior}. Each client node has 6 GB
+physical memory, the block size is set so as to mitigate the cache effect. In
+addition, the test harness program will issue the following command at the
+beginning of each test:
 
@@
 
-\begin{figure}[h]
+\begin{Verbatim}
+# sync
+# echo 3 | tee /proc/sys/vm/drop_caches
+\end{Verbatim}
+
+Here, 0 is the default value of \verb!drop_cahces!; 1 is to free pagecaches, 2
+is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
+
+Our first round of test was less than ideal as we encountered various issue. For
+the sake of completeness, we still first summarized the results, then discuss
+the further tuning efforts and improvements.
+
+The full permutation of IOR parameters are not explored due to IO errors we ran
+into. We were, however, able to record results in two extreme case as far as
+transfer size is concerned: 4KB and 4MB, using the same number of OSS servers
+(4) and same block size (8GB), the results are illustrated in Figure
+\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
+
+\begin{figure}[H]
 \centering
@@
 
-Each client node has 6 GB physical memory, the block size is set so as to
-mitigate the cache effect. In addition, the test harness program will issue the
-following command at the beginning of each test: 
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_cahces!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-The full permutation of IOR parameters are not explored due to IO errors we ran
-into (that is to be further investigated by the InkTank team). For the two
-extreme cases we were to able to record, see Figure \ref{fig:ior4k} and
-\ref{fig:ior4m}, we make the following observations:
-
 \begin{itemize}
@@
 
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=5in]{data/mdtest}
+%\caption{mdtest of single MDS}
+%\label{fig:mdtest1c}
+%\end{figure}
+
+We will describe the efforts and results on performance improvement in the
+following sections.
+
+\section{Improving RADOS Performance}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=5in]{parametric}
+\caption{Evaluating parameter impact through sweeping test}
+\label{fig:parametric}
+\end{figure}
+
+After the initial test results were found, various combinations of tweaks were
+attempted including changing the number of filestore op threads, putting all
+of the journals on the same disks as the data, doubling the OSD count, and
+upgrading Ceph to a development version which reduces the seek overhead caused
+by \texttt{pginfo} and \texttt{pglog} updates on XFS (These enhancements are
+now included as of the Ceph Cuttlefish release).  The two biggest improvements
+resulted from disabling CRC32c checksums and increasing the OSD count on the
+server.  With these changes, we are seeing better results.
+
+A script written by Inktank for internal Ceph testing was used to perform
+parametric sweeps over Ceph configuration parameters to examine how different
+tuning options affect performance on the DDN platform. The result of this
+parameter probing is illustrated in Figure~\ref{fig:parametric}.
+
+As a result of this testing, performance was again improved slightly by
+increasing the size of various Ceph buffers and queues, enabling aio journals,
+and increasing the number of OSD op threads.
+
+\subsection{Disable Cache Mirroring on DDN}
+
+Despite the excellent write throughput we saw during the individual server
+tests, throughput did not scale.  A significant amount of time was spent
+investigating this phenomena. Ultimately, we were able to replicate this finding
+when running concurrent disk throughput tests directly on the servers without
+Ceph involved. The 2nd RAID processor on each DDN controller would max out when
+3 or more LUNs were written concurrently. It turns out the root of the problem
+is attributed to a regression on DDN firmware update - in particular, the cache
+mirroring is not behaving as it should be.
+
 \begin{figure}[htb]
 \centering
-\includegraphics[width=5in]{data/mdtest}
-\caption{mdtest of single MDS}
-\label{fig:mdtest1c}
+\includegraphics[width=4in]{rados-after-ddn}
+\caption{Evaluating RADOS bench after disabling cache mirroring}
+\label{fig:rados-ddn-mirror-disabled}
 \end{figure}
+
+With cache mirroring disabled write performance when using all 4 servers
+improved dramatically, as illustrated in
+Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS for example, we hit over
+5.5GB/s from the clients.  When accounting for journal writes, that is over
+11GB/s to the disks and very close to what the DDN chassis is capable of doing. 
+Unfortunately, read performance did not scale as well.
+
+\subsection{Disable TCP autotuning}
+
+During these tests, a trend that previously had been seen became more apparent.
+During reads, there were periods of high performance followed by periods of low
+performance or outright stalls that could last for up to 20 seconds at a time. 
+After several hours of diagnostics, Inktank observed that outstanding operations
+on the clients were not being shown as outstanding on the OSDs.  This appeared
+to be very similar to a problem Jim Schutt at Sandia National labs encountered
+with TCP autotuning in the Linux Kernel.
+\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}.
+TCP auto tuning enables TCP window scaling by default and automatically adjust
+the TCP receive window for each connection based on link conditions such as
+bandwidth delay product. We have observed this will make a notable improvement
+on Ceph read performance, as the results shown in
+Figure~\ref{fig:rados-tcp-auto-disabled}.
+
+Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
+
+\begin{Verbatim}
+     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
+\end{Verbatim}
+
+Recent versions of Ceph work around this issue by manually controlling the TCP
+buffer size.  The testing at ORNL directly influenced and motivated the creation
+of this feature!
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
+\caption{Evaluating RADOS bench after TCP auto tuning disabled}
+\label{fig:rados-tcp-auto-disabled}
+\end{figure}
+
+%\begin{figure}[htb]
+%\includegraphics[width=5in]{rados-064-oss}
+%\end{figure}
+
+\subsection{Repeating RADOS Scaling Test}
+
+We now repeated previous RADOS scaling test with these improvements in place.
+The first test was done on a single node with RADOS bench to see how close the
+underlying object store could get to the node hardware limitations as the number
+of OSDs/LUNs used on the node increase. Note all the tests performed are against
+XFS formatted storage.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=5in]{rados-064-osd}
+\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4MB IO, 8 Client Nodes}
+\label{fig:rados-064-osd}
+\end{figure}
+
+In the single server case as shown in Figure~\ref{fig:rados-064-osd},
+performance gets very close to the hardware limits at roughly 9 OSDs per server
+and then mostly levels out.
+
+We also repeated tests looking at RADOS Bench performance as the
+number of OSD server nodes increases. The result is summarized in
+Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
+scales nearly linearly for both reads and writes.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=5in]{rados-064-oss}
+\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4MB IO, 8 Client Nodes}
+\label{fig:rados-064-oss}
+\end{figure}
+
+\section{Improving Ceph File System Performance}
+
+The initial stability issues we encountered are fixed by moving Ceph version
+from 0.48/0.55 to 0.64, latest stable at the time. Now IOR test can proceed to
+finish even during long runs. It is another sign of showing how much Ceph
+development is in flux.
+
+Another fix comes the way we create the pool: the default data pool being used
+by previous CephFS cluster are set to 2x replication, which can potentially
+halve the write performance. Even with these changes in place, Inktank still
+reproduced the less-than-ideal write performance and very poor read
+performance as observed by ORNL.  Further, by increasing the number of IOR
+processes per client node, read performance actually degraded further
+indicating some kind of contention either on the clients or on the OSD
+servers.
+
+\subsection{Disabling Client CRC32}
+
+ORNL at this point was able to both make more client nodes available and also
+install a profiling tool called \textbb{perf} that is extremely useful for
+profiling both kernel and user space code.  Profiling with perf showed high CPU
+utilization on the client due to crc32c processing in the Ceph kernel client. 
+Luckily crc32 checksums can be disabled by changing the CephFS mount options:
+
+\begin{Verbatim}
+mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
+\end{Verbatim}
+
+With client CRC32 disabled, we repeated the IOR test and the results are showin
+in Figure~\ref{fig:ior-no-client-crc32}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=4in]{ior-client-no-crc32}
+\caption{IOR test with no client side CRC32}
+\label{fig:ior-no-client-crc32}
+\end{figure}
+
+We observed that IOR write throughput increased dramatically and is now very
+close to the throughput we were able to achieve with RADOS Bench, but reads
+continued to be slow, and continued to inversely scale with the number of client
+processes.  Please note that since these tests were performed, Inktank has
+implemented SSE4 based CRC32 code for Intel CPUs.  While any kernel based CRC32
+processing should have already been using SSE4 instructions on Intel CPUs, this
+will allow any user land Ceph processes to process CRC32 checksums with
+significantly less overhead.
+
+\subsection{Improving IOR Read Performance}
+
+Deeper analysis with perf showed that there was heavy lock contention during
+parallel compaction in the Linux kernel memory manager.  This behavior was first
+observed roughly in the kernel 3.5 time frame which happens to be the kernel
+that ORNL had installed on the test systems.\footnote{For more information,
+please refer to \url{http://lwn.net/Articles/517082/} and
+\url{https://patchwork.kernel.org/patch/1338691/}.}
+
+ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
+RADOS bench test to verify that there was no degradation vs previous tests.  The
+results were extremely positive.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=4in]{rados-kernel-35vs39}
+\caption{RADOS bench: Kernel 3.5 vs. 3.9}
+\label{fig:rados-kernel}
+\end{figure}
+
+With the kernel changes writes performance improved slightly, while read
+performance improved dramatically.  In addition to the kernel change, Sage Weil
+suggested increasing the amount of read ahead being performed by the CephFS
+kernel client:
+
+\begin{Verbatim}[samepage=true]
+mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
+   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
+\end{Verbatim}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=4in]{ior-kernel-39}
+\caption{Kernel changes to 3.9, IOR with 4MB transfer size}
+\label{fig:ior-kernel-39}
+\end{figure}
+
+By installing a new kernel, increasing read ahead, and increasing the number of
+client IOR processes, we were able to achieve a very satisfactory result on this
+test run.
+
+\subsection{Repeating IOR Scaling Test}
+
+As before, we ran IOR scaling test with two cases: transfer size 4K and 4M.
+These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
+seeing a much improved picture of read and write performance, very much in
+line with RADOS bench performance.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=5in]{ior-064-4k}
+\includegraphics[width=5in]{ior-064-4m}
+\caption{IOR Scaling Test: 4KB and 4MB transfer size}
+\label{fig:ior-064}
+\end{figure}
+
+We observe that a couple of places where the average write throughput is quite a
+bit lower than the max.  This behavior was observed during other tests as well,
+indicating that we may have periods of time where write throughput is
+temporarily degrading.  Despite these issues, performance general seems to be
+improving as the number of clients increases.  Writes seem to be topping out at
+around 5.2GB/s (which is roughly what we would expect).  Reads seem to be
+topping out anywhere from 5.6-7GB/s, however it is unclear if read performance
+would continue scaling with more clients and get closer to the 8GB/s+ numbers we
+saw with RADOS Bench.
 
@@
 
-Each test iterates 5 times and we are showing the max. Figure
-\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-directory (prefixed with d) and file (prefixed with f) operations, against the
-number of clients. Due to the scale difference, it doesn't convey the
-magnitude of lower numbers. We summarize the results as follows:
+Each test iterates 5 times and we are showing the max. 
+We summarize the results as follows:
+
+%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
+%directory (prefixed with d) and file (prefixed with f) operations, against the
+%number of clients. Due to the scale difference, it doesn't convey the
+%magnitude of lower numbers.
 
@@
 
-\section*{Appendix: CRUSH Map}
+\section*{Appendix A - CephFS Final Mount Command}
+
+\begin{Verbatim}
+mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
+      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
+\end{Verbatim}
+
+\section*{Appendix B - OSD File System Options}
+
+\input{osd_fs.txt}
+
+\section*{Appendix C - CRUSH Map}
 
@@
 
+\section*{Appendix D - Final ceph.conf}
+
+\input{ceph-short.txt}
+
 \end{document}

### 2013-08-15 cover.tex
update with mark's input

\thispagestyle{empty}

\hfill ORNL/TM-2013/151

\vspace{3em}

\begin{center}
National Center for Computatational Sciences
\end{center}

\vspace{3em}

\begin{center}
\textbf\textsc{\Large Ceph Parallel File System Evaluation Report}\\
\rule{5in}{1pt}%
\end{center}

\vspace{0.5in}

\begin{center}
\begin{tabular}{ c c }
Feiyi Wang  &  Mark Nelson \\ 
ORNL/NCCS & Inktank Inc. \\
\end{tabular}
\end{center}

\vspace{0.25in}

\begin{center}
Other contributors: \\
\vspace{1em}
Sarp Oral\\
Doug Fuller\\
Scotty Atchley\\
Blake Caldwell\\
James Simmons\\
Brad Settlemyer\\
Jason Hill\\
Sage Weil (Inktank Inc.)
\end{center}

\vfill

\begin{center}
Prepared by \\
OAK RIDGE NATIONAL LABORATORY\\
Oak Ridge, Tennessee 37831-6283 \\ 
managed by \\
UT-BATTELLE, LLC \\
for the \\
U.S. DEPARTMENT OF ENERGY\\ 
under contract DE-AC05-00OR22725
\end{center}

\pagebreak

### 2013-08-15 data/plot_ior.R

@@ -1,3 +1,4 @@
+require("ggplot2")
 
 plot_xfs <- function(file) {
     cat("Processing: ", file, "\n")
@@ -14,7 +15,7 @@ plot_xfs <- function(file) {
     xmax=as.integer(max(df$np))
 
     quartz(type="pdf", file=paste("ior_", tsize, ".pdf", sep =""))
-    theme_set(theme_bw(base_family="Lucida Grande"))
+    theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(np, bw,
             data=df,
             shape=factor(df$mode),
@@ -23,7 +24,7 @@ plot_xfs <- function(file) {
             # geom=c("point", "smooth"),
             ylab="Max (MB/s)\n",
             xlab="\nNum of clients",
-            main=paste("4 OSS servers, blocksize=8GB, transfer size=", tsize,sep=""))
+            main=paste("IOR: transfer size=", tsize,sep=""))
     g = g + scale_shape_discrete(name="IO mode")
     g = g + scale_color_discrete(name="IO mode")
     g = g + geom_point(size=3)

### 2013-08-15 data/plot_rados_client.R

@@ -1,3 +1,4 @@
+require("ggplot2")
 
 plot_xfs <- function(file) {
     cat("Processing: ", file, "\n")
@@ -12,7 +13,7 @@ plot_xfs <- function(file) {
     xmax=as.integer(max(df$client.num))
 
     quartz(type="pdf", file="rados_client.pdf")
-    theme_set(theme_bw(base_family="Lucida Grande"))
+    theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(client.num, bw,
             data=df,
             shape=factor(df$mode),

### 2013-08-15 data/plot_rados_osd.R

@@ -1,3 +1,4 @@
+require("ggplot2")
 
 plot_xfs <- function(file) {
     cat("Processing: ", file, "\n")
@@ -12,7 +13,7 @@ plot_xfs <- function(file) {
     xmax=as.integer(max(df$osd.num))
 
     quartz(type="pdf", file="rados_osd.pdf")
-    theme_set(theme_bw(base_family="Lucida Grande"))
+    theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(osd.num, bw,
             data=df,
             shape=factor(df$mode),
@@ -21,14 +22,18 @@ plot_xfs <- function(file) {
             # geom=c("point", "smooth"),
             ylab="Max (MB/s)\n",
             xlab="\nNum of OSDs",
-            main="Scaling OSD on a single server single client")
+            main="Single server, single client")
+    
     g = g + scale_shape_discrete(name="IO mode")
     g = g + scale_color_discrete(name="IO mode")
     g = g + geom_point(size=3.5)
     g = g + geom_line(size=1.5)
+    
+    # will (not) place lengend on the top
     g = g + opts(legend.position="top")
-    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
-                    as.integer((ymax-ymin)/5)))
+    
+    #g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+    #                as.integer((ymax-ymin)/5)))
     g = g + scale_x_continuous(breaks=seq(xmin, xmax))
 
     g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))

### 2013-08-15 data/plot_rados_server.R

@@ -1,4 +1,4 @@
-
+require("ggplot2")
 plot_xfs <- function(file) {
     cat("Processing: ", file, "\n")
     df=read.csv(file, strip.white=TRUE)
@@ -12,22 +12,22 @@ plot_xfs <- function(file) {
     xmax=as.integer(max(df$node.num))
 
     quartz(type="pdf", file="rados_server.pdf")
-    theme_set(theme_bw(base_family="Lucida Grande"))
+    theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(node.num, bw,
             data=df,
             shape=factor(df$mode),
             color=factor(df$mode),
             ylab="Max (MB/s)\n",
             xlab="\nNum of servers",
-            main="Scaling server numbers: 4 clients, 4 processes on each")
+            main="Scaling server numbers")
     g = g + scale_shape_discrete(name="IO mode")
     g = g + scale_color_discrete(name="IO mode")
     g = g + geom_point(size=3.5)
     #g = g + geom_smooth(method=loess, se=FALSE)
     g = g + geom_line(size=1.5)
     g = g + opts(legend.position="top")
-    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
-                    as.integer((ymax-ymin)/5)))
+    #g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+    #                as.integer((ymax-ymin)/5)))
     g = g + scale_x_continuous(breaks=seq(xmin, xmax))
 
     g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))

### 2013-08-15 data/plotxdd.R

@@ -1,3 +1,4 @@
+require("ggplot2")
 
 plot_xdd <- function(f, m) {
     cat("Processing: ", f, m , "\n")
@@ -12,7 +13,7 @@ plot_xdd <- function(f, m) {
     xmax=as.integer(max(df$dev.num))
 
     quartz(type="pdf", file=paste("xdd-", m, ".pdf", sep=""))
-    theme_set(theme_bw(base_family="Lucida Grande"))
+    theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(dev.num, bw,
             data=df,
             shape=factor(df$qd),

### 2013-08-15 data/plotxfs.R

@@ -1,3 +1,4 @@
+require("ggplot2")
 
 plot_xfs <- function(file) {
     cat("Processing: ", file, "\n")

### 2013-08-16 ceph-eval.tex
add table of content and list of figures

@@
 \input{cover}
+
+\pagebreak
+\thispagestyle{empty}
+\tableofcontents
+
+\pagebreak
+\thispagestyle{empty}
+\listoffigures
+
+\clearpage
+\pagenumbering{arabic}
 
@@
 ORNL at this point was able to both make more client nodes available and also
-install a profiling tool called \textbb{perf} that is extremely useful for
-profiling both kernel and user space code.  Profiling with perf showed high CPU
-utilization on the client due to crc32c processing in the Ceph kernel client. 
-Luckily crc32 checksums can be disabled by changing the CephFS mount options:
+install a profiling tool called \verb!perf! that is extremely useful for
+profiling both kernel and user space code.  Profiling with \verb!perf! showed
+high CPU utilization on the client due to crc32c processing in the Ceph kernel
+client.  Luckily crc32 checksums can be disabled by changing the CephFS mount
+options:
 
@@
 \section*{Appendix A - CephFS Final Mount Command}
+\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
 
@@
 \section*{Appendix B - OSD File System Options}
+\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
 
@@
 \section*{Appendix C - CRUSH Map}
+\addcontentsline{toc}{section}{Appendix C - CRUSH map}
 
@@
 \section*{Appendix D - Final ceph.conf}
+\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
 

### 2013-08-16 ceph-eval.tex
apply scott's patch

@@
 \usepackage{setspace}
+\usepackage{color,soul}
 
@@
 \author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-Brad Settlemyer, Scotty Atchley, Jason Hill, Mark Nelson}
+Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
 
@@
 file system, Ceph, for a deep-dive study. It covers a wide range of technical
-topics: from system setup, deployment, administration to internal mechanism. In
+topics: from system setup, deployment, administration to \hl{internal mechanism}. In
 comparison to other parallel file systems, Ceph has a number of distinctive
@@
   \item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. CRUSH algorithm allows the client side to pre-calculate the layout
-  info, and take failure domain, hierarchical storage tiers into placement
-  consideration.
+  CRUSH. The CRUSH algorithm allows a client to pre-calculate the layout
+  info, while taking into consideration failure domains and hierarchical storage tiers.
 
-  \item From the on start, Ceph is designed to manage metadata and name space
+  \item From the start, Ceph's design anticipated managing metadata and the name space
   with a cluster of metadata servers.
 
-\item Ceph is designed with the assumption that system is composed with
-unreliable components, so replication and failure detection and tolerance are
+\item Ceph's design assumes that the system is composed of
+unreliable components; fault-detection and fault-tolerance (e.g., replication) are
 the norm rather than the exception. This is in line with the expectation of
@@
 
-\item Most of Ceph code base are in user-space. Generally speaking, it makes the
-system easier to debug and maintain. The client side support has long been
+\item Most of the Ceph processes reside in user-space. Generally speaking, it makes the
+system easier to debug and maintain. The client-side support has long been
 integrated into Linux mainline kernel, which make the deployment and out-of-box
@@
 As part of this effort, we set up a dedicated testbed within NCCS for Ceph
-system evaluation. The goal is to investigate the feasibility of Ceph system as
+system evaluation. The goal is to investigate the feasibility of using the Ceph system as
 a potential candidate for our next-generation HPC storage solution.
@@
 our results, please keep in mind that Ceph is such a moving target that its
-code base is changing rapidly. In between releases, we often see different
-outcomes. We will try to make clear when such change happens in the report.
+code base is changing rapidly. In between releases, we often experienced different
+outcomes. We will try to make clear when such changes happened in the report.
 
@@
 
-The storage backend we have for this evaluation is DDN's SFA10K. It consists of
-200 SAS drives and 280 SATA drives, driven by 4 hosts. Each host has 2 IB QDR
-connections to the storage backend. We configure and use 4 Mellanox IB cards as
+We used Data Direct Network's (DDN) SFA10K as the storage backend during this evaluation. It consists of
+200 SAS drives and 280 SATA drives, driven by four hosts. Each host has two InfiniBand (IB) QDR
+connections to the storage backend. We configured and used four Mellanox IB cards as the
 primary connections, which by calculation can saturate the maximum theoretical
-throughput, around 11 - 12 GB/s. The connection diagram is illustrated as the
+throughput (11-12 GB/s). The connection diagram is illustrated as the
 following:
@@
 
-The hosts are running Redhat 6.3 with 3.5.1 kernel (rhl-ceph image), Glibc 2.12
-with syncfs support, locally patched. The Ceph version is 0.55 release in the
-initial test, then upgraded to 0.64 and 0.67RC for second round of test. For a
-complete a list of hosts that are running ceph images, you can do:
+The hosts ran Redhat 6.3 with 3.5.1 kernel (rhl-ceph image), Glibc 2.12
+with syncfs support, locally patched. We used the Ceph 0.55 release in the
+initial tests, then upgraded to 0.64 and then to 0.67RC for second round of tests. For a
+complete a list of hosts that are running ceph images, one can execute:
 
 \begin{Verbatim}
-grep "rhel6-ceph" /etc/gedi/MAC.info
+$ grep "rhel6-ceph" /etc/gedi/MAC.info
 \end{Verbatim}
@@
 We first establish the baseline performance by measuring block I/O performance.
-At the block level, with LUN configured as RAID6 8+2, we have the following
+At the block level, with each LUN configured with RAID6 8+2, we have the following
 results:
@@
     SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with 4 SAS LUNs & ~ 2.8 GB/s \\
-    Single host with 7 SATA LUNs & ~ 2.6 GB/s \\
+    Single host with four SAS LUNs & ~ 2.8 GB/s \\
+    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
     \bottomrule
@@
 
-Single host refers to one of 4 tick-oss nodes, which drives the entire SSU.
-Overall, the entire SSU performance can perform at 11GB/s, comparing to
-theoretical maximum of 12GB/s.
+Single host refers to one of four tick-oss nodes, which drives the entire SSU.
+Overall, the entire SSU performance can perform at 11 GB/s, comparing to
+theoretical maximum of 12 GB/s.
 
@@
 
-Note that we are using IP over IB for networking, since Ceph doesn't have
-native IB support\footnote{Inktank is developing rsocket alternative to better take
-advantage of IB fabric}.
-A single host with IP over IB (QDR) can perform at 2.7 GB per second with
-Mellanox recommended tuning applied. With all 4 hosts (OSD servers), we expect
-the aggregate throughput is in the neighborhood of 10GB/s.
+Note, Ceph uses the BSD Sockets interface in the \texttt{SOCK\_STREAM} mode (i.e., TCP).
+Because our testbed has IB, we used IP over IB (IPoIB) for networking\footnote{Inktank is 
+investigating using rsockets to improve performance when using an IB fabric}.
+A pair of hosts connected by IB QDR using IPoIB can transfer data at 2.7 GB/s if the
+hosts are tuned per recommendations from Mellanox. With all four hosts (OSD servers), we would expect
+the aggregate throughput to be in the neighborhood of 10 GB/s.
 
-Unfortunately there was not enough time to do more detailed analysis of network
-bisection bandwidth. Later, we will see RADOS is performing a
-maximum of 5 to 6 GB per seconds driven by 4 hosts.  So, this test shows that we
-have enough network bandwidth, i.e., IP over IB is not a bottleneck in this
-case.
+Unfortunately there was not enough time to do more detailed analysis of the network
+performance. Later, we will see RADOS is performing a
+maximum of 5-6 GB/s driven by four hosts.  So, this test shows that we
+have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
+case).
 
@@
 
-As we plan to use XFS file system as the backend local file system for Ceph, we
-examine XFS against SFA10K to acquire a set of sensible configuration parameters
-for optimized performance. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write), and this is the
-configurations we selected: mount with \verb!nobarrier,noatim,inode64! options.
+Ceph supports multiple backend file systems including btrfs, ext4, and xfs.
+Due to its performance and maturity, we chose to use XFS. We
+experimented with XFS to acquire a set of sensible configuration parameters
+which hopefully provided optimal performance for the SFA10K. We sampled a selected set of parameters (block size,
+queue depth, request size, sequential read and write). We settled on the following
+configuration: mount with \verb!nobarrier,noatim,inode64! options.
 The \verb!inode64! option had a notable improvement on sequential write (around
@@
 
+%% Can the graphs be adjusted to have the same values in the Y axis?
 \begin{figure}[htb]
@@
 
-The read and write result are summarized in Figure~\ref{fig:xfs-read}
-and Figure~\ref{fig:xfs-write}. These scaling test on the number of devices
-indicates that XFS can get to peak read performance with 5 SATA LUNs, then there
-is a bit of degradation from there. The parameter space explored regarding to
-the queue depth doesn't seem to make any obvious difference on the performance
-though.
+%% Are the read and write graphs wrong or should the second sentence below be about write
+%% instead of read?
+The read and write results are summarized in Figures~\ref{fig:xfs-read}
+and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
+indicates that XFS can get to the peak \hl{read} performance with five SATA LUNs, then there
+is a bit of degradation from there. Changes to
+the queue depth do not seem to make any obvious difference on the performance.
 
@@
 
-RADOS is Ceph object store, a foundational component for CephFS file
+RADOS is the Ceph object store, a foundational component for CephFS file
 system. There are three types of scaling tests we are interested at RADOS layer:
@@
 
-Our system setup poses some limitation on the scalability test we want to
-perform. In particular, we currently have 4 OSS server, 8 clients, and 11 OSD
-per clients. So the scaling test will be within these constraints.
+Our system setup poses some limitation on the scalability tests we want to
+perform. In particular, we currently have four OSS servers, eight clients, and eleven OSD servers
+per client. The scaling tests will be within these constraints.
 
-An open source tool developed by Inktank called RADOS bench was do perform
+We use the open-source tool RADOS bench, developed by Inktank, to perform our
 initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
@@
 
-We've observed that using more than one client processes and lots of concurrent
-operations is important when performing these tests.  8 Client processes are
-used with 32 concurrent 4MB Objects in flight each, and a pool is created for
+We have observed that using two or more client processes and many concurrent
+operations are important when performing these tests.  We tested eight client processes 
+with 32 concurrent 4 MB objects in flight each. We created a pool for
 each RADOS bench process to ensure that object reads come from independent pools
@@
 node before every test to ensure no data or metadata is in cache.  All tests
-were run with 1X replication.  Unfortunately at this time only XFS was present
-and usable for the underlying OSDs so BTRFS and EXT4 file systems were not
+were run with replication set to one.  Only XFS was present
+and usable for the underlying OSDs, so BTRFS and EXT4 file systems were not
 tested at this time.
@@
 In the following test, a single Ceph host drives $n$ number of OSDs, where $n$
-increases from 1 to 11. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with 4 concurrent process. In this test
-case, we observe that Ceph OSS exhibits near linear scalability up to 9
-OSDs, and still have room to grow at 11 OSDs. This suggests that we have not reached the
-saturation point yet. It requires provisioning of more OSDs at SFA10K backend.
+increases from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
+We ran the test against a single client with four concurrent processes. In this test
+case, we observe that the OSS exhibits near linear scalability up to nine
+OSDs, and is still trending upwards at eleven OSDs. This suggests that we have not reached the
+saturation point yet. Additional testing would require provisioning more OSDs on the SFA10K backend.
 
@@
 
-In this test, we exercise OSS number from 1 to 4, driven by 4 clients with 4
-concurrent process for each client. Each addition of OSS adds 11 more OSDs into
-the play. We observe that Ceph exhibits linear scaling property with regard to
+In this test, we exercise OSS number from one to four, driven by four clients with four
+concurrent process for each client. Each addition of OSS adds eleven more OSDs into
+play. We observe that Ceph exhibits linear scaling property with regard to
 number of servers as well, at least in the given set of servers. However, the peak
@@
 For the write, the reason behind it is attributed to the way Ceph perform
-journaling: Ceph doesn't support the meta-data only journaling, therefore every
+journaling: Ceph does not support the meta-data only journaling, therefore every
 write is equivalent of a double-write: once to the data device, once to the
 journaling device. It effectively cut the system bandwidth in half. That said,
-it doesn't explain the read performance - though it is better than write, but is
+it does not explain the read performance - though it is better than write, but is
 still far from the theoretical maximum.
@@
     \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it won't read from the write cache. \\ \midrule
+        ordering for read back so it will not read from the write cache. \\ \midrule
     \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
@@
 into. We were, however, able to record results in two extreme case as far as
-transfer size is concerned: 4KB and 4MB, using the same number of OSS servers
-(4) and same block size (8GB), the results are illustrated in Figure
+transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
+(4) and same block size (8 GB), the results are illustrated in Figure
 \ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
@@
 
-With cache mirroring disabled write performance when using all 4 servers
+With cache mirroring disabled write performance when using all four servers
 improved dramatically, as illustrated in
 Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS for example, we hit over
-5.5GB/s from the clients.  When accounting for journal writes, that is over
-11GB/s to the disks and very close to what the DDN chassis is capable of doing. 
+5.5 GB/s from the clients.  When accounting for journal writes, that is over
+11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
 Unfortunately, read performance did not scale as well.
@@
 \includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4MB IO, 8 Client Nodes}
+\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB IO, 8 Client Nodes}
 \label{fig:rados-064-osd}
@@
 \includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4MB IO, 8 Client Nodes}
+\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4 MB IO, 8 Client Nodes}
 \label{fig:rados-064-oss}
@@
 \includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with no client side CRC32}
+\caption{IOR test with no client-side CRC32}
 \label{fig:ior-no-client-crc32}
@@
 \includegraphics[width=4in]{ior-kernel-39}
-\caption{Kernel changes to 3.9, IOR with 4MB transfer size}
+\caption{Kernel changes to 3.9, IOR with 4 MB transfer size}
 \label{fig:ior-kernel-39}
@@
 
-As before, we ran IOR scaling test with two cases: transfer size 4K and 4M.
+As before, we ran IOR scaling test with two cases: transfer size 4 KB and 4 MB.
 These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
@@
 \includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4KB and 4MB transfer size}
+\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
 \label{fig:ior-064}
@@
 improving as the number of clients increases.  Writes seem to be topping out at
-around 5.2GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to the 8GB/s+ numbers we
+around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
+topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
+would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
 saw with RADOS Bench.
@@
 
-\item \verb!-n 1000!: this is per client file \textit{and} directories. For 8
-clients, the number of files and directories is 8,000. Since we didn't specify
+\item \verb!-n 1000!: this is per client file \textit{and} directories. For eight
+clients, the number of files and directories is 8,000. Since we did not specify
 either \verb!-D! or \verb!-F!, so this is a mixture of both.
@@
 
-Each test iterates 5 times and we are showing the max. 
+Each test iterates five times and we are showing the max. 
 We summarize the results as follows:
@@
   replication for pools, but this will take a toll somewhere in the processing
-  and we don't know if this is significant.
+  and we do not know if this is significant.
 

### 2013-08-16 ceph-eval.tex
Address Scott's two questions in the text
1. read should be write. 2. Figure 2 and 3 now have the same Y axis

@@
 and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
-indicates that XFS can get to the peak \hl{read} performance with five SATA LUNs, then there
-is a bit of degradation from there. Changes to
+indicates that XFS can get to the peak write performance with five SATA LUNs,
+then there is a bit of degradation from there. Changes to
 the queue depth do not seem to make any obvious difference on the performance.

### 2013-08-16 data/plotxdd.R

@@ -28,8 +28,7 @@ plot_xdd <- function(f, m) {
     g = g + geom_point(size=3.5)
     g = g + geom_line(size=1.5)
     g = g + opts(legend.position="top")
-    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
-                    as.integer((ymax-ymin)/5)))
+    g = g + coord_cartesian(ylim=c(0,3500)) + scale_y_continuous(breaks=seq(0, 3500,500))
     g = g + scale_x_continuous(breaks=seq(xmin, xmax))
     g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
     g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))

### 2013-08-16 data/plotxfs.R

@@ -13,7 +13,7 @@ plot_xfs <- function(file) {
     xmax=as.integer(max(df$num.dev))
 
     quartz(type="pdf", file="xfs.pdf")
-    theme_set(theme_bw(base_family="Lucida Grande"))
+    theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(num.dev, bw.max,
             data=df,
             shape=factor(df$mode),
@@ -28,8 +28,8 @@ plot_xfs <- function(file) {
     g = g + geom_point(size=3.5)
     g = g + geom_smooth(size=1.5)
     g = g + opts(legend.position="top")
-    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
-                    as.integer((ymax-ymin)/5)))
+    #g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+    #                as.integer((ymax-ymin)/5)))
     g = g + scale_x_continuous(breaks=seq(xmin, xmax))
     g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))
     g = g + opts(panel.grid.minor = theme_line(color="grey80", size = 0.7, linetype = "dotted"))

### 2013-08-16 ceph-eval.tex
update metadata section

@@
 
+\begin{figure}[htb]
+\centering
+%% -- 1st figure
+\begin{minipage}[t]{0.5\linewidth}
+\centering
+\includegraphics[width=3in]{data/mdtest-fcreate}
+\caption{file creation vs.  \# of clients}
+\label{fig:mdtest-fcreate}
+\end{minipage}%
+\begin{minipage}[t]{0.5\linewidth}
+\centering
+\includegraphics[width=3in]{data/mdtest-dcreate}
+\caption{directory creation vs. \# of clients}
+\label{fig:mdtest-dcreate}
+\end{minipage}%
+\end{figure}
+
 In our particular setup, we have only one metadata server (MDS)
@@
 
+The results also show that file creation rate is signficantly lower than
+directory creation rate. We stipulated two contributing factors: one is the file
+creation is associated with 1 MB data write and followed by a fsync operation,
+which is a rather heavy weight operation compare to directory creation. Another
+factor is that we obtained above results from early version of Ceph without all
+the tunings and improvement applied. Therefore, we repeated the same test on the
+latest CephFS 0.64. The result is illustrated in
+Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
+improvement on the file creation rate. We also note that as number of clients
+increase, the file creation rate decreases rapidly, which suggested some form of
+lock contention. This presents some interesting issues to be investigated
+further.
+
 \begin{figure}[htb]
 \centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{file creation vs.  \# of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{directory creation vs. \# of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
+\includegraphics[width=4in]{mdtest-064-file-create}
+\caption{mdtest of file creation on Ceph 0.64}
+\label{fig:mdtest-064-file-create}
 \end{figure}

### 2013-08-16 ceph-eval.tex
patch with Doug's input

@@
 
-NCCS contracted Inktank, the major developer behind the open-sourced parallel
+NCCS contracted Inktank, the major developer behind the open-source parallel
 file system, Ceph, for a deep-dive study. It covers a wide range of technical
-topics: from system setup, deployment, administration to \hl{internal mechanism}. In
+topics from system setup, deployment, administration to \hl{internal mechanisms}. In
 comparison to other parallel file systems, Ceph has a number of distinctive
@@
   \item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate the layout
-  info, while taking into consideration failure domains and hierarchical storage tiers.
+  CRUSH. The CRUSH algorithm allows a client to pre-calculate layout
+  information while taking into consideration failure domains and hierarchical storage tiers.
 
@@
 unreliable components; fault-detection and fault-tolerance (e.g., replication) are
-the norm rather than the exception. This is in line with the expectation of
+the norm rather than the exception. This is in line with the expectations of
 exascale computing.
@@
 
-\item Most of the Ceph processes reside in user-space. Generally speaking, it makes the
+\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
 system easier to debug and maintain. The client-side support has long been
@@
 
-As part of this effort, we set up a dedicated testbed within NCCS for Ceph
+As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
 system evaluation. The goal is to investigate the feasibility of using the Ceph system as
-a potential candidate for our next-generation HPC storage solution.
+a candidate for our next-generation HPC storage solution.
 This report presents our experience, results, and observations. While evaluating
@@
 code base is changing rapidly. In between releases, we often experienced different
-outcomes. We will try to make clear when such changes happened in the report.
+outcomes. We will try to make clear in the report when such changes occurred.
 
@@
 
-We used Data Direct Network's (DDN) SFA10K as the storage backend during this evaluation. It consists of
-200 SAS drives and 280 SATA drives, driven by four hosts. Each host has two InfiniBand (IB) QDR
+We used Data Direct Networks' (DDN) SFA10K as the storage backend during this evaluation. It consists of
+200 SAS drives and 280 SATA drives driven by four hosts. Each host has two InfiniBand (IB) QDR
 connections to the storage backend. We configured and used four Mellanox IB cards as the
-primary connections, which by calculation can saturate the maximum theoretical
-throughput (11-12 GB/s). The connection diagram is illustrated as the
-following:
+primary connections, which by calculation can saturate the controller's maximum theoretical
+throughput (11-12 GB/s). The connection diagram is illustrated below:`
 
@@
 
-The hosts ran Redhat 6.3 with 3.5.1 kernel (rhl-ceph image), Glibc 2.12
+The hosts ran Redhat 6.3 with kernel version 3.5.1 (rhl-ceph image), Glibc 2.12
 with syncfs support, locally patched. We used the Ceph 0.55 release in the
@@
 \subsection*{Block I/O}
-We first establish the baseline performance by measuring block I/O performance.
+We first establish baseline performance by measuring block I/O performance.
 At the block level, with each LUN configured with RAID6 8+2, we have the following
@@
 
-Single host refers to one of four tick-oss nodes, which drives the entire SSU.
-Overall, the entire SSU performance can perform at 11 GB/s, comparing to
+Single host refers to one of four tick-oss nodes, which drives the entire system.
+Overall, the entire system can perform at 11 GB/s, compared to its
 theoretical maximum of 12 GB/s.
@@
 
-Note, Ceph uses the BSD Sockets interface in the \texttt{SOCK\_STREAM} mode (i.e., TCP).
+Note that Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
 Because our testbed has IB, we used IP over IB (IPoIB) for networking\footnote{Inktank is 
@@
 
-Base upon past experience and further experimentation, we started out on the
+Base upon past experience and further experimentation, we started out with the
 following set of tuning parameters:
@@
 then there is a bit of degradation from there. Changes to
-the queue depth do not seem to make any obvious difference on the performance.
+the queue depth do not seem to make any obvious difference in the performance.
 
@@
 RADOS is the Ceph object store, a foundational component for CephFS file
-system. There are three types of scaling tests we are interested at RADOS layer:
+system. There are three types of scaling tests we are interested at the RADOS layer:
 
@@
 
-Our system setup poses some limitation on the scalability tests we want to
+Our system setup poses some limitations on the scalability tests we want to
 perform. In particular, we currently have four OSS servers, eight clients, and eleven OSD servers
@@
 
-We use the open-source tool RADOS bench, developed by Inktank, to perform our
+We use the open-source tool RADOS Bench, developed by Inktank, to perform our
 initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
@@
 with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS bench process to ensure that object reads come from independent pools
-(RADOS bench is not smart enough to ensure that objects are not read by multiple
+each RADOS Bench process to ensure that object reads come from independent pools
+(RADOS Bench is not smart enough to ensure that objects are not read by multiple
 processes and thus possibly cached).  A sync and flush is performed on every
@@
 
-In the following test, a single Ceph host drives $n$ number of OSDs, where $n$
+In the following test, a single Ceph host drives $n$ OSDs, where $n$
 increases from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
@@
 
-In this test, we exercise OSS number from one to four, driven by four clients with four
-concurrent process for each client. Each addition of OSS adds eleven more OSDs into
-play. We observe that Ceph exhibits linear scaling property with regard to
+In this test, we exercise OSS numbers from one to four, driven by four clients with four
+concurrent process for each client. Each additional OSS adds eleven more OSDs into
+play. We observe that Ceph exhibits linear scaling with regard to
 number of servers as well, at least in the given set of servers. However, the peak
-performance we are seeing is about the half of what are expecting from SFA10K.
-For the write, the reason behind it is attributed to the way Ceph perform
-journaling: Ceph does not support the meta-data only journaling, therefore every
-write is equivalent of a double-write: once to the data device, once to the
-journaling device. It effectively cut the system bandwidth in half. That said,
-it does not explain the read performance - though it is better than write, but is
+performance we are seeing is about the half of what are expecting from the SFA10K.
+For writes, it is attributed to the way Ceph performs
+journaling: Ceph does not support meta-data only journaling, therefore every
+write is the equivalent of a double-write: once to the data device, once to the
+journaling device. This effectively cuts the system bandwidth in half. That said,
+it does not explain the read performance -- it is better than write, but 
 still far from the theoretical maximum.
@@
 
-We use synthetic IOR benchmark suite for file system level test. The particular
-parameter setup is show in Table \ref{tbl:ior}. Each client node has 6 GB
-physical memory, the block size is set so as to mitigate the cache effect. In
-addition, the test harness program will issue the following command at the
+We used the synthetic IOR benchmark suite the for file system level test. The particular
+parameter setup is show in Table \ref{tbl:ior}. Each client node has 6 GB of
+physical memory, the block size is set so as to mitigate cache effects. In
+addition, the test harness program will issue the following commands at the
 beginning of each test:
@@
 
-Our first round of test was less than ideal as we encountered various issue. For
-the sake of completeness, we still first summarized the results, then discuss
-the further tuning efforts and improvements.
+Our first round of tests was less than ideal as we encountered various issues. For
+the sake of completeness, we first summarize the results, then discuss
+further tuning efforts and improvements.
 
-The full permutation of IOR parameters are not explored due to IO errors we ran
-into. We were, however, able to record results in two extreme case as far as
+The full permutation of IOR parameters were not explored due to IO errors we encountered.
+We were, however, able to record results in two extreme cases as far as
 transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
@@
 \begin{itemize}
-  \item The small read performance is almost an anomaly - we need to
-  investigate why it is so low compare to write.
+  \item The small read performance is almost an anomaly -- we need to
+  investigate why it is so low compare to write performance.
   \item The large read performance is almost half of the write performance,
-  which is the opposite of RADOS level. 
-  \item The write performance is cut in half compare to what we can obtain from
-  RADOS benchmark. And number of clients reaches 8, there is a significant
+  which is the opposite of the RADOS-level results. 
+  \item The write performance is half of what we can obtain from
+  RADOS Bench. When number of clients reaches 8, there is a significant
   performance drop as well. 
@@
 As a result of this testing, performance was again improved slightly by
-increasing the size of various Ceph buffers and queues, enabling aio journals,
+increasing the size of various Ceph buffers and queues, enabling AIO journals,
 and increasing the number of OSD op threads.
 
-\subsection{Disable Cache Mirroring on DDN}
+\subsection{Disable Cache Mirroring on controllers}
 
@@
 tests, throughput did not scale.  A significant amount of time was spent
-investigating this phenomena. Ultimately, we were able to replicate this finding
+investigating this phenomenon. Ultimately, we were able to replicate this finding
 when running concurrent disk throughput tests directly on the servers without
@@
 3 or more LUNs were written concurrently. It turns out the root of the problem
-is attributed to a regression on DDN firmware update - in particular, the cache
-mirroring is not behaving as it should be.
+was a regression on DDN firmware update -- in particular, the cache
+mirroring was not behaving as it should.
 
@@
 
-With cache mirroring disabled write performance when using all four servers
+With cache mirroring disabled, write performance when using all four servers
 improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS for example, we hit over
+Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
 5.5 GB/s from the clients.  When accounting for journal writes, that is over
@@
 \footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}.
-TCP auto tuning enables TCP window scaling by default and automatically adjust
+TCP auto tuning enables TCP window scaling by default and automatically adjusts
 the TCP receive window for each connection based on link conditions such as
@@
 
-We now repeated previous RADOS scaling test with these improvements in place.
-The first test was done on a single node with RADOS bench to see how close the
+We now repeated the previous RADOS scaling tests with these improvements in place.
+The first test was done on a single node with RADOS Bench to see how close the
 underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increase. Note all the tests performed are against
-XFS formatted storage.
+of OSDs/LUNs used on the node increased. Note all the tests performed were against
+XFS-formatted storage.
 
@@
 We also repeated tests looking at RADOS Bench performance as the
-number of OSD server nodes increases. The result is summarized in
+number of OSD server nodes increases. The results are summarized in
 Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
@@
 
-The initial stability issues we encountered are fixed by moving Ceph version
-from 0.48/0.55 to 0.64, latest stable at the time. Now IOR test can proceed to
-finish even during long runs. It is another sign of showing how much Ceph
+The initial stability issues we encountered are fixed by moving 
+from Ceph version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test could
+complete even during long runs. This is another sign of how much Ceph
 development is in flux.
 
-Another fix comes the way we create the pool: the default data pool being used
+Another fix comes in the way we create the pool: the default data pool being used
 by previous CephFS cluster are set to 2x replication, which can potentially
@@
 high CPU utilization on the client due to crc32c processing in the Ceph kernel
-client.  Luckily crc32 checksums can be disabled by changing the CephFS mount
+client.  Luckily, crc32 checksums can be disabled by changing the CephFS mount
 options:
@@
 close to the throughput we were able to achieve with RADOS Bench, but reads
-continued to be slow, and continued to inversely scale with the number of client
+continued to be slow and continued to scale inversely with the number of client
 processes.  Please note that since these tests were performed, Inktank has
-implemented SSE4 based CRC32 code for Intel CPUs.  While any kernel based CRC32
+implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based CRC32
 processing should have already been using SSE4 instructions on Intel CPUs, this
-will allow any user land Ceph processes to process CRC32 checksums with
+will allow any user-land Ceph processes to process CRC32 checksums with
 significantly less overhead.
@@
 ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
-RADOS bench test to verify that there was no degradation vs previous tests.  The
+RADOS Bench test to verify that there was no degradation vs previous tests.  The
 results were extremely positive.
@@
 performance improved dramatically.  In addition to the kernel change, Sage Weil
-suggested increasing the amount of read ahead being performed by the CephFS
+suggested increasing the amount of read-ahead being performed by the CephFS
 kernel client:
@@
 
-By installing a new kernel, increasing read ahead, and increasing the number of
+By installing a new kernel, increasing read-ahead, and increasing the number of
 client IOR processes, we were able to achieve a very satisfactory result on this
@@
 
-As before, we ran IOR scaling test with two cases: transfer size 4 KB and 4 MB.
+As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
 These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
@@
 
-We observe that a couple of places where the average write throughput is quite a
-bit lower than the max.  This behavior was observed during other tests as well,
+We observe a couple of places where the average write throughput is quite a
+bit lower than the maximum.  This behavior was observed during other tests as well,
 indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance general seems to be
+temporarily degrading.  Despite these issues, performance generally seems to be
 improving as the number of clients increases.  Writes seem to be topping out at
@@
   \item Ceph is built on the assumption that the underlying hardware components
-  is unreliable, with little or no redundancy and failure detection capability.
-  This is not the case in this leadership computing facilities. We have disabled
+  are unreliable, with little or no redundancy and failure detection capability.
+  This is not the case in leadership computing facilities. We have disabled
   replication for pools, but this will take a toll somewhere in the processing
@@
 
-  \item Ceph do \textbf{metadata + data} journaling, which is fine for host
+  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
   system that has locally attached disk. However, this presents a problem in DDN
@@
 
-  \item Ceph is observed to have consist results and linear scalability at the
+  \item Ceph is observed to have consistent results and linear scalability at the
   RADOS level. However, it broke down at the file system level with synthetic
-  benchmark suite such as IOR. We have experience large performance swings
+  benchmark suites such as IOR. We have experienced large performance swings
   during different runs, very low read performance when transfer size is small,
   and IO errors tend to happen when system is under stress (more clients and
-  large transfer size). These are not particularly reproducible results, but it
+  large transfer sizes). These are not particularly reproducible results, but it
   suggests the level of maturity still have a long way to go.
@@
 This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed with different OSD configurations, the map will
+re-create different testbed subests with different OSD configurations, the map will
 change accordingly.

### 2013-08-19 ceph-eval.tex
Merge scott's patch for 7-11

@@
 
-Here, 0 is the default value of \verb!drop_cahces!; 1 is to free pagecaches, 2
+Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
 is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
@@
 
-The full permutation of IOR parameters were not explored due to IO errors we encountered.
+The full permutation of IOR parameters were not explored due to I/O errors we encountered.
 We were, however, able to record results in two extreme cases as far as
@@
 \ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
+
+%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
+%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
 
@@
 
-After the initial test results were found, various combinations of tweaks were
-attempted including changing the number of filestore op threads, putting all
+After the initial test results, we tried various combinations of tweaks
+including changing the number of filestore op threads, putting all
 of the journals on the same disks as the data, doubling the OSD count, and
 upgrading Ceph to a development version which reduces the seek overhead caused
-by \texttt{pginfo} and \texttt{pglog} updates on XFS (These enhancements are
+by \texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are
 now included as of the Ceph Cuttlefish release).  The two biggest improvements
@@
 
-A script written by Inktank for internal Ceph testing was used to perform
-parametric sweeps over Ceph configuration parameters to examine how different
+We ran a script written by Inktank for internal Ceph testing to perform
+sweeps over Ceph configuration parameters to examine how different
 tuning options affect performance on the DDN platform. The result of this
@@
 
-As a result of this testing, performance was again improved slightly by
+As a result of this testing, we improved performance slightly by
 increasing the size of various Ceph buffers and queues, enabling AIO journals,
@@
 Despite the excellent write throughput we saw during the individual server
-tests, throughput did not scale.  A significant amount of time was spent
+tests, throughput did not scale.  We spent a significant amount of time
 investigating this phenomenon. Ultimately, we were able to replicate this finding
 when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The 2nd RAID processor on each DDN controller would max out when
-3 or more LUNs were written concurrently. It turns out the root of the problem
+Ceph involved. The second RAID processor on each DDN controller would max out when
+three or more LUNs were written concurrently. It turns out the root of the problem
 was a regression on DDN firmware update -- in particular, the cache
 mirroring was not behaving as it should.
+
+%% SCOTT - is running with cache mirroring off and option for a production system or not?
+%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
+%% with it or not?
 
@@
 to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux Kernel.
-\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}.
+with TCP autotuning in the Linux Kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
 TCP auto tuning enables TCP window scaling by default and automatically adjusts
@@
 
+%% SCOTT - the title in the figure needs to change IO to I/O
+
+%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
+%% on the single server?
+
 \begin{figure}[htb]
@@
 \includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB IO, 8 Client Nodes}
+\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
 \label{fig:rados-064-osd}
@@
 
+%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
+%% Do they no measure the same thing (i.e. a single server)? If not, the text
+%% needs to make it more clear.
+
 \begin{figure}[htb]
@@
 \includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4 MB IO, 8 Client Nodes}
+\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
 \label{fig:rados-064-oss}
@@
 ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
-RADOS Bench test to verify that there was no degradation vs previous tests.  The
+RADOS Bench test to verify that there was no degradation versus previous tests.  The
 results were extremely positive.
@@
 
+%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
+%% mention that 15 shows the filesystem performance?
+
 \begin{figure}[htb]
@@
 line with RADOS bench performance.
+
+%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
+%% as to why 4 KB performance is better than 4 MB performance?
 
@@
 configured. Therefore, this is not a scalability test on the performance of
-clustered MDS, which would be very interesting and might as well come later.
+clustered MDS, which would be very interesting.
 Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
@@
   SFA10-like hardware, where the backend LUNs are exposed as block device
-  through SRP over IB. The journaling write would requires double bandwidth
-  compare to Lustre-like metadata only journaling mechanism. For Ceph to anything
-  viable in this facility, there has to be a solution for this.
+  through SCSI Request Protocol (SRP) over IB. The journaling write requires twice the bandwidth
+  compare to Lustre-like metadata-only journaling mechanism. For Ceph to be
+  viable in this facility, we will need to address this.
 
-  \item Ceph is observed to have consistent results and linear scalability at the
-  RADOS level. However, it broke down at the file system level with synthetic
+  \item We observed consistent results and linear scalability at the
+  RADOS level. However, we did not observe the same at the file system level with synthetic
   benchmark suites such as IOR. We have experienced large performance swings
   during different runs, very low read performance when transfer size is small,
-  and IO errors tend to happen when system is under stress (more clients and
+  and I/O errors tend to happen when system is under stress (more clients and
   large transfer sizes). These are not particularly reproducible results, but it
-  suggests the level of maturity still have a long way to go.
+  suggests that there are opporunities for code improvement and maturation.
 

### 2013-08-19 ceph-eval.tex
Misc fixs
Update branch mgmt in readme; update figures 11, 12 with I/O and better
labels; clarify "client network max" and "writes (including journals)"
on those figures as well.

@@
 
+%% FEIYI: 6, 7 all fixed.
+
 \begin{figure}[H]
@@
 was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.
+mirroring was not behaving as it should.\footnote{DDN recently released a new
+firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
+a chance to verify it during our test cycle.}
 
@@
 %% with it or not?
+
+%% FEIYI: add footnote to clarify the issue.
 
@@
 
-In the single server case as shown in Figure~\ref{fig:rados-064-osd},
-performance gets very close to the hardware limits at roughly 9 OSDs per server
-and then mostly levels out.
+In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
+(including Journals)'' refers to how much data is actually being written out the
+DDN chasis, and blue line is how much data the clients are writing.
+We observe that performance gets very close to the hardware limits at roughly 9
+OSDs per server and then mostly levels out.
 
-We also repeated tests looking at RADOS Bench performance as the
-number of OSD server nodes increases. The results are summarized in
+We also repeated tests looking at RADOS Bench performance as the number of OSD
+server nodes increases from one to four. The results are summarized in
 Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
@@
 
-The initial stability issues we encountered are fixed by moving 
-from Ceph version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test could
-complete even during long runs. This is another sign of how much Ceph
+The initial stability issues we encountered are fixed by moving from Ceph
+version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test
+could complete even during long runs. This is another sign of how much Ceph
 development is in flux.
@@
 \includegraphics[width=4in]{ior-kernel-39}
-\caption{Kernel changes to 3.9, IOR with 4 MB transfer size}
+\caption{CephFS performance with Kernel changes to 3.9, IOR with 4 MB transfer
+size}
 \label{fig:ior-kernel-39}

### 2013-08-19 data/plot_ior.R

@@ -30,8 +30,9 @@ plot_xfs <- function(file) {
     g = g + geom_point(size=3)
     g = g + geom_line(size=1.5)
     g = g + opts(legend.position="top")
-    g = g + scale_y_continuous(breaks=seq(ymin, ymax,
-                    as.integer((ymax-ymin)/5)))
+    #g = g + scale_y_continuous(breaks=seq(ymin, ymax,
+    #                as.integer((ymax-ymin)/5)))
+    g = g + coord_cartesian(ylim=c(0,2500)) + scale_y_continuous(breaks=seq(0, 2500,500))
     g = g + scale_x_continuous(breaks=seq(xmin, xmax))
 
     g = g + opts(panel.grid.major = theme_line(color="grey80", size = 0.7, linetype = "dashed"))

### 2013-08-20 ceph-eval.tex
Incoporate Sarp's changes on 1-7.

@@
 \setmainfont{rosario}
-\setmonofont{Consolas}
+%\setmonofont{Consolas}
 %\setmainfont{Times}
-%\setmonofont{Inconsolata}
+\setmonofont{Inconsolata}
 %\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont[Scale=0.8]{Courier}
+%\setmonofont{Courier}
 
-\title{Ceph Parallel File System Evaluation Report}
-\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
+%\title{Ceph Parallel File System Evaluation Report}
+%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
+%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
 
@@
 
-NCCS contracted Inktank, the major developer behind the open-source parallel
-file system, Ceph, for a deep-dive study. It covers a wide range of technical
-topics from system setup, deployment, administration to \hl{internal mechanisms}. In
-comparison to other parallel file systems, Ceph has a number of distinctive
+National Center for Computational Sciences (NCCS), in collaboration with
+Inktank Inc, has prepared a detailed performance and scalability study of
+Ceph file system. Ceph is originated from Sage Weil's PhD research
+at UC Santa Cruz around 2007 and it is designed to be a reliable, scalable
+fault-tolerant parallel file system. Inktank is now the major developer behind
+the open-source parallel file system to sheperd its development and provide
+commerical support.
+
+In comparison to other parallel file systems, Ceph has a number of distinctive
 features:
@@
 \begin{itemize}
+
 \item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate layout
-  information while taking into consideration failure domains and hierarchical storage tiers.
+  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
+  placement and layout while taking into consideration failure domains and
+  hierarchical storage tiers.
 
@@
 the norm rather than the exception. This is in line with the expectations of
-exascale computing.
+Exascale computing.
 
 \item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the actual data can take advantage of this
+\texttt{RADOS}. Both metadata and the file data can take advantage of this
 uniformity.
@@
 system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which make the deployment and out-of-box
-experience easier.
+integrated into Linux mainline kernel, which eases the deployment and out-of-box
+experience.
 
@@
 As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-system evaluation. The goal is to investigate the feasibility of using the Ceph system as
-a candidate for our next-generation HPC storage solution.
+file system evaluation. The goal of our study is to investigate the feasibility
+of using the Ceph for our future HPC storage deployment.
 This report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph is such a moving target that its
-code base is changing rapidly. In between releases, we often experienced different
-outcomes. We will try to make clear in the report when such changes occurred.
+our results, please keep in mind that Ceph has not matured yet for scientific
+HPC community that its code base is changing rapidly. In between releases, we
+often experienced different outcomes. We will try to make clear in the report
+when such changes occurred.
 
@@
 
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this evaluation. It consists of
-200 SAS drives and 280 SATA drives driven by four hosts. Each host has two InfiniBand (IB) QDR
-connections to the storage backend. We configured and used four Mellanox IB cards as the
-primary connections, which by calculation can saturate the controller's maximum theoretical
-throughput (11-12 GB/s). The connection diagram is illustrated below:`
+We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
+evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
+various RAID levels by two active-active RAID controllers. The exported RAID
+groups by these controllers are driven by four hosts.
+Each host has two InfiniBand (IB) QDR connections to the storage backend.
+We used a single dualport Mellanox connectX IB card per host.
+By our calculation, this setup can saturate SFA10K's maximum theoretical
+throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
+Figure~\ref{fig:ddn-sfa10k}.
 
@@
 \includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K Hardware Diagram}
+\caption{DDN SFA10K Hardware and Host Connection Diagram}
+\label{fig:ddn-sfa10k}
 \end{figure}
 
-The supporting infrastructure nodes are summarized in the following table:
+Our Ceph testbed employs a collection of testing nodes. These nodes and their
+roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
+discussion, we use ``servers'', ``osd servers'', ``server hosts''
+interchangably. We will emphasize with ``client'' prefix when we want to
+distinguish it from above.
 
@@
     \end{tabular}
-
+\caption{Support nodes involved in Ceph testbed}
+\label{tbl:ceph-test-nodes}
 \end{table}
 
-The hosts ran Redhat 6.3 with kernel version 3.5.1 (rhl-ceph image), Glibc 2.12
-with syncfs support, locally patched. We used the Ceph 0.55 release in the
-initial tests, then upgraded to 0.64 and then to 0.67RC for second round of tests. For a
-complete a list of hosts that are running ceph images, one can execute:
+All hosts  (client and servers) were configured with Redhat 6.3 and kernel
+version 3.5.1 (rhl-ceph image), Glibc 2.12 with syncfs support, locally patched.
+We used the Ceph 0.55 release in the initial tests, upgraded to 0.64 and then to
+0.67RC for a final round of tests.
 
-\begin{Verbatim}
-$ grep "rhel6-ceph" /etc/gedi/MAC.info
-\end{Verbatim}
+%For a complete a list of hosts that are running ceph images, one can execute:
+
+%\begin{Verbatim}
+%$ grep "rhel6-ceph" /etc/gedi/MAC.info
+%\end{Verbatim}
 
 \section{Baseline Performance}
+\label{sec:block-io}
 
-\subsection*{Block I/O}
-We first establish baseline performance by measuring block I/O performance.
-At the block level, with each LUN configured with RAID6 8+2, we have the following
-results:
+\subsection{Block I/O over Native IB}
+We first established baseline performance by measuring observed block I/O
+performance.
+At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
+following results as shown in Table~\ref{tbl:block-io-baseline}.
 
@@
 \end{tabular}
-
+\caption{Block I/O performances on single LUN and single host}
+\label{tbl:block-io-baseline}
 \end{table}
 
-Single host refers to one of four tick-oss nodes, which drives the entire system.
-Overall, the entire system can perform at 11 GB/s, compared to its
-theoretical maximum of 12 GB/s.
+Single host in this table refers to one of four tick-oss nodes. Four tick-oss
+nodes drive the SFA10K backend storage. Overall, we observe that the entire
+system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
+12 GB/s.
 
-\subsection*{IP over IB}
+\subsection{IP over IB}
 
-Note that Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our testbed has IB, we used IP over IB (IPoIB) for networking\footnote{Inktank is 
-investigating using rsockets to improve performance when using an IB fabric}.
-A pair of hosts connected by IB QDR using IPoIB can transfer data at 2.7 GB/s if the
-hosts are tuned per recommendations from Mellanox. With all four hosts (OSD servers), we would expect
-the aggregate throughput to be in the neighborhood of 10 GB/s.
+Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
+Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
+networking\footnote{As of writing of this report, Inktank is investigating using
+rsockets to improve performance with IB fabric}. Through simple
+\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
+IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
+from Mellanox). With all four hosts (OSD servers), we expect the aggregate
+throughput to be in the neighborhood of 10 GB/s.
 
@@
 performance. Later, we will see RADOS is performing a
-maximum of 5-6 GB/s driven by four hosts.  So, this test shows that we
+maximum of 5-6 GB/s driven by four hosts.  So, it shows that we
 have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
@@
 
-\section{The Starting Point of System Tuning}
+\section{System Tuning}
 
 Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters:
+following set of tuning parameters on OSD servers:
 
@@
 \end{tabular}
-
+\caption{System tuning parameters}
 \end{table}
 
-\section{XFS Performance}
+\section{XFS Performance As Backend File System}
 
-Ceph supports multiple backend file systems including btrfs, ext4, and xfs.
-Due to its performance and maturity, we chose to use XFS. We
-experimented with XFS to acquire a set of sensible configuration parameters
-which hopefully provided optimal performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the following
+Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
+Due to its performance and maturity, we chose XFS. We experimented with XFS to
+acquire a set of configuration parameters which provided optimal performance for
+the SFA10K. We sampled a selected set of parameters (block size, queue depth,
+request size, sequential read and write). We settled on the following
 configuration: mount with \verb!nobarrier,noatim,inode64! options.
@@
 %% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
 \centering
 \includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read scaling on \# of devices}
+\caption{XFS read performance scaling on number of devices}
 \label{fig:xfs-read}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
+\end{figure}
+
+\begin{figure}[htb]
 \centering
 \includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write scaling on \# of devices}
+\caption{XFS write performance scaling on number of devices}
 \label{fig:xfs-write}
-\end{minipage}%
 \end{figure}
 
-%% Are the read and write graphs wrong or should the second sentence below be about write
-%% instead of read?
-The read and write results are summarized in Figures~\ref{fig:xfs-read}
-and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
-indicates that XFS can get to the peak write performance with five SATA LUNs,
-then there is a bit of degradation from there. Changes to
-the queue depth do not seem to make any obvious difference in the performance.
+%\begin{figure}[htb]
+%\centering
+%% -- 1st figure
+%\begin{minipage}[t]{0.5\linewidth}
+%\centering
+%\includegraphics[width=3in]{data/xdd-read}
+%\caption{XFS read performance scaling on number of devices}
+%\label{fig:xfs-read}
+%\end{minipage}%
+%\begin{minipage}[t]{0.5\linewidth}
+%\centering
+%\includegraphics[width=3in]{data/xdd-write}
+%\caption{XFS write performance scaling on number of devices}
+%\label{fig:xfs-write}
+%\end{minipage}%
+%\end{figure}
+
+% % Are the read and write graphs wrong or should the second sentence below be
+% about write % instead of read?
+The read and write performance results are summarized in
+Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These show
+scaling behavior over the number of LUNs, which indicates that XFS can reach
+the peak write performance with five SATA LUNs. Increasing number of LUNs
+beyond 5, degradation happened. 
+Changes to the queue depth was not observed to make any obvious difference in
+the performance. For these tests, we used the \verb!xdd! benchmark with direct
+I/O and a request size of 32 KB.
 
@@
 
-RADOS is the Ceph object store, a foundational component for CephFS file
-system. There are three types of scaling tests we are interested at the RADOS layer:
+RADOS is the Ceph object store, the foundational component for CephFS file
+system. There are two types of scaling tests we are interested at the RADOS
+layer:
 
 \begin{itemize}
-  \item scaling on the number of servers
-  \item scaling on the number of clients
-  \item scaling on the number of OSDs
+  \item scaling on the number of OSD servers
+  \item scaling on the number of OSDs per OSD server
 \end{itemize}
 
-Our system setup poses some limitations on the scalability tests we want to
-perform. In particular, we currently have four OSS servers, eight clients, and eleven OSD servers
-per client. The scaling tests will be within these constraints.
+Our system setup poses some limitations on the scalability tests we wanted to
+perform. In particular, we currently had four OSD servers, eight clients, and
+eleven OSD servers per client. The scaling tests, therefore, will be within
+these constraints.
 
-We use the open-source tool RADOS Bench, developed by Inktank, to perform our
+We used the open-source RADOS Bench tool, developed by Inktank, to perform our
 initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
@@
 
-We have observed that using two or more client processes and many concurrent
+We observed that using two or more client processes and many concurrent
 operations are important when performing these tests.  We tested eight client processes 
@@
 node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  Only XFS was present
-and usable for the underlying OSDs, so BTRFS and EXT4 file systems were not
-tested at this time.
+were run with replication set to one.  The backend file systems were XFS,
+BTRFS and EXT4 file systems were not tested at this time.
 
-\subsection{Scaling on number of OSDs}
+\subsection{Scaling on number of OSDs per server}
 
-In the following test, a single Ceph host drives $n$ OSDs, where $n$
-increases from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this test
-case, we observe that the OSS exhibits near linear scalability up to nine
-OSDs, and is still trending upwards at eleven OSDs. This suggests that we have not reached the
-saturation point yet. Additional testing would require provisioning more OSDs on the SFA10K backend.
+In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
+from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
+We ran the test against a single client with four concurrent processes. In this
+test case, we observe that the OSD server exhibits near linear scalability up to
+nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
+have not reached the saturation point yet. Additional testing would require
+provisioning more OSDs on the SFA10K backend.
 
@@
 \includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on \# of OSDs}
+\caption{RADOS scaling on number of OSDs}
 \label{fig:osd-scale}
@@
 \includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on \# of servers}
+\caption{RADOS scaling on number of servers}
 \label{fig:oss-scale}
@@
 
-\subsection{Scaling on number of servers}
+\subsection{Scaling on number of OSD servers}
 
-In this test, we exercise OSS numbers from one to four, driven by four clients with four
-concurrent process for each client. Each additional OSS adds eleven more OSDs into
-play. We observe that Ceph exhibits linear scaling with regard to
-number of servers as well, at least in the given set of servers. However, the peak
-performance we are seeing is about the half of what are expecting from the SFA10K.
-For writes, it is attributed to the way Ceph performs
-journaling: Ceph does not support meta-data only journaling, therefore every
-write is the equivalent of a double-write: once to the data device, once to the
-journaling device. This effectively cuts the system bandwidth in half. That said,
-it does not explain the read performance -- it is better than write, but 
-still far from the theoretical maximum.
+In this test, we exercise OSD servers from one to four, driven by four hosts
+each with four RADOS Bench process. Each additional OSD server
+adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
+regard to number of servers as well, at least in the given set of servers.
+However, the peak performance we are seeing is about the half of what are
+expecting from the SFA10K (compare to the baseline block I/O perforamnce number
+presented in Section~\ref{sec:block-io}).
+
+For writes, the lost performance is attributed to the way Ceph performs
+journaling:
+Ceph does not support meta-data only journaling, therefore every write is the
+equivalent of a double-write: once to the data device, once to the journaling
+device. This effectively cuts the observed system bandwidth in half. That said,
+it does not explain the read performance -- it is a little better than write,
+but still far from the theoretical maximum.
 
@@
 
-We used the synthetic IOR benchmark suite the for file system level test. The particular
-parameter setup is show in Table \ref{tbl:ior}. Each client node has 6 GB of
-physical memory, the block size is set so as to mitigate cache effects. In
-addition, the test harness program will issue the following commands at the
-beginning of each test:
+We used the synthetic IOR benchmark suite for file system level performance and
+scalability test.
+The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
+has 6 GB of physical memory, the block size is set so as to mitigate cache
+effects. In addition, the test harness program issues the following commands
+at the beginning of each test:
 
@@
 We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
-(4) and same block size (8 GB), the results are illustrated in Figure
+transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
+(4) and fixed block size (8 GB), the results are illustrated in Figure
 \ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
@@
 \includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4k transfer size}
+\caption{IOR tests: 4 KB transfer size}
 \label{fig:ior4k}
@@
 \includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4m transfer size}
+\caption{IOR tests: 4 MB transfer size}
 \label{fig:ior4m}
@@
 \begin{itemize}
-  \item The small read performance is almost an anomaly -- we need to
-  investigate why it is so low compare to write performance.
-  \item The large read performance is almost half of the write performance,
-  which is the opposite of the RADOS-level results. 
-  \item The write performance is half of what we can obtain from
+  \item The small read (4 KB transfer size) performance is almost an anomaly --
+  we will investigate why it is so low compare to write performance and improved
+  results in Section~\ref{sec:improve-ior}.
+  \item The large read (4 MB transfer size) performance is almost half of the
+  RADOS read performance.
+
+  \item The write performance is also about half of what we can obtain from
   RADOS Bench. When number of clients reaches 8, there is a significant
@@
 After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all
-of the journals on the same disks as the data, doubling the OSD count, and
-upgrading Ceph to a development version which reduces the seek overhead caused
-by \texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are
-now included as of the Ceph Cuttlefish release).  The two biggest improvements
-resulted from disabling CRC32c checksums and increasing the OSD count on the
-server.  With these changes, we are seeing better results.
+including changing the number of filestore op threads, putting all of the
+journals on the same disks as the data, doubling the OSD count, and upgrading
+Ceph to a development version which reduces the seek overhead caused by
+\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
+included as of the Ceph Cuttlefish release, v0.61).  The two biggest
+improvements resulted from disabling CRC32c checksums and increasing the OSD
+count on the server.  With these changes, we are seeing better results.
 
@@
 
-Despite the excellent write throughput we saw during the individual server
-tests, throughput did not scale.  We spent a significant amount of time
+During a second round of test performed by Inktank, we noticed a dramatic drop
+on RADOS performance: even though write throughput on individual server met the
+expectation, it did not scale across servers.
+
+We spent a significant amount of time
 investigating this phenomenon. Ultimately, we were able to replicate this finding
@@
 \includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
+\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
+nodes}
 \label{fig:rados-064-oss}
@@
 \section{Improving Ceph File System Performance}
+\label{sec:improve-ior}
 
@@
 \includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with no client-side CRC32}
+\caption{IOR test with disabling client-side CRC32}
 \label{fig:ior-no-client-crc32}
@@
 \includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{file creation vs.  \# of clients}
+\caption{File creation vs.  number of clients}
 \label{fig:mdtest-fcreate}
@@
 \includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{directory creation vs. \# of clients}
+\caption{Directory creation vs. number of clients}
 \label{fig:mdtest-dcreate}

### 2013-08-20 data/plotxdd.R

@@ -21,8 +21,8 @@ plot_xdd <- function(f, m) {
             method=loess,
             #geom=c("point", "smooth"),
             ylab="Max (MB/s)\n",
-            xlab="\nNum of Devices",
-            main=paste("XFS ", m, " xdd -dio, req.size=32768", sep=""))
+            xlab="\nNum of LUNs",
+            main=paste("XFS ", m, " performance\n (xdd -dio, req.size=32768)", sep=""))
     g = g + scale_shape_discrete(name="queue depth")
     g = g + scale_color_discrete(name="queue depth")
     g = g + geom_point(size=3.5)

### 2013-08-20 ceph-eval.tex
add parameter notes for sweeping test

@@
 tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}.
+parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
+to Appendix E for explanations of these probed parameters.
 
@@
 
+\section*{Appendix E - Tuning Parameters}
+\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
+
+For parameter sweep, here are the settings we iterated through.  Some of these
+are "compound" settings where we increased or decreased multiple things in the
+ceph.conf file at the same time to reduce the number of permutations that would
+need to be tested.
+
+\input{tuning.txt}
+
 \end{document}

### 2013-08-20 ceph-eval.tex
Add XFS justification and Brtfs footnote

@@
 Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its performance and maturity, we chose XFS. We experimented with XFS to
-acquire a set of configuration parameters which provided optimal performance for
-the SFA10K. We sampled a selected set of parameters (block size, queue depth,
-request size, sequential read and write). We settled on the following
-configuration: mount with \verb!nobarrier,noatim,inode64! options.
+Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
+should be noted that in testing cases while we can compare XFS vs.
+Brtfs, Brtfs generally shows better performance results.} We experimented with
+XFS to acquire a set of configuration parameters which provided optimal
+performance for the SFA10K. We sampled a selected set of parameters (block size,
+queue depth, request size, sequential read and write). We settled on the
+following configuration: mount with \verb!nobarrier,noatim,inode64! options.
 The \verb!inode64! option had a notable improvement on sequential write (around

### 2013-08-21 ceph-eval.tex
updated ceph-eval

@@
 
-The initial stability issues we encountered are fixed by moving from Ceph
-version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test
-could complete even during long runs. This is another sign of how much Ceph
-development is in flux.
+The initial stability issues mentioned in chapters (X,Y,Z) are fixed by
+migrating from Ceph version 0.48/0.55 to 0.64, the latest stable version at the
+time of writing this report.  Upgrading to the latest stable Ceph release
+allowed us to run a full IOR parameter sweep for the first time since we
+started evaluating the performance and scalability of the Ceph file system.
+This is another sign of how much Ceph development is currently in flux.
 
-Another fix comes in the way we create the pool: the default data pool being used
-by previous CephFS cluster are set to 2x replication, which can potentially
-halve the write performance. Even with these changes in place, Inktank still
-reproduced the less-than-ideal write performance and very poor read
-performance as observed by ORNL.  Further, by increasing the number of IOR
-processes per client node, read performance actually degraded further
-indicating some kind of contention either on the clients or on the OSD
-servers.
+Another fix introduced by Ceph version 0.64 was in pool creation.  The default
+data pool used by previous Ceph version were set to 2x replication at the
+minimum. This potentially halved the write performance. With version 0.64 we
+now had the ability to set the replication level to 1, which is the preferred
+value for a HPC environment like ours running on high-end and reliable storage
+backend hardware (e.g. DDN SFA10K).
+
+Even with these two changes in place, less-than-ideal write performance and
+very poor read performances were observed during our tests.  We also observed
+that by increasing the number of IOR processes per client node, the read
+performance degraded even further indicating some kind of contention either on
+the clients or on the OSD servers.
 
@@
 
-ORNL at this point was able to both make more client nodes available and also
-install a profiling tool called \verb!perf! that is extremely useful for
-profiling both kernel and user space code.  Profiling with \verb!perf! showed
-high CPU utilization on the client due to crc32c processing in the Ceph kernel
-client.  Luckily, crc32 checksums can be disabled by changing the CephFS mount
-options:
+At this point, we were able to both make more client nodes available for Ceph
+file system-level testing and also install a profiling tool called \verb!perf!
+that is extremely useful for profiling both kernel and user space codes.
+Profiling with \verb!perf! showed high CPU utilization on test clients due to
+crc32c processing in the Ceph kernel client.  crc32 checksums can be disabled
+by changing the CephFS mount options:
 
@@
 
-With client CRC32 disabled, we repeated the IOR test and the results are showin
+With client CRC32 disabled, we repeated the IOR tests. New results are shown in
 in Figure~\ref{fig:ior-no-client-crc32}.
@@
 We observed that IOR write throughput increased dramatically and is now very
-close to the throughput we were able to achieve with RADOS Bench, but reads
-continued to be slow and continued to scale inversely with the number of client
-processes.  Please note that since these tests were performed, Inktank has
-implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based CRC32
-processing should have already been using SSE4 instructions on Intel CPUs, this
-will allow any user-land Ceph processes to process CRC32 checksums with
-significantly less overhead.
+close and comparable to the RADOS Bench performance. Read performance continued
+to be poor and continued to scale inversely with the increasing number of
+client processes.  Please note that, since these tests were performed, Inktank
+has implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based
+CRC32 processing should have already been using SSE4 instructions on Intel
+CPUs, this update will allow any user-land Ceph processes to process CRC32
+checksums with significantly less overhead.
 
@@
 parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which happens to be the kernel
-that ORNL had installed on the test systems.\footnote{For more information,
+observed roughly in the kernel 3.5 time frame which was the kernel
+installed on our test systems.\footnote{For more information,
 please refer to \url{http://lwn.net/Articles/517082/} and
@@
 
-ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
-RADOS Bench test to verify that there was no degradation versus previous tests.  The
-results were extremely positive.
+We upgraded our test systems with kernel version 3.9 and performed a
+RADOS Bench test.  The
+results were extremely positive and presented in Figure~\ref{fig:rados-kernel-35vs39}.
 
@@
 
-With the kernel changes writes performance improved slightly, while read
-performance improved dramatically.  In addition to the kernel change, Sage Weil
-suggested increasing the amount of read-ahead being performed by the CephFS
-kernel client:
+As can be seen, with the 3.9 kernel, while there was a slight improvement on
+write performance, read performance improved dramatically.  In addition to the
+kernel change, Sage Weil from InkTank suggested increasing the amount of CephFS
+client kernel read-ahead cache size as:
 
@@
 
+IOR results reflecting the read-ahead cache size change are presented in
+Figure~\ref{fig:ior-kernel-39}.
+
 \begin{figure}[htb]
@@
 
-By installing a new kernel, increasing read-ahead, and increasing the number of
-client IOR processes, we were able to achieve a very satisfactory result on this
-test run.
+By installing a newer kernel, increasing read-ahead cache size, and increasing the number of
+client IOR processes, we were able to achieve very satisfactory I/O performance.
 
-\subsection{Repeating IOR Scaling Test}
+\subsection{Repeating the IOR Scaling Test}
 
 As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
-seeing a much improved picture of read and write performance, very much in
-line with RADOS bench performance.
+These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we saw
+saw  improved read and write performance. These new read and write performance are in
+line with observed RADOS bench performance.
 
@@
 
-We observe a couple of places where the average write throughput is quite a
-bit lower than the maximum.  This behavior was observed during other tests as well,
+Throughout our IOR testing, we observed that the average write throughput is 
+lower than the maximum.  This behavior was observed during other tests as well,
 indicating that we may have periods of time where write throughput is
 temporarily degrading.  Despite these issues, performance generally seems to be
-improving as the number of clients increases.  Writes seem to be topping out at
+improving with respect to increasing number of clients.  Writes seem to be topping out at
 around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
 topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
-saw with RADOS Bench.
+would continue scaling with more clients and get closer to ~8 GB/s  we
+obervered with RADOS Bench.
 
@@
 
-In our particular setup, we have only one metadata server (MDS)
-configured. Therefore, this is not a scalability test on the performance of
-clustered MDS, which would be very interesting.
-Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
-scales. The particular parameters we use for testing are:
+In our particular setup, we only had one metadata server (MDS) configured.
+Therefore, this is not a scalability test on the performance of Ceph clustered
+MDS, which would have been very interesting.  Instead, we focus on a single MDS
+performance and exercise it with up to 8 clients to observe the single MDS
+performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
+used for this test are:
 
@@
 \item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform sync after it. This is a more realistic use case scenario than just
-open, close and removal.
+perform a sync operation.  This is a more realistic use case scenario than just
+open, close and removal sequence of metadata operations.
 
-\item \verb!-n 1000!: this is per client file \textit{and} directories. For eight
-clients, the number of files and directories is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, so this is a mixture of both.
+\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
+clients, the total number of files and directories in the workload is 8,000. Since we did not specify
+either \verb!-D! or \verb!-F!, this is a mixture of both.
 
@@
 
-Each test iterates five times and we are showing the max. 
+Each test iterates five times and we are presenting the maximum out of all five iterations. 
 We summarize the results as follows:
@@
 
-\item Within a single sharing mode (either shared or unique directory), the
-directory stat and file stat, as well as file read exhibit strong linear
-scaling property.
+\item Within a single sharing mode (either shared or unique directory), stat
+operations for directories and files exhibit strong linear scaling. Same strong
+linear scaling is also observed for file read operations.
 
@@
 
-\item Though the same saturation or degradation trend is not observed for file
-creation, it is likely due to we have not put enough of workload stress on MDS.
+\item Though the same saturation (or degradation) trend is not observed for file
+creation operation, it is likely due to lack of workload stress on MDS.
 
@@
 
-This is preliminary observations from mostly performance perspective:
+Below are our preliminary observations from mostly performance perspective:
 
@@
 are unreliable, with little or no redundancy and failure detection capability.
-  This is not the case in leadership computing facilities. We have disabled
-  replication for pools, but this will take a toll somewhere in the processing
-  and we do not know if this is significant.
+This assumption is not valid for high-end HPC centers like ours. We have
+disabled replication for pools, but this will take a toll somewhere in the
+processing and we do not know yet if this would be significant.
 
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
-  system that has locally attached disk. However, this presents a problem in DDN
-  SFA10-like hardware, where the backend LUNs are exposed as block device
-  through SCSI Request Protocol (SRP) over IB. The journaling write requires twice the bandwidth
-  compare to Lustre-like metadata-only journaling mechanism. For Ceph to be
-  viable in this facility, we will need to address this.
+  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
+host systems that has locally attached disk. However, this presents a problem
+in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
+devices through SCSI Request Protocol (SRP) over IB. The journaling write
+requires twice the bandwidth compare to Lustre-like metadata-only journaling
+mechanism. For Ceph to be viable in this facility, journaling operations will
+need to further design and engineering.
 
-  \item We observed consistent results and linear scalability at the
-  RADOS level. However, we did not observe the same at the file system level with synthetic
-  benchmark suites such as IOR. We have experienced large performance swings
-  during different runs, very low read performance when transfer size is small,
-  and I/O errors tend to happen when system is under stress (more clients and
-  large transfer sizes). These are not particularly reproducible results, but it
-  suggests that there are opporunities for code improvement and maturation.
+  \item We observed consistent results and linear scalability at the RADOS
+level. However, we did not observe the same at the file system level. We have
+experienced large performance swings during different runs, very low read
+performance when transfer size is small, and I/O errors tend to happen when
+system is under stress (more clients and large transfer sizes). These are not
+particularly reproducible results, but it suggests that there are opportunities
+for code improvement and maturation.
 

### 2013-08-21 cover.tex
Fix scott's name
Final (maybe) round of update for tech report version

@@
 \begin{center}
-\textbf\textsc{\Large Ceph Parallel File System Evaluation Report}\\
+\textbf{\Large Ceph Parallel File System Evaluation Report}\\
 \rule{5in}{1pt}%
@@
 Doug Fuller\\
-Scotty Atchley\\
+Scott Atchley\\
 Blake Caldwell\\

### 2013-08-21 report.tex
Final (maybe) round of update for tech report version

--- 2013-08-21 ceph-eval.tex
@@
 National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, has prepared a detailed performance and scalability study of
-Ceph file system. Ceph is originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it is designed to be a reliable, scalable
+Inktank Inc, prepared this performance and scalability study of
+Ceph file system. Ceph originated from Sage Weil's PhD research
+at UC Santa Cruz around 2007 and it was designed to be a reliable, scalable
 fault-tolerant parallel file system. Inktank is now the major developer behind
 the open-source parallel file system to sheperd its development and provide
-commerical support.
+commercial support.
 
@@
   CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration failure domains and
+  placement and layout while taking into consideration of failure domains and
   hierarchical storage tiers.
@@
 \item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers.
+  with a cluster of metadata servers. It utilized a dynamic subtree partitioning
+  strategy to continuously adapt metadata distribution to current demands.
 
-\item Ceph's design assumes that the system is composed of
-unreliable components; fault-detection and fault-tolerance (e.g., replication) are
-the norm rather than the exception. This is in line with the expectations of
-Exascale computing.
+\item Ceph's design assumes that the system is composed of unreliable
+components; fault-detection and fault-tolerance (e.g., replication) are the
+norm rather than the exception. This is in line with the expectations and
+future directions of Exascale computing.
 
@@
 As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the feasibility
-of using the Ceph for our future HPC storage deployment.
-This report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph has not matured yet for scientific
-HPC community that its code base is changing rapidly. In between releases, we
-often experienced different outcomes. We will try to make clear in the report
-when such changes occurred.
+file system evaluation. The goal of our study is to investigate the
+feasibility of using the Ceph for our future HPC storage deployment.  This
+report presents our experience, results, and observations. While evaluating
+our results, please keep in mind that Ceph is still a relatively
+\textit{young} parallel file system and its code base is changing rapidly. In
+between releases, we often experienced different stability and performance
+outcomes.  We will try to make clear in the report when such changes occurred.
 
@@
 \includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K Hardware and Host Connection Diagram}
+\caption{DDN SFA10K hardware and host connection diagram}
 \label{fig:ddn-sfa10k}
@@
 All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 (rhl-ceph image), Glibc 2.12 with syncfs support, locally patched.
-We used the Ceph 0.55 release in the initial tests, upgraded to 0.64 and then to
-0.67RC for a final round of tests.
+version 3.5.1 initially, and later upgraded to 3.9 (rhl-ceph image), Glibc
+2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
+release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
+round of tests.
 
@@
 \subsection{Block I/O over Native IB}
-We first established baseline performance by measuring observed block I/O
-performance.
+
+We first established baseline performance by measuring block I/O performance.
 At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
@@
 
-Unfortunately there was not enough time to do more detailed analysis of the network
-performance. Later, we will see RADOS is performing a
-maximum of 5-6 GB/s driven by four hosts.  So, it shows that we
-have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
-case).
+Unfortunately there was not enough time to do more detailed analysis of the
+network performance. However, as we observed later, RADOS is performing no
+more than 8 GB/s driven by four server hosts. This confirms that we have
+provisioned enough network bandwidth. In other words, IP over IB is not a
+bottleneck in this case.
 
@@
 % about write % instead of read?
+
 The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These show
-scaling behavior over the number of LUNs, which indicates that XFS can reach
-the peak write performance with five SATA LUNs. Increasing number of LUNs
-beyond 5, degradation happened. 
-Changes to the queue depth was not observed to make any obvious difference in
-the performance. For these tests, we used the \verb!xdd! benchmark with direct
-I/O and a request size of 32 KB.
+Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These graphs
+show scaling behavior over the number of LUNs, which indicates that XFS can
+reach the peak write performance with just five SATA LUNs. Increasing number
+of LUNs beyond 5, degradation happened.  Also, we did not observe any obvious
+differences in performance when varying the queue depth parameter.  For these
+tests, we used the \verb!xdd! benchmark with direct I/O and a request size of
+32 KB.
 
@@
 
-RADOS is the Ceph object store, the foundational component for CephFS file
-system. There are two types of scaling tests we are interested at the RADOS
-layer:
+RADOS is a reliable distributed object store, the foundational component for
+CephFS file system. There are two types of scaling tests we are interested at
+the RADOS layer:
 
@@
 \section{Ceph File System Performance: Initial Test}
-
+\label{sec:ior-initial}
 We used the synthetic IOR benchmark suite for file system level performance and
@@
 \begin{itemize}
-  \item The small read (4 KB transfer size) performance is almost an anomaly --
-  we will investigate why it is so low compare to write performance and improved
-  results in Section~\ref{sec:improve-ior}.
+
+  \item The small read (4 KB transfer size) performance is almost an anomaly
+  -- we will investigate why it is so low compare to write performance and
+  present improved results in Section~\ref{sec:improve-ior}.
+
   \item The large read (4 MB transfer size) performance is almost half of the
@@
   performance drop as well.
+
 \end{itemize}
@@
 
-\subsection{Disable Cache Mirroring on controllers}
+\subsection{Disable Cache Mirroring on Controllers}
 
@@
 to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux Kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
-TCP auto tuning enables TCP window scaling by default and automatically adjusts
+with TCP autotuning in the Linux
+kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}} TCP auto tuning enables TCP window scaling by default and automatically adjusts
 the TCP receive window for each connection based on link conditions such as
@@
 
-The initial stability issues mentioned in chapters (X,Y,Z) are fixed by
-migrating from Ceph version 0.48/0.55 to 0.64, the latest stable version at the
+The initial stability issues mentioned in Section~\ref{sec:ior-initial} are
+fixed by migrating from Ceph version 0.48/0.55 to 0.64, the latest stable version at the
 time of writing this report.  Upgrading to the latest stable Ceph release
@@
 Another fix introduced by Ceph version 0.64 was in pool creation.  The default
-data pool used by previous Ceph version were set to 2x replication at the
-minimum. This potentially halved the write performance. With version 0.64 we
-now had the ability to set the replication level to 1, which is the preferred
-value for a HPC environment like ours running on high-end and reliable storage
-backend hardware (e.g. DDN SFA10K).
+data pool used by previous Ceph version were set to 2x replication by mistake.
+This potentially halved the write performance. With version 0.64 we explicitly
+set the replication level to 1, which is the preferred value for a HPC
+environment like ours running on high-end and reliable storage backend hardware
+(e.g. DDN SFA10K).
 
@@
 
-We upgraded our test systems with kernel version 3.9 and performed a
-RADOS Bench test.  The
-results were extremely positive and presented in Figure~\ref{fig:rados-kernel-35vs39}.
+We upgraded our test systems with kernel version 3.9 and performed RADOS Bench
+test.  The results were extremely positive and presented in
+Figure~\ref{fig:rados-kernel}.
 
@@
 \includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Kernel 3.5 vs. 3.9}
+\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
 \label{fig:rados-kernel}
@@
 \includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with Kernel changes to 3.9, IOR with 4 MB transfer
+\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
 size}
@@
 
-\item Within a single sharing mode (either shared or unique directory), stat
+\item With either shared or unique directory (\verb!-u!), stat
 operations for directories and files exhibit strong linear scaling. Same strong
@@
 
-\item Though the same saturation (or degradation) trend is not observed for file
-creation operation, it is likely due to lack of workload stress on MDS.
+\item Though the same saturation (or degradation) trend was not observed for
+file creation operation, it is likely due to lack of workload stress on MDS.
 
@@
 This assumption is not valid for high-end HPC centers like ours. We have
-disabled replication for pools, but this will take a toll somewhere in the
-processing and we do not know yet if this would be significant.
+disabled replication for pools, we haven't measured and quantified
+processing overhead and we do not know yet if this would be significant.
 

### 2013-08-21 data/gen.sh

@@ -3,8 +3,8 @@ Rscript plotxfs.R xfs.csv
 Rscript plot_rados_osd.R rados_osd.csv
 Rscript plot_rados_client.R rados_client.csv
 Rscript plot_rados_server.R rados_server.csv
-Rscript plot_ior.R ior-8c-4k-scaling.dat
-Rscript plot_ior.R ior-8c-4m-scaling.dat
+Rscript plot_ior.R ior-8c-4KB-scaling.dat
+Rscript plot_ior.R ior-8c-4MB-scaling.dat
 Rscript plotxdd.R xdd-read.csv read
 Rscript plotxdd.R xdd-write.csv write
 

### 2013-08-21 abstract.tex
first cut of abstract

Ceph is designed to be a reliable and scalable fault tolerant parallel file
system with a number of intriguing features. In collaboration with its major
developer, Inktank Inc, we studied the feasibility of using Ceph for future
HPC storage deployment. This paper presents our experiments, results and
observations from mostly performance and scalability perspective. Our work
made two unique contributions. First, this evaluation is performed under a
realistic setup using state-of-the-art backend storage (Data Direct Network's
SFA10K),  although typical in large-scale HPC environment, but atypical for
average commercial off-the-shelf setup.  Second, our path of investigation,
tuning efforts, and findings made a direct contribution to Ceph's development,
it should also benefit community at large. Throughout the evaluation, we can
see that Ceph is under fast-paced development and maturing with great promise.

### 2013-08-21 baseline.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-20 ceph-eval.tex
@@
-\documentclass{article}
-
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
-\section{Introduction}
-
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, has prepared a detailed performance and scalability study of
-Ceph file system. Ceph is originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it is designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commerical support.
-
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration failure domains and
-  hierarchical storage tiers.
-
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers.
-
-\item Ceph's design assumes that the system is composed of
-unreliable components; fault-detection and fault-tolerance (e.g., replication) are
-the norm rather than the exception. This is in line with the expectations of
-Exascale computing.
-
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
-
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
-
-\end{itemize}
-
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the feasibility
-of using the Ceph for our future HPC storage deployment.
-This report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph has not matured yet for scientific
-HPC community that its code base is changing rapidly. In between releases, we
-often experienced different outcomes. We will try to make clear in the report
-when such changes occurred.
-
-\section{Testbed Environment Description}
-
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K Hardware and Host Connection Diagram}
-\label{fig:ddn-sfa10k}
-\end{figure}
-
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
-
-\begin{table}[H]
-\centering
-    \begin{tabular}{ll}
-    \toprule
-    Node & Role \\
-    \midrule
-    tick-mds1 & Ceph monitor node \\
-    spoon46 & Ceph MDS node \\
-    tick-oss[1-4] & Ceph OSD servers \\
-    spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
-    \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
-\end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 (rhl-ceph image), Glibc 2.12 with syncfs support, locally patched.
-We used the Ceph 0.55 release in the initial tests, upgraded to 0.64 and then to
-0.67RC for a final round of tests.
-
-%For a complete a list of hosts that are running ceph images, one can execute:
-
-%\begin{Verbatim}
-%$ grep "rhel6-ceph" /etc/gedi/MAC.info
-%\end{Verbatim}
-
 \section{Baseline Performance}
@@
 \centering
-\begin{tabular}{ll}
-    \toprule
+\caption{Block I/O performances on single LUN and single host}
+\label{tbl:block-io-baseline}
+
+\begin{tabular}{| l | l |}
+    \hline
     SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
+    SATA single LUN sequential read & ~955 MB/s \\
     Single host with four SAS LUNs & ~ 2.8 GB/s \\
     Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
+    \hline
 \end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
 \end{table}
@@
 
-Unfortunately there was not enough time to do more detailed analysis of the network
-performance. Later, we will see RADOS is performing a
-maximum of 5-6 GB/s driven by four hosts.  So, it shows that we
-have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
-case).
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
-\section{XFS Performance As Backend File System}
-
-Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
-should be noted that in testing cases while we can compare XFS vs.
-Brtfs, Brtfs generally shows better performance results.} We experimented with
-XFS to acquire a set of configuration parameters which provided optimal
-performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the
-following configuration: mount with \verb!nobarrier,noatim,inode64! options.
-The \verb!inode64! option had a notable improvement on sequential write (around
-20\%).
-
-%% Can the graphs be adjusted to have the same values in the Y axis?
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\centering
-\includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read performance scaling on number of devices}
-\label{fig:xfs-read}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write performance scaling on number of devices}
-\label{fig:xfs-write}
-\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%% -- 1st figure
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-read}
-%\caption{XFS read performance scaling on number of devices}
-%\label{fig:xfs-read}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-write}
-%\caption{XFS write performance scaling on number of devices}
-%\label{fig:xfs-write}
-%\end{minipage}%
-%\end{figure}
-
-% % Are the read and write graphs wrong or should the second sentence below be
-% about write % instead of read?
-The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These show
-scaling behavior over the number of LUNs, which indicates that XFS can reach
-the peak write performance with five SATA LUNs. Increasing number of LUNs
-beyond 5, degradation happened. 
-Changes to the queue depth was not observed to make any obvious difference in
-the performance. For these tests, we used the \verb!xdd! benchmark with direct
-I/O and a request size of 32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is the Ceph object store, the foundational component for CephFS file
-system. There are two types of scaling tests we are interested at the RADOS
-layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
-
-We used the open-source RADOS Bench tool, developed by Inktank, to perform our
-initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
-writes out objects to the underlying object storage as fast as possible, and
-then later reads those objects in the same order as they were written.
-
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
-
-\subsection{Scaling on number of OSDs per server}
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
-nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
-have not reached the saturation point yet. Additional testing would require
-provisioning more OSDs on the SFA10K backend.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
-\label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
-\label{fig:oss-scale}
-\end{minipage}%
-\end{figure}
-
-\subsection{Scaling on number of OSD servers}
-
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
-
-\section{Ceph File System Performance: Initial Test}
-
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
-
-\begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
-\caption{IOR parameter setup}
-\label{tbl:ior}
-\end{table}
-
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
-
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
-
-%% FEIYI: 6, 7 all fixed.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
-
-\begin{itemize}
-  \item The small read (4 KB transfer size) performance is almost an anomaly --
-  we will investigate why it is so low compare to write performance and improved
-  results in Section~\ref{sec:improve-ior}.
-  \item The large read (4 MB transfer size) performance is almost half of the
-  RADOS read performance.
-
-  \item The write performance is also about half of what we can obtain from
-  RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well. 
-\end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
-
-We will describe the efforts and results on performance improvement in the
-following sections.
-
-\section{Improving RADOS Performance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=5in]{parametric}
-\caption{Evaluating parameter impact through sweeping test}
-\label{fig:parametric}
-\end{figure}
-
-After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
-journals on the same disks as the data, doubling the OSD count, and upgrading
-Ceph to a development version which reduces the seek overhead caused by
-\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
-
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
-
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
-
-\subsection{Disable Cache Mirroring on controllers}
-
-During a second round of test performed by Inktank, we noticed a dramatic drop
-on RADOS performance: even though write throughput on individual server met the
-expectation, it did not scale across servers.
-
-We spent a significant amount of time
-investigating this phenomenon. Ultimately, we were able to replicate this finding
-when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The second RAID processor on each DDN controller would max out when
-three or more LUNs were written concurrently. It turns out the root of the problem
-was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.\footnote{DDN recently released a new
-firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
-a chance to verify it during our test cycle.}
-
-%% SCOTT - is running with cache mirroring off and option for a production system or not?
-%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
-%% with it or not?
-
-%% FEIYI: add footnote to clarify the issue.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-after-ddn}
-\caption{Evaluating RADOS bench after disabling cache mirroring}
-\label{fig:rados-ddn-mirror-disabled}
-\end{figure}
-
-With cache mirroring disabled, write performance when using all four servers
-improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
-5.5 GB/s from the clients.  When accounting for journal writes, that is over
-11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
-Unfortunately, read performance did not scale as well.
-
-\subsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux Kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
-TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
-
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
-\subsection{Repeating RADOS Scaling Test}
-
-We now repeated the previous RADOS scaling tests with these improvements in place.
-The first test was done on a single node with RADOS Bench to see how close the
-underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
-XFS-formatted storage.
-
-%% SCOTT - the title in the figure needs to change IO to I/O
-
-%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
-%% on the single server?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
-\label{fig:rados-064-osd}
-\end{figure}
-
-In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
-
-We also repeated tests looking at RADOS Bench performance as the number of OSD
-server nodes increases from one to four. The results are summarized in
-Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
-scales nearly linearly for both reads and writes.
-
-%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
-%% Do they no measure the same thing (i.e. a single server)? If not, the text
-%% needs to make it more clear.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
-nodes}
-\label{fig:rados-064-oss}
-\end{figure}
-
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
-
-The initial stability issues we encountered are fixed by moving from Ceph
-version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test
-could complete even during long runs. This is another sign of how much Ceph
-development is in flux.
-
-Another fix comes in the way we create the pool: the default data pool being used
-by previous CephFS cluster are set to 2x replication, which can potentially
-halve the write performance. Even with these changes in place, Inktank still
-reproduced the less-than-ideal write performance and very poor read
-performance as observed by ORNL.  Further, by increasing the number of IOR
-processes per client node, read performance actually degraded further
-indicating some kind of contention either on the clients or on the OSD
-servers.
-
-\subsection{Disabling Client CRC32}
-
-ORNL at this point was able to both make more client nodes available and also
-install a profiling tool called \verb!perf! that is extremely useful for
-profiling both kernel and user space code.  Profiling with \verb!perf! showed
-high CPU utilization on the client due to crc32c processing in the Ceph kernel
-client.  Luckily, crc32 checksums can be disabled by changing the CephFS mount
-options:
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
-
-With client CRC32 disabled, we repeated the IOR test and the results are showin
-in Figure~\ref{fig:ior-no-client-crc32}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with disabling client-side CRC32}
-\label{fig:ior-no-client-crc32}
-\end{figure}
-
-We observed that IOR write throughput increased dramatically and is now very
-close to the throughput we were able to achieve with RADOS Bench, but reads
-continued to be slow and continued to scale inversely with the number of client
-processes.  Please note that since these tests were performed, Inktank has
-implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based CRC32
-processing should have already been using SSE4 instructions on Intel CPUs, this
-will allow any user-land Ceph processes to process CRC32 checksums with
-significantly less overhead.
-
-\subsection{Improving IOR Read Performance}
-
-Deeper analysis with perf showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which happens to be the kernel
-that ORNL had installed on the test systems.\footnote{For more information,
-please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
-
-ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
-RADOS Bench test to verify that there was no degradation versus previous tests.  The
-results were extremely positive.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Kernel 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
-
-With the kernel changes writes performance improved slightly, while read
-performance improved dramatically.  In addition to the kernel change, Sage Weil
-suggested increasing the amount of read-ahead being performed by the CephFS
-kernel client:
-
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
-%% mention that 15 shows the filesystem performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with Kernel changes to 3.9, IOR with 4 MB transfer
-size}
-\label{fig:ior-kernel-39}
-\end{figure}
-
-By installing a new kernel, increasing read-ahead, and increasing the number of
-client IOR processes, we were able to achieve a very satisfactory result on this
-test run.
-
-\subsection{Repeating IOR Scaling Test}
-
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
-seeing a much improved picture of read and write performance, very much in
-line with RADOS bench performance.
-
-%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
-%% as to why 4 KB performance is better than 4 MB performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
-\label{fig:ior-064}
-\end{figure}
-
-We observe a couple of places where the average write throughput is quite a
-bit lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving as the number of clients increases.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
-saw with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
-\end{figure}
-
-In our particular setup, we have only one metadata server (MDS)
-configured. Therefore, this is not a scalability test on the performance of
-clustered MDS, which would be very interesting.
-Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
-scales. The particular parameters we use for testing are:
-
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform sync after it. This is a more realistic use case scenario than just
-open, close and removal.
-
-\item \verb!-n 1000!: this is per client file \textit{and} directories. For eight
-clients, the number of files and directories is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, so this is a mixture of both.
-
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
-
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
-
-\end{itemize}
-
-Each test iterates five times and we are showing the max. 
-We summarize the results as follows:
-
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
-
-\begin{itemize}
-
-\item Within a single sharing mode (either shared or unique directory), the
-directory stat and file stat, as well as file read exhibit strong linear
-scaling property.
-
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
-
-\item Though the same saturation or degradation trend is not observed for file
-creation, it is likely due to we have not put enough of workload stress on MDS.
-
-\end{itemize}
-
-The results also show that file creation rate is signficantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results from early version of Ceph without all
-the tunings and improvement applied. Therefore, we repeated the same test on the
-latest CephFS 0.64. The result is illustrated in
-Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
-improvement on the file creation rate. We also note that as number of clients
-increase, the file creation rate decreases rapidly, which suggested some form of
-lock contention. This presents some interesting issues to be investigated
-further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
-\section{Observations and Conclusions}
-
-This is preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
-  are unreliable, with little or no redundancy and failure detection capability.
-  This is not the case in leadership computing facilities. We have disabled
-  replication for pools, but this will take a toll somewhere in the processing
-  and we do not know if this is significant.
-
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
-  system that has locally attached disk. However, this presents a problem in DDN
-  SFA10-like hardware, where the backend LUNs are exposed as block device
-  through SCSI Request Protocol (SRP) over IB. The journaling write requires twice the bandwidth
-  compare to Lustre-like metadata-only journaling mechanism. For Ceph to be
-  viable in this facility, we will need to address this.
-
-  \item We observed consistent results and linear scalability at the
-  RADOS level. However, we did not observe the same at the file system level with synthetic
-  benchmark suites such as IOR. We have experienced large performance swings
-  during different runs, very low read performance when transfer size is small,
-  and I/O errors tend to happen when system is under stress (more clients and
-  large transfer sizes). These are not particularly reproducible results, but it
-  suggests that there are opporunities for code improvement and maturation.
-
-\end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}
+Unfortunately there was not enough time to do more detailed analysis of the
+network performance. However, as we observed later, RADOS is performing no
+more than 8 GB/s driven by four server hosts. This confirms that we have
+provisioned enough network bandwidth. In other words, IP over IB is not a
+bottleneck in this case.

### 2013-08-21 ceph-initial.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-20 ceph-eval.tex
@@
-\documentclass{article}
+\section{Ceph RADOS Scaling: Initial Results}
 
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
-\section{Introduction}
-
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, has prepared a detailed performance and scalability study of
-Ceph file system. Ceph is originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it is designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commerical support.
-
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration failure domains and
-  hierarchical storage tiers.
-
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers.
-
-\item Ceph's design assumes that the system is composed of
-unreliable components; fault-detection and fault-tolerance (e.g., replication) are
-the norm rather than the exception. This is in line with the expectations of
-Exascale computing.
-
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
-
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
-
-\end{itemize}
-
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the feasibility
-of using the Ceph for our future HPC storage deployment.
-This report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph has not matured yet for scientific
-HPC community that its code base is changing rapidly. In between releases, we
-often experienced different outcomes. We will try to make clear in the report
-when such changes occurred.
-
-\section{Testbed Environment Description}
-
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K Hardware and Host Connection Diagram}
-\label{fig:ddn-sfa10k}
-\end{figure}
-
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
-
-\begin{table}[H]
-\centering
-    \begin{tabular}{ll}
-    \toprule
-    Node & Role \\
-    \midrule
-    tick-mds1 & Ceph monitor node \\
-    spoon46 & Ceph MDS node \\
-    tick-oss[1-4] & Ceph OSD servers \\
-    spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
-    \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
-\end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 (rhl-ceph image), Glibc 2.12 with syncfs support, locally patched.
-We used the Ceph 0.55 release in the initial tests, upgraded to 0.64 and then to
-0.67RC for a final round of tests.
-
-%For a complete a list of hosts that are running ceph images, one can execute:
-
-%\begin{Verbatim}
-%$ grep "rhel6-ceph" /etc/gedi/MAC.info
-%\end{Verbatim}
-
-\section{Baseline Performance}
-\label{sec:block-io}
-
-\subsection{Block I/O over Native IB}
-We first established baseline performance by measuring observed block I/O
-performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with four SAS LUNs & ~ 2.8 GB/s \\
-    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
-\end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
-\end{table}
-
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
-
-\subsection{IP over IB}
-
-Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
-
-Unfortunately there was not enough time to do more detailed analysis of the network
-performance. Later, we will see RADOS is performing a
-maximum of 5-6 GB/s driven by four hosts.  So, it shows that we
-have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
-case).
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
-\section{XFS Performance As Backend File System}
-
-Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
-should be noted that in testing cases while we can compare XFS vs.
-Brtfs, Brtfs generally shows better performance results.} We experimented with
-XFS to acquire a set of configuration parameters which provided optimal
-performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the
-following configuration: mount with \verb!nobarrier,noatim,inode64! options.
-The \verb!inode64! option had a notable improvement on sequential write (around
-20\%).
-
-%% Can the graphs be adjusted to have the same values in the Y axis?
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\centering
-\includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read performance scaling on number of devices}
-\label{fig:xfs-read}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write performance scaling on number of devices}
-\label{fig:xfs-write}
-\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%% -- 1st figure
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-read}
-%\caption{XFS read performance scaling on number of devices}
-%\label{fig:xfs-read}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-write}
-%\caption{XFS write performance scaling on number of devices}
-%\label{fig:xfs-write}
-%\end{minipage}%
-%\end{figure}
-
-% % Are the read and write graphs wrong or should the second sentence below be
-% about write % instead of read?
-The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These show
-scaling behavior over the number of LUNs, which indicates that XFS can reach
-the peak write performance with five SATA LUNs. Increasing number of LUNs
-beyond 5, degradation happened. 
-Changes to the queue depth was not observed to make any obvious difference in
-the performance. For these tests, we used the \verb!xdd! benchmark with direct
-I/O and a request size of 32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is the Ceph object store, the foundational component for CephFS file
-system. There are two types of scaling tests we are interested at the RADOS
-layer:
+RADOS is a reliable distributed object store, the foundational component for
+CephFS file system. There are two types of scaling tests we are interested at
+the RADOS layer:
 
@@
 
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
+\begin{figure}[!t]
 \centering
@@
 \label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
+\end{figure}
+
+\begin{figure}[!t]
 \centering
@@
 \label{fig:oss-scale}
-\end{minipage}%
 \end{figure}
@@
 \begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
 \caption{IOR parameter setup}
 \label{tbl:ior}
+\centering
+\begin{tabular}{p{0.8in} | p{2in}}
+    \hline
+    IOR parameter & Note \\ \hline
+    \verb!-F! & file per process \\ \hline
+    \verb!-a POSIX! & use POSIX API \\ \hline
+    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
+        ordering for read back so it will not read from the write cache. \\
+        \hline
+    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\ \hline  
+    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \hline
+    \verb!-b 8g or 16g! & the block size \\ \hline
+    \verb!-t 4k to 4m! & the transfer size \\ \hline
+    \verb!-o file! & mandatory test file  \\    
+    \hline
+\end{tabular}
 \end{table}
@@
 
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
+\begin{figure*}[!t]
 
-%% FEIYI: 6, 7 all fixed.
+\centerline{\subfloat[4 KB transfer size]
+{\includegraphics[width=3in]{data/ior_4k}
+\label{fig:ior4k}}
+\hfil
+\subfloat[4 MB transfer size]
+{\includegraphics[width=3in]{data/ior_4m}
+\label{fig:ior4m}}
+}% end of centerline
+\caption{CephFS scalability test with IOR}
 
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
+\end{figure*}
 
 \begin{itemize}
-  \item The small read (4 KB transfer size) performance is almost an anomaly --
-  we will investigate why it is so low compare to write performance and improved
-  results in Section~\ref{sec:improve-ior}.
+
+  \item The small read (4 KB transfer size) performance is almost an anomaly
+  -- we will investigate why it is so low compare to write performance and
+  present improved results in Section~\ref{sec:improve-ior}.
+
   \item The large read (4 MB transfer size) performance is almost half of the
@@
   performance drop as well.
+
 \end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
 
@@
 following sections.
-
-\section{Improving RADOS Performance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=5in]{parametric}
-\caption{Evaluating parameter impact through sweeping test}
-\label{fig:parametric}
-\end{figure}
-
-After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
-journals on the same disks as the data, doubling the OSD count, and upgrading
-Ceph to a development version which reduces the seek overhead caused by
-\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
-
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
-
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
-
-\subsection{Disable Cache Mirroring on controllers}
-
-During a second round of test performed by Inktank, we noticed a dramatic drop
-on RADOS performance: even though write throughput on individual server met the
-expectation, it did not scale across servers.
-
-We spent a significant amount of time
-investigating this phenomenon. Ultimately, we were able to replicate this finding
-when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The second RAID processor on each DDN controller would max out when
-three or more LUNs were written concurrently. It turns out the root of the problem
-was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.\footnote{DDN recently released a new
-firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
-a chance to verify it during our test cycle.}
-
-%% SCOTT - is running with cache mirroring off and option for a production system or not?
-%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
-%% with it or not?
-
-%% FEIYI: add footnote to clarify the issue.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-after-ddn}
-\caption{Evaluating RADOS bench after disabling cache mirroring}
-\label{fig:rados-ddn-mirror-disabled}
-\end{figure}
-
-With cache mirroring disabled, write performance when using all four servers
-improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
-5.5 GB/s from the clients.  When accounting for journal writes, that is over
-11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
-Unfortunately, read performance did not scale as well.
-
-\subsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux Kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
-TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
-
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
-\subsection{Repeating RADOS Scaling Test}
-
-We now repeated the previous RADOS scaling tests with these improvements in place.
-The first test was done on a single node with RADOS Bench to see how close the
-underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
-XFS-formatted storage.
-
-%% SCOTT - the title in the figure needs to change IO to I/O
-
-%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
-%% on the single server?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
-\label{fig:rados-064-osd}
-\end{figure}
-
-In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
-
-We also repeated tests looking at RADOS Bench performance as the number of OSD
-server nodes increases from one to four. The results are summarized in
-Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
-scales nearly linearly for both reads and writes.
-
-%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
-%% Do they no measure the same thing (i.e. a single server)? If not, the text
-%% needs to make it more clear.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
-nodes}
-\label{fig:rados-064-oss}
-\end{figure}
-
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
-
-The initial stability issues we encountered are fixed by moving from Ceph
-version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test
-could complete even during long runs. This is another sign of how much Ceph
-development is in flux.
-
-Another fix comes in the way we create the pool: the default data pool being used
-by previous CephFS cluster are set to 2x replication, which can potentially
-halve the write performance. Even with these changes in place, Inktank still
-reproduced the less-than-ideal write performance and very poor read
-performance as observed by ORNL.  Further, by increasing the number of IOR
-processes per client node, read performance actually degraded further
-indicating some kind of contention either on the clients or on the OSD
-servers.
-
-\subsection{Disabling Client CRC32}
-
-ORNL at this point was able to both make more client nodes available and also
-install a profiling tool called \verb!perf! that is extremely useful for
-profiling both kernel and user space code.  Profiling with \verb!perf! showed
-high CPU utilization on the client due to crc32c processing in the Ceph kernel
-client.  Luckily, crc32 checksums can be disabled by changing the CephFS mount
-options:
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
-
-With client CRC32 disabled, we repeated the IOR test and the results are showin
-in Figure~\ref{fig:ior-no-client-crc32}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with disabling client-side CRC32}
-\label{fig:ior-no-client-crc32}
-\end{figure}
-
-We observed that IOR write throughput increased dramatically and is now very
-close to the throughput we were able to achieve with RADOS Bench, but reads
-continued to be slow and continued to scale inversely with the number of client
-processes.  Please note that since these tests were performed, Inktank has
-implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based CRC32
-processing should have already been using SSE4 instructions on Intel CPUs, this
-will allow any user-land Ceph processes to process CRC32 checksums with
-significantly less overhead.
-
-\subsection{Improving IOR Read Performance}
-
-Deeper analysis with perf showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which happens to be the kernel
-that ORNL had installed on the test systems.\footnote{For more information,
-please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
-
-ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
-RADOS Bench test to verify that there was no degradation versus previous tests.  The
-results were extremely positive.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Kernel 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
-
-With the kernel changes writes performance improved slightly, while read
-performance improved dramatically.  In addition to the kernel change, Sage Weil
-suggested increasing the amount of read-ahead being performed by the CephFS
-kernel client:
-
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
-%% mention that 15 shows the filesystem performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with Kernel changes to 3.9, IOR with 4 MB transfer
-size}
-\label{fig:ior-kernel-39}
-\end{figure}
-
-By installing a new kernel, increasing read-ahead, and increasing the number of
-client IOR processes, we were able to achieve a very satisfactory result on this
-test run.
-
-\subsection{Repeating IOR Scaling Test}
-
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
-seeing a much improved picture of read and write performance, very much in
-line with RADOS bench performance.
-
-%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
-%% as to why 4 KB performance is better than 4 MB performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
-\label{fig:ior-064}
-\end{figure}
-
-We observe a couple of places where the average write throughput is quite a
-bit lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving as the number of clients increases.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
-saw with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
-\end{figure}
-
-In our particular setup, we have only one metadata server (MDS)
-configured. Therefore, this is not a scalability test on the performance of
-clustered MDS, which would be very interesting.
-Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
-scales. The particular parameters we use for testing are:
-
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform sync after it. This is a more realistic use case scenario than just
-open, close and removal.
-
-\item \verb!-n 1000!: this is per client file \textit{and} directories. For eight
-clients, the number of files and directories is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, so this is a mixture of both.
-
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
-
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
-
-\end{itemize}
-
-Each test iterates five times and we are showing the max. 
-We summarize the results as follows:
-
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
-
-\begin{itemize}
-
-\item Within a single sharing mode (either shared or unique directory), the
-directory stat and file stat, as well as file read exhibit strong linear
-scaling property.
-
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
-
-\item Though the same saturation or degradation trend is not observed for file
-creation, it is likely due to we have not put enough of workload stress on MDS.
-
-\end{itemize}
-
-The results also show that file creation rate is signficantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results from early version of Ceph without all
-the tunings and improvement applied. Therefore, we repeated the same test on the
-latest CephFS 0.64. The result is illustrated in
-Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
-improvement on the file creation rate. We also note that as number of clients
-increase, the file creation rate decreases rapidly, which suggested some form of
-lock contention. This presents some interesting issues to be investigated
-further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
-\section{Observations and Conclusions}
-
-This is preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
-  are unreliable, with little or no redundancy and failure detection capability.
-  This is not the case in leadership computing facilities. We have disabled
-  replication for pools, but this will take a toll somewhere in the processing
-  and we do not know if this is significant.
-
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
-  system that has locally attached disk. However, this presents a problem in DDN
-  SFA10-like hardware, where the backend LUNs are exposed as block device
-  through SCSI Request Protocol (SRP) over IB. The journaling write requires twice the bandwidth
-  compare to Lustre-like metadata-only journaling mechanism. For Ceph to be
-  viable in this facility, we will need to address this.
-
-  \item We observed consistent results and linear scalability at the
-  RADOS level. However, we did not observe the same at the file system level with synthetic
-  benchmark suites such as IOR. We have experienced large performance swings
-  during different runs, very low read performance when transfer size is small,
-  and I/O errors tend to happen when system is under stress (more clients and
-  large transfer sizes). These are not particularly reproducible results, but it
-  suggests that there are opporunities for code improvement and maturation.
-
-\end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}

### 2013-08-21 ceph-meta.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-21 report.tex
@@
-\documentclass{article}
-
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
-\section{Introduction}
-
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, prepared this performance and scalability study of
-Ceph file system. Ceph originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it was designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commercial support.
-
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration of failure domains and
-  hierarchical storage tiers.
-
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers. It utilized a dynamic subtree partitioning
-  strategy to continuously adapt metadata distribution to current demands.
-
-\item Ceph's design assumes that the system is composed of unreliable
-components; fault-detection and fault-tolerance (e.g., replication) are the
-norm rather than the exception. This is in line with the expectations and
-future directions of Exascale computing.
-
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
-
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
-
-\end{itemize}
-
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the
-feasibility of using the Ceph for our future HPC storage deployment.  This
-report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph is still a relatively
-\textit{young} parallel file system and its code base is changing rapidly. In
-between releases, we often experienced different stability and performance
-outcomes.  We will try to make clear in the report when such changes occurred.
-
-\section{Testbed Environment Description}
-
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
+\section{Metadata Performance}
 
@@
 \centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K hardware and host connection diagram}
-\label{fig:ddn-sfa10k}
-\end{figure}
-
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
-
-\begin{table}[H]
-\centering
-    \begin{tabular}{ll}
-    \toprule
-    Node & Role \\
-    \midrule
-    tick-mds1 & Ceph monitor node \\
-    spoon46 & Ceph MDS node \\
-    tick-oss[1-4] & Ceph OSD servers \\
-    spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
-    \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
-\end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 initially, and later upgraded to 3.9 (rhl-ceph image), Glibc
-2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
-release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
-round of tests.
-
-%For a complete a list of hosts that are running ceph images, one can execute:
-
-%\begin{Verbatim}
-%$ grep "rhel6-ceph" /etc/gedi/MAC.info
-%\end{Verbatim}
-
-\section{Baseline Performance}
-\label{sec:block-io}
-
-\subsection{Block I/O over Native IB}
-
-We first established baseline performance by measuring block I/O performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with four SAS LUNs & ~ 2.8 GB/s \\
-    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
-\end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
-\end{table}
-
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
-
-\subsection{IP over IB}
-
-Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
-
-Unfortunately there was not enough time to do more detailed analysis of the
-network performance. However, as we observed later, RADOS is performing no
-more than 8 GB/s driven by four server hosts. This confirms that we have
-provisioned enough network bandwidth. In other words, IP over IB is not a
-bottleneck in this case.
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
-\section{XFS Performance As Backend File System}
-
-Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
-should be noted that in testing cases while we can compare XFS vs.
-Brtfs, Brtfs generally shows better performance results.} We experimented with
-XFS to acquire a set of configuration parameters which provided optimal
-performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the
-following configuration: mount with \verb!nobarrier,noatim,inode64! options.
-The \verb!inode64! option had a notable improvement on sequential write (around
-20\%).
-
-%% Can the graphs be adjusted to have the same values in the Y axis?
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\centering
-\includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read performance scaling on number of devices}
-\label{fig:xfs-read}
+\includegraphics[width=3in]{data/mdtest-fcreate}
+\caption{File creation vs.  number of clients}
+\label{fig:mdtest-fcreate}
 \end{figure}
@@
 \centering
-\includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write performance scaling on number of devices}
-\label{fig:xfs-write}
-\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%% -- 1st figure
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-read}
-%\caption{XFS read performance scaling on number of devices}
-%\label{fig:xfs-read}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-write}
-%\caption{XFS write performance scaling on number of devices}
-%\label{fig:xfs-write}
-%\end{minipage}%
-%\end{figure}
-
-% % Are the read and write graphs wrong or should the second sentence below be
-% about write % instead of read?
-
-The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These graphs
-show scaling behavior over the number of LUNs, which indicates that XFS can
-reach the peak write performance with just five SATA LUNs. Increasing number
-of LUNs beyond 5, degradation happened.  Also, we did not observe any obvious
-differences in performance when varying the queue depth parameter.  For these
-tests, we used the \verb!xdd! benchmark with direct I/O and a request size of
-32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is a reliable distributed object store, the foundational component for
-CephFS file system. There are two types of scaling tests we are interested at
-the RADOS layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
-
-We used the open-source RADOS Bench tool, developed by Inktank, to perform our
-initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
-writes out objects to the underlying object storage as fast as possible, and
-then later reads those objects in the same order as they were written.
-
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
-
-\subsection{Scaling on number of OSDs per server}
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
-nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
-have not reached the saturation point yet. Additional testing would require
-provisioning more OSDs on the SFA10K backend.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
-\label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
-\label{fig:oss-scale}
-\end{minipage}%
-\end{figure}
-
-\subsection{Scaling on number of OSD servers}
-
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
-
-\section{Ceph File System Performance: Initial Test}
-\label{sec:ior-initial}
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
-
-\begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
-\caption{IOR parameter setup}
-\label{tbl:ior}
-\end{table}
-
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
-
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
-
-%% FEIYI: 6, 7 all fixed.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
-
-\begin{itemize}
-
-  \item The small read (4 KB transfer size) performance is almost an anomaly
-  -- we will investigate why it is so low compare to write performance and
-  present improved results in Section~\ref{sec:improve-ior}.
-
-  \item The large read (4 MB transfer size) performance is almost half of the
-  RADOS read performance.
-
-  \item The write performance is also about half of what we can obtain from
-  RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well.
-
-\end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
-
-We will describe the efforts and results on performance improvement in the
-following sections.
-
-\section{Improving RADOS Performance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=5in]{parametric}
-\caption{Evaluating parameter impact through sweeping test}
-\label{fig:parametric}
-\end{figure}
-
-After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
-journals on the same disks as the data, doubling the OSD count, and upgrading
-Ceph to a development version which reduces the seek overhead caused by
-\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
-
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
-
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
-
-\subsection{Disable Cache Mirroring on Controllers}
-
-During a second round of test performed by Inktank, we noticed a dramatic drop
-on RADOS performance: even though write throughput on individual server met the
-expectation, it did not scale across servers.
-
-We spent a significant amount of time
-investigating this phenomenon. Ultimately, we were able to replicate this finding
-when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The second RAID processor on each DDN controller would max out when
-three or more LUNs were written concurrently. It turns out the root of the problem
-was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.\footnote{DDN recently released a new
-firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
-a chance to verify it during our test cycle.}
-
-%% SCOTT - is running with cache mirroring off and option for a production system or not?
-%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
-%% with it or not?
-
-%% FEIYI: add footnote to clarify the issue.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-after-ddn}
-\caption{Evaluating RADOS bench after disabling cache mirroring}
-\label{fig:rados-ddn-mirror-disabled}
-\end{figure}
-
-With cache mirroring disabled, write performance when using all four servers
-improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
-5.5 GB/s from the clients.  When accounting for journal writes, that is over
-11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
-Unfortunately, read performance did not scale as well.
-
-\subsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux
-kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}} TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
-
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
-\subsection{Repeating RADOS Scaling Test}
-
-We now repeated the previous RADOS scaling tests with these improvements in place.
-The first test was done on a single node with RADOS Bench to see how close the
-underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
-XFS-formatted storage.
-
-%% SCOTT - the title in the figure needs to change IO to I/O
-
-%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
-%% on the single server?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
-\label{fig:rados-064-osd}
-\end{figure}
-
-In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
-
-We also repeated tests looking at RADOS Bench performance as the number of OSD
-server nodes increases from one to four. The results are summarized in
-Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
-scales nearly linearly for both reads and writes.
-
-%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
-%% Do they no measure the same thing (i.e. a single server)? If not, the text
-%% needs to make it more clear.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
-nodes}
-\label{fig:rados-064-oss}
-\end{figure}
-
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
-
-The initial stability issues mentioned in Section~\ref{sec:ior-initial} are
-fixed by migrating from Ceph version 0.48/0.55 to 0.64, the latest stable version at the
-time of writing this report.  Upgrading to the latest stable Ceph release
-allowed us to run a full IOR parameter sweep for the first time since we
-started evaluating the performance and scalability of the Ceph file system.
-This is another sign of how much Ceph development is currently in flux.
-
-Another fix introduced by Ceph version 0.64 was in pool creation.  The default
-data pool used by previous Ceph version were set to 2x replication by mistake.
-This potentially halved the write performance. With version 0.64 we explicitly
-set the replication level to 1, which is the preferred value for a HPC
-environment like ours running on high-end and reliable storage backend hardware
-(e.g. DDN SFA10K).
-
-Even with these two changes in place, less-than-ideal write performance and
-very poor read performances were observed during our tests.  We also observed
-that by increasing the number of IOR processes per client node, the read
-performance degraded even further indicating some kind of contention either on
-the clients or on the OSD servers.
-
-\subsection{Disabling Client CRC32}
-
-At this point, we were able to both make more client nodes available for Ceph
-file system-level testing and also install a profiling tool called \verb!perf!
-that is extremely useful for profiling both kernel and user space codes.
-Profiling with \verb!perf! showed high CPU utilization on test clients due to
-crc32c processing in the Ceph kernel client.  crc32 checksums can be disabled
-by changing the CephFS mount options:
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
-
-With client CRC32 disabled, we repeated the IOR tests. New results are shown in
-in Figure~\ref{fig:ior-no-client-crc32}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with disabling client-side CRC32}
-\label{fig:ior-no-client-crc32}
-\end{figure}
-
-We observed that IOR write throughput increased dramatically and is now very
-close and comparable to the RADOS Bench performance. Read performance continued
-to be poor and continued to scale inversely with the increasing number of
-client processes.  Please note that, since these tests were performed, Inktank
-has implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based
-CRC32 processing should have already been using SSE4 instructions on Intel
-CPUs, this update will allow any user-land Ceph processes to process CRC32
-checksums with significantly less overhead.
-
-\subsection{Improving IOR Read Performance}
-
-Deeper analysis with perf showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which was the kernel
-installed on our test systems.\footnote{For more information,
-please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
-
-We upgraded our test systems with kernel version 3.9 and performed RADOS Bench
-test.  The results were extremely positive and presented in
-Figure~\ref{fig:rados-kernel}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
-
-As can be seen, with the 3.9 kernel, while there was a slight improvement on
-write performance, read performance improved dramatically.  In addition to the
-kernel change, Sage Weil from InkTank suggested increasing the amount of CephFS
-client kernel read-ahead cache size as:
-
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
-%% mention that 15 shows the filesystem performance?
-
-IOR results reflecting the read-ahead cache size change are presented in
-Figure~\ref{fig:ior-kernel-39}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
-size}
-\label{fig:ior-kernel-39}
-\end{figure}
-
-By installing a newer kernel, increasing read-ahead cache size, and increasing the number of
-client IOR processes, we were able to achieve very satisfactory I/O performance.
-
-\subsection{Repeating the IOR Scaling Test}
-
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we saw
-saw  improved read and write performance. These new read and write performance are in
-line with observed RADOS bench performance.
-
-%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
-%% as to why 4 KB performance is better than 4 MB performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
-\label{fig:ior-064}
-\end{figure}
-
-Throughout our IOR testing, we observed that the average write throughput is 
-lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving with respect to increasing number of clients.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to ~8 GB/s  we
-obervered with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
 \includegraphics[width=3in]{data/mdtest-dcreate}
@@
 \label{fig:mdtest-dcreate}
-\end{minipage}%
 \end{figure}
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=3.5in]{mdtest-064-file-create}
+\caption{mdtest of file creation on Ceph 0.64}
+\label{fig:mdtest-064-file-create}
+\end{figure}
+
 The results also show that file creation rate is signficantly lower than
@@
 further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
-\section{Observations and Conclusions}
-
-Below are our preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
-are unreliable, with little or no redundancy and failure detection capability.
-This assumption is not valid for high-end HPC centers like ours. We have
-disabled replication for pools, we haven't measured and quantified
-processing overhead and we do not know yet if this would be significant.
-
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
-host systems that has locally attached disk. However, this presents a problem
-in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
-devices through SCSI Request Protocol (SRP) over IB. The journaling write
-requires twice the bandwidth compare to Lustre-like metadata-only journaling
-mechanism. For Ceph to be viable in this facility, journaling operations will
-need to further design and engineering.
-
-  \item We observed consistent results and linear scalability at the RADOS
-level. However, we did not observe the same at the file system level. We have
-experienced large performance swings during different runs, very low read
-performance when transfer size is small, and I/O errors tend to happen when
-system is under stress (more clients and large transfer sizes). These are not
-particularly reproducible results, but it suggests that there are opportunities
-for code improvement and maturation.
-
-\end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}

### 2013-08-21 ceph-tuning.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-21 report.tex
@@
-\documentclass{article}
-
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
-\section{Introduction}
-
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, prepared this performance and scalability study of
-Ceph file system. Ceph originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it was designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commercial support.
-
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration of failure domains and
-  hierarchical storage tiers.
-
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers. It utilized a dynamic subtree partitioning
-  strategy to continuously adapt metadata distribution to current demands.
-
-\item Ceph's design assumes that the system is composed of unreliable
-components; fault-detection and fault-tolerance (e.g., replication) are the
-norm rather than the exception. This is in line with the expectations and
-future directions of Exascale computing.
-
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
-
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
-
-\end{itemize}
-
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the
-feasibility of using the Ceph for our future HPC storage deployment.  This
-report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph is still a relatively
-\textit{young} parallel file system and its code base is changing rapidly. In
-between releases, we often experienced different stability and performance
-outcomes.  We will try to make clear in the report when such changes occurred.
-
-\section{Testbed Environment Description}
-
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K hardware and host connection diagram}
-\label{fig:ddn-sfa10k}
-\end{figure}
-
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
-
-\begin{table}[H]
-\centering
-    \begin{tabular}{ll}
-    \toprule
-    Node & Role \\
-    \midrule
-    tick-mds1 & Ceph monitor node \\
-    spoon46 & Ceph MDS node \\
-    tick-oss[1-4] & Ceph OSD servers \\
-    spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
-    \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
-\end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 initially, and later upgraded to 3.9 (rhl-ceph image), Glibc
-2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
-release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
-round of tests.
-
-%For a complete a list of hosts that are running ceph images, one can execute:
-
-%\begin{Verbatim}
-%$ grep "rhel6-ceph" /etc/gedi/MAC.info
-%\end{Verbatim}
-
-\section{Baseline Performance}
-\label{sec:block-io}
-
-\subsection{Block I/O over Native IB}
-
-We first established baseline performance by measuring block I/O performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with four SAS LUNs & ~ 2.8 GB/s \\
-    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
-\end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
-\end{table}
-
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
-
-\subsection{IP over IB}
-
-Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
-
-Unfortunately there was not enough time to do more detailed analysis of the
-network performance. However, as we observed later, RADOS is performing no
-more than 8 GB/s driven by four server hosts. This confirms that we have
-provisioned enough network bandwidth. In other words, IP over IB is not a
-bottleneck in this case.
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
-\section{XFS Performance As Backend File System}
-
-Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
-should be noted that in testing cases while we can compare XFS vs.
-Brtfs, Brtfs generally shows better performance results.} We experimented with
-XFS to acquire a set of configuration parameters which provided optimal
-performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the
-following configuration: mount with \verb!nobarrier,noatim,inode64! options.
-The \verb!inode64! option had a notable improvement on sequential write (around
-20\%).
-
-%% Can the graphs be adjusted to have the same values in the Y axis?
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\centering
-\includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read performance scaling on number of devices}
-\label{fig:xfs-read}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write performance scaling on number of devices}
-\label{fig:xfs-write}
-\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%% -- 1st figure
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-read}
-%\caption{XFS read performance scaling on number of devices}
-%\label{fig:xfs-read}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-write}
-%\caption{XFS write performance scaling on number of devices}
-%\label{fig:xfs-write}
-%\end{minipage}%
-%\end{figure}
-
-% % Are the read and write graphs wrong or should the second sentence below be
-% about write % instead of read?
-
-The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These graphs
-show scaling behavior over the number of LUNs, which indicates that XFS can
-reach the peak write performance with just five SATA LUNs. Increasing number
-of LUNs beyond 5, degradation happened.  Also, we did not observe any obvious
-differences in performance when varying the queue depth parameter.  For these
-tests, we used the \verb!xdd! benchmark with direct I/O and a request size of
-32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is a reliable distributed object store, the foundational component for
-CephFS file system. There are two types of scaling tests we are interested at
-the RADOS layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
-
-We used the open-source RADOS Bench tool, developed by Inktank, to perform our
-initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
-writes out objects to the underlying object storage as fast as possible, and
-then later reads those objects in the same order as they were written.
-
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
-
-\subsection{Scaling on number of OSDs per server}
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
-nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
-have not reached the saturation point yet. Additional testing would require
-provisioning more OSDs on the SFA10K backend.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
-\label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
-\label{fig:oss-scale}
-\end{minipage}%
-\end{figure}
-
-\subsection{Scaling on number of OSD servers}
-
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
-
-\section{Ceph File System Performance: Initial Test}
-\label{sec:ior-initial}
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
-
-\begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
-\caption{IOR parameter setup}
-\label{tbl:ior}
-\end{table}
-
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
-
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
-
-%% FEIYI: 6, 7 all fixed.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
-
-\begin{itemize}
-
-  \item The small read (4 KB transfer size) performance is almost an anomaly
-  -- we will investigate why it is so low compare to write performance and
-  present improved results in Section~\ref{sec:improve-ior}.
-
-  \item The large read (4 MB transfer size) performance is almost half of the
-  RADOS read performance.
-
-  \item The write performance is also about half of what we can obtain from
-  RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well.
-
-\end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
-
-We will describe the efforts and results on performance improvement in the
-following sections.
-
 \section{Improving RADOS Performance}
@@
 \centering
-\includegraphics[width=5in]{parametric}
+\includegraphics[width=3.5in]{parametric}
 \caption{Evaluating parameter impact through sweeping test}
@@
 \centering
-\includegraphics[width=4in]{rados-after-ddn}
+\includegraphics[width=3.5in]{rados-after-ddn}
 \caption{Evaluating RADOS bench after disabling cache mirroring}
@@
 
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux
-kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}} TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
+During these tests, a trend that previously had been seen became more
+apparent.  During reads, there were periods of high performance followed by
+periods of low performance or outright stalls that could last for up to 20
+seconds at a time.  After several hours of diagnostics, Inktank observed that
+outstanding operations on the clients were not being shown as outstanding on
+the OSDs.  This appeared to be very similar to a problem Jim Schutt at Sandia
+National labs encountered with TCP autotuning in the Linux
+kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
+TCP auto tuning enables TCP window scaling by default and automatically
+adjusts the TCP receive window for each connection based on link conditions
+such as bandwidth delay product. We have observed this will make a notable
+improvement on Ceph read performance, as the results shown in
 Figure~\ref{fig:rados-tcp-auto-disabled}.
@@
 \centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
+\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
 \caption{Evaluating RADOS bench after TCP auto tuning disabled}
@@
 \centering
-\includegraphics[width=5in]{rados-064-osd}
+\includegraphics[width=3.5in]{rados-064-osd}
 \caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
@@
 \centering
-\includegraphics[width=5in]{rados-064-oss}
+\includegraphics[width=3.5in]{rados-064-oss}
 \caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
@@
 \centering
-\includegraphics[width=4in]{ior-client-no-crc32}
+\includegraphics[width=3.5in]{ior-client-no-crc32}
 \caption{IOR test with disabling client-side CRC32}
@@
 \centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
+\includegraphics[width=3.5in]{rados-kernel-35vs39}
 \caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
@@
 \centering
-\includegraphics[width=4in]{ior-kernel-39}
+\includegraphics[width=3.5in]{ior-kernel-39}
 \caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
@@
 \centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
+\includegraphics[width=3.5in]{ior-064-4k}
+\includegraphics[width=3.5in]{ior-064-4m}
 \caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
@@
 obervered with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
-\end{figure}
-
-In our particular setup, we only had one metadata server (MDS) configured.
-Therefore, this is not a scalability test on the performance of Ceph clustered
-MDS, which would have been very interesting.  Instead, we focus on a single MDS
-performance and exercise it with up to 8 clients to observe the single MDS
-performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
-used for this test are:
-
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform a sync operation.  This is a more realistic use case scenario than just
-open, close and removal sequence of metadata operations.
-
-\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
-clients, the total number of files and directories in the workload is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, this is a mixture of both.
-
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
-
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
-
-\end{itemize}
-
-Each test iterates five times and we are presenting the maximum out of all five iterations. 
-We summarize the results as follows:
-
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
-
-\begin{itemize}
-
-\item With either shared or unique directory (\verb!-u!), stat
-operations for directories and files exhibit strong linear scaling. Same strong
-linear scaling is also observed for file read operations.
-
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
-
-\item Though the same saturation (or degradation) trend was not observed for
-file creation operation, it is likely due to lack of workload stress on MDS.
-
-\end{itemize}
-
-The results also show that file creation rate is signficantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results from early version of Ceph without all
-the tunings and improvement applied. Therefore, we repeated the same test on the
-latest CephFS 0.64. The result is illustrated in
-Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
-improvement on the file creation rate. We also note that as number of clients
-increase, the file creation rate decreases rapidly, which suggested some form of
-lock contention. This presents some interesting issues to be investigated
-further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
-\section{Observations and Conclusions}
-
-Below are our preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
-are unreliable, with little or no redundancy and failure detection capability.
-This assumption is not valid for high-end HPC centers like ours. We have
-disabled replication for pools, we haven't measured and quantified
-processing overhead and we do not know yet if this would be significant.
-
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
-host systems that has locally attached disk. However, this presents a problem
-in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
-devices through SCSI Request Protocol (SRP) over IB. The journaling write
-requires twice the bandwidth compare to Lustre-like metadata-only journaling
-mechanism. For Ceph to be viable in this facility, journaling operations will
-need to further design and engineering.
-
-  \item We observed consistent results and linear scalability at the RADOS
-level. However, we did not observe the same at the file system level. We have
-experienced large performance swings during different runs, very low read
-performance when transfer size is small, and I/O errors tend to happen when
-system is under stress (more clients and large transfer sizes). These are not
-particularly reproducible results, but it suggests that there are opportunities
-for code improvement and maturation.
-
-\end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}

### 2013-08-21 conclusion.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-21 report.tex
@@
-\documentclass{article}
-
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
-\section{Introduction}
-
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, prepared this performance and scalability study of
-Ceph file system. Ceph originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it was designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commercial support.
-
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration of failure domains and
-  hierarchical storage tiers.
-
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers. It utilized a dynamic subtree partitioning
-  strategy to continuously adapt metadata distribution to current demands.
-
-\item Ceph's design assumes that the system is composed of unreliable
-components; fault-detection and fault-tolerance (e.g., replication) are the
-norm rather than the exception. This is in line with the expectations and
-future directions of Exascale computing.
-
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
-
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
-
-\end{itemize}
-
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the
-feasibility of using the Ceph for our future HPC storage deployment.  This
-report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph is still a relatively
-\textit{young} parallel file system and its code base is changing rapidly. In
-between releases, we often experienced different stability and performance
-outcomes.  We will try to make clear in the report when such changes occurred.
-
-\section{Testbed Environment Description}
-
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K hardware and host connection diagram}
-\label{fig:ddn-sfa10k}
-\end{figure}
-
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
-
-\begin{table}[H]
-\centering
-    \begin{tabular}{ll}
-    \toprule
-    Node & Role \\
-    \midrule
-    tick-mds1 & Ceph monitor node \\
-    spoon46 & Ceph MDS node \\
-    tick-oss[1-4] & Ceph OSD servers \\
-    spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
-    \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
-\end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 initially, and later upgraded to 3.9 (rhl-ceph image), Glibc
-2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
-release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
-round of tests.
-
-%For a complete a list of hosts that are running ceph images, one can execute:
-
-%\begin{Verbatim}
-%$ grep "rhel6-ceph" /etc/gedi/MAC.info
-%\end{Verbatim}
-
-\section{Baseline Performance}
-\label{sec:block-io}
-
-\subsection{Block I/O over Native IB}
-
-We first established baseline performance by measuring block I/O performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with four SAS LUNs & ~ 2.8 GB/s \\
-    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
-\end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
-\end{table}
-
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
-
-\subsection{IP over IB}
-
-Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
-
-Unfortunately there was not enough time to do more detailed analysis of the
-network performance. However, as we observed later, RADOS is performing no
-more than 8 GB/s driven by four server hosts. This confirms that we have
-provisioned enough network bandwidth. In other words, IP over IB is not a
-bottleneck in this case.
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
-\section{XFS Performance As Backend File System}
-
-Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
-should be noted that in testing cases while we can compare XFS vs.
-Brtfs, Brtfs generally shows better performance results.} We experimented with
-XFS to acquire a set of configuration parameters which provided optimal
-performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the
-following configuration: mount with \verb!nobarrier,noatim,inode64! options.
-The \verb!inode64! option had a notable improvement on sequential write (around
-20\%).
-
-%% Can the graphs be adjusted to have the same values in the Y axis?
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\centering
-\includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read performance scaling on number of devices}
-\label{fig:xfs-read}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write performance scaling on number of devices}
-\label{fig:xfs-write}
-\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%% -- 1st figure
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-read}
-%\caption{XFS read performance scaling on number of devices}
-%\label{fig:xfs-read}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-write}
-%\caption{XFS write performance scaling on number of devices}
-%\label{fig:xfs-write}
-%\end{minipage}%
-%\end{figure}
-
-% % Are the read and write graphs wrong or should the second sentence below be
-% about write % instead of read?
-
-The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These graphs
-show scaling behavior over the number of LUNs, which indicates that XFS can
-reach the peak write performance with just five SATA LUNs. Increasing number
-of LUNs beyond 5, degradation happened.  Also, we did not observe any obvious
-differences in performance when varying the queue depth parameter.  For these
-tests, we used the \verb!xdd! benchmark with direct I/O and a request size of
-32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is a reliable distributed object store, the foundational component for
-CephFS file system. There are two types of scaling tests we are interested at
-the RADOS layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
-
-We used the open-source RADOS Bench tool, developed by Inktank, to perform our
-initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
-writes out objects to the underlying object storage as fast as possible, and
-then later reads those objects in the same order as they were written.
-
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
-
-\subsection{Scaling on number of OSDs per server}
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
-nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
-have not reached the saturation point yet. Additional testing would require
-provisioning more OSDs on the SFA10K backend.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
-\label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
-\label{fig:oss-scale}
-\end{minipage}%
-\end{figure}
-
-\subsection{Scaling on number of OSD servers}
-
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
-
-\section{Ceph File System Performance: Initial Test}
-\label{sec:ior-initial}
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
-
-\begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
-\caption{IOR parameter setup}
-\label{tbl:ior}
-\end{table}
-
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
-
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
-
-%% FEIYI: 6, 7 all fixed.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
-
-\begin{itemize}
-
-  \item The small read (4 KB transfer size) performance is almost an anomaly
-  -- we will investigate why it is so low compare to write performance and
-  present improved results in Section~\ref{sec:improve-ior}.
-
-  \item The large read (4 MB transfer size) performance is almost half of the
-  RADOS read performance.
-
-  \item The write performance is also about half of what we can obtain from
-  RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well.
-
-\end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
-
-We will describe the efforts and results on performance improvement in the
-following sections.
-
-\section{Improving RADOS Performance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=5in]{parametric}
-\caption{Evaluating parameter impact through sweeping test}
-\label{fig:parametric}
-\end{figure}
-
-After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
-journals on the same disks as the data, doubling the OSD count, and upgrading
-Ceph to a development version which reduces the seek overhead caused by
-\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
-
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
-
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
-
-\subsection{Disable Cache Mirroring on Controllers}
-
-During a second round of test performed by Inktank, we noticed a dramatic drop
-on RADOS performance: even though write throughput on individual server met the
-expectation, it did not scale across servers.
-
-We spent a significant amount of time
-investigating this phenomenon. Ultimately, we were able to replicate this finding
-when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The second RAID processor on each DDN controller would max out when
-three or more LUNs were written concurrently. It turns out the root of the problem
-was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.\footnote{DDN recently released a new
-firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
-a chance to verify it during our test cycle.}
-
-%% SCOTT - is running with cache mirroring off and option for a production system or not?
-%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
-%% with it or not?
-
-%% FEIYI: add footnote to clarify the issue.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-after-ddn}
-\caption{Evaluating RADOS bench after disabling cache mirroring}
-\label{fig:rados-ddn-mirror-disabled}
-\end{figure}
-
-With cache mirroring disabled, write performance when using all four servers
-improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
-5.5 GB/s from the clients.  When accounting for journal writes, that is over
-11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
-Unfortunately, read performance did not scale as well.
-
-\subsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux
-kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}} TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
-
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
-\subsection{Repeating RADOS Scaling Test}
-
-We now repeated the previous RADOS scaling tests with these improvements in place.
-The first test was done on a single node with RADOS Bench to see how close the
-underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
-XFS-formatted storage.
-
-%% SCOTT - the title in the figure needs to change IO to I/O
-
-%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
-%% on the single server?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
-\label{fig:rados-064-osd}
-\end{figure}
-
-In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
-
-We also repeated tests looking at RADOS Bench performance as the number of OSD
-server nodes increases from one to four. The results are summarized in
-Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
-scales nearly linearly for both reads and writes.
-
-%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
-%% Do they no measure the same thing (i.e. a single server)? If not, the text
-%% needs to make it more clear.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
-nodes}
-\label{fig:rados-064-oss}
-\end{figure}
-
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
-
-The initial stability issues mentioned in Section~\ref{sec:ior-initial} are
-fixed by migrating from Ceph version 0.48/0.55 to 0.64, the latest stable version at the
-time of writing this report.  Upgrading to the latest stable Ceph release
-allowed us to run a full IOR parameter sweep for the first time since we
-started evaluating the performance and scalability of the Ceph file system.
-This is another sign of how much Ceph development is currently in flux.
-
-Another fix introduced by Ceph version 0.64 was in pool creation.  The default
-data pool used by previous Ceph version were set to 2x replication by mistake.
-This potentially halved the write performance. With version 0.64 we explicitly
-set the replication level to 1, which is the preferred value for a HPC
-environment like ours running on high-end and reliable storage backend hardware
-(e.g. DDN SFA10K).
-
-Even with these two changes in place, less-than-ideal write performance and
-very poor read performances were observed during our tests.  We also observed
-that by increasing the number of IOR processes per client node, the read
-performance degraded even further indicating some kind of contention either on
-the clients or on the OSD servers.
-
-\subsection{Disabling Client CRC32}
-
-At this point, we were able to both make more client nodes available for Ceph
-file system-level testing and also install a profiling tool called \verb!perf!
-that is extremely useful for profiling both kernel and user space codes.
-Profiling with \verb!perf! showed high CPU utilization on test clients due to
-crc32c processing in the Ceph kernel client.  crc32 checksums can be disabled
-by changing the CephFS mount options:
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
-
-With client CRC32 disabled, we repeated the IOR tests. New results are shown in
-in Figure~\ref{fig:ior-no-client-crc32}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with disabling client-side CRC32}
-\label{fig:ior-no-client-crc32}
-\end{figure}
-
-We observed that IOR write throughput increased dramatically and is now very
-close and comparable to the RADOS Bench performance. Read performance continued
-to be poor and continued to scale inversely with the increasing number of
-client processes.  Please note that, since these tests were performed, Inktank
-has implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based
-CRC32 processing should have already been using SSE4 instructions on Intel
-CPUs, this update will allow any user-land Ceph processes to process CRC32
-checksums with significantly less overhead.
-
-\subsection{Improving IOR Read Performance}
-
-Deeper analysis with perf showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which was the kernel
-installed on our test systems.\footnote{For more information,
-please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
-
-We upgraded our test systems with kernel version 3.9 and performed RADOS Bench
-test.  The results were extremely positive and presented in
-Figure~\ref{fig:rados-kernel}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
-
-As can be seen, with the 3.9 kernel, while there was a slight improvement on
-write performance, read performance improved dramatically.  In addition to the
-kernel change, Sage Weil from InkTank suggested increasing the amount of CephFS
-client kernel read-ahead cache size as:
-
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
-%% mention that 15 shows the filesystem performance?
-
-IOR results reflecting the read-ahead cache size change are presented in
-Figure~\ref{fig:ior-kernel-39}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
-size}
-\label{fig:ior-kernel-39}
-\end{figure}
-
-By installing a newer kernel, increasing read-ahead cache size, and increasing the number of
-client IOR processes, we were able to achieve very satisfactory I/O performance.
-
-\subsection{Repeating the IOR Scaling Test}
-
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we saw
-saw  improved read and write performance. These new read and write performance are in
-line with observed RADOS bench performance.
-
-%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
-%% as to why 4 KB performance is better than 4 MB performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
-\label{fig:ior-064}
-\end{figure}
-
-Throughout our IOR testing, we observed that the average write throughput is 
-lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving with respect to increasing number of clients.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to ~8 GB/s  we
-obervered with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
-\end{figure}
-
-In our particular setup, we only had one metadata server (MDS) configured.
-Therefore, this is not a scalability test on the performance of Ceph clustered
-MDS, which would have been very interesting.  Instead, we focus on a single MDS
-performance and exercise it with up to 8 clients to observe the single MDS
-performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
-used for this test are:
-
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform a sync operation.  This is a more realistic use case scenario than just
-open, close and removal sequence of metadata operations.
-
-\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
-clients, the total number of files and directories in the workload is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, this is a mixture of both.
-
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
-
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
-
-\end{itemize}
-
-Each test iterates five times and we are presenting the maximum out of all five iterations. 
-We summarize the results as follows:
-
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
-
-\begin{itemize}
-
-\item With either shared or unique directory (\verb!-u!), stat
-operations for directories and files exhibit strong linear scaling. Same strong
-linear scaling is also observed for file read operations.
-
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
-
-\item Though the same saturation (or degradation) trend was not observed for
-file creation operation, it is likely due to lack of workload stress on MDS.
-
-\end{itemize}
-
-The results also show that file creation rate is signficantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results from early version of Ceph without all
-the tunings and improvement applied. Therefore, we repeated the same test on the
-latest CephFS 0.64. The result is illustrated in
-Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
-improvement on the file creation rate. We also note that as number of clients
-increase, the file creation rate decreases rapidly, which suggested some form of
-lock contention. This presents some interesting issues to be investigated
-further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
 \section{Observations and Conclusions}
@@
 \end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}

### 2013-08-21 introduction.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-21 report.tex
@@
-\documentclass{article}
-
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
 \section{Introduction}
@@
 outcomes.  We will try to make clear in the report when such changes occurred.
-
-\section{Testbed Environment Description}
-
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K hardware and host connection diagram}
-\label{fig:ddn-sfa10k}
-\end{figure}
-
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
-
-\begin{table}[H]
-\centering
-    \begin{tabular}{ll}
-    \toprule
-    Node & Role \\
-    \midrule
-    tick-mds1 & Ceph monitor node \\
-    spoon46 & Ceph MDS node \\
-    tick-oss[1-4] & Ceph OSD servers \\
-    spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
-    \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
-\end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 initially, and later upgraded to 3.9 (rhl-ceph image), Glibc
-2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
-release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
-round of tests.
-
-%For a complete a list of hosts that are running ceph images, one can execute:
-
-%\begin{Verbatim}
-%$ grep "rhel6-ceph" /etc/gedi/MAC.info
-%\end{Verbatim}
-
-\section{Baseline Performance}
-\label{sec:block-io}
-
-\subsection{Block I/O over Native IB}
-
-We first established baseline performance by measuring block I/O performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with four SAS LUNs & ~ 2.8 GB/s \\
-    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
-\end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
-\end{table}
-
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
-
-\subsection{IP over IB}
-
-Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
-
-Unfortunately there was not enough time to do more detailed analysis of the
-network performance. However, as we observed later, RADOS is performing no
-more than 8 GB/s driven by four server hosts. This confirms that we have
-provisioned enough network bandwidth. In other words, IP over IB is not a
-bottleneck in this case.
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
-\section{XFS Performance As Backend File System}
-
-Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
-should be noted that in testing cases while we can compare XFS vs.
-Brtfs, Brtfs generally shows better performance results.} We experimented with
-XFS to acquire a set of configuration parameters which provided optimal
-performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the
-following configuration: mount with \verb!nobarrier,noatim,inode64! options.
-The \verb!inode64! option had a notable improvement on sequential write (around
-20\%).
-
-%% Can the graphs be adjusted to have the same values in the Y axis?
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\centering
-\includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read performance scaling on number of devices}
-\label{fig:xfs-read}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write performance scaling on number of devices}
-\label{fig:xfs-write}
-\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%% -- 1st figure
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-read}
-%\caption{XFS read performance scaling on number of devices}
-%\label{fig:xfs-read}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-write}
-%\caption{XFS write performance scaling on number of devices}
-%\label{fig:xfs-write}
-%\end{minipage}%
-%\end{figure}
-
-% % Are the read and write graphs wrong or should the second sentence below be
-% about write % instead of read?
-
-The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These graphs
-show scaling behavior over the number of LUNs, which indicates that XFS can
-reach the peak write performance with just five SATA LUNs. Increasing number
-of LUNs beyond 5, degradation happened.  Also, we did not observe any obvious
-differences in performance when varying the queue depth parameter.  For these
-tests, we used the \verb!xdd! benchmark with direct I/O and a request size of
-32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is a reliable distributed object store, the foundational component for
-CephFS file system. There are two types of scaling tests we are interested at
-the RADOS layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
-
-We used the open-source RADOS Bench tool, developed by Inktank, to perform our
-initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
-writes out objects to the underlying object storage as fast as possible, and
-then later reads those objects in the same order as they were written.
-
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
-
-\subsection{Scaling on number of OSDs per server}
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
-nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
-have not reached the saturation point yet. Additional testing would require
-provisioning more OSDs on the SFA10K backend.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
-\label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
-\label{fig:oss-scale}
-\end{minipage}%
-\end{figure}
-
-\subsection{Scaling on number of OSD servers}
-
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
-
-\section{Ceph File System Performance: Initial Test}
-\label{sec:ior-initial}
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
-
-\begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
-\caption{IOR parameter setup}
-\label{tbl:ior}
-\end{table}
-
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
-
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
-
-%% FEIYI: 6, 7 all fixed.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
-
-\begin{itemize}
-
-  \item The small read (4 KB transfer size) performance is almost an anomaly
-  -- we will investigate why it is so low compare to write performance and
-  present improved results in Section~\ref{sec:improve-ior}.
-
-  \item The large read (4 MB transfer size) performance is almost half of the
-  RADOS read performance.
-
-  \item The write performance is also about half of what we can obtain from
-  RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well.
-
-\end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
-
-We will describe the efforts and results on performance improvement in the
-following sections.
-
-\section{Improving RADOS Performance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=5in]{parametric}
-\caption{Evaluating parameter impact through sweeping test}
-\label{fig:parametric}
-\end{figure}
-
-After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
-journals on the same disks as the data, doubling the OSD count, and upgrading
-Ceph to a development version which reduces the seek overhead caused by
-\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
-
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
-
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
-
-\subsection{Disable Cache Mirroring on Controllers}
-
-During a second round of test performed by Inktank, we noticed a dramatic drop
-on RADOS performance: even though write throughput on individual server met the
-expectation, it did not scale across servers.
-
-We spent a significant amount of time
-investigating this phenomenon. Ultimately, we were able to replicate this finding
-when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The second RAID processor on each DDN controller would max out when
-three or more LUNs were written concurrently. It turns out the root of the problem
-was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.\footnote{DDN recently released a new
-firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
-a chance to verify it during our test cycle.}
-
-%% SCOTT - is running with cache mirroring off and option for a production system or not?
-%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
-%% with it or not?
-
-%% FEIYI: add footnote to clarify the issue.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-after-ddn}
-\caption{Evaluating RADOS bench after disabling cache mirroring}
-\label{fig:rados-ddn-mirror-disabled}
-\end{figure}
-
-With cache mirroring disabled, write performance when using all four servers
-improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
-5.5 GB/s from the clients.  When accounting for journal writes, that is over
-11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
-Unfortunately, read performance did not scale as well.
-
-\subsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux
-kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}} TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
-
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
-\subsection{Repeating RADOS Scaling Test}
-
-We now repeated the previous RADOS scaling tests with these improvements in place.
-The first test was done on a single node with RADOS Bench to see how close the
-underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
-XFS-formatted storage.
-
-%% SCOTT - the title in the figure needs to change IO to I/O
-
-%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
-%% on the single server?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
-\label{fig:rados-064-osd}
-\end{figure}
-
-In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
-
-We also repeated tests looking at RADOS Bench performance as the number of OSD
-server nodes increases from one to four. The results are summarized in
-Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
-scales nearly linearly for both reads and writes.
-
-%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
-%% Do they no measure the same thing (i.e. a single server)? If not, the text
-%% needs to make it more clear.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
-nodes}
-\label{fig:rados-064-oss}
-\end{figure}
-
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
-
-The initial stability issues mentioned in Section~\ref{sec:ior-initial} are
-fixed by migrating from Ceph version 0.48/0.55 to 0.64, the latest stable version at the
-time of writing this report.  Upgrading to the latest stable Ceph release
-allowed us to run a full IOR parameter sweep for the first time since we
-started evaluating the performance and scalability of the Ceph file system.
-This is another sign of how much Ceph development is currently in flux.
-
-Another fix introduced by Ceph version 0.64 was in pool creation.  The default
-data pool used by previous Ceph version were set to 2x replication by mistake.
-This potentially halved the write performance. With version 0.64 we explicitly
-set the replication level to 1, which is the preferred value for a HPC
-environment like ours running on high-end and reliable storage backend hardware
-(e.g. DDN SFA10K).
-
-Even with these two changes in place, less-than-ideal write performance and
-very poor read performances were observed during our tests.  We also observed
-that by increasing the number of IOR processes per client node, the read
-performance degraded even further indicating some kind of contention either on
-the clients or on the OSD servers.
-
-\subsection{Disabling Client CRC32}
-
-At this point, we were able to both make more client nodes available for Ceph
-file system-level testing and also install a profiling tool called \verb!perf!
-that is extremely useful for profiling both kernel and user space codes.
-Profiling with \verb!perf! showed high CPU utilization on test clients due to
-crc32c processing in the Ceph kernel client.  crc32 checksums can be disabled
-by changing the CephFS mount options:
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
-
-With client CRC32 disabled, we repeated the IOR tests. New results are shown in
-in Figure~\ref{fig:ior-no-client-crc32}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with disabling client-side CRC32}
-\label{fig:ior-no-client-crc32}
-\end{figure}
-
-We observed that IOR write throughput increased dramatically and is now very
-close and comparable to the RADOS Bench performance. Read performance continued
-to be poor and continued to scale inversely with the increasing number of
-client processes.  Please note that, since these tests were performed, Inktank
-has implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based
-CRC32 processing should have already been using SSE4 instructions on Intel
-CPUs, this update will allow any user-land Ceph processes to process CRC32
-checksums with significantly less overhead.
-
-\subsection{Improving IOR Read Performance}
-
-Deeper analysis with perf showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which was the kernel
-installed on our test systems.\footnote{For more information,
-please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
-
-We upgraded our test systems with kernel version 3.9 and performed RADOS Bench
-test.  The results were extremely positive and presented in
-Figure~\ref{fig:rados-kernel}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
-
-As can be seen, with the 3.9 kernel, while there was a slight improvement on
-write performance, read performance improved dramatically.  In addition to the
-kernel change, Sage Weil from InkTank suggested increasing the amount of CephFS
-client kernel read-ahead cache size as:
-
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
-%% mention that 15 shows the filesystem performance?
-
-IOR results reflecting the read-ahead cache size change are presented in
-Figure~\ref{fig:ior-kernel-39}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer
-size}
-\label{fig:ior-kernel-39}
-\end{figure}
-
-By installing a newer kernel, increasing read-ahead cache size, and increasing the number of
-client IOR processes, we were able to achieve very satisfactory I/O performance.
-
-\subsection{Repeating the IOR Scaling Test}
-
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we saw
-saw  improved read and write performance. These new read and write performance are in
-line with observed RADOS bench performance.
-
-%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
-%% as to why 4 KB performance is better than 4 MB performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
-\label{fig:ior-064}
-\end{figure}
-
-Throughout our IOR testing, we observed that the average write throughput is 
-lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving with respect to increasing number of clients.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to ~8 GB/s  we
-obervered with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
-\end{figure}
-
-In our particular setup, we only had one metadata server (MDS) configured.
-Therefore, this is not a scalability test on the performance of Ceph clustered
-MDS, which would have been very interesting.  Instead, we focus on a single MDS
-performance and exercise it with up to 8 clients to observe the single MDS
-performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
-used for this test are:
-
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform a sync operation.  This is a more realistic use case scenario than just
-open, close and removal sequence of metadata operations.
-
-\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
-clients, the total number of files and directories in the workload is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, this is a mixture of both.
-
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
-
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
-
-\end{itemize}
-
-Each test iterates five times and we are presenting the maximum out of all five iterations. 
-We summarize the results as follows:
-
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
-
-\begin{itemize}
-
-\item With either shared or unique directory (\verb!-u!), stat
-operations for directories and files exhibit strong linear scaling. Same strong
-linear scaling is also observed for file read operations.
-
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
-
-\item Though the same saturation (or degradation) trend was not observed for
-file creation operation, it is likely due to lack of workload stress on MDS.
-
-\end{itemize}
-
-The results also show that file creation rate is signficantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results from early version of Ceph without all
-the tunings and improvement applied. Therefore, we repeated the same test on the
-latest CephFS 0.64. The result is illustrated in
-Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
-improvement on the file creation rate. We also note that as number of clients
-increase, the file creation rate decreases rapidly, which suggested some form of
-lock contention. This presents some interesting issues to be investigated
-further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
-\section{Observations and Conclusions}
-
-Below are our preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
-are unreliable, with little or no redundancy and failure detection capability.
-This assumption is not valid for high-end HPC centers like ours. We have
-disabled replication for pools, we haven't measured and quantified
-processing overhead and we do not know yet if this would be significant.
-
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
-host systems that has locally attached disk. However, this presents a problem
-in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
-devices through SCSI Request Protocol (SRP) over IB. The journaling write
-requires twice the bandwidth compare to Lustre-like metadata-only journaling
-mechanism. For Ceph to be viable in this facility, journaling operations will
-need to further design and engineering.
-
-  \item We observed consistent results and linear scalability at the RADOS
-level. However, we did not observe the same at the file system level. We have
-experienced large performance swings during different runs, very low read
-performance when transfer size is small, and I/O errors tend to happen when
-system is under stress (more clients and large transfer sizes). These are not
-particularly reproducible results, but it suggests that there are opportunities
-for code improvement and maturation.
-
-\end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}

### 2013-08-21 testbed.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-20 ceph-eval.tex
@@
-\documentclass{article}
-
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
-\section{Introduction}
-
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, has prepared a detailed performance and scalability study of
-Ceph file system. Ceph is originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it is designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commerical support.
-
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration failure domains and
-  hierarchical storage tiers.
-
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers.
-
-\item Ceph's design assumes that the system is composed of
-unreliable components; fault-detection and fault-tolerance (e.g., replication) are
-the norm rather than the exception. This is in line with the expectations of
-Exascale computing.
-
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
-
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
-
-\end{itemize}
-
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the feasibility
-of using the Ceph for our future HPC storage deployment.
-This report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph has not matured yet for scientific
-HPC community that its code base is changing rapidly. In between releases, we
-often experienced different outcomes. We will try to make clear in the report
-when such changes occurred.
-
 \section{Testbed Environment Description}
@@
 \centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K Hardware and Host Connection Diagram}
+\includegraphics[width=3in]{figs/sfa10k}
+\caption{DDN SFA10K hardware and host connection diagram}
 \label{fig:ddn-sfa10k}
@@
 
-\begin{table}[H]
+\begin{table}[!t]
 \centering
+\caption{Support nodes involved in Ceph testbed}
+\label{tbl:ceph-test-nodes}
     \begin{tabular}{ll}
-    \toprule
+    \hline
     Node & Role \\
-    \midrule
+    \hline
     tick-mds1 & Ceph monitor node \\
@@
     spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
+    \hline
     \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
 \end{table}
@@
 %\end{Verbatim}
-
-\section{Baseline Performance}
-\label{sec:block-io}
-
-\subsection{Block I/O over Native IB}
-We first established baseline performance by measuring observed block I/O
-performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with four SAS LUNs & ~ 2.8 GB/s \\
-    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
-\end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
-\end{table}
-
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
-
-\subsection{IP over IB}
-
-Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
-
-Unfortunately there was not enough time to do more detailed analysis of the network
-performance. Later, we will see RADOS is performing a
-maximum of 5-6 GB/s driven by four hosts.  So, it shows that we
-have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
-case).
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
-\section{XFS Performance As Backend File System}
-
-Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
-Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
-should be noted that in testing cases while we can compare XFS vs.
-Brtfs, Brtfs generally shows better performance results.} We experimented with
-XFS to acquire a set of configuration parameters which provided optimal
-performance for the SFA10K. We sampled a selected set of parameters (block size,
-queue depth, request size, sequential read and write). We settled on the
-following configuration: mount with \verb!nobarrier,noatim,inode64! options.
-The \verb!inode64! option had a notable improvement on sequential write (around
-20\%).
-
-%% Can the graphs be adjusted to have the same values in the Y axis?
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\centering
-\includegraphics[width=3in]{data/xdd-read}
-\caption{XFS read performance scaling on number of devices}
-\label{fig:xfs-read}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/xdd-write}
-\caption{XFS write performance scaling on number of devices}
-\label{fig:xfs-write}
-\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%% -- 1st figure
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-read}
-%\caption{XFS read performance scaling on number of devices}
-%\label{fig:xfs-read}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-%\centering
-%\includegraphics[width=3in]{data/xdd-write}
-%\caption{XFS write performance scaling on number of devices}
-%\label{fig:xfs-write}
-%\end{minipage}%
-%\end{figure}
-
-% % Are the read and write graphs wrong or should the second sentence below be
-% about write % instead of read?
-The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These show
-scaling behavior over the number of LUNs, which indicates that XFS can reach
-the peak write performance with five SATA LUNs. Increasing number of LUNs
-beyond 5, degradation happened. 
-Changes to the queue depth was not observed to make any obvious difference in
-the performance. For these tests, we used the \verb!xdd! benchmark with direct
-I/O and a request size of 32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is the Ceph object store, the foundational component for CephFS file
-system. There are two types of scaling tests we are interested at the RADOS
-layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
-
-We used the open-source RADOS Bench tool, developed by Inktank, to perform our
-initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
-writes out objects to the underlying object storage as fast as possible, and
-then later reads those objects in the same order as they were written.
-
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
-
-\subsection{Scaling on number of OSDs per server}
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
-nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
-have not reached the saturation point yet. Additional testing would require
-provisioning more OSDs on the SFA10K backend.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
-\label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
-\label{fig:oss-scale}
-\end{minipage}%
-\end{figure}
-
-\subsection{Scaling on number of OSD servers}
-
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
-
-\section{Ceph File System Performance: Initial Test}
-
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
-
-\begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
-\caption{IOR parameter setup}
-\label{tbl:ior}
-\end{table}
-
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
-
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
-
-%% FEIYI: 6, 7 all fixed.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
-
-\begin{itemize}
-  \item The small read (4 KB transfer size) performance is almost an anomaly --
-  we will investigate why it is so low compare to write performance and improved
-  results in Section~\ref{sec:improve-ior}.
-  \item The large read (4 MB transfer size) performance is almost half of the
-  RADOS read performance.
-
-  \item The write performance is also about half of what we can obtain from
-  RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well. 
-\end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
-
-We will describe the efforts and results on performance improvement in the
-following sections.
-
-\section{Improving RADOS Performance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=5in]{parametric}
-\caption{Evaluating parameter impact through sweeping test}
-\label{fig:parametric}
-\end{figure}
-
-After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
-journals on the same disks as the data, doubling the OSD count, and upgrading
-Ceph to a development version which reduces the seek overhead caused by
-\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
-
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
-
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
-
-\subsection{Disable Cache Mirroring on controllers}
-
-During a second round of test performed by Inktank, we noticed a dramatic drop
-on RADOS performance: even though write throughput on individual server met the
-expectation, it did not scale across servers.
-
-We spent a significant amount of time
-investigating this phenomenon. Ultimately, we were able to replicate this finding
-when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The second RAID processor on each DDN controller would max out when
-three or more LUNs were written concurrently. It turns out the root of the problem
-was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.\footnote{DDN recently released a new
-firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
-a chance to verify it during our test cycle.}
-
-%% SCOTT - is running with cache mirroring off and option for a production system or not?
-%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
-%% with it or not?
-
-%% FEIYI: add footnote to clarify the issue.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-after-ddn}
-\caption{Evaluating RADOS bench after disabling cache mirroring}
-\label{fig:rados-ddn-mirror-disabled}
-\end{figure}
-
-With cache mirroring disabled, write performance when using all four servers
-improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
-5.5 GB/s from the clients.  When accounting for journal writes, that is over
-11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
-Unfortunately, read performance did not scale as well.
-
-\subsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux Kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
-TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
-
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
-\subsection{Repeating RADOS Scaling Test}
-
-We now repeated the previous RADOS scaling tests with these improvements in place.
-The first test was done on a single node with RADOS Bench to see how close the
-underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
-XFS-formatted storage.
-
-%% SCOTT - the title in the figure needs to change IO to I/O
-
-%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
-%% on the single server?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
-\label{fig:rados-064-osd}
-\end{figure}
-
-In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
-
-We also repeated tests looking at RADOS Bench performance as the number of OSD
-server nodes increases from one to four. The results are summarized in
-Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
-scales nearly linearly for both reads and writes.
-
-%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
-%% Do they no measure the same thing (i.e. a single server)? If not, the text
-%% needs to make it more clear.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
-nodes}
-\label{fig:rados-064-oss}
-\end{figure}
-
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
-
-The initial stability issues we encountered are fixed by moving from Ceph
-version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test
-could complete even during long runs. This is another sign of how much Ceph
-development is in flux.
-
-Another fix comes in the way we create the pool: the default data pool being used
-by previous CephFS cluster are set to 2x replication, which can potentially
-halve the write performance. Even with these changes in place, Inktank still
-reproduced the less-than-ideal write performance and very poor read
-performance as observed by ORNL.  Further, by increasing the number of IOR
-processes per client node, read performance actually degraded further
-indicating some kind of contention either on the clients or on the OSD
-servers.
-
-\subsection{Disabling Client CRC32}
-
-ORNL at this point was able to both make more client nodes available and also
-install a profiling tool called \verb!perf! that is extremely useful for
-profiling both kernel and user space code.  Profiling with \verb!perf! showed
-high CPU utilization on the client due to crc32c processing in the Ceph kernel
-client.  Luckily, crc32 checksums can be disabled by changing the CephFS mount
-options:
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
-
-With client CRC32 disabled, we repeated the IOR test and the results are showin
-in Figure~\ref{fig:ior-no-client-crc32}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with disabling client-side CRC32}
-\label{fig:ior-no-client-crc32}
-\end{figure}
-
-We observed that IOR write throughput increased dramatically and is now very
-close to the throughput we were able to achieve with RADOS Bench, but reads
-continued to be slow and continued to scale inversely with the number of client
-processes.  Please note that since these tests were performed, Inktank has
-implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based CRC32
-processing should have already been using SSE4 instructions on Intel CPUs, this
-will allow any user-land Ceph processes to process CRC32 checksums with
-significantly less overhead.
-
-\subsection{Improving IOR Read Performance}
-
-Deeper analysis with perf showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which happens to be the kernel
-that ORNL had installed on the test systems.\footnote{For more information,
-please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
-
-ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
-RADOS Bench test to verify that there was no degradation versus previous tests.  The
-results were extremely positive.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Kernel 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
-
-With the kernel changes writes performance improved slightly, while read
-performance improved dramatically.  In addition to the kernel change, Sage Weil
-suggested increasing the amount of read-ahead being performed by the CephFS
-kernel client:
-
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
-%% mention that 15 shows the filesystem performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with Kernel changes to 3.9, IOR with 4 MB transfer
-size}
-\label{fig:ior-kernel-39}
-\end{figure}
-
-By installing a new kernel, increasing read-ahead, and increasing the number of
-client IOR processes, we were able to achieve a very satisfactory result on this
-test run.
-
-\subsection{Repeating IOR Scaling Test}
-
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
-seeing a much improved picture of read and write performance, very much in
-line with RADOS bench performance.
-
-%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
-%% as to why 4 KB performance is better than 4 MB performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
-\label{fig:ior-064}
-\end{figure}
-
-We observe a couple of places where the average write throughput is quite a
-bit lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving as the number of clients increases.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
-saw with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
-\end{figure}
-
-In our particular setup, we have only one metadata server (MDS)
-configured. Therefore, this is not a scalability test on the performance of
-clustered MDS, which would be very interesting.
-Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
-scales. The particular parameters we use for testing are:
-
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform sync after it. This is a more realistic use case scenario than just
-open, close and removal.
-
-\item \verb!-n 1000!: this is per client file \textit{and} directories. For eight
-clients, the number of files and directories is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, so this is a mixture of both.
-
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
-
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
-
-\end{itemize}
-
-Each test iterates five times and we are showing the max. 
-We summarize the results as follows:
-
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
-
-\begin{itemize}
-
-\item Within a single sharing mode (either shared or unique directory), the
-directory stat and file stat, as well as file read exhibit strong linear
-scaling property.
-
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
-
-\item Though the same saturation or degradation trend is not observed for file
-creation, it is likely due to we have not put enough of workload stress on MDS.
-
-\end{itemize}
-
-The results also show that file creation rate is signficantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results from early version of Ceph without all
-the tunings and improvement applied. Therefore, we repeated the same test on the
-latest CephFS 0.64. The result is illustrated in
-Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
-improvement on the file creation rate. We also note that as number of clients
-increase, the file creation rate decreases rapidly, which suggested some form of
-lock contention. This presents some interesting issues to be investigated
-further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
-\section{Observations and Conclusions}
-
-This is preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
-  are unreliable, with little or no redundancy and failure detection capability.
-  This is not the case in leadership computing facilities. We have disabled
-  replication for pools, but this will take a toll somewhere in the processing
-  and we do not know if this is significant.
-
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
-  system that has locally attached disk. However, this presents a problem in DDN
-  SFA10-like hardware, where the backend LUNs are exposed as block device
-  through SCSI Request Protocol (SRP) over IB. The journaling write requires twice the bandwidth
-  compare to Lustre-like metadata-only journaling mechanism. For Ceph to be
-  viable in this facility, we will need to address this.
-
-  \item We observed consistent results and linear scalability at the
-  RADOS level. However, we did not observe the same at the file system level with synthetic
-  benchmark suites such as IOR. We have experienced large performance swings
-  during different runs, very low read performance when transfer size is small,
-  and I/O errors tend to happen when system is under stress (more clients and
-  large transfer sizes). These are not particularly reproducible results, but it
-  suggests that there are opporunities for code improvement and maturation.
-
-\end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}

### 2013-08-21 xfs.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.

--- 2013-08-20 ceph-eval.tex
@@
-\documentclass{article}
-
-\usepackage{fontspec}
-\usepackage{mathptm}
-\usepackage{comment}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{microtype}
-\usepackage{fancyvrb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color,soul}
-
-\usepackage[colorlinks = true,%
-            linkcolor = blue,%
-            urlcolor  = blue,%
-            citecolor = blue,%
-            anchorcolor = blue]{hyperref}
-
-\onehalfspacing
-
-\defaultfontfeatures{Mapping=tex-text}
-
-\setmainfont{rosario}
-%\setmonofont{Consolas}
-%\setmainfont{Times}
-\setmonofont{Inconsolata}
-%\setmonofont[Scale=0.8]{Monaco}
-%\setmonofont{Courier}
-
-%\title{Ceph Parallel File System Evaluation Report}
-%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
-%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}
-
-%% adjust float figure placement
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\topfraction}{1.00}
-\renewcommand{\bottomfraction}{0.70}
-\renewcommand{\floatpagefraction}{0.85}
-
-\graphicspath{{./figs/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-
-\begin{document}
-
-\input{cover}
-
-\pagebreak
-\thispagestyle{empty}
-\tableofcontents
-
-\pagebreak
-\thispagestyle{empty}
-\listoffigures
-
-\clearpage
-\pagenumbering{arabic}
-
-%\maketitle
-%\authorrunning{}
-%\titlerunning{}
-
-\section{Introduction}
-
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, has prepared a detailed performance and scalability study of
-Ceph file system. Ceph is originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it is designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commerical support.
-
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration failure domains and
-  hierarchical storage tiers.
-
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers.
-
-\item Ceph's design assumes that the system is composed of
-unreliable components; fault-detection and fault-tolerance (e.g., replication) are
-the norm rather than the exception. This is in line with the expectations of
-Exascale computing.
-
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
-
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
-
-\end{itemize}
-
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the feasibility
-of using the Ceph for our future HPC storage deployment.
-This report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph has not matured yet for scientific
-HPC community that its code base is changing rapidly. In between releases, we
-often experienced different outcomes. We will try to make clear in the report
-when such changes occurred.
-
-\section{Testbed Environment Description}
-
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{figs/sfa10k}
-\caption{DDN SFA10K Hardware and Host Connection Diagram}
-\label{fig:ddn-sfa10k}
-\end{figure}
-
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
-
-\begin{table}[H]
-\centering
-    \begin{tabular}{ll}
-    \toprule
-    Node & Role \\
-    \midrule
-    tick-mds1 & Ceph monitor node \\
-    spoon46 & Ceph MDS node \\
-    tick-oss[1-4] & Ceph OSD servers \\
-    spoon28-31, spoon37-41 & Ceph client nodes \\
-    \bottomrule
-
-    \end{tabular}
-\caption{Support nodes involved in Ceph testbed}
-\label{tbl:ceph-test-nodes}
-\end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 (rhl-ceph image), Glibc 2.12 with syncfs support, locally patched.
-We used the Ceph 0.55 release in the initial tests, upgraded to 0.64 and then to
-0.67RC for a final round of tests.
-
-%For a complete a list of hosts that are running ceph images, one can execute:
-
-%\begin{Verbatim}
-%$ grep "rhel6-ceph" /etc/gedi/MAC.info
-%\end{Verbatim}
-
-\section{Baseline Performance}
-\label{sec:block-io}
-
-\subsection{Block I/O over Native IB}
-We first established baseline performance by measuring observed block I/O
-performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    SAS single LUN sequential read & ~1.4 GB/s \\
-    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
-    Single host with four SAS LUNs & ~ 2.8 GB/s \\
-    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
-    \bottomrule
-\end{tabular}
-\caption{Block I/O performances on single LUN and single host}
-\label{tbl:block-io-baseline}
-\end{table}
-
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
-
-\subsection{IP over IB}
-
-Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
-
-Unfortunately there was not enough time to do more detailed analysis of the network
-performance. Later, we will see RADOS is performing a
-maximum of 5-6 GB/s driven by four hosts.  So, it shows that we
-have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
-case).
-
-\section{System Tuning}
-
-Base upon past experience and further experimentation, we started out with the
-following set of tuning parameters on OSD servers:
-
-\begin{table}[htb]
-\centering
-\begin{tabular}{ll}
-    \toprule
-    \verb!nr_requests! & 2048 \\
-    \verb!read_ahead_kb! & 4096 \\
-    \verb!scheduler! & deadline \\
-    \bottomrule
-\end{tabular}
-\caption{System tuning parameters}
-\end{table}
-
 \section{XFS Performance As Backend File System}
@@
 % about write % instead of read?
+
 The read and write performance results are summarized in
-Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These show
-scaling behavior over the number of LUNs, which indicates that XFS can reach
-the peak write performance with five SATA LUNs. Increasing number of LUNs
-beyond 5, degradation happened. 
-Changes to the queue depth was not observed to make any obvious difference in
-the performance. For these tests, we used the \verb!xdd! benchmark with direct
-I/O and a request size of 32 KB.
-
-\section{Ceph RADOS Scaling: Initial Test}
-
-RADOS is the Ceph object store, the foundational component for CephFS file
-system. There are two types of scaling tests we are interested at the RADOS
-layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
-
-We used the open-source RADOS Bench tool, developed by Inktank, to perform our
-initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
-writes out objects to the underlying object storage as fast as possible, and
-then later reads those objects in the same order as they were written.
-
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
-
-\subsection{Scaling on number of OSDs per server}
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
-nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
-have not reached the saturation point yet. Additional testing would require
-provisioning more OSDs on the SFA10K backend.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
-\label{fig:osd-scale}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
-\label{fig:oss-scale}
-\end{minipage}%
-\end{figure}
-
-\subsection{Scaling on number of OSD servers}
-
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
-
-\section{Ceph File System Performance: Initial Test}
-
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
-
-\begin{table}[tb]
-\centering
-\begin{tabular}{p{1.5in} | p{3in}}
-    \toprule
-    IOR parameter & Note \\ \midrule
-    \verb!-F! & file per process \\ \midrule
-    \verb!-a POSIX! & use POSIX API \\ \midrule
-    \verb!-w -r -C! & do both write and read test, \verb!-C! is to change task
-        ordering for read back so it will not read from the write cache. \\ \midrule
-    \verb!-i 3 -d 5! & 3 iterations and delay 5 seconds betewen iterations \\
-    \midrule  
-    \verb!-e! & perform \verb!fsync()! upon POSIX write close \\ \midrule
-    \verb!-b 8g or 16g! & the block size \\ \midrule
-    \verb!-t 4k to 4m! & the transfer size \\ \midrule
-    \verb!-o file! & mandatory test file  \\    
-    \bottomrule
-\end{tabular}
-\caption{IOR parameter setup}
-\label{tbl:ior}
-\end{table}
-
-\begin{Verbatim}
-# sync
-# echo 3 | tee /proc/sys/vm/drop_caches
-\end{Verbatim}
-
-Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
-is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.
-
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
-
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
-%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?
-
-%% FEIYI: 6, 7 all fixed.
-
-\begin{figure}[H]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4k}
-\caption{IOR tests: 4 KB transfer size}
-\label{fig:ior4k}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/ior_4m}
-\caption{IOR tests: 4 MB transfer size}
-\label{fig:ior4m}
-\end{minipage}%
-\end{figure}
-
-\begin{itemize}
-  \item The small read (4 KB transfer size) performance is almost an anomaly --
-  we will investigate why it is so low compare to write performance and improved
-  results in Section~\ref{sec:improve-ior}.
-  \item The large read (4 MB transfer size) performance is almost half of the
-  RADOS read performance.
-
-  \item The write performance is also about half of what we can obtain from
-  RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well. 
-\end{itemize}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=5in]{data/mdtest}
-%\caption{mdtest of single MDS}
-%\label{fig:mdtest1c}
-%\end{figure}
-
-We will describe the efforts and results on performance improvement in the
-following sections.
-
-\section{Improving RADOS Performance}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=5in]{parametric}
-\caption{Evaluating parameter impact through sweeping test}
-\label{fig:parametric}
-\end{figure}
-
-After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
-journals on the same disks as the data, doubling the OSD count, and upgrading
-Ceph to a development version which reduces the seek overhead caused by
-\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
-
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
-
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
-
-\subsection{Disable Cache Mirroring on controllers}
-
-During a second round of test performed by Inktank, we noticed a dramatic drop
-on RADOS performance: even though write throughput on individual server met the
-expectation, it did not scale across servers.
-
-We spent a significant amount of time
-investigating this phenomenon. Ultimately, we were able to replicate this finding
-when running concurrent disk throughput tests directly on the servers without
-Ceph involved. The second RAID processor on each DDN controller would max out when
-three or more LUNs were written concurrently. It turns out the root of the problem
-was a regression on DDN firmware update -- in particular, the cache
-mirroring was not behaving as it should.\footnote{DDN recently released a new
-firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
-a chance to verify it during our test cycle.}
-
-%% SCOTT - is running with cache mirroring off and option for a production system or not?
-%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
-%% with it or not?
-
-%% FEIYI: add footnote to clarify the issue.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-after-ddn}
-\caption{Evaluating RADOS bench after disabling cache mirroring}
-\label{fig:rados-ddn-mirror-disabled}
-\end{figure}
-
-With cache mirroring disabled, write performance when using all four servers
-improved dramatically, as illustrated in
-Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
-5.5 GB/s from the clients.  When accounting for journal writes, that is over
-11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
-Unfortunately, read performance did not scale as well.
-
-\subsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After several hours of diagnostics, Inktank observed that outstanding operations
-on the clients were not being shown as outstanding on the OSDs.  This appeared
-to be very similar to a problem Jim Schutt at Sandia National labs encountered
-with TCP autotuning in the Linux Kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
-TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this will make a notable improvement
-on Ceph read performance, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
-
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4.0in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
-\subsection{Repeating RADOS Scaling Test}
-
-We now repeated the previous RADOS scaling tests with these improvements in place.
-The first test was done on a single node with RADOS Bench to see how close the
-underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
-XFS-formatted storage.
-
-%% SCOTT - the title in the figure needs to change IO to I/O
-
-%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
-%% on the single server?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
-\label{fig:rados-064-osd}
-\end{figure}
-
-In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
-
-We also repeated tests looking at RADOS Bench performance as the number of OSD
-server nodes increases from one to four. The results are summarized in
-Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
-scales nearly linearly for both reads and writes.
-
-%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
-%% Do they no measure the same thing (i.e. a single server)? If not, the text
-%% needs to make it more clear.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{rados-064-oss}
-\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
-nodes}
-\label{fig:rados-064-oss}
-\end{figure}
-
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
-
-The initial stability issues we encountered are fixed by moving from Ceph
-version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test
-could complete even during long runs. This is another sign of how much Ceph
-development is in flux.
-
-Another fix comes in the way we create the pool: the default data pool being used
-by previous CephFS cluster are set to 2x replication, which can potentially
-halve the write performance. Even with these changes in place, Inktank still
-reproduced the less-than-ideal write performance and very poor read
-performance as observed by ORNL.  Further, by increasing the number of IOR
-processes per client node, read performance actually degraded further
-indicating some kind of contention either on the clients or on the OSD
-servers.
-
-\subsection{Disabling Client CRC32}
-
-ORNL at this point was able to both make more client nodes available and also
-install a profiling tool called \verb!perf! that is extremely useful for
-profiling both kernel and user space code.  Profiling with \verb!perf! showed
-high CPU utilization on the client due to crc32c processing in the Ceph kernel
-client.  Luckily, crc32 checksums can be disabled by changing the CephFS mount
-options:
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
-
-With client CRC32 disabled, we repeated the IOR test and the results are showin
-in Figure~\ref{fig:ior-no-client-crc32}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-client-no-crc32}
-\caption{IOR test with disabling client-side CRC32}
-\label{fig:ior-no-client-crc32}
-\end{figure}
-
-We observed that IOR write throughput increased dramatically and is now very
-close to the throughput we were able to achieve with RADOS Bench, but reads
-continued to be slow and continued to scale inversely with the number of client
-processes.  Please note that since these tests were performed, Inktank has
-implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based CRC32
-processing should have already been using SSE4 instructions on Intel CPUs, this
-will allow any user-land Ceph processes to process CRC32 checksums with
-significantly less overhead.
-
-\subsection{Improving IOR Read Performance}
-
-Deeper analysis with perf showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which happens to be the kernel
-that ORNL had installed on the test systems.\footnote{For more information,
-please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
-
-ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
-RADOS Bench test to verify that there was no degradation versus previous tests.  The
-results were extremely positive.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{rados-kernel-35vs39}
-\caption{RADOS bench: Kernel 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
-
-With the kernel changes writes performance improved slightly, while read
-performance improved dramatically.  In addition to the kernel change, Sage Weil
-suggested increasing the amount of read-ahead being performed by the CephFS
-kernel client:
-
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
-%% mention that 15 shows the filesystem performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{ior-kernel-39}
-\caption{CephFS performance with Kernel changes to 3.9, IOR with 4 MB transfer
-size}
-\label{fig:ior-kernel-39}
-\end{figure}
-
-By installing a new kernel, increasing read-ahead, and increasing the number of
-client IOR processes, we were able to achieve a very satisfactory result on this
-test run.
-
-\subsection{Repeating IOR Scaling Test}
-
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
-seeing a much improved picture of read and write performance, very much in
-line with RADOS bench performance.
-
-%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
-%% as to why 4 KB performance is better than 4 MB performance?
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=5in]{ior-064-4k}
-\includegraphics[width=5in]{ior-064-4m}
-\caption{IOR Scaling Test: 4 KB and 4 MB transfer size}
-\label{fig:ior-064}
-\end{figure}
-
-We observe a couple of places where the average write throughput is quite a
-bit lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving as the number of clients increases.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
-saw with RADOS Bench.
-
-\section{Metadata Performance}
-
-\begin{figure}[htb]
-\centering
-%% -- 1st figure
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{minipage}%
-\begin{minipage}[t]{0.5\linewidth}
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{minipage}%
-\end{figure}
-
-In our particular setup, we have only one metadata server (MDS)
-configured. Therefore, this is not a scalability test on the performance of
-clustered MDS, which would be very interesting.
-Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
-scales. The particular parameters we use for testing are:
-
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform sync after it. This is a more realistic use case scenario than just
-open, close and removal.
-
-\item \verb!-n 1000!: this is per client file \textit{and} directories. For eight
-clients, the number of files and directories is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, so this is a mixture of both.
-
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
-
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
-
-\end{itemize}
-
-Each test iterates five times and we are showing the max. 
-We summarize the results as follows:
-
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
-
-\begin{itemize}
-
-\item Within a single sharing mode (either shared or unique directory), the
-directory stat and file stat, as well as file read exhibit strong linear
-scaling property.
-
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
-
-\item Though the same saturation or degradation trend is not observed for file
-creation, it is likely due to we have not put enough of workload stress on MDS.
-
-\end{itemize}
-
-The results also show that file creation rate is signficantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results from early version of Ceph without all
-the tunings and improvement applied. Therefore, we repeated the same test on the
-latest CephFS 0.64. The result is illustrated in
-Figure~\ref{fig:mdtest-064-file-create}. As expected, we observed a significant
-improvement on the file creation rate. We also note that as number of clients
-increase, the file creation rate decreases rapidly, which suggested some form of
-lock contention. This presents some interesting issues to be investigated
-further.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=4in]{mdtest-064-file-create}
-\caption{mdtest of file creation on Ceph 0.64}
-\label{fig:mdtest-064-file-create}
-\end{figure}
-
-\section{Observations and Conclusions}
-
-This is preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
-  are unreliable, with little or no redundancy and failure detection capability.
-  This is not the case in leadership computing facilities. We have disabled
-  replication for pools, but this will take a toll somewhere in the processing
-  and we do not know if this is significant.
-
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
-  system that has locally attached disk. However, this presents a problem in DDN
-  SFA10-like hardware, where the backend LUNs are exposed as block device
-  through SCSI Request Protocol (SRP) over IB. The journaling write requires twice the bandwidth
-  compare to Lustre-like metadata-only journaling mechanism. For Ceph to be
-  viable in this facility, we will need to address this.
-
-  \item We observed consistent results and linear scalability at the
-  RADOS level. However, we did not observe the same at the file system level with synthetic
-  benchmark suites such as IOR. We have experienced large performance swings
-  during different runs, very low read performance when transfer size is small,
-  and I/O errors tend to happen when system is under stress (more clients and
-  large transfer sizes). These are not particularly reproducible results, but it
-  suggests that there are opporunities for code improvement and maturation.
-
-\end{itemize}
-
-\section*{Appendix A - CephFS Final Mount Command}
-\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}
-
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-      name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
-\end{Verbatim}
-
-\section*{Appendix B - OSD File System Options}
-\addcontentsline{toc}{section}{Appendix B - OSD File System Options}
-
-\input{osd_fs.txt}
-
-\section*{Appendix C - CRUSH Map}
-\addcontentsline{toc}{section}{Appendix C - CRUSH map}
-
-This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
-change accordingly.
-
-\input{crush.txt}
-
-\section*{Appendix D - Final ceph.conf}
-\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
-
-\input{ceph-short.txt}
-
-\section*{Appendix E - Tuning Parameters}
-\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}
-
-For parameter sweep, here are the settings we iterated through.  Some of these
-are "compound" settings where we increased or decreased multiple things in the
-ceph.conf file at the same time to reduce the number of permutations that would
-need to be tested.
-
-\input{tuning.txt}
-
-\end{document}
+Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These graphs
+show scaling behavior over the number of LUNs, which indicates that XFS can
+reach the peak write performance with just five SATA LUNs. Increasing number
+of LUNs beyond 5, degradation happened.  Also, we did not observe any obvious
+differences in performance when varying the queue depth parameter.  For these
+tests, we used the \verb!xdd! benchmark with direct I/O and a request size of
+32 KB.

### 2013-08-22 abstract.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.
updated the abstract

@@
-Ceph is designed to be a reliable and scalable fault tolerant parallel file
-system with a number of intriguing features. In collaboration with its major
-developer, Inktank Inc, we studied the feasibility of using Ceph for future
-HPC storage deployment. This paper presents our experiments, results and
-observations from mostly performance and scalability perspective. Our work
-made two unique contributions. First, this evaluation is performed under a
-realistic setup using state-of-the-art backend storage (Data Direct Network's
-SFA10K),  although typical in large-scale HPC environment, but atypical for
-average commercial off-the-shelf setup.  Second, our path of investigation,
-tuning efforts, and findings made a direct contribution to Ceph's development,
-it should also benefit community at large. Throughout the evaluation, we can
-see that Ceph is under fast-paced development and maturing with great promise.
+\begin{abstract}
+
+%Ceph is designed to be a reliable and scalable fault tolerant parallel file
+%system with a number of intriguing features.
+
+Ceph is an open-source and emerging distributed parallel file and storage
+system technology. It is designed to provide file system-level and object-level
+access to data. Ceph, by design, assumes running on unreliable and commodity
+storage and network hardware and provides reliability and fault-tolerance
+through pre-calculated and controlled object placement and data replication.
+
+In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
+technology for future high-performance computing (HPC) environments, like ours.
+This paper presents our evaluation methodology, experiments, results and
+observations from mostly parallel I/O performance and scalability perspectives.
+Our work made two unique contributions. First, our evaluation is performed
+under a realistic setup for a large-scale capability HPC environment like ours
+using a commercial high-end storage system (Data Direct Network's SFA10K).
+%although typical in large-scale HPC environment, but atypical for average
+%commercial off-the-shelf setup.  
+Second, our path of investigation, tuning efforts, and findings made direct
+contributions to Ceph's development and improved code quality, scalability, and
+performance. These changes should also benefit the Ceph and HPC community at
+large. Throughout the evaluation, we observed that Ceph still is an evloving
+technology and is under fast-paced development and maturing with great promise.
+
+\end{abstract}

### 2013-08-22 abstract.tex
polish on abstract

@@
 
-Ceph is an open-source and emerging distributed parallel file and storage
-system technology. It is designed to provide file system-level and object-level
-access to data. Ceph, by design, assumes running on unreliable and commodity
-storage and network hardware and provides reliability and fault-tolerance
-through pre-calculated and controlled object placement and data replication.
+Ceph is an open-source and emerging parallel distributed file and storage
+system technology. It is designed to provide file system-level and
+object-level access to data. By design, Ceph assumes running on unreliable and
+commodity storage and network hardware and provides reliability and
+fault-tolerance through pre-calculated and controlled object placement and
+data replication.
 
 In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
-technology for future high-performance computing (HPC) environments, like ours.
-This paper presents our evaluation methodology, experiments, results and
-observations from mostly parallel I/O performance and scalability perspectives.
-Our work made two unique contributions. First, our evaluation is performed
-under a realistic setup for a large-scale capability HPC environment like ours
-using a commercial high-end storage system (Data Direct Network's SFA10K).
+technology for future high-performance computing (HPC) environments.  This
+paper presents our evaluation methodology, experiments, results and
+observations from mostly parallel I/O performance and scalability
+perspectives.  Our work made two unique contributions. First, our evaluation
+is performed under a realistic setup for a large-scale capability HPC
+environment like ours using a commercial high-end storage system (Data Direct
+Network's SFA10K).
 %although typical in large-scale HPC environment, but atypical for average
@@
 Second, our path of investigation, tuning efforts, and findings made direct
-contributions to Ceph's development and improved code quality, scalability, and
-performance. These changes should also benefit the Ceph and HPC community at
-large. Throughout the evaluation, we observed that Ceph still is an evloving
-technology and is under fast-paced development and maturing with great promise.
+contributions to Ceph's development and improved code quality, scalability,
+and performance. These changes should also benefit both Ceph and HPC community
+at large. Throughout the evaluation, we observed that Ceph still is an
+evolving technology under fast-paced development and showing with great
+promises.
 

### 2013-08-22 abstract.tex
some more minor changes to the abstract

@@
 Ceph is an open-source and emerging parallel distributed file and storage
-system technology. It is designed to provide file system-level and
-object-level access to data. By design, Ceph assumes running on unreliable and
-commodity storage and network hardware and provides reliability and
-fault-tolerance through pre-calculated and controlled object placement and
-data replication.
+system technology. It is designed to provide file system-level and object-level
+access to data. By design, Ceph assumes running on unreliable and commodity
+storage and network hardware and provides reliability and fault-tolerance
+through pre-calculated and controlled object placement and data replication.
 
 In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
-technology for future high-performance computing (HPC) environments.  This
-paper presents our evaluation methodology, experiments, results and
-observations from mostly parallel I/O performance and scalability
-perspectives.  Our work made two unique contributions. First, our evaluation
-is performed under a realistic setup for a large-scale capability HPC
-environment like ours using a commercial high-end storage system (Data Direct
-Network's SFA10K).
+technology for high-performance computing (HPC) environments.  This paper
+presents our evaluation methodology, experiments, results and observations from
+mostly parallel I/O performance and scalability perspectives.  Our work made
+two unique contributions. First, our evaluation is performed under a realistic
+setup for a large-scale capability HPC environment like ours using a commercial
+high-end storage system.
+% (Data Direct Network's SFA10K).
 %although typical in large-scale HPC environment, but atypical for average
@@
 Second, our path of investigation, tuning efforts, and findings made direct
-contributions to Ceph's development and improved code quality, scalability,
-and performance. These changes should also benefit both Ceph and HPC community
-at large. Throughout the evaluation, we observed that Ceph still is an
-evolving technology under fast-paced development and showing with great
-promises.
+contributions to Ceph's development and improved code quality, scalability, and
+performance. These changes should also benefit both Ceph and HPC communities at
+large. Throughout the evaluation, we observed that Ceph still is an evolving
+technology under fast-paced development and showing with great promises.
 

### 2013-08-22 data/gen.sh
add replication level test dataset and plots

@@ -8,3 +8,5 @@ Rscript plot_ior.R ior-8c-4MB-scaling.dat
 Rscript plotxdd.R xdd-read.csv read
 Rscript plotxdd.R xdd-write.csv write
 
+# generate RADOS bench result for different replication level
+Rscript plot_replication.R 

### 2013-08-22 data/plot_replication.R

@@ -1,0 +1,39 @@
+library("ggplot2")
+
+# read data, skip comments
+df = read.csv(file="replication.csv", comment.char = "#")
+
+
+quartz(type="pdf", file="rep.pdf")
+theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
+
+
+g = ggplot(df, aes(x=rep, y=bw, fill=factor(mode))) +
+    geom_bar(stat="identity", position="dodge", color="black") +
+    scale_fill_brewer(type="qual", palette=3)
+
+
+
+# g = g + theme((aspect.ratio=1)
+
+
+# g = g + ggtitle("RADOS bench throughput \n with different replication levels\n")
+g = g + xlab("\nReplication Levels") + ylab("Throughput\n")
+
+# change legend position
+g = g + theme(legend.position="top")
+
+# hide the legend title
+g = g + guides(fill=guide_legend(title=NULL))
+
+# make more breaks along Y
+g = g + scale_y_continuous(breaks=seq(0, 10000,2000))
+
+# change grid line display
+#g = g + theme(panel.grid.major = element_line(color="grey80", size = 0.7, linetype = "dashed"))
+#g = g + theme(panel.grid.minor = element_line(color="grey80", size = 0.7, linetype = "dotted"))
+
+
+
+print(g)
+dev.off()

### 2013-08-22 ceph-initial.tex
add replication level test dataset and plots
add paper flow and organization into introduction

@@
-\section{Ceph RADOS Scaling: Initial Results}
+\section{Ceph Evaluation: Initial Results}
+\label{sec:ceph-initial}
+
+\subsection{Ceph RADOS Scaling}
 
@@
 
-\subsection{Scaling on number of OSDs per server}
+\subsubsection{Scaling on number of OSDs per server}
 
@@
 
-\subsection{Scaling on number of OSD servers}
+\subsubsection{Scaling on number of OSD servers}
 
@@
 
-\section{Ceph File System Performance: Initial Test}
-\label{sec:ior-initial}
-We used the synthetic IOR benchmark suite for file system level performance and
-scalability test.
-The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
-has 6 GB of physical memory, the block size is set so as to mitigate cache
-effects. In addition, the test harness program issues the following commands
-at the beginning of each test:
+\subsection{Ceph File System Performance}
+
+We used the synthetic IOR benchmark suite for file system level performance
+and scalability test.  The particular parameter setup is show in Table
+\ref{tbl:ior}. Each client node has 6 GB of physical memory, the block size is
+set so as to mitigate cache effects. In addition, the test harness program
+issues the following commands at the beginning of each test:
 
@@
 
-\begin{Verbatim}
+\begin{Verbatim}[fontsize=\small]
 # sync

### 2013-08-22 introduction.tex
add paper flow and organization into introduction

@@
 feasibility of using the Ceph for our future HPC storage deployment.  This
-report presents our experience, results, and observations. While evaluating
+paper presents our experience, results, and observations. While evaluating
 our results, please keep in mind that Ceph is still a relatively
@@
 between releases, we often experienced different stability and performance
-outcomes.  We will try to make clear in the report when such changes occurred.
+outcomes.  We will try to make clear in the writing when such changes occurred.
+
+This paper is organized as follows. Section~\ref{sec:testbed} gives an
+overview on our general test and evaluation methodology as well as testbed
+environment; Following it, Section~\ref{sec:baseline} establishes the baseline
+performance and expectations for all critical components on the data path;
+Section~\ref{sec:ceph-initial} discusses our early results bottom up: from
+middle tier RADOS object layer to the file system-level. Then in
+Section~\ref{sec:ceph-tuning} we highlight the investigative and tuning
+effort, we compare results before and after, and how the process eventually
+bring the system performance to a respectable state.
+Section~\ref{sec:ceph-meta} present our preliminary findings on Ceph's
+metadata performance. Finally, Section~\ref{sec:conclusion} summarizes our
+findings, observations, and future works.

### 2013-08-23 introduction.tex
update introduction section

--- 2013-08-21 introduction.tex
@@
 
-National Center for Computational Sciences (NCCS), in collaboration with
-Inktank Inc, prepared this performance and scalability study of
-Ceph file system. Ceph originated from Sage Weil's PhD research
-at UC Santa Cruz around 2007 and it was designed to be a reliable, scalable
-fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
-commercial support.
+National Center for Computational Sciences (NCCS) runs one of the largest HPC
+storage system built on top of Lustre parallel file system. The latest
+installation of Spider II is designed to operate at over 1 TB/s peak
+throughput with 40 PB of raw capacity. As a scratch file system connected to a
+leadership computing platform at the scale of Titan, Spider II emphasizes
+\textit{capability} over \textit{capacity}. However, we also recognize that
+there are a wide variety of scientific data and workloads with different
+performance and data access requirements, e.g., RESTful interface, S3-like
+API, cloud solution integration, to name a few.
 
-In comparison to other parallel file systems, Ceph has a number of distinctive
-features:
+Ceph\cite{Weil:2006:Ceph} originated from Sage Weil's PhD research at UC Santa
+Cruz at 2007 and it was designed to be a reliable, scalable fault-tolerant
+parallel file system.  Inktank is now the major developer behind the
+open-source parallel file system to shepherd its development and provide
+commercial support.  In comparison to other parallel file systems, Ceph has a
+number of distinctive features:
 
@@
 
-\item From the start, Ceph's design anticipated managing metadata and the name space
-  with a cluster of metadata servers. It utilized a dynamic subtree partitioning
-  strategy to continuously adapt metadata distribution to current demands.
+  \item From the start, Ceph's design anticipated managing metadata and the
+  name space with a cluster of metadata servers. It utilized a dynamic subtree
+  partitioning strategy to continuously adapt metadata distribution to current
+  demands.
 
@@
 
-\item Ceph is built on top of a unified object management layer,
-\texttt{RADOS}. Both metadata and the file data can take advantage of this
-uniformity.
+  \item Ceph is built on top of a unified object management layer, RADOS. Both
+  metadata and the file data can take advantage of this uniformity. On top of
+  RADOS, Ceph build and project a host of other features such as RESTful
+  interface, S3 and Swift-compliant API, cloud integration.
 
@@
 
-As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
-file system evaluation. The goal of our study is to investigate the
-feasibility of using the Ceph for our future HPC storage deployment.  This
-report presents our experience, results, and observations. While evaluating
-our results, please keep in mind that Ceph is still a relatively
-\textit{young} parallel file system and its code base is changing rapidly. In
-between releases, we often experienced different stability and performance
-outcomes.  We will try to make clear in the report when such changes occurred.
+As interesting and feature-rich as Ceph may be, our environment and the sheer
+scale of its potential application drive us to first look into its scalability
+and performance.  As part of the study, we set up a dedicated testbed within
+NCCS for the Ceph file system evaluation. The goal of our study is to
+investigate the feasibility of using the Ceph for our future HPC storage
+deployment. This paper presents our experience, results, and observations.
+While evaluating our results, please keep in mind that Ceph is still a
+relatively \textit{young} parallel file system and its code base is changing
+rapidly. In between releases, we often experienced different stability and
+performance outcomes.  We will try to make clear in the writing when such
+changes occurred.
+
+This paper is organized as follows. Section~\ref{sec:testbed} gives an
+overview on our general test and evaluation methodology as well as testbed
+environment; Following it, Section~\ref{sec:baseline} establishes the baseline
+performance and expectations for all critical components on the data path;
+Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
+bottom up: from middle tier RADOS object layer to the file system-level and
+then metadata performance. In Section~\ref{sec:ceph-tuning} we highlight the
+investigative and tuning effort, we compare results before and after, and how
+the process eventually bring the system performance to a respectable state.
+Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
+and future works.

### 2013-08-23 introduction.tex
Add spider2 references

@@
 storage system built on top of Lustre parallel file system. The latest
-installation of Spider II is designed to operate at over 1 TB/s peak
+installation of Spider II\cite{spider2} is designed to operate at over 1 TB/s peak
 throughput with 40 PB of raw capacity. As a scratch file system connected to a
@@
 As interesting and feature-rich as Ceph may be, our environment and the sheer
-scale of its potential application drive us to first look into its scalability
-and performance.  As part of the study, we set up a dedicated testbed within
-NCCS for the Ceph file system evaluation. The goal of our study is to
-investigate the feasibility of using the Ceph for our future HPC storage
-deployment. This paper presents our experience, results, and observations.
-While evaluating our results, please keep in mind that Ceph is still a
-relatively \textit{young} parallel file system and its code base is changing
-rapidly. In between releases, we often experienced different stability and
-performance outcomes.  We will try to make clear in the writing when such
-changes occurred.
+scale of its potential application drive us to first look into the all
+important scalability and performance aspect of it.  As part of the study, we
+set up a dedicated testbed within NCCS for the Ceph file system evaluation.
+The goal of our study is to investigate the feasibility of using the Ceph for
+our future HPC storage deployment. This paper presents our experience,
+results, and observations.  While evaluating our results, please keep in mind
+that Ceph is still a relatively \textit{young} parallel file system and its
+code base is changing rapidly. In between releases, we often experienced
+different stability and performance outcomes.  We will try to make clear in
+the writing when such changes occurred.
 

### 2013-08-23 ceph-initial.tex
split metadata discussion into two: before and after, remove cache mirror subsection

@@
 
-We will describe the efforts and results on performance improvement in the
-following sections.
+\subsection{Metadata Performance Evaluation}
+
+In our particular setup, we only had one metadata server (MDS) configured.
+Therefore, this is not a scalability test on the performance of Ceph clustered
+MDS, which would have been very interesting.  Instead, we focus on a single MDS
+performance and exercise it with up to 8 clients to observe the single MDS
+performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
+used for this test are:
+
+\begin{itemize}
+\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
+perform a sync operation.  This is a more realistic use case scenario than just
+open, close and removal sequence of metadata operations.
+
+\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
+clients, the total number of files and directories in the workload is 8,000. Since we did not specify
+either \verb!-D! or \verb!-F!, this is a mixture of both.
+
+\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
+Lustre file system, where you can have single client multiple mounts (for
+increasing workload per client), here we just give the test an explicit home.
+
+\item \verb!-u!: without this option, we are exercising shared directory; with
+this option, we are exercising unique directories.
+
+\end{itemize}
+
+Each test iterates five times and we are presenting the maximum out of all five iterations. 
+We summarize the results as follows:
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=3in]{data/mdtest-fcreate}
+\caption{File creation vs.  number of clients}
+\label{fig:mdtest-fcreate}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=3in]{data/mdtest-dcreate}
+\caption{Directory creation vs. number of clients}
+\label{fig:mdtest-dcreate}
+\end{figure}
+
+%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
+%directory (prefixed with d) and file (prefixed with f) operations, against the
+%number of clients. Due to the scale difference, it doesn't convey the
+%magnitude of lower numbers.
+
+\begin{itemize}
+
+\item With either shared or unique directory (\verb!-u!), stat
+operations for directories and files exhibit strong linear scaling. Same strong
+linear scaling is also observed for file read operations.
+
+\item While the other operations seems unaffected or flat by the number of
+clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
+\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
+contention for shared directory. The performance degradation amount to 50\% or
+more.
+
+\item Though the same saturation (or degradation) trend was not observed for
+file creation operation, it is likely due to lack of workload stress on MDS.
+
+\end{itemize}
+
+The results also show that file creation rate is signficantly lower than
+directory creation rate. We stipulated two contributing factors: one is the file
+creation is associated with 1 MB data write and followed by a fsync operation,
+which is a rather heavy weight operation compare to directory creation. Another
+factor is that we obtained above results while both RADOS and file
+system-level performance are not tuned for optimal, yet.
+
+Next, we will describe the efforts and results on performance improvement at
+both RADOS and file system-level. As consequence, we expect to see improved
+metadata performance as well.

### 2013-08-23 ceph-tuning.tex
add paper flow and organization into introduction
split metadata discussion into two: before and after, remove cache mirror subsection

@@
-\section{Improving RADOS Performance}
+\section{Tuning, Optimization and Improvements}
+\label{sec:ceph-tuning}
+
+\subsection{Improving RADOS Performance}
 
@@
 
-\subsection{Disable Cache Mirroring on Controllers}
+\begin{comment}
+
+\subsubsection{Disable Cache Mirroring on Controllers}
 
@@
 
-\subsection{Disable TCP autotuning}
+\end{comment}
+
+\subsubsection{Disable TCP autotuning}
 
@@
 
-\begin{Verbatim}
-     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
+\begin{Verbatim}[fontsize=\small]
+ echo 0 | sudo tee 
+   /proc/sys/net/ipv4/tcp_moderate_rcvbuf
 \end{Verbatim}
@@
 
-\subsection{Repeating RADOS Scaling Test}
+\subsubsection{Repeating RADOS Scaling Test}
 
@@
 
-\section{Improving Ceph File System Performance}
-\label{sec:improve-ior}
+\subsection{Improving Ceph File System Performance}
+\label{sec:ceph-tuning-fs}
 
@@
 
-\subsection{Disabling Client CRC32}
+\subsubsection{Disabling Client CRC32}
 
@@
 
-\begin{Verbatim}
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
+\begin{Verbatim}[fontsize=\small]
+mount -t ceph 10.37.248.43:6789:/ 
+    /mnt/ceph -o name=admin,nocrc
 \end{Verbatim}
@@
 
-\subsection{Improving IOR Read Performance}
+\subsubsection{Improving IOR Read Performance}
 
@@
 
-\begin{Verbatim}[samepage=true]
-mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
-   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
+\begin{Verbatim}[samepage=true, fontsize=\small]
+mount -t ceph 10.37.248.43:6789:/ 
+  /mnt/ceph -o name=admin,nocrc,
+  readdir_max_bytes=4104304,
+  readdir_max_entries=8192
 \end{Verbatim}
@@
 
-\subsection{Repeating the IOR Scaling Test}
+\subsubsection{Repeating the IOR Scaling Test}
 
@@
 obervered with RADOS Bench.
+
+\subsection{Revisit Metadata Performance}
+
+Our previous results show that file creation rate is significantly lower than
+directory creation rate. Also, we conjectured two reasons: one is the file
+creation is associated with 1 MB data write and followed by a fsync operation.
+Another reason being that we obtained above results from early version of Ceph
+without all the tunings and improvement applied.
+
+Therefore, we repeated the same test on the latest CephFS 0.64. The result is
+illustrated in Figure~\ref{fig:mdtest-064-file-create}. As expected, we
+observed a significant improvement on the file creation rate. We also note
+that as number of clients increase, the file creation rate decreases rapidly,
+which suggested some form of lock contention. This presents some interesting
+issues to be investigated further.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=3.5in]{mdtest-064-file-create}
+\caption{mdtest of file creation on Ceph 0.64}
+\label{fig:mdtest-064-file-create}
+\end{figure}

### 2013-08-23 report.tex
fix typos

@@
 fault-tolerant parallel file system. Inktank is now the major developer behind
-the open-source parallel file system to sheperd its development and provide
+the open-source parallel file system to shepherd its development and provide
 commercial support.
@@
 discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
+interchangeably. We will emphasize with ``client'' prefix when we want to
 distinguish it from above.
@@
 However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
+expecting from the SFA10K (compare to the baseline block I/O performance number
 presented in Section~\ref{sec:block-io}).
@@
 would continue scaling with more clients and get closer to ~8 GB/s  we
-obervered with RADOS Bench.
+observed with RADOS Bench.
 
@@
 
-The results also show that file creation rate is signficantly lower than
+The results also show that file creation rate is significantly lower than
 directory creation rate. We stipulated two contributing factors: one is the file
@@
 This crush map is just an example of full OSD mapping. As we create and
-re-create different testbed subests with different OSD configurations, the map will
+re-create different testbed setups with different OSD configurations, the map will
 change accordingly.

### 2013-08-27 introduction.tex
changes to the introduction

--- 2013-08-23 introduction.tex
@@
 
-National Center for Computational Sciences (NCCS) runs one of the largest HPC
-storage system built on top of Lustre parallel file system. The latest
-installation of Spider II is designed to operate at over 1 TB/s peak
-throughput with 40 PB of raw capacity. As a scratch file system connected to a
-leadership computing platform at the scale of Titan, Spider II emphasizes
-\textit{capability} over \textit{capacity}. However, we also recognize that
-there are a wide variety of scientific data and workloads with different
-performance and data access requirements, e.g., RESTful interface, S3-like
-API, cloud solution integration, to name a few.
+Oak Ridge Leadership Computing Facility (OLCF) at Oak Ridge National Laboratory
+(ORNL) has a long history of deploying and running very-large-scale
+high-performance computing (HPC) systems~\cite{top500-ornl}. The facility
+hosted the Jaguar supercomputer up until recently, which was upgraded to the
+Titan supercomputer. In order to satisfy the I/O demand of such supercomputers
+(as well as, other OLCF computational, analysis, and visualization clusters),
+OLCF also hosts large-scale file and storage systems. Lustre has been OLCF's
+choice as the distributed parallel file system.  The latest incarnation of such
+large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II
+is the forklift-upgrade of its predecessor, Spider, which was deployed in 2008.
+Spider II, deployed in 20013, is designed to operate at over 1 TB/s peak
+aggregate I/O throughput and has a 40 PB of raw disk capacity. As the scratch
+file system connected to a leadership computing platform at the scale of Titan,
+Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
+also recognize that there are a wide variety of scientific data and workloads
+with different performance and data access requirements (e.g., RESTful
+interface, S3-like API, cloud solution integration) which might not be
+efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
+file and storage system technologies.
 
@@
 Cruz at 2007 and it was designed to be a reliable, scalable fault-tolerant
-parallel file system.  Inktank is now the major developer behind the
-open-source parallel file system to shepherd its development and provide
-commercial support.  In comparison to other parallel file systems, Ceph has a
-number of distinctive features:
+parallel file system.  Since then, Ceph has been open-sourced and Inktank is
+now the major developer behind it.  In comparison to other parallel file
+systems, Ceph has a number of distinctive features:
 
@@
 
-  \item From the start, Ceph's design anticipated managing metadata and the
-  name space with a cluster of metadata servers. It utilized a dynamic subtree
-  partitioning strategy to continuously adapt metadata distribution to current
+  \item From the start, Ceph's design anticipated managing meta data and the
+  name space with a cluster of meta data servers. It utilized a dynamic subtree
+  partitioning strategy to continuously adapt meta data distribution to current
   demands.
@@
   \item Ceph is built on top of a unified object management layer, RADOS. Both
-  metadata and the file data can take advantage of this uniformity. On top of
+  meta data and the file data can take advantage of this uniformity. On top of
   RADOS, Ceph build and project a host of other features such as RESTful
@@
 
-\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
-system easier to debug and maintain. The client-side support has long been
-integrated into Linux mainline kernel, which eases the deployment and out-of-box
-experience.
+  \item Most of the Ceph processes reside in user-space. Generally speaking,
+this makes the system easier to debug and maintain. The client-side support has
+long been integrated into Linux mainline kernel, which eases the deployment and
+out-of-box experience.
 
@@
 
-As interesting and feature-rich as Ceph may be, our environment and the sheer
-scale of its potential application drive us to first look into its scalability
-and performance.  As part of the study, we set up a dedicated testbed within
-NCCS for the Ceph file system evaluation. The goal of our study is to
-investigate the feasibility of using the Ceph for our future HPC storage
-deployment. This paper presents our experience, results, and observations.
-While evaluating our results, please keep in mind that Ceph is still a
-relatively \textit{young} parallel file system and its code base is changing
-rapidly. In between releases, we often experienced different stability and
-performance outcomes.  We will try to make clear in the writing when such
-changes occurred.
+As interesting and feature-rich as Ceph may be,  scalability and performance
+are our top priorities due to the unique requirements our environment.  As part
+of this study, we set up a dedicated testbed within OLCF to understand and
+evaluate Ceph.  Our goal was to investigate the feasibility of using the Ceph
+for our future HPC storage deployments. This paper presents our experience,
+results, and observations.  While evaluating our results, please keep in mind
+that Ceph is still a relatively \textit{young} parallel file system and its
+code base is changing rapidly. In between releases, we often experienced
+different stability and performance outcomes.  We will try to make clear in the
+writing when such changes occurred.
 
@@
 bottom up: from middle tier RADOS object layer to the file system-level and
-then metadata performance. In Section~\ref{sec:ceph-tuning} we highlight the
+then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
 investigative and tuning effort, we compare results before and after, and how

### 2013-08-27 testbed.tex
add paper flow and organization into introduction
updated the tesbed description

@@
 \section{Testbed Environment Description}
+\label{sec:testbed}
 
-We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
-evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
-various RAID levels by two active-active RAID controllers. The exported RAID
-groups by these controllers are driven by four hosts.
-Each host has two InfiniBand (IB) QDR connections to the storage backend.
-We used a single dualport Mellanox connectX IB card per host.
-By our calculation, this setup can saturate SFA10K's maximum theoretical
-throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
+We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
+evaluation. SFA10K organizes disks into various RAID levels by two
+active-active RAID controllers. The exported RAID groups (LUNs) by these
+controllers are driven by four server hosts (oss-[1-4]).  Each server host has two InfiniBand
+(IB) QDR connections to the storage backend.  We used a single dual-port
+Mellanox ConnectX IB QDR card per host.  By our calculation, this setup is
+adequate to drive the SFA10K at its maximum theoretical throughput (roughly 12
+GB/s). Server hosts and SFA10K connection diagram is illustrated in
 Figure~\ref{fig:ddn-sfa10k}.
@@
 
-Our Ceph testbed employs a collection of testing nodes. These nodes and their
-roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
-discussion, we use ``servers'', ``osd servers'', ``server hosts''
-interchangably. We will emphasize with ``client'' prefix when we want to
-distinguish it from above.
+Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
+10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
+has two SAS links per controller (four in total). The SATA and SAS disks in our
+testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
+disks per tray). Each SFA10K RAID controller has two RAID processors and each
+RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
+groups by the RAID processors (software RAID) and then exported to connected
+server hosts over the IB connections. Since each DDN SFA10K controller is a
+stand-alone computer system running Linux, CPU and memory affinity while
+organizing disks into RAID groups and exporting them is crucial for obtaining
+top performance out of an SFA10K system.
+
+Our Ceph testbed employs a collection of nodes, including the server hosts
+(oss-[1-4]). These nodes and their roles are summarized in
+Table~\ref{tbl:ceph-test-nodes}. In the following discussion, we use
+``servers'', ``osd servers'', ``server hosts'' interchangeably. We will
+emphasize with ``client'' prefix when we want to distinguish it from above.
 

### 2013-08-27 testbed.tex
more changes to section 2.

@@
 %\end{Verbatim}
+
+Our testing methodology is bottom to top. We start our evaluation from the
+lowest level (i.e. block-level) and work our way up to the top (i.e. file
+system-level). We establish an expected theoretical performance of a given
+hardware or software layer and then compare that with the observed results of
+our experiments. Each added new layer to the stack introduces new bottlenecks
+and re-defines the expected theoretical performance of the overall system. We
+will explain each component or layer and its expected performance before we
+present our observed results.
+
+Our tools for benchmarking and evaluating different layers also change as we go
+up the stack.  For example, a tool perfect for assessing block-level
+performance over a single server host might be completely inadequate for
+observing parallel file system performance over multiple clients. As we present
+our evaluations, we will also introduce and explain our benchmark tools, in
+this paper.

### 2013-08-27 testbed.tex
minor changes to section 2

@@
 Our testing methodology is bottom to top. We start our evaluation from the
-lowest level (i.e. block-level) and work our way up to the top (i.e. file
-system-level). We establish an expected theoretical performance of a given
-hardware or software layer and then compare that with the observed results of
-our experiments. Each added new layer to the stack introduces new bottlenecks
-and re-defines the expected theoretical performance of the overall system. We
-will explain each component or layer and its expected performance before we
-present our observed results.
+lowest level (i.e. block-level)  to establish a baseline performance and work
+our way up to the top (i.e. file system-level). We establish an expected
+theoretical performance of a given hardware or software layer and then compare
+that with the observed results of our experiments. Each added new layer to the
+stack introduces new bottlenecks and re-defines the expected theoretical
+performance of the overall system. We will explain each component or layer and
+its expected performance before we present our observed results.
 
 Our tools for benchmarking and evaluating different layers also change as we go
-up the stack.  For example, a tool perfect for assessing block-level
+up in the stack.  For example, a tool perfect for assessing block-level
 performance over a single server host might be completely inadequate for

### 2013-08-28 baseline.tex
add paper flow and organization into introduction
changes to the basline section

@@
-\section{Baseline Performance}
-\label{sec:block-io}
+\section{Establishing A Baseline Performance}
+\label{sec:baseline}
 
@@
 
-We first established baseline performance by measuring block I/O performance.
-At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
-following results as shown in Table~\ref{tbl:block-io-baseline}.
+The lowest layer in the system are the exposed LUNs to the server hosts from
+the RAID controllers.  These LUNs are mostly configured as a RAID6 8+2 array (8
+data disks and 2 \textit{P} and \textit{Q} disks). In our earlier tests we
+observed that a 7.2K RPM SAS disk can perform at ~140 MB/s for 128 kB
+sequential I/O requests and a 7.2K RPM SATA disk can do ~36 MB/s. For these
+tests, all disk caches were turned off. Therefore, in 8 data disk RAID group
+with 1 MB sequential I/O requests (each disks sees 128 kB chunks of the
+request) the expected aggregate performance would be ~1.12 GB/s for a SAS RAID
+group and ~288 MB/s for a SATA RAID group, if there are no caches along the I/O
+path.  With the caches turned on, especially the write-back cache on the DDN
+RAID controller, we observe a significant performance improvement. In our
+day-to-day HPC operations we run our storage systems with write-back cache
+turned on on RAID controllers, if and only if, there is a method of
+cache-mirroring between the two active-active RAID controllers to recover from
+a single controller failure scenario. With the write-back cache on we observe
+~1.4 GB/s per RAID 6 8+2 SAS group and ~955 MB/s per RAID 6 8+2 SATA group, for
+1 MB sequential I/O. These two performance numbers will be used as a baseline
+in our study and they are presented in Table~\ref{tbl:block-io-baseline}.  For
+these tests, the 8+2 RAID 6 groups are exported to the server hosts using SCSI
+RDMA Protocol (SRP) over IB protocol (which is the default for our normal HPC
+configurations). For a SATA disk group this translates into roughly 120
+MB/s/disk and for a SAS disk group it is 175 MB/s. As can be seen, SATA RAID
+groups benefit from caching more than SAS groups.
+
+For above tests the RAID groups are exported over physical 4x IB QDR links.
+These links can provide up to 40 Gbits/s signalling rate and 32 Gbits/s actual
+data rate (reduction is due to 8/10 encoding scheme). Therefore, each IB QDR
+link can perform at 3.2 GB/s, while in practice we see around 3 GB/s as the
+best case.
+
+As mentioned earlier, we had 280 SATA disks and 200 SAS disks. Organizing these
+into RAID 6 8+2 groups will yield 28 SATA and 20 SAS RAID 6 8+2 groups. We had
+4 server hosts in our testbed and evenly distributing these on to 4 server
+hosts translates into 8 SATA LUNs and 4 SAS LUNs per server host (when a RAID
+group is exported to a server host, it is labeled as a LUN from the server host
+point of view).
+
+Next, we established the baseline performance for a single server host. We
+exercised all seven SATA LUNs concurrently form a single server host at the
+block-level. This resulted in an aggregate performance of roughly 2.6 GB/s.
+Repeating the same test using only four SAS LUNs yielded around 2.8 GB/s
+aggregate performance for 1 MB sequential I/O. These two numbers will be used
+as single server host aggregate baseline performance for this study. These are
+also presented in presented in Table~\ref{tbl:block-io-baseline}.
+
+It is worth mentioning that we used our in-house developed synthetic benchmark,
+\textit{fair-lio} for all our block-level testing.  fair-lio has better
+sequential I/O characteristics compared to commonly used XDD benchmark and it
+is asynchronous and based on the Linux libaio library.
 
@@
 
-Single host in this table refers to one of four tick-oss nodes. Four tick-oss
-nodes drive the SFA10K backend storage. Overall, we observe that the entire
-system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
-12 GB/s.
+When exercising all 28 SATA LUNs from all four server hosts in parallel, we
+observed an 11 GB/s aggregate performance. Same level of performance was
+observed using all 20 SAS LUNs from four server hosts in parallel. Comparing
+these to the advertised peak performance of 12 GB/s of the DDN SFA10K, we
+concluded that our test setup is well configured to drive the backend disk
+system at full performance and we are limited by the RAID controller
+performance. Going forward in this study, 11 GB/s will be used the peak
+baseline for the entire test configuration.
 
-\subsection{IP over IB}
+\subsection{Establishing an IP over IB Baseline Performance}
 
 Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
-Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
-networking\footnote{As of writing of this report, Inktank is investigating using
-rsockets to improve performance with IB fabric}. Through simple
-\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
-IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
-from Mellanox). With all four hosts (OSD servers), we expect the aggregate
-throughput to be in the neighborhood of 10 GB/s.
+Because our entire testbed is built on IB QDR fabric (including client to
+server host connections over a 108-port Mellanox IB QDR switch), we used IP
+over IB (IPoIB) for networking\footnote{As of writing of this report, Inktank
+is investigating using rsockets to improve performance with IB fabric}. Through
+simple \verb!netperf! tests, we observed that a pair of hosts connected by IB
+QDR using IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per
+recommendations from Mellanox). With all four server hosts (OSD servers), we
+expect the aggregate throughput to be in the neighborhood of 11 GB/s.
 

### 2013-08-28 ceph-initial.tex
changes here and there

@@
 perform a sync operation.  This is a more realistic use case scenario than just
-open, close and removal sequence of metadata operations.
+open, close and unlink sequence of metadata operations.
 
-\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
-clients, the total number of files and directories in the workload is 8,000. Since we did not specify
-either \verb!-D! or \verb!-F!, this is a mixture of both.
+\item \verb!-n 1000!: Per client file \textit{and} directory workload. For
+eight clients, the total number of files and directories in the workload is
+8,000. Since we did not specify either \verb!-D! (indicates a directory only
+workload) or \verb!-F! (indicates a file only workload), this is a mixture of
+both directory and file workloads.
 
@@
 \item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories.
+this option, we are exercising unique directories per test client processes.
 
@@
 
-\item While the other operations seems unaffected or flat by the number of
-clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
-\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
-contention for shared directory. The performance degradation amount to 50\% or
-more.
+\item While the other operations seems unaffected or performance remains the
+same by the number of clients, it is not so if we zoom in, see
+figures \ref{fig:mdtest-fcreate} and \ref{fig:mdtest-dcreate}:  as number of clients
+increases, we observed the contention for shared directory. The performance
+degradation amount to 50\% or more.
 

### 2013-08-28 ceph-tuning.tex
changes here and there

@@
 
-We ran a script written by Inktank for internal Ceph testing to perform
-sweeps over Ceph configuration parameters to examine how different
-tuning options affect performance on the DDN platform. The result of this
-parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
-to Appendix E for explanations of these probed parameters.
+We swept over Ceph configuration parameters to examine how different tuning
+options affect performance on the DDN platform. The result of this parameter
+probing is illustrated in Figure~\ref{fig:parametric}. Please refer to Appendix
+E for explanations of these probed parameters.
 
@@
 
-During these tests, a trend that previously had been seen became more
-apparent.  During reads, there were periods of high performance followed by
-periods of low performance or outright stalls that could last for up to 20
-seconds at a time.  After several hours of diagnostics, Inktank observed that
-outstanding operations on the clients were not being shown as outstanding on
-the OSDs.  This appeared to be very similar to a problem Jim Schutt at Sandia
-National labs encountered with TCP autotuning in the Linux
+During these tests, a trend that previously had been seen became more apparent.
+During reads, there were periods of high performance followed by periods of low
+performance or outright stalls that could last for up to 20 seconds at a time.
+After running diagnostics, we observed that outstanding operations on the
+clients were not being shown as outstanding on the OSDs.  This appeared to be
+very similar to a problem Jim Schutt at Sandia National labs encountered with
+TCP autotuning in the Linux
 kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
-TCP auto tuning enables TCP window scaling by default and automatically
-adjusts the TCP receive window for each connection based on link conditions
-such as bandwidth delay product. We have observed this will make a notable
-improvement on Ceph read performance, as the results shown in
+TCP auto tuning enables TCP window scaling by default and automatically adjusts
+the TCP receive window for each connection based on link conditions such as
+bandwidth delay product. We have observed this improving the performance
+significantly on Ceph read operations, as the results shown in
 Figure~\ref{fig:rados-tcp-auto-disabled}.
 
-Luckily, the fix was fairly straight forward by issuing the following command on all nodes:
+Luckily, the fix was fairly straight forward by issuing the following command
+on all nodes:
 
@@
 Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.  The testing at ORNL directly influenced and motivated the creation
-of this feature!
+buffer size.
 

### 2013-08-28 introduction.tex
fixed ORNL TOP500 footnote

@@
 (ORNL) has a long history of deploying and running very-large-scale
-high-performance computing (HPC) systems~\cite{top500-ornl}. The facility
-hosted the Jaguar supercomputer up until recently, which was upgraded to the
-Titan supercomputer. In order to satisfy the I/O demand of such supercomputers
-(as well as, other OLCF computational, analysis, and visualization clusters),
-OLCF also hosts large-scale file and storage systems. Lustre has been OLCF's
-choice as the distributed parallel file system.  The latest incarnation of such
+high-performance computing (HPC)
+systems~\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
+the Jaguar supercomputer up until recently, which was upgraded to the Titan
+supercomputer. In order to satisfy the I/O demand of such supercomputers (as
+well as, other OLCF computational, analysis, and visualization clusters), OLCF
+also hosts large-scale file and storage systems. Lustre has been OLCF's choice
+as the distributed parallel file system.  The latest incarnation of such
 large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II

### 2013-08-28 ceph-initial.tex
changes here and there, again

@@
 
-We used the synthetic IOR benchmark suite for file system level performance
-and scalability test.  The particular parameter setup is show in Table
-\ref{tbl:ior}. Each client node has 6 GB of physical memory, the block size is
-set so as to mitigate cache effects. In addition, the test harness program
-issues the following commands at the beginning of each test:
+We used the synthetic IOR benchmark
+suite\footnote{\url{http://sourceforge.net/projects/ior-sio/}} for file system
+level performance and scalability test.  The particular parameter setup is show
+in Table \ref{tbl:ior}. Each client node has 6 GB of physical memory, the block
+size is set so as to mitigate cache effects. In addition, the test harness
+program issues the following commands at the beginning of each test:
 
@@
 performance and exercise it with up to 8 clients to observe the single MDS
-performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
-used for this test are:
+performance scaling. We used
+mdtest\footnote{\url{http://sourceforge.net/projects/mdtest/}} as our benchmark
+tool. Mdtest parameters used for this test are:
 

### 2013-08-28 ceph-tuning.tex
changes here and there, again

@@
 underlying object store could get to the node hardware limitations as the number
-of OSDs/LUNs used on the node increased. Note all the tests performed were against
+of OSDs/LUNs used on the node increased. All the tests performed were against
 XFS-formatted storage.
@@
 \includegraphics[width=3.5in]{rados-064-osd}
-\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
+\caption{RADOS Bench Scaling on number of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
 \label{fig:rados-064-osd}
@@
 In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
-(including Journals)'' refers to how much data is actually being written out the
-DDN chasis, and blue line is how much data the clients are writing.
-We observe that performance gets very close to the hardware limits at roughly 9
-OSDs per server and then mostly levels out.
+(including Journals)'' refers to how much data is actually being written out
+the DDN SFA10K (observed directly from the controllers), and blue line is how
+much data the clients are writing.  We observe that performance observed by the
+DDN controllers gets very close to the hardware limits at roughly 9 OSDs per
+server and then mostly levels out.
 
@@
 Profiling with \verb!perf! showed high CPU utilization on test clients due to
-crc32c processing in the Ceph kernel client.  crc32 checksums can be disabled
+CRC32c processing in the Ceph kernel client.  CRC32 checksums can be disabled
 by changing the CephFS mount options:
@@
 
-Deeper analysis with perf showed that there was heavy lock contention during
+Deeper analysis with \verb!perf! showed that there was heavy lock contention during
 parallel compaction in the Linux kernel memory manager.  This behavior was first
@@
 write performance, read performance improved dramatically.  In addition to the
-kernel change, Sage Weil from InkTank suggested increasing the amount of CephFS
-client kernel read-ahead cache size as:
+kernel change, the amount of CephFS
+client kernel read-ahead cache size was improved as:
 
@@
 
-By installing a newer kernel, increasing read-ahead cache size, and increasing the number of
-client IOR processes, we were able to achieve very satisfactory I/O performance.
+By installing a newer kernel, increasing read-ahead cache size, and increasing
+the number of client IOR processes, we were able to achieve very satisfactory
+I/O performance at the Ceph file system-level.
 
@@
 
-As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
-These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we saw
-saw  improved read and write performance. These new read and write performance are in
-line with observed RADOS bench performance.
+As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4
+MB.  These results are illustrated in Figure~\ref{fig:ior-064}, respectively.
+As expected, we saw saw  improved read and write performance. These new read
+and write performance are in line with observed RADOS bench performance.
 
@@
 temporarily degrading.  Despite these issues, performance generally seems to be
-improving with respect to increasing number of clients.  Writes seem to be topping out at
-around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
+improving with respect to increasing number of clients.  Writes seem to be
+topping out at around 5.2 GB/s (which is roughly what we would expect due to
+journalling effectively halving the write performance).  Reads seem to be
 topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to ~8 GB/s  we
-obervered with RADOS Bench.
+would continue scaling with more clients and get closer to ~8 GB/s we observed 
+with RADOS Bench.
 
-\subsection{Revisit Metadata Performance}
+\subsection{Revisiting Metadata Performance}
 
@@
 directory creation rate. Also, we conjectured two reasons: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation.
-Another reason being that we obtained above results from early version of Ceph
-without all the tunings and improvement applied.
+creation is associated with 1 MB data write and followed by a \verb!fsync!
+operation.  Another reason being that we obtained above results from early
+version of Ceph without all the tunings and improvement applied.
 

### 2013-08-28 conclusion.tex
add paper flow and organization into introduction
changes here and there, again

@@
 \section{Observations and Conclusions}
+\label{sec:conclusion}
 
@@
 in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
-devices through SCSI Request Protocol (SRP) over IB. The journaling write
-requires twice the bandwidth compare to Lustre-like metadata-only journaling
-mechanism. For Ceph to be viable in this facility, journaling operations will
-need to further design and engineering.
+devices through IB over SRP protocol. The journaling write requires twice the
+bandwidth compared to Lustre-like meta data-only journaling mechanism. For Ceph
+to be viable in large-scale capability HPC environments like ours, journaling
+operations will need to further design and engineering.
 

### 2013-08-28 src/ceph-test.py
add test script

@@ -1,0 +1,397 @@
+#!/chexport/users/fwang2/python/bin/python
+
+import argparse
+import os
+import time
+import subprocess
+import yaml
+import shutil
+import sys
+
+global ior_config, cluster_config, mpi_config, mdtest_config
+
+IOR_cmd = "/chexport/users/fwang2/bin/IOR"
+MDTEST_cmd = "/chexport/users/fwang2/bin/mdtest"
+INIT_cmd = "/chexport/users/nhm/apps/bin/ceph-init"
+CEPH_cmd = "/chexport/users/nhm/local/bin/ceph"
+MKCEPHFS_cmd = "/chexport/users/nhm/local/sbin/mkcephfs"
+MPI_cmd = "mpirun"
+MON_addr = "10.37.248.43:6789"
+
+def parse_args():
+    parser = argparse.ArgumentParser(description="IOR Test")
+    parser.add_argument('--iorconf', nargs=1, default="ior.yaml", help = "YAML config file")
+    parser.add_argument('--cephconf', nargs=1, default="default.ceph.conf",
+            help="Default ceph configuration file")
+
+    action = parser.add_mutually_exclusive_group(required=True)
+
+    action.add_argument("--mount", action="store_true", help = "Mount cephfs")
+    action.add_argument("--umount", action="store_true", help = "Umount cephfs")
+    action.add_argument("--rebuild", action="store_true", help = "Setup Ceph from scratch")
+    action.add_argument("--tuneup", action="store_true", help = "Tuneup parameters for Ceph cluster")
+    action.add_argument("--restart", action="store_true", help = "Start up Ceph")
+    action.add_argument("--reboot-clients", action="store_true", help = "Reboot Ceph clients")
+    action.add_argument("--shutdown", action="store_true", help = "Shutdown Ceph")
+    action.add_argument("--runtests", action="store_true", help = "Run IOR tests")
+    action.add_argument("--distconf", action="store_true", help = "Distribute Ceph configuration file")
+    action.add_argument("--checkfs", action="store_true", help = "Check cephfs health")
+    action.add_argument("--mdtest", action="store_true", help = "CephFS metadata test")
+
+    args = parser.parse_args()
+
+    print args
+
+    return args
+
+
+def pdsh(nodes, command):
+    args = ['pdsh', "-w", nodes, command]
+    print('pdsh: %s' % args)
[…]

### 2013-08-28 src/xdd-run.py

@@ -1,0 +1,137 @@
+#!/chexport/users/fwang2/python/bin/python
+
+
+import argparse
+import os
+import time
+import subprocess
+import yaml
+import shutil
+import sys
+import shlex
+
+from tcommons import *
+
+global config
+
+XDD_cmd = "/chexport/users/fwang2/bin/xdd"
+MPI_cmd = "mpirun"
+
+def parse_args():
+    parser = argparse.ArgumentParser(description="XDD Test")
+    parser.add_argument('config_file', help = "YAML config file")
+
+    args = parser.parse_args()
+    return args
+
+
+def pdsh(nodes, command):
+    args = ['pdsh', '-R', "ssh", "-w", nodes, command]
+    print('pdsh: %s' % args)
+    return subprocess.Popen(args, stdout=subprocess.PIPE,
+            stderr=subprocess.PIPE)
+
+def pdcp(nodes, flags, localfile, remotefile):
+    args=['pdcp', '-R', 'ssh', '-w', nodes, localfile, remotefile]
+    if flags:
+        args=['pdcp', '-R', 'ssh', '-w', nodes, flags, localfile, remotefile]
+
+    return subprocess.Popen(args, stdout=subprocess.PIPE,
+            stderr=subprocess.PIPE)
+
+def read_config(config_file):
+    config = {}
+    try:
+        with file(config_file) as f:
+            g = yaml.safe_load_all(f)
+            for new in g:
+                config.update(new)
+    except IOError, e:
+        raise argparse.ArgumentTypeError(str(e))
+
+    return config
+
+def make_remote_dir(remote_dir):
+    print 'Making remote directory: %s' % remote_dir
+    head = cluster_config['head']
+    pdsh(head, 'mkdir -p -m0755 -- %s' % remote_dir)
+
+def init_datafile():
+    dir = config.get('outdir', '/tmp')
+    if not os.path.exists(dir):
+        os.makedirs(dir)
+
+    filename = time.strftime("xdd.%Y.%m%d.%H%M.%S.dat")
+    path = os.path.join(config['outdir'], filename)
+    with open(path, "w") as f:
+        f.write("mode,\t qd,\treqsize,\t dev.num,\t bw\n")
+
+    return path
+
+def create_local_file(target, size):
+    ''' note the test file name is fixed on tfile '''
+    target = target.strip()
[…]

### 2013-08-28 src/ceph-client-mount.sh
add a few maybe out-of-date scripts

@@ -1,0 +1,6 @@
+#!/bin/bash
+#pdsh -w sppon[37-41] "umount /mnt/cephfs"
+pdsh -w spoon[37-41] "mkdir -p /mnt/cephfs"
+pdsh -w spoon[37-41] "mount -t ceph 172.30.248.51:6789:/ /mnt/cephfs -o name=admin,secret=AQDiPNtQiFVwKhAA5Li8SW5W+ZgVD/NXnYMXIw=="
+pdsh -w spoon[37-41] "ls -l /mnt/cephfs" | dshbak -c
+

### 2013-08-28 src/ceph-format-storage.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+host=`hostname -s`
+for i in /dev/mapper/${host}-storage*; do
+   umount $i
+   echo "mkfs.xfs -f -i size=1024 -b size=4k -d sunit=256,swidth=2048 $i"
+   mkfs.xfs -f -i size=1024 -b size=4k -d sunit=256,swidth=2048 $i
+done

### 2013-08-28 src/ceph-mount-storage.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+# Mounts the storage and makes convenient device links for the 
+# devices that ceph osds use
+host=`hostname -s`
+for i in 0 1 2 3 4 5; do 
+   echo mkdir -p /mnt/ceph/storage${i}
+   mkdir -p /mnt/ceph/storage${i}
+   echo mount -t xfs -o noatime,nobarrier,inode64 /dev/mapper/${host}-storage${i} /mnt/ceph/storage${i}
+   mount -t xfs -o noatime,nobarrier,inode64 /dev/mapper/${host}-storage${i} /mnt/ceph/storage${i}
+   echo ln -s /dev/mapper/${host}-storage${i} /dev/ceph-storage${i}
+   ln -sf /dev/mapper/${host}-storage${i} /dev/ceph-storage${i}
+   echo ln -s /dev/mapper/${host}-journal${i} /dev/ceph-journal${i}
+   ln -sf /dev/mapper/${host}-journal${i} /dev/ceph-journal${i}
+done

### 2013-08-28 introduction.tex
addded the boilerplate text

--- 2013-08-27 introduction.tex
@@
 
-Oak Ridge Leadership Computing Facility (OLCF) at Oak Ridge National Laboratory
-(ORNL) has a long history of deploying and running very-large-scale
-high-performance computing (HPC) systems~\cite{top500-ornl}. The facility
-hosted the Jaguar supercomputer up until recently, which was upgraded to the
-Titan supercomputer. In order to satisfy the I/O demand of such supercomputers
-(as well as, other OLCF computational, analysis, and visualization clusters),
-OLCF also hosts large-scale file and storage systems. Lustre has been OLCF's
-choice as the distributed parallel file system.  The latest incarnation of such
+Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
+supported by, and used the resources of, the Oak Ridge Leadership Computing
+Facility, located in the National Center for Computational Sciences at ORNL,
+which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
+DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
+of deploying and running very-large-scale high-performance computing (HPC)
+systems~\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
+the Jaguar supercomputer up until recently, which was upgraded to the Titan
+supercomputer. In order to satisfy the I/O demand of such supercomputers (as
+well as, other OLCF computational, analysis, and visualization clusters), OLCF
+also hosts large-scale file and storage systems. Lustre has been OLCF's choice
+as the distributed parallel file system.  The latest incarnation of such
 large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II

### 2013-08-28 introduction.tex
minor fix

@@
 of deploying and running very-large-scale high-performance computing (HPC)
-systems~\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
+systems\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
 the Jaguar supercomputer up until recently, which was upgraded to the Titan

### 2013-08-28 src/check_tick.sh
add missing shell and config files

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+pdsh -w tick-oss[1-4] 'for i in $(ls /dev/sd*); do echo -n "$i "; \
+    /chexport/users/hilljj/sbin/ddn_prio_alua $i; done' | dshbak -c
+
+#printf "Checking mpath tuning parameters\n"
+#pdsh -w tick-oss[1-4] "cat /sys/block/dm-1/queue/scheduler" | dshbak -c

### 2013-08-28 src/setqp.py

@@ -1,0 +1,40 @@
+#!/chexport/users/fwang2/python/bin/python
+
+import os
+import fnmatch
+import argparse
+
+def parse_args():
+    parser = argparse.ArgumentParser(description='Continuously run ceph tests.')
+    parser.add_argument(
+        'param',
+        help = 'The param to set',
+        )
+    parser.add_argument(
+        'value',
+        help = 'The value to set',
+        )
+    args = parser.parse_args()
+    return args
+
+ctx = parse_args()
+path = "/dev/mapper"
+listing = os.listdir(path)
+devs = []
+for infile in listing:
+    infile = os.path.join(path, infile)
+    if fnmatch.fnmatch(infile, '*tick*') and os.path.islink(infile):
+        dev = os.path.realpath(infile)
+#        dev = filter(lambda c: not c.isdigit(), os.path.realpath(infile))
+        devs.append(dev.split('/')[-1])
+
+devs = list(set(devs))
+
+for dev in devs:
+    f = open("/sys/block/%s/queue/%s" % (dev,ctx.param), "r+")
+    print "old: %s, %s" % (dev, f.read())
+    f.write(ctx.value)
+    f.seek(0,0)
+    print "new: %s, %s" % (dev, f.read())
+    f.close()
+

### 2013-08-29 src/makecephconf.py
import mark's initial code

@@ -1,0 +1,128 @@
+#!/ccs/home/nhm/apps/bin/python
+import argparse
+import os
+import subprocess
+import sys
+import yaml
+import time
+import copy
+
+def read_config(config_file):
+    config = {}
+    try:
+        with file(config_file) as f:
+            g = yaml.safe_load_all(f)
+            for new in g:
+                config.update(new)
+    except IOError, e:
+        raise argparse.ArgumentTypeError(str(e))
+    return config
+
+def parse_args():
+    parser = argparse.ArgumentParser(description='Continuously run ceph tests.')
+    parser.add_argument(
+        '--target',
+        required = True,
+        help = 'Directory where the config files should go.',
+        )
+    parser.add_argument(
+        'config_file',
+        help = 'YAML config file.',
+        )
+    args = parser.parse_args()
+    return args
+
+def populate(l, name, value):
+    name = name.replace("_", " ")
+    l.append("        %s = %s" % (name, value))
+
+def mkosds(lists, yaml):
+    i = 0
+    for server in yaml.get('osd_servers', []):
+        for j in xrange(0, yaml.get('osds_per_server', 0)):
+#            for k in xrange(0, yaml.get('osds_per_device', 0)):
+                name = "osd.%d" % i
+                lists[name] = []
+                lists[name].append("        host = %s" % server)
+                lists[name].append("        osd data = /mnt/osd-device-%d-data" % j)
+#                lists[name].append("        osd journal = /dev/mapper/%s-sata-l%d" % (server, j + yaml.get('osds_per_server', 0)))
+                lists[name].append("        osd journal = /mnt/osd-device-%d-data/journal" % j)
+                i += 1
+
+def writescript(f, param, value, conf):
+    for fs,rtconf in sorted(runtests_conf.iteritems()):
+        pdir = param
+        if value:
+            pdir = "%s_%s"  % (param, value)
+        f.write("%s --conf %s --archive %s/%s/%s %s\n" % (runtests_exec, conf, outdir, fs, pdir, rtconf))
+
+def parametric(lists, yaml):
+    if "global" not in lists:
+        lists["global"] = []
+    scriptname = "%s/runme.sh" % target
+    f = open(scriptname,'w')
+    f.write("#!/bin/bash\n")
+
+    # the default
+    filename = "%s/default.ceph.conf" % target
+    writefile(lists, filename)
+    writescript(f, "default", "", filename)
+
+    for param,value in sorted(yaml.iteritems()):
[…]

### 2013-08-29 src/runtests.py

@@ -1,0 +1,504 @@
+#!/ccs/home/nhm/apps/bin/python
+import argparse
+import os
+import subprocess
+import sys
+import yaml
+import time
+import shutil
+
+ceph_cmd = "/chexport/users/nhm/local/bin/ceph"
+mkcephfs_cmd = "/chexport/users/nhm/local/sbin/mkcephfs"
+cephosd_cmd = "/chexport/users/nhm/local/bin/ceph-osd"
+cephmon_cmd = "/chexport/users/nhm/local/bin/ceph-mon"
+rados_cmd = "/chexport/users/nhm/local/bin/rados"
+mds_cmd = "/chexport/users/nhm/local/bin/ceph-mds"
+
+#ceph_cmd = "/usr/local/bin/ceph"
+#mkcephfs_cmd = "/usr/local/sbin/mkcephfs"
+#cephosd_cmd = "/usr/local/bin/ceph-osd"
+#cephmon_cmd = "/usr/local/bin/ceph-mon"
+#rados_cmd = "/usr/local/bin/rados"
+
+head = ''
+clients = ''
+servers = ''
+mons = ''
+rgws = ''
+mds = ''
+
+iterations = sys.maxint
+rebuild_every_test = False
+osds_per_node = 0 
+user = 'nhm'
+
+def get_nodes(nodes):
+    seen = {}
+    ret = ''
+    for node in nodes:
+        if node and not node in seen:
+            if ret:
+                ret += ','
+            ret += '%s' % node
+            seen[node] = True
+#    print ret
+#    ret = ','.join(set(ret.split(',')))
+#    print ret
+    return ret
+
+def pdsh(nodes, command):
+    args = ['pdsh', '-R', 'ssh', '-w', nodes, command]
+    print('pdsh: %s' % args)
+    return subprocess.Popen(args, stdout=subprocess.PIPE, stderr=subprocess.PIPE)
+
+def ORNL_sudopdsh(nodes, command):
+    nodeslist = nodes.split(",")
+    i = 0
+    sudocommand = "if "
+    for node in nodeslist: 
+        # Stripe off the username and @ symbol if present
+        node = node.rpartition("@")[2]
+        if i != 0:
+            sudocommand += " || "
+        i += 1
+        sudocommand += "[[ `hostname -s` = %s ]]" % node
+    sudocommand += "; then %s; fi" % command
+
+    args = ['sudo', 'pdsh', '-g', 'ceph',  sudocommand]
+    print sudocommand    
[…]

### 2013-08-29 src/runtests.py
fix runtests.py to run as root, add needed ceph.conf as well

@@ -64,7 +64,8 @@ def ORNL_sudopdsh(nodes, command):
         sudocommand += "[[ `hostname -s` = %s ]]" % node
     sudocommand += "; then %s; fi" % command
 
-    args = ['sudo', 'pdsh', '-g', 'ceph',  sudocommand]
+    #args = ['sudo', 'pdsh', '-g', 'ceph',  sudocommand]
+    args = ['pdsh', '-g', 'ceph',  sudocommand]
     print sudocommand    
     return subprocess.Popen(args, stdout=subprocess.PIPE, stderr=subprocess.PIPE)
 

### 2013-08-29 src/makecephconf.py
fix /tmp/mnt in makecephconf.py

@@ -44,9 +44,9 @@ def mkosds(lists, yaml):
                 name = "osd.%d" % i
                 lists[name] = []
                 lists[name].append("        host = %s" % server)
-                lists[name].append("        osd data = /mnt/osd-device-%d-data" % j)
+                lists[name].append("        osd data = /tmp/mnt/osd-device-%d-data" % j)
 #                lists[name].append("        osd journal = /dev/mapper/%s-sata-l%d" % (server, j + yaml.get('osds_per_server', 0)))
-                lists[name].append("        osd journal = /mnt/osd-device-%d-data/journal" % j)
+                lists[name].append("        osd journal = /tmp/mnt/osd-device-%d-data/journal" % j)
                 i += 1
 
 def writescript(f, param, value, conf):

### 2013-08-29 src/run-1-server-osd_scaling.sh
add osd scaling script

@@ -1,0 +1,28 @@
+
+#!/bin/bash
+
+rm -rf ../raw/1-node-3-osd
+rm -rf ../raw/1-node-5-osd
+rm -rf ../raw/1-node-7-osd
+rm -rf ../raw/1-node-9-osd
+rm -rf ../raw/1-node-11-osd
+
+
+./makecephconf.py --target . 1_server_osd_scaling/1-node-3-osd.yaml
+./runme.sh
+
+./makecephconf.py --target . 1_server_osd_scaling/1-node-5-osd.yaml
+./runme.sh
+
+./makecephconf.py --target . 1_server_osd_scaling/1-node-7-osd.yaml
+./runme.sh
+
+./makecephconf.py --target . 1_server_osd_scaling/1-node-9-osd.yaml
+./runme.sh
+
+./makecephconf.py --target . 1_server_osd_scaling/1-node-11-osd.yaml
+./runme.sh
+
+
+
+

### 2013-08-29 data/gen.sh
update bar drawing to be the same style

@@ -10,3 +10,8 @@ Rscript plotxdd.R xdd-write.csv write
 
 # generate RADOS bench result for different replication level
 Rscript plot_replication.R 
+
+Rscript plot_autotune.R rados-4s-4c-autotune-disabled.csv autotune-disabled.pdf
+Rscript plot_autotune.R rados-4s-4c-autotune-enabled.csv autotune-enabled.pdf
+
+Rscript plot_ior_no_crc.R ior_no_crc.pdf

### 2013-08-29 data/plot_autotune.R

@@ -1,0 +1,48 @@
+library("ggplot2")
+
+plot_autotune <- function (inf, outf) {
+
+# read data, skip comments
+df = read.csv(inf, comment.char = "#", strip.white = TRUE)
+
+quartz(type="pdf", file=outf, width=10, height=6)
+theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
+
+
+g = ggplot(df, aes(x=filesystem, y=bw, fill=factor(mode))) +
+    geom_bar(stat="identity", position="dodge", color="black") +
+    scale_fill_brewer(type="qual", palette=1)
+
+
+
+# g = g + theme((aspect.ratio=1)
+
+
+# g = g + ggtitle("RADOS bench throughput \n with different replication levels\n")
+g = g + xlab("\nOSD File System") + ylab("Throughput (MB /s) \n")
+
+# change legend position
+g = g + theme(legend.position="top")
+
+# hide the legend title
+g = g + guides(fill=guide_legend(title=NULL))
+
+# make more breaks along Y
+g = g + scale_y_continuous(breaks=seq(0, 6000,1000))
+
+# change grid line display
+#g = g + theme(panel.grid.major = element_line(color="grey80", size = 0.7, linetype = "dashed"))
+#g = g + theme(panel.grid.minor = element_line(color="grey80", size = 0.7, linetype = "dotted"))
+
+
+
+print(g)
+dev.off()
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+print(args)
+options(warn=-1)
+plot_autotune(args[1], args[2])
+         

### 2013-08-29 data/plot_ior_kernel_change.R

@@ -1,0 +1,48 @@
+library("ggplot2")
+
+myplot <- function (inf, outf) {
+
+# read data, skip comments
+df = read.csv(inf, comment.char = "#", strip.white = TRUE)
+
+quartz(type="pdf", file=outf, width=10, height=6)
+theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
+
+
+g = ggplot(df, aes(x=mode, y=bw, fill=factor(mode))) +
+    geom_bar(stat="identity", position="dodge", color="black", width=0.5) +
+    scale_fill_brewer(type="qual", palette=1)
+
+
+
+# g = g + theme((aspect.ratio=1)
+
+
+g = g + xlab("\n16GB BlockSize, 4 MB Read Ahead, 8 Client Nodes") + ylab("Throughput (MB /s) \n")
+
+# change legend position
+g = g + theme(legend.position="top")
+#g = g + coord_fixed(ratio=5)
+
+# hide the legend title
+g = g + guides(fill=guide_legend(title=NULL))
+
+# make more breaks along Y
+g = g + scale_y_continuous(breaks=seq(0, 9000,1000))
+
+# change grid line display
+#g = g + theme(panel.grid.major = element_line(color="grey80", size = 0.7, linetype = "dashed"))
+#g = g + theme(panel.grid.minor = element_line(color="grey80", size = 0.7, linetype = "dotted"))
+
+
+
+print(g)
+dev.off()
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+print(args)
+options(warn=-1)
+myplot(args[1], args[2])
+         

### 2013-08-29 data/plot_ior_no_crc.R

@@ -1,0 +1,48 @@
+library("ggplot2")
+
+plot_no_client_crc <- function (inf, outf) {
+
+# read data, skip comments
+df = read.csv(inf, comment.char = "#", strip.white = TRUE)
+
+quartz(type="pdf", file=outf, width=10, height=6)
+theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
+
+
+g = ggplot(df, aes(x=clients, y=bw, fill=factor(mode))) +
+    geom_bar(stat="identity", position="dodge", color="black") +
+    scale_fill_brewer(type="qual", palette=1)
+
+
+
+# g = g + theme((aspect.ratio=1)
+
+
+# g = g + ggtitle("RADOS bench throughput \n with different replication levels\n")
+g = g + xlab("\nClient Nodes") + ylab("Throughput (MB /s) \n")
+
+# change legend position
+g = g + theme(legend.position="top")
+
+# hide the legend title
+g = g + guides(fill=guide_legend(title=NULL))
+
+# make more breaks along Y
+g = g + scale_y_continuous(breaks=seq(0, 6000,1000))
+
+# change grid line display
+#g = g + theme(panel.grid.major = element_line(color="grey80", size = 0.7, linetype = "dashed"))
+#g = g + theme(panel.grid.minor = element_line(color="grey80", size = 0.7, linetype = "dotted"))
+
+
+
+print(g)
+dev.off()
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+print(args)
+options(warn=-1)
+plot_no_client_crc(args[1], args[2])
+         

### 2013-08-29 data/plot_rados_kernel_change.R

@@ -1,0 +1,49 @@
+library("ggplot2")
+
+myplot <- function (inf, outf) {
+
+# read data, skip comments
+df = read.csv(inf, comment.char = "#", strip.white = TRUE)
+
+quartz(type="pdf", file=outf, width=10, height=6)
+theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
+
+
+g = ggplot(df, aes(x=kernel, y=bw, fill=factor(mode))) +
+    geom_bar(stat="identity", position="dodge", color="black") +
+    scale_fill_brewer(type="qual", palette=1)
+
+
+
+# g = g + theme((aspect.ratio=1)
+
+
+# g = g + ggtitle("RADOS bench throughput \n with different replication levels\n")
+g = g + xlab("\nOSD File System") + ylab("Throughput (MB /s) \n")
+
+# change legend position
+g = g + theme(legend.position="top")
+#g = g + coord_fixed(ratio=5)
+
+# hide the legend title
+g = g + guides(fill=guide_legend(title=NULL))
+
+# make more breaks along Y
+g = g + scale_y_continuous(breaks=seq(0, 9000,1000))
+
+# change grid line display
+#g = g + theme(panel.grid.major = element_line(color="grey80", size = 0.7, linetype = "dashed"))
+#g = g + theme(panel.grid.minor = element_line(color="grey80", size = 0.7, linetype = "dotted"))
+
+
+
+print(g)
+dev.off()
+}
+
+
+args = commandArgs(trailingOnly = TRUE)
+print(args)
+options(warn=-1)
+myplot(args[1], args[2])
+         

### 2013-08-29 abstract.tex
minor changes
fix the flow and minor typos

@@
 In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
-technology for high-performance computing (HPC) environments.  This paper
+technology for scientific high-performance computing (HPC) environments.  This paper
 presents our evaluation methodology, experiments, results and observations from
@@
 large. Throughout the evaluation, we observed that Ceph still is an evolving
-technology under fast-paced development and showing with great promises.
+technology under fast-paced development and showing great promises.
 

### 2013-08-29 ceph-initial.tex
fix the flow and minor typos

@@
-\section{Ceph Evaluation: Initial Results}
+\section{Ceph Evaluation: Initial Results and Tunings}
 \label{sec:ceph-initial}
@@
 
-We observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client processes 
-with 32 concurrent 4 MB objects in flight each. We created a pool for
-each RADOS Bench process to ensure that object reads come from independent pools
-(RADOS Bench is not smart enough to ensure that objects are not read by multiple
-processes and thus possibly cached).  A sync and flush is performed on every
-node before every test to ensure no data or metadata is in cache.  All tests
-were run with replication set to one.  The backend file systems were XFS,
-BTRFS and EXT4 file systems were not tested at this time.
+\subsubsection{Disable TCP autotuning}
+
+\begin{figure}[htb]
+\centering
+%\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
+\includegraphics[width=3.5in]{autotune-enabled}
+\caption{Evaluating RADOS bench \textbf{with} TCP auto tuning, 4 servers, 4
+clients, 4 MB I/O}
+\label{fig:rados-tcp-autotune}
+\end{figure}
+
+During our early tests, a trend that previously had been seen became more
+apparent.  During reads, there were periods of high performance followed by
+periods of low performance or outright stalls that could last for up to 20
+seconds at a time.  RADOS bench recorded poor read performance across
+different backend file systems, as shown in
+Figure~\ref{fig:rados-tcp-autotune}.
+
+After running diagnostics, we observed that outstanding operations on the
+clients were not being shown as outstanding on the OSDs.  This appeared to be
+very similar to a problem Jim Schutt at Sandia National labs encountered with
+TCP autotuning in the Linux
+kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
+TCP auto tuning enables TCP window scaling by default and automatically adjusts
+the TCP receive window for each connection based on link conditions such as
+bandwidth delay product. We have observed this improving the performance
+significantly on Ceph read operations. As shown in
+Figure~\ref{fig:rados-tcp-autotune-disabled}.
+
+Luckily, the fix was fairly straight forward by issuing the following command
+on all nodes:
+
+\begin{Verbatim}[fontsize=\small]
+ echo 0 | sudo tee 
+   /proc/sys/net/ipv4/tcp_moderate_rcvbuf
+\end{Verbatim}
+
+Recent versions of Ceph work around this issue by manually controlling the TCP
+buffer size.
+
+\begin{figure}[htb]
+\centering
+%\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
+\includegraphics[width=3.5in]{autotune-disabled}
+\caption{Evaluating RADOS bench with TCP auto tuning \textbf{disabled},  4 servers, 4
+clients, 4 MB I/O}
+\label{fig:rados-tcp-autotune-disabled}
+\end{figure}
+
+We also observed that using two or more client processes and many concurrent
+operations are important when performing these tests.  We tested eight client
+processes with 32 concurrent 4 MB objects in flight each. We created a pool
+for each RADOS Bench process to ensure that object reads come from independent
+pools (RADOS Bench is not smart enough to ensure that objects are not read by
+multiple processes and thus possibly cached).  A sync and flush is performed
+on every node before every test to ensure no data or metadata is in cache.
+All tests were run with replication set to one.
 
@@
 \subsection{Ceph File System Performance}
+\label{sec:ior-initial}
 
@@
   \item The small read (4 KB transfer size) performance is almost an anomaly
-  -- we will investigate why it is so low compare to write performance and
-  present improved results in Section~\ref{sec:improve-ior}.
 
@@
 \end{itemize}
+
+The bottom line is, though we have obtained decent performance number at RADOS
+level, but it did not translate into file system-level performance. We will
+investigate why it is so low compare to write performance and present improved
+results in Section~\ref{sec:ceph-tuning}.
 

### 2013-08-29 ceph-tuning.tex
update bar drawing to be the same style
fix the flow and minor typos

@@
-\section{Tuning, Optimization and Improvements}
+\section{Further Optimization and Improvements}
 \label{sec:ceph-tuning}
@@
 
-\end{comment}
-
-\subsubsection{Disable TCP autotuning}
-
-During these tests, a trend that previously had been seen became more apparent.
-During reads, there were periods of high performance followed by periods of low
-performance or outright stalls that could last for up to 20 seconds at a time.
-After running diagnostics, we observed that outstanding operations on the
-clients were not being shown as outstanding on the OSDs.  This appeared to be
-very similar to a problem Jim Schutt at Sandia National labs encountered with
-TCP autotuning in the Linux
-kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
-TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this improving the performance
-significantly on Ceph read operations, as the results shown in
-Figure~\ref{fig:rados-tcp-auto-disabled}.
-
-Luckily, the fix was fairly straight forward by issuing the following command
-on all nodes:
-
-\begin{Verbatim}[fontsize=\small]
- echo 0 | sudo tee 
-   /proc/sys/net/ipv4/tcp_moderate_rcvbuf
-\end{Verbatim}
-
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
-\caption{Evaluating RADOS bench after TCP auto tuning disabled}
-\label{fig:rados-tcp-auto-disabled}
-\end{figure}
-
-%\begin{figure}[htb]
-%\includegraphics[width=5in]{rados-064-oss}
-%\end{figure}
-
 \subsubsection{Repeating RADOS Scaling Test}
@@
 
+\end{comment}
+
 \subsection{Improving Ceph File System Performance}
@@
 \centering
-\includegraphics[width=3.5in]{ior-client-no-crc32}
+%\includegraphics[width=3.5in]{ior-client-no-crc32}
+\includegraphics[width=3.5in]{ior_no_crc}
 \caption{IOR test with disabling client-side CRC32}
@@
 \centering
-\includegraphics[width=3.5in]{rados-kernel-35vs39}
+%\includegraphics[width=3.5in]{rados-kernel-35vs39}
+\includegraphics[width=3.5in]{rados_kernel}
 \caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
@@
 \centering
-\includegraphics[width=3.5in]{ior-kernel-39}
+%\includegraphics[width=3.5in]{ior-kernel-39}
+\includegraphics[width=3.5in]{ior_kernel_change}
 \caption{CephFS performance with kernel changes to 3.9, IOR with 4 MB transfer

### 2013-08-29 ceph-initial.tex
Clarify rados 8 client scaling number

@@
 
+\subsubsection{Scaling on number of OSDs per server}
+
 We also observed that using two or more client processes and many concurrent
@@
 All tests were run with replication set to one.
-
-\subsubsection{Scaling on number of OSDs per server}
 
@@
 \includegraphics[width=3in]{data/rados_osd}
-\caption{RADOS scaling on number of OSDs}
+\caption{RADOS scaling on number of OSDs: single server single client}
 \label{fig:osd-scale}
 \end{figure}
+
+\subsubsection{Scaling on number of OSD servers}
 
@@
 \includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers}
+\caption{RADOS scaling on number of servers, with 8 clients}
 \label{fig:oss-scale}
@@
 
-\subsubsection{Scaling on number of OSD servers}
-
 In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server
-adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
-regard to number of servers as well, at least in the given set of servers.
+each with four RADOS Bench process. Each additional OSD server adds eleven
+more OSDs into play. The results are illustrated in
+Figure~\ref{fig:oss-scale}. We notice that the read performance improved about
+10% given eight clients instead of four, but write performance is mostly flat
+for reason explained below. We also observe that Ceph exhibits linear scaling
+with regard to number of servers, at least in the given number of servers.
 However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O perforamnce number
-presented in Section~\ref{sec:block-io}).
+expecting from the SFA10K (compare to the baseline block I/O performance
+number presented in Section~\ref{sec:block-io}).
 
 For writes, the lost performance is attributed to the way Ceph performs
-journaling:
-Ceph does not support meta-data only journaling, therefore every write is the
-equivalent of a double-write: once to the data device, once to the journaling
-device. This effectively cuts the observed system bandwidth in half. That said,
-it does not explain the read performance -- it is a little better than write,
-but still far from the theoretical maximum.
+journaling: Ceph does not support meta-data only journaling, therefore every
+write is the equivalent of a double-write: once to the data device, once to
+the journaling device. This effectively cuts the observed system bandwidth in
+half. That said, it does not explain the read performance -- it is a little
+better than write, but still far from the theoretical maximum.
 

### 2013-08-29 ceph-initial.tex
fix graphing color, remove commands, fit in 8 pages

@@
 TCP autotuning in the Linux
-kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
+kernel\cite{Jim:tcptune}.
 TCP auto tuning enables TCP window scaling by default and automatically adjusts
 the TCP receive window for each connection based on link conditions such as
-bandwidth delay product. We have observed this improving the performance
-significantly on Ceph read operations. As shown in
-Figure~\ref{fig:rados-tcp-autotune-disabled}.
+bandwidth delay product.
+
+\begin{figure}[htb]
+\centering
+%\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
+\includegraphics[width=3.5in]{autotune-disabled}
+\caption{Evaluating RADOS bench with TCP auto tuning \textbf{disabled},  4 servers, 4
+clients, 4 MB I/O}
+\label{fig:rados-tcp-autotune-disabled}
+\end{figure}
 
@@
 
+With this change in place, We have observed this improving the performance
+significantly on Ceph read operations. As shown in
+Figure~\ref{fig:rados-tcp-autotune-disabled}.
+
 Recent versions of Ceph work around this issue by manually controlling the TCP
 buffer size.
-
-\begin{figure}[htb]
-\centering
-%\includegraphics[width=3.5in]{rados-after-ddn-tcptune}
-\includegraphics[width=3.5in]{autotune-disabled}
-\caption{Evaluating RADOS bench with TCP auto tuning \textbf{disabled},  4 servers, 4
-clients, 4 MB I/O}
-\label{fig:rados-tcp-autotune-disabled}
-\end{figure}
 
@@
 
-\begin{figure}[!t]
+\begin{figure}[htb]
 \centering
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{data/rados_server}
-\caption{RADOS scaling on number of servers, with 8 clients}
-\label{fig:oss-scale}
-\end{figure}
-
 In this test, we exercise OSD servers from one to four, driven by four hosts
 each with four RADOS Bench process. Each additional OSD server adds eleven
-more OSDs into play. The results are illustrated in
-Figure~\ref{fig:oss-scale}. We notice that the read performance improved about
-10% given eight clients instead of four, but write performance is mostly flat
-for reason explained below. We also observe that Ceph exhibits linear scaling
-with regard to number of servers, at least in the given number of servers.
-However, the peak performance we are seeing is about the half of what are
-expecting from the SFA10K (compare to the baseline block I/O performance
-number presented in Section~\ref{sec:block-io}).
+more OSDs into play.  Figure~\ref{fig:oss-scale} summarized the results.
+Comparing to Figure~\ref{fig:rados-tcp-autotune-disabled}, the read
+performance improved about 10\% given eight clients instead of four, but write
+performance is mostly flat for reason explained below. We also observe that
+Ceph exhibits linear scaling with regard to number of servers, at least in the
+given number of servers.  However, the peak performance we are seeing is about
+the half of what are expecting from the SFA10K (compare to the baseline block
+I/O performance number presented in Section~\ref{sec:block-io}).
 
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=3in]{data/rados_server}
+\caption{RADOS scaling on number of servers, with 8 clients}
+\label{fig:oss-scale}
+\end{figure}
+
 \subsection{Ceph File System Performance}
@@
 
+\begin{figure*}[!t]
+
+\centerline{\subfloat[4 KB transfer size]
+{\includegraphics[width=3in]{data/ior_4k}
+\label{fig:ior4k}}
+\hfil
+\subfloat[4 MB transfer size]
+{\includegraphics[width=3in]{data/ior_4m}
+\label{fig:ior4m}}
+}% end of centerline
+\caption{CephFS scalability test with IOR}
+
+\end{figure*}
+
 We used the synthetic IOR benchmark
-suite\footnote{\url{http://sourceforge.net/projects/ior-sio/}} for file system
-level performance and scalability test.  The particular parameter setup is show
-in Table \ref{tbl:ior}. Each client node has 6 GB of physical memory, the block
+suite\cite{ior} for file system
+level performance and scalability test.  
+Each client node has 6 GB of physical memory, the block
 size is set so as to mitigate cache effects. In addition, the test harness
-program issues the following commands at the beginning of each test:
+program issues commands at the beginning of each test to free pagecache,
+dentries and inodes.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%   COMMENT OUT IOR parameter table 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{comment}
 
@@
 
-Our first round of tests was less than ideal as we encountered various issues. For
-the sake of completeness, we first summarize the results, then discuss
-further tuning efforts and improvements.
+\end{comment}
 
-The full permutation of IOR parameters were not explored due to I/O errors we encountered.
-We were, however, able to record results in two extreme cases as far as
-transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
-(4) and fixed block size (8 GB), the results are illustrated in Figure
-\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:
-
-\begin{figure*}[!t]
-
-\centerline{\subfloat[4 KB transfer size]
-{\includegraphics[width=3in]{data/ior_4k}
-\label{fig:ior4k}}
-\hfil
-\subfloat[4 MB transfer size]
-{\includegraphics[width=3in]{data/ior_4m}
-\label{fig:ior4m}}
-}% end of centerline
-\caption{CephFS scalability test with IOR}
-
-\end{figure*}
+Our initial tests was less than ideal as we encountered various issues.  The
+full permutation of IOR parameters sweep were not explored due to I/O errors
+we encountered.  We were, however, able to record results in two extreme cases
+as far as transfer size is concerned: 4 KB and 4 MB, using a fixed number of
+OSD servers (4) and fixed block size (8 GB), the results are illustrated in
+Figure \ref{fig:ior4k} and \ref{fig:ior4m}, we make the following
+observations:
 
@@
   RADOS Bench. When number of clients reaches 8, there is a significant
-  performance drop as well.
+  performance drop, which is a poor sign for scalability.
 

### 2013-08-29 ceph-tuning.tex
fix graphing color, remove commands, fit in 8 pages

@@
 The initial stability issues mentioned in Section~\ref{sec:ior-initial} are
-fixed by migrating from Ceph version 0.48/0.55 to 0.64, the latest stable version at the
-time of writing this report.  Upgrading to the latest stable Ceph release
-allowed us to run a full IOR parameter sweep for the first time since we
-started evaluating the performance and scalability of the Ceph file system.
-This is another sign of how much Ceph development is currently in flux.
+fixed by migrating from Ceph version 0.48/0.55 to 0.64, the latest stable
+version at the time of writing this report.  Upgrading to the latest stable
+Ceph release allowed us to run a full IOR parameter sweep for the first time
+since we started evaluating the performance and scalability of the Ceph file
+system.  This is another sign of how much Ceph development is currently in
+flux.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% removed for space
+
+\begin{comment}
 
@@
 
-Even with these two changes in place, less-than-ideal write performance and
-very poor read performances were observed during our tests.  We also observed
-that by increasing the number of IOR processes per client node, the read
+\end{comment}
+
+Even with these changes in place, less-than-ideal write performance and very
+poor read performances were observed during our tests.  We also observed that
+by increasing the number of IOR processes per client node, the read
 performance degraded even further indicating some kind of contention either on
@@
 Profiling with \verb!perf! showed high CPU utilization on test clients due to
-CRC32c processing in the Ceph kernel client.  CRC32 checksums can be disabled
-by changing the CephFS mount options:
+CRC32c processing in the Ceph kernel client.
 
-\begin{Verbatim}[fontsize=\small]
-mount -t ceph 10.37.248.43:6789:/ 
-    /mnt/ceph -o name=admin,nocrc
-\end{Verbatim}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% removed
+
+%CRC32 checksums can be disabled
+%by changing the CephFS mount options:
+
+%\begin{Verbatim}[fontsize=\small]
+%mount -t ceph 10.37.248.43:6789:/ 
+%    /mnt/ceph -o name=admin,nocrc
+%\end{Verbatim}
 
@@
 test.  The results were extremely positive and presented in
-Figure~\ref{fig:rados-kernel}.
+Figure~\ref{fig:rados-kernel}. As can be seen, with the 3.9 kernel, while
+there was a slight improvement on write performance, read performance improved
+dramatically.  In addition to the kernel change, the amount of CephFS client
+kernel read-ahead cache size was increased as well.
 
@@
 
-As can be seen, with the 3.9 kernel, while there was a slight improvement on
-write performance, read performance improved dramatically.  In addition to the
-kernel change, the amount of CephFS
-client kernel read-ahead cache size was improved as:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% REMOVED to save space
 
-\begin{Verbatim}[samepage=true, fontsize=\small]
-mount -t ceph 10.37.248.43:6789:/ 
-  /mnt/ceph -o name=admin,nocrc,
-  readdir_max_bytes=4104304,
-  readdir_max_entries=8192
-\end{Verbatim}
+%\begin{Verbatim}[samepage=true, fontsize=\small]
+%mount -t ceph 10.37.248.43:6789:/ 
+%  /mnt/ceph -o name=admin,nocrc,
+%  readdir_max_bytes=4104304,
+%  readdir_max_entries=8192
+% \end{Verbatim}
 

### 2013-08-29 data/gen.sh

@@ -1,10 +1,18 @@
 #!/bin/bash
 Rscript plotxfs.R xfs.csv
 Rscript plot_rados_osd.R rados_osd.csv
+
+# scaling on the number of client
 Rscript plot_rados_client.R rados_client.csv
+
+# scaling on the number of servers
 Rscript plot_rados_server.R rados_server.csv
+
+# ior scaling 4KB and 4MB
 Rscript plot_ior.R ior-8c-4KB-scaling.dat
 Rscript plot_ior.R ior-8c-4MB-scaling.dat
+
+
 Rscript plotxdd.R xdd-read.csv read
 Rscript plotxdd.R xdd-write.csv write
 
@@ -14,4 +22,11 @@ Rscript plot_replication.R
 Rscript plot_autotune.R rados-4s-4c-autotune-disabled.csv autotune-disabled.pdf
 Rscript plot_autotune.R rados-4s-4c-autotune-enabled.csv autotune-enabled.pdf
 
+# generate Fig 10, IOR test with disabling client side CRC32
 Rscript plot_ior_no_crc.R ior_no_crc.pdf
+
+# generate rados bench with kernel change
+Rscript plot_rados_kernel_change.R rados_kernel.csv rados_kernel.pdf
+
+# generate ior with kernel change
+

### 2013-08-29 data/plot_autotune.R

@@ -10,8 +10,9 @@ theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
 
 
 g = ggplot(df, aes(x=filesystem, y=bw, fill=factor(mode))) +
-    geom_bar(stat="identity", position="dodge", color="black") +
-    scale_fill_brewer(type="qual", palette=1)
+    geom_bar(stat="identity", position="dodge", color="black", width=0.6) +
+    scale_fill_manual(values=c("greenyellow", "red"))
+    #scale_fill_brewer(type="qual", palette=1)
 
 
 

### 2013-08-29 data/plot_ior_kernel_change.R

@@ -11,7 +11,8 @@ theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
 
 g = ggplot(df, aes(x=mode, y=bw, fill=factor(mode))) +
     geom_bar(stat="identity", position="dodge", color="black", width=0.5) +
-    scale_fill_brewer(type="qual", palette=1)
+    scale_fill_manual(values=c("greenyellow", "red"))
+    #scale_fill_brewer(type="qual", palette=1)
 
 
 

### 2013-08-29 data/plot_ior_no_crc.R

@@ -10,8 +10,10 @@ theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
 
 
 g = ggplot(df, aes(x=clients, y=bw, fill=factor(mode))) +
-    geom_bar(stat="identity", position="dodge", color="black") +
-    scale_fill_brewer(type="qual", palette=1)
+    geom_bar(stat="identity", position="dodge", color="black", width=0.5) +
+    scale_fill_manual(values=c("greenyellow", "red"))
+
+    #scale_fill_brewer(type="qual", palette=1)
 
 
 

### 2013-08-29 data/plot_rados_kernel_change.R

@@ -10,8 +10,9 @@ theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
 
 
 g = ggplot(df, aes(x=kernel, y=bw, fill=factor(mode))) +
-    geom_bar(stat="identity", position="dodge", color="black") +
-    scale_fill_brewer(type="qual", palette=1)
+    geom_bar(stat="identity", position="dodge", color="black", width=0.5) +
+    scale_fill_manual(values=c("greenyellow", "red"))
+    #scale_fill_brewer(type="qual", palette=1)
 
 
 

### 2013-08-29 data/plot_rados_osd.R

@@ -12,7 +12,7 @@ plot_xfs <- function(file) {
     xmin=as.integer(min(df$osd.num))
     xmax=as.integer(max(df$osd.num))
 
-    quartz(type="pdf", file="rados_osd.pdf")
+    quartz(type="pdf", file="rados_osd.pdf", width=10, height=7)
     theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(osd.num, bw,
             data=df,
@@ -21,13 +21,12 @@ plot_xfs <- function(file) {
             method=loess,
             # geom=c("point", "smooth"),
             ylab="Max (MB/s)\n",
-            xlab="\nNum of OSDs",
-            main="Single server, single client")
+            xlab="\nNum of OSDs")
     
     g = g + scale_shape_discrete(name="IO mode")
     g = g + scale_color_discrete(name="IO mode")
-    g = g + geom_point(size=3.5)
-    g = g + geom_line(size=1.5)
+    g = g + geom_point(size=9)
+    g = g + geom_line(size=3)
     
     # will (not) place lengend on the top
     g = g + opts(legend.position="top")

### 2013-08-29 data/plot_rados_server.R

@@ -1,5 +1,5 @@
 require("ggplot2")
-plot_xfs <- function(file) {
+myplot <- function(file) {
     cat("Processing: ", file, "\n")
     df=read.csv(file, strip.white=TRUE)
 
@@ -11,20 +11,20 @@ plot_xfs <- function(file) {
     xmin=as.integer(min(df$node.num))
     xmax=as.integer(max(df$node.num))
 
-    quartz(type="pdf", file="rados_server.pdf")
+    quartz(type="pdf", file="rados_server.pdf", width=10, height=7)
     theme_set(theme_bw(base_family="Lucida Grande", base_size=18))
     g = qplot(node.num, bw,
             data=df,
             shape=factor(df$mode),
             color=factor(df$mode),
             ylab="Max (MB/s)\n",
-            xlab="\nNum of servers",
-            main="Scaling server numbers")
+            xlab="\nNum of servers")
+    
     g = g + scale_shape_discrete(name="IO mode")
     g = g + scale_color_discrete(name="IO mode")
-    g = g + geom_point(size=3.5)
+    g = g + geom_point(size=9)
     #g = g + geom_smooth(method=loess, se=FALSE)
-    g = g + geom_line(size=1.5)
+    g = g + geom_line(size=3)
     g = g + opts(legend.position="top")
     #g = g + scale_y_continuous(breaks=seq(ymin, ymax,
     #                as.integer((ymax-ymin)/5)))
@@ -41,6 +41,6 @@ plot_xfs <- function(file) {
 
 args = commandArgs(trailingOnly = TRUE)
 options(warn=-1)
-plot_xfs(args[1])
+myplot(args[1])
 
 

### 2013-08-29 abstract.tex
minor fixing on abstract

@@
 Ceph is an open-source and emerging parallel distributed file and storage
-system technology. It is designed to provide file system-level and object-level
-access to data. By design, Ceph assumes running on unreliable and commodity
+system technology. By design, Ceph assumes running on unreliable and commodity
 storage and network hardware and provides reliability and fault-tolerance
-through pre-calculated and controlled object placement and data replication.
+through controlled object placement and data replication.
 

### 2013-08-29 conclusion.tex
polish conclusion section

@@
 
-Below are our preliminary observations from mostly performance perspective:
-
-\begin{itemize}
-
-  \item Ceph is built on the assumption that the underlying hardware components
+Ceph is built on the assumption that the underlying hardware components
 are unreliable, with little or no redundancy and failure detection capability.
@@
 
-  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
-host systems that has locally attached disk. However, this presents a problem
-in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
-devices through IB over SRP protocol. The journaling write requires twice the
-bandwidth compared to Lustre-like meta data-only journaling mechanism. For Ceph
-to be viable in large-scale capability HPC environments like ours, journaling
-operations will need to further design and engineering.
+Ceph performs \textbf{metadata + data} journaling, which is fine for host
+systems that have locally attached disks. However, this presents a problem in
+DDN SFA10K-like hardware, where the backend LUNs are exposed as block devices
+through IB over SRP protocol. The journaling write requires twice the
+bandwidth compared to Lustre-like meta data-only journaling mechanism. For
+Ceph to be viable in large-scale capability HPC environments like ours,
+journaling operations will need further design and more engineering efforts.
 
-  \item We observed consistent results and linear scalability at the RADOS
-level. However, we did not observe the same at the file system level. We have
-experienced large performance swings during different runs, very low read
-performance when transfer size is small, and I/O errors tend to happen when
-system is under stress (more clients and large transfer sizes). These are not
-particularly reproducible results, but it suggests that there are opportunities
-for code improvement and maturation.
+In our earlier tests, we experienced large performance swings during different
+runs, low read performance when transfer size is small, and I/O errors tend to
+happen when system is under stress (more clients and large transfer sizes).
+However, with systematic performance engineering and development efforts, we
+have seen a steady improvement through different releases. As of now, Ceph
+system on our testbed is able to perform close to 80\% of raw hardware
+capability at RADOS level and close to 70\% at file system level. This is
+still no comparison to Lustre yet, but by no means a small feat for such a
+\textit{young} technology. It is, in fact, a very respectable level of
+performance.
 
-\end{itemize}
+%The current design on journaling write does present a challenge in
+%our IB-switched storage hardware. As BTRFS and other backend file system
+%mature, we are seeing promising signs for Ceph to take advantage for a
+%better journaling design.

### 2013-08-30 introduction.tex
integrating sage's text
there are two missing references

@@
 
-Ceph\cite{Weil:2006:Ceph} originated from Sage Weil's PhD research at UC Santa
-Cruz at 2007 and it was designed to be a reliable, scalable fault-tolerant
-parallel file system.  Since then, Ceph has been open-sourced and Inktank is
-now the major developer behind it.  In comparison to other parallel file
+Ceph\cite{Weil:2006:Ceph} is a distributed storage system designed for
+scalability, reliability, and performance.  The system is based on a
+distributed object storage service called RADOS (reliable autonomic distributed
+object store) that manages the distribution, replication, and migration of
+objects.  On top of that reliable storage abstraction Ceph builds a range of
+services, including a block storage abstraction (RBD, or rados block device)
+and a cache-coherent distributed file system (CephFS).
+
+Data objects are distributed across storage daemons (ceph-osd) using
+CRUSH\cite{crush}, a deterministic hashing function that allows administrators
+to define flexible placement policies over a hierarchical cluster structure
+(e.g., disks, hosts, racks, rows, datacenters).  Because the location of
+objects can be calculated based on the object identifier and cluster layout
+(similar to consistent hashing~\cite{..}), there is no need for a metadata
+index or server for the RADOS object store. Further, because CRUSH provides an
+authoritative view of data placement, storage daemons can coordinate directly
+to handle data replications, recovery, or object migratation in the face of
+failure or cluster topology changes.  A small cluster of monitors (ceph-mon
+daemons) use Paxos to provide consensus on the current cluster layout, but do
+not need to explicitly coordinate migration or recovery activities.
+
+CephFS builds a distributed cache-coherent file system on top of the object
+storage service provided by RADOS.  Files are striped over objects stored and
+replicated by RADOS, while a separate cluster of metadata servers (ceph-mds
+daemons) manage the file system namespace and coordinate client access to
+files.
+
+Ceph metadata servers store all metadata in RADOS object, which provides a
+shared, highly-available, and reliable storage backend.  Unlike many other
+distributed file system architectures, Ceph also embeds inodes inside
+directories in the common case, allowing entire directories to read from RADOS
+into the metadata server cache or prefetched into the client cache using a
+single request.
+
+Client hosts that mount the file system communicate with one or more metadata
+servers to traverse the namespace but perform file IO by reading and writing
+directly to RADOS objects that contain the file data.  The metadata server
+cluster monitors the temperature of cached metadata and periodically adjusts
+the distribution of the namespace across the MDS cluster by migrating
+responsibility for arbitrary subtrees of the hierarchy between a dynamic pool
+of active ceph-mds daemons.  This dynamic subtree partitioning~\cite{..}
+strategy is both adaptive and highly scalable, allowing additional metadata
+server daemons to be added or removed at any time, making it ideally suited
+both for large-scale workloads with bursty workloads or general purpose
+clusters whose workloads grow or contract over time.
+
+In comparison to other parallel file
 systems, Ceph has a number of distinctive features:
 
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 

### 2013-08-30 conclusion.tex
changes here and there

@@
 
-Ceph is built on the assumption that the underlying hardware components
-are unreliable, with little or no redundancy and failure detection capability.
-This assumption is not valid for high-end HPC centers like ours. We have
-disabled replication for pools, we haven't measured and quantified
-processing overhead and we do not know yet if this would be significant.
+Ceph is built on the assumption that the underlying hardware components are
+unreliable, with little or no redundancy and failure detection capability.
+This assumption is not valid for high-end HPC centers like OLCF. We have
+disabled replication for pools, haven't measured and quantified processing
+overhead, and we do not know yet if this would be significant. Investigating
+this remains as a future work.
 
@@
 bandwidth compared to Lustre-like meta data-only journaling mechanism. For
-Ceph to be viable in large-scale capability HPC environments like ours,
-journaling operations will need further design and more engineering efforts.
+Ceph to be viable in large-scale capability HPC environments like OLCF,
+journaling operations need further design and more engineering efforts.
 
@@
 system on our testbed is able to perform close to 80\% of raw hardware
-capability at RADOS level and close to 70\% at file system level. This is
-still no comparison to Lustre yet, but by no means a small feat for such a
-\textit{young} technology. It is, in fact, a very respectable level of
-performance.
+capability at RADOS level and close to 70\% at file system level (after
+accounting for journaling overheads) . This is still no comparison to Lustre
+yet, but by no means a small feat for such a \textit{young} technology. It is,
+in fact, a very respectable level of performance.
 

### 2013-08-30 introduction.tex
changes here and there

@@
 large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II
-is the forklift-upgrade of its predecessor, Spider, which was deployed in 2008.
-Spider II, deployed in 20013, is designed to operate at over 1 TB/s peak
+is the upgrade of its predecessor, Spider, which was deployed in 2008.
+Spider II, deployed in 2013, is designed to operate at over 1 TB/s peak
 aggregate I/O throughput and has a 40 PB of raw disk capacity. As the scratch
@@
 
+\begin{comment}
 In comparison to other parallel file
@@
 
-\begin{comment}
 \begin{itemize}
@@
 are our top priorities due to the unique requirements our environment.  As part
-of this study, we set up a dedicated testbed within OLCF to understand and
-evaluate Ceph.  Our goal was to investigate the feasibility of using the Ceph
-for our future HPC storage deployments. This paper presents our experience,
-results, and observations.  While evaluating our results, please keep in mind
-that Ceph is still a relatively \textit{young} parallel file system and its
-code base is changing rapidly. In between releases, we often experienced
-different stability and performance outcomes.  We will try to make clear in the
-writing when such changes occurred.
+of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
+Our goal was to investigate the feasibility of using the Ceph for future
+large-scale scientific HPC storage deployments. This paper presents our
+experience, results, and observations.  While evaluating our results, please
+keep in mind that Ceph is still a relatively \textit{young} parallel file
+system and its code base is changing rapidly. In between releases, we often
+experienced different stability and performance outcomes.  We will try to make
+clear in the writing when such changes occurred.
 

### 2013-08-30 testbed.tex
changes here and there

@@
-\section{Testbed Environment Description}
+\section{Testbed Environment and Test Methodology}
 \label{sec:testbed}
@@
 evaluation. SFA10K organizes disks into various RAID levels by two
-active-active RAID controllers. The exported RAID groups (LUNs) by these
-controllers are driven by four server hosts (oss-[1-4]).  Each server host has two InfiniBand
-(IB) QDR connections to the storage backend.  We used a single dual-port
-Mellanox ConnectX IB QDR card per host.  By our calculation, this setup is
-adequate to drive the SFA10K at its maximum theoretical throughput (roughly 12
-GB/s). Server hosts and SFA10K connection diagram is illustrated in
+active-active RAID controllers. Exported RAID groups (LUNs) by these
+controllers are driven by four server hosts (oss-[1-4]).  Each server host has
+two InfiniBand (IB) QDR connections to the storage backend.  We used a single
+dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
+setup is adequate to drive the SFA10K at its maximum theoretical throughput
+(roughly 12 GB/s). Server hosts and SFA10K connection diagram is illustrated in
 Figure~\ref{fig:ddn-sfa10k}.
@@
 All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 initially, and later upgraded to 3.9 (rhl-ceph image), Glibc
+version 3.5.1 initially, and later upgraded to 3.9, Glibc
 2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55

### 2013-09-05 src/ceph-test.py
update misc (1) meta ske (2) test scripts

@@ -10,19 +10,19 @@ import sys
 
 global ior_config, cluster_config, mpi_config, mdtest_config
 
-IOR_cmd = "/chexport/users/fwang2/bin/IOR"
-MDTEST_cmd = "/chexport/users/fwang2/bin/mdtest"
-INIT_cmd = "/chexport/users/nhm/apps/bin/ceph-init"
-CEPH_cmd = "/chexport/users/nhm/local/bin/ceph"
-MKCEPHFS_cmd = "/chexport/users/nhm/local/sbin/mkcephfs"
-MPI_cmd = "mpirun"
-MON_addr = "10.37.248.43:6789"
+# IOR_cmd = "/chexport/users/fwang2/bin/IOR"
+# MDTEST_cmd = "/chexport/users/fwang2/bin/mdtest"
+# INIT_cmd = "/chexport/users/nhm/apps/bin/ceph-init"
+# CEPH_cmd = "/chexport/users/nhm/local/bin/ceph"
+# MKCEPHFS_cmd = "/chexport/users/nhm/local/sbin/mkcephfs"
+# MPI_cmd = "mpirun"
+# MON_addr = "10.37.248.43:6789"
 
 def parse_args():
-    parser = argparse.ArgumentParser(description="IOR Test")
-    parser.add_argument('--iorconf', nargs=1, default="ior.yaml", help = "YAML config file")
+    parser = argparse.ArgumentParser(description="Ceph Test Harness Program")
+    parser.add_argument('--conf', nargs=1, default="ior.yaml", help = "YAML config file")
     parser.add_argument('--cephconf', nargs=1, default="default.ceph.conf",
-            help="Default ceph configuration file")
+            help="Default Ceph configuration file")
 
     action = parser.add_mutually_exclusive_group(required=True)
 
@@ -33,10 +33,11 @@ def parse_args():
     action.add_argument("--restart", action="store_true", help = "Start up Ceph")
     action.add_argument("--reboot-clients", action="store_true", help = "Reboot Ceph clients")
     action.add_argument("--shutdown", action="store_true", help = "Shutdown Ceph")
-    action.add_argument("--runtests", action="store_true", help = "Run IOR tests")
+    action.add_argument("--ior", action="store_true", help = "Run IOR tests")
     action.add_argument("--distconf", action="store_true", help = "Distribute Ceph configuration file")
     action.add_argument("--checkfs", action="store_true", help = "Check cephfs health")
[…]

### 2013-09-05 src/clear_cache.sh

@@ -1,0 +1,2 @@
+echo 3 | tee /proc/sys/vm/drop_caches && sync
+

### 2013-09-05 src/ior-strace.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+BSIZE=1g
+strace -T -o strace.out IOR -a POSIX -e -F -b $BSIZE -t 1m -r -w -C -i 1 -d 5 -o /mnt/cephfs/tfile 
+

### 2013-09-05 src/ipoib-set-datagram.sh

@@ -1,0 +1,5 @@
+#!/bin/sh
+
+echo datagram > /sys/class/net/$1/mode
+
+ifconfig $1 | grep -iE "mtu|inet addr|$1"

### 2013-09-05 src/rebuild-2.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+mkcephfs -a -c /etc/ceph/ceph.conf
+

### 2013-09-05 src/rebuild.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+cd /chexport/users/fwang2
+pdsh -w tick-oss[1-4] "rm -rf /mnt/ceph/storage[0-5]/*"
+pdsh -w tick-mds1 "rm -rf /tmp/ceph; mkdir -p /tmp/ceph/mon.a" 
+
+mkcephfs -a -c ./ceph.conf --mkfs
+

### 2013-09-05 src/refresh.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+cd /chexport/users/fwang2
+cp -f ./ceph.conf /etc/ceph/ceph.conf
+pdsh -w tick-oss[1-4],spoon46 "mkdir -p /var/log/ceph; mkdir -p /var/run/ceph"
+service ceph -a -c /etc/ceph/ceph.conf start
+

### 2013-09-05 src/reset-ceph-conf.sh

@@ -1,0 +1,20 @@
+#!/bin/bash
+
+if [ $# -ne 1 ]; then
+	printf "need ceph.conf\n"
+	exit 1
+fi
+
+CEPH_CONF=$1
+
+pdsh -w tick-mds1,tick-oss3,spoon46,spoon[37-41] "cp -f /chexport/users/fwang2/$1 /etc/ceph/ceph.conf"
+
+pdsh -w spoon[37-41] "umount /mnt/cephfs"
+service ceph -a -c /etc/ceph/ceph.conf stop
+service ceph -a -c /etc/ceph/ceph.conf start
+
+pdsh -w spoon[37-41] "mount -t ceph 172.30.248.51:6789:/ /mnt/cephfs -o name=admin,secret=AQD2+8hQODJjBRAA8q7bu6O9Xqp/t1Pwi4MS3A=="
+
+pdsh -w spoon[37-41] "ls /mnt/cephfs" | dshbak -c  
+
+

### 2013-09-05 abstract.tex

@@
 
-In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
+We evaluated the Ceph
 technology for scientific high-performance computing (HPC) environments.  This paper
@@
 two unique contributions. First, our evaluation is performed under a realistic
-setup for a large-scale capability HPC environment like ours using a commercial
+setup for a large-scale capability HPC environment using a commercial
 high-end storage system.

### 2013-09-05 baseline.tex
changes here and there

@@
 \subsection{Block I/O over Native IB} 
+\label{sec:block-io}
 
 The lowest layer in the system are the exposed LUNs to the server hosts from
-the RAID controllers.  These LUNs are mostly configured as a RAID6 8+2 array (8
-data disks and 2 \textit{P} and \textit{Q} disks). In our earlier tests we
-observed that a 7.2K RPM SAS disk can perform at ~140 MB/s for 128 kB
-sequential I/O requests and a 7.2K RPM SATA disk can do ~36 MB/s. For these
-tests, all disk caches were turned off. Therefore, in 8 data disk RAID group
-with 1 MB sequential I/O requests (each disks sees 128 kB chunks of the
-request) the expected aggregate performance would be ~1.12 GB/s for a SAS RAID
-group and ~288 MB/s for a SATA RAID group, if there are no caches along the I/O
-path.  With the caches turned on, especially the write-back cache on the DDN
-RAID controller, we observe a significant performance improvement. In our
-day-to-day HPC operations we run our storage systems with write-back cache
-turned on on RAID controllers, if and only if, there is a method of
-cache-mirroring between the two active-active RAID controllers to recover from
-a single controller failure scenario. With the write-back cache on we observe
-~1.4 GB/s per RAID 6 8+2 SAS group and ~955 MB/s per RAID 6 8+2 SATA group, for
-1 MB sequential I/O. These two performance numbers will be used as a baseline
-in our study and they are presented in Table~\ref{tbl:block-io-baseline}.  For
-these tests, the 8+2 RAID 6 groups are exported to the server hosts using SCSI
-RDMA Protocol (SRP) over IB protocol (which is the default for our normal HPC
-configurations). For a SATA disk group this translates into roughly 120
-MB/s/disk and for a SAS disk group it is 175 MB/s. As can be seen, SATA RAID
-groups benefit from caching more than SAS groups.
+the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
+disks and 2 \textit{P} and \textit{Q} disks). In our earlier tests we observed
+that a 7.2K RPM SAS disk can perform at \textasciitilde140 MB/s for 128 kB
+sequential I/O requests and a 7.2K RPM SATA disk can do \textasciitilde36 MB/s.
+For these tests, all disk caches were turned off. Therefore, in 8 data disk
+RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
+the request) the expected aggregate performance would be \textasciitilde1.12
+GB/s for a SAS RAID group and \textasciitilde288 MB/s for a SATA RAID group, if
+there are no caches along the I/O path.  With the caches turned on, especially
+the write-back cache on the DDN RAID controller, we observe a significant
+performance improvement. In our day-to-day HPC operations we run our storage
+systems with write-back cache turned on on RAID controllers, if and only if,
+there is a method of cache-mirroring between the two active-active RAID
+controllers. With the write-back cache on we observe \textasciitilde1.4 GB/s
+per RAID 6 8+2 SAS group and  \textasciitilde955 MB/s per RAID 6 8+2 SATA
+group, for 1 MB sequential I/O.  These two performance numbers will be used as
+a baseline in our study and they are presented in
+Table~\ref{tbl:block-io-baseline}.  For these tests, the 8+2 RAID 6 groups are
+exported to the server hosts using SCSI RDMA Protocol (SRP) over IB protocol
+(which is the default for our normal HPC configurations). For a SATA disk group
+this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
+MB/s/disk. As can be seen, SATA RAID groups benefit from caching more than SAS
+groups.
 
@@
 4 server hosts in our testbed and evenly distributing these on to 4 server
-hosts translates into 8 SATA LUNs and 4 SAS LUNs per server host (when a RAID
-group is exported to a server host, it is labeled as a LUN from the server host
-point of view).
+hosts translates into 7 SATA LUNs and 4 SAS LUNs per server host.
 
@@
 as single server host aggregate baseline performance for this study. These are
-also presented in presented in Table~\ref{tbl:block-io-baseline}.
+also presented in Table~\ref{tbl:block-io-baseline}.
 
@@
 sequential I/O characteristics compared to commonly used XDD benchmark and it
-is asynchronous and based on the Linux libaio library.
+is asynchronous and based on the Linux \verb!libaio! library.
 
@@
 \centering
-\caption{Block I/O performances on single LUN and single host}
+\caption{Baseline block I/O performance summary}
 \label{tbl:block-io-baseline}
 
-\begin{tabular}{| l | l |}
+\begin{tabular}{ l | l }
     \hline
@@
 concluded that our test setup is well configured to drive the backend disk
-system at full performance and we are limited by the RAID controller
+system at close to full performance and we are limited by the RAID controller
 performance. Going forward in this study, 11 GB/s will be used the peak

### 2013-09-05 introduction.tex

@@
 Data objects are distributed across storage daemons (ceph-osd) using
-CRUSH\cite{crush}, a deterministic hashing function that allows administrators
-to define flexible placement policies over a hierarchical cluster structure
-(e.g., disks, hosts, racks, rows, datacenters).  Because the location of
-objects can be calculated based on the object identifier and cluster layout
-(similar to consistent hashing~\cite{..}), there is no need for a metadata
-index or server for the RADOS object store. Further, because CRUSH provides an
-authoritative view of data placement, storage daemons can coordinate directly
-to handle data replications, recovery, or object migratation in the face of
-failure or cluster topology changes.  A small cluster of monitors (ceph-mon
-daemons) use Paxos to provide consensus on the current cluster layout, but do
-not need to explicitly coordinate migration or recovery activities.
+CRUSH\cite{Weil:2006:Crush}, a deterministic hashing function that allows
+administrators to define flexible placement policies over a hierarchical
+cluster structure (e.g., disks, hosts, racks, rows, datacenters).  Because the
+location of objects can be calculated based on the object identifier and
+cluster layout (similar to consistent hashing~\cite{karger1997consistent}),
+there is no need for a metadata index or server for the RADOS object store.
+Further, because CRUSH provides an authoritative view of data placement,
+storage daemons can coordinate directly to handle data replications, recovery,
+or object migration in the face of failure or cluster topology changes.  A
+small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus on
+the current cluster layout, but do not need to explicitly coordinate migration
+or recovery activities.
 
@@
 responsibility for arbitrary subtrees of the hierarchy between a dynamic pool
-of active ceph-mds daemons.  This dynamic subtree partitioning~\cite{..}
-strategy is both adaptive and highly scalable, allowing additional metadata
-server daemons to be added or removed at any time, making it ideally suited
-both for large-scale workloads with bursty workloads or general purpose
-clusters whose workloads grow or contract over time.
+of active ceph-mds daemons.  This dynamic subtree
+partitioning~\cite{Weil:2004:dynamic} strategy is both adaptive and highly
+scalable, allowing additional metadata server daemons to be added or removed
+at any time, making it ideally suited both for large-scale workloads with
+bursty workloads or general purpose clusters whose workloads grow or contract
+over time.
 

### 2013-09-05 testbed.tex

@@
 
+\begin{comment}
 Our Ceph testbed employs a collection of nodes, including the server hosts
 (oss-[1-4]). These nodes and their roles are summarized in
-Table~\ref{tbl:ceph-test-nodes}. In the following discussion, we use
-``servers'', ``osd servers'', ``server hosts'' interchangeably. We will
-emphasize with ``client'' prefix when we want to distinguish it from above.
+Table~\ref{tbl:ceph-test-nodes}. 
+\end{comment}
 
+In the following discussion, we use ``servers'', ``osd servers'', ``server
+hosts'' interchangeably. We will emphasize with ``client'' prefix when we want
+to distinguish it from above.  All hosts  (client and servers) were configured
+with Redhat 6.3 and kernel version 3.5.1 initially, and later upgraded to 3.9,
+Glibc 2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and
+0.55 release in the initial tests, upgraded to 0.64 and then to 0.67RC for a
+final round of tests.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% REMOVED
+\begin{comment}
 \begin{table}[!t]
@@
 \end{table}
-
-All hosts  (client and servers) were configured with Redhat 6.3 and kernel
-version 3.5.1 initially, and later upgraded to 3.9, Glibc
-2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
-release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
-round of tests.
+\end{comment}
 
@@
 
-Our tools for benchmarking and evaluating different layers also change as we go
-up in the stack.  For example, a tool perfect for assessing block-level
+Our tools for benchmarking and evaluating different layers also change as we
+go up in the stack.  For example, a tool perfect for assessing block-level
 performance over a single server host might be completely inadequate for
-observing parallel file system performance over multiple clients. As we present
-our evaluations, we will also introduce and explain our benchmark tools, in
-this paper.
+observing parallel file system performance over multiple clients. As we
+present our evaluations, we will also introduce and explain our benchmark
+tools along the way.

### 2013-09-05 src/ceph-test.py
bring back basic funcs of test harness

@@ -1,4 +1,4 @@
-#!/chexport/users/fwang2/python/bin/python
+#!/usr/bin/env python
 
 import argparse
 import os
@@ -8,21 +8,36 @@ import yaml
 import shutil
 import sys
 
+from color import hprint, eprint
+
 global ior_config, cluster_config, mpi_config, mdtest_config
 
-# IOR_cmd = "/chexport/users/fwang2/bin/IOR"
-# MDTEST_cmd = "/chexport/users/fwang2/bin/mdtest"
-# INIT_cmd = "/chexport/users/nhm/apps/bin/ceph-init"
-# CEPH_cmd = "/chexport/users/nhm/local/bin/ceph"
-# MKCEPHFS_cmd = "/chexport/users/nhm/local/sbin/mkcephfs"
-# MPI_cmd = "mpirun"
-# MON_addr = "10.37.248.43:6789"
+IOR_cmd = "/ccs/techint/home/fwang2/local/bin/IOR"
+MDTEST_cmd = "/ccs/techint/home/fwang2/local/bin/mdtest"
+INIT_cmd = "/ccs/techint/home/fwang2/local/bin/ceph-init"
+
+# this command requires cooporation from remote host's LD_LIBRARY_PATH
+# for example, spoon37:/root/.bashrc, I have the following:
+#
+# export LD_LIBRARY_PATH=/ccs/techint/home/fwang2/local/lib64:/ccs/techint/home/fwang2/local/lib:$LD_LIBRARY_PATH
+# export PATH=/ccs/techint/home/fwang2/local/bin:/ccs/techint/home/fwang2/local/sbin:$PATH
+
+CEPH_cmd = "/ccs/techint/home/fwang2/local/bin/ceph"
+
+
+MKCEPHFS_cmd = "/ccs/techint/home/fwang2/local/sbin/mkcephfs"
+MPI_cmd = "mpirun"
+
+# Monitor host: spoon41
+MON_addr = "10.37.248.43:6789"
 
 def parse_args():
     parser = argparse.ArgumentParser(description="Ceph Test Harness Program")
-    parser.add_argument('--conf', nargs=1, default="ior.yaml", help = "YAML config file")
+    parser.add_argument('--conf', nargs=1, default="ceph.yaml", help = "YAML config file")
     parser.add_argument('--cephconf', nargs=1, default="default.ceph.conf",
             help="Default Ceph configuration file")
+
+    parser.add_argument("--gen", action="store_true", help="Generate configure permutations")
 
[…]

### 2013-09-05 src/mark/makecephconf.py

@@ -44,9 +44,9 @@ def mkosds(lists, yaml):
                 name = "osd.%d" % i
                 lists[name] = []
                 lists[name].append("        host = %s" % server)
-                lists[name].append("        osd data = /tmp/mnt/osd-device-%d-data" % j)
+                lists[name].append("        osd data = /mnt/osd-device-%d-data" % j)
 #                lists[name].append("        osd journal = /dev/mapper/%s-sata-l%d" % (server, j + yaml.get('osds_per_server', 0)))
-                lists[name].append("        osd journal = /tmp/mnt/osd-device-%d-data/journal" % j)
+                lists[name].append("        osd journal = /mnt/osd-device-%d-data/journal" % j)
                 i += 1
 
 def writescript(f, param, value, conf):

### 2013-09-05 src/mark/runme.sh

@@ -1,0 +1,2 @@
+#!/bin/bash
+/ccs/techint/home/fwang2/ceph-report/src/runtests.py --conf /autofs/na3_techint/home/fwang2/ceph-report/src/default.ceph.conf --archive /ccs/techint/home/fwang2/ceph-report/raw/1-node-11-osd/xfs/default /ccs/techint/home/fwang2/ceph-report/src/1_server_osd_scaling/runtests-1c-11osd.xfs.yaml

### 2013-09-05 src/cephtest.py
update ceph test script

@@ -10,7 +10,8 @@ import sys
 
 from color import hprint, eprint
 
-global ior_config, cluster_config, mpi_config, mdtest_config
+global ceph_config, ior_config, cluster_config, mpi_config, mdtest_config, ceph_config_table
+global para_config, xfs_config, btrfs_config, ext4_config
 
 IOR_cmd = "/ccs/techint/home/fwang2/local/bin/IOR"
 MDTEST_cmd = "/ccs/techint/home/fwang2/local/bin/mdtest"
@@ -37,7 +38,6 @@ def parse_args():
     parser.add_argument('--cephconf', nargs=1, default="default.ceph.conf",
             help="Default Ceph configuration file")
 
-    parser.add_argument("--gen", action="store_true", help="Generate configure permutations")
 
     action = parser.add_mutually_exclusive_group(required=True)
 
@@ -49,8 +49,7 @@ def parse_args():
     action.add_argument("--reboot-clients", action="store_true", help = "Reboot Ceph clients")
     action.add_argument("--shutdown", action="store_true", help = "Shutdown Ceph")
     action.add_argument("--ior", action="store_true", help = "Run IOR tests")
-    action.add_argument("--distconf", action="store_true", help = "Distribute Ceph configuration file")
-    action.add_argument("--checkfs", action="store_true", help = "Check cephfs health")
+    action.add_argument("--check-health", action="store_true", help = "Check Ceph Health")
     action.add_argument("--mdtest", action="store_true", help = "CephFS metadata test")
     action.add_argument("--rados", action="store_true", help = "Ceph Rados Bench")
 
@@ -151,10 +150,13 @@ def get_server_nodes():
 
 
 def stop_ceph():
+    hprint("Stopping ceph ...")
     pdsh(get_server_nodes(), INIT_cmd + ' stop')
     pdsh(get_server_nodes(), 'killall -9 ceph-osd;killall -9 ceph-mon;killall -9 ceph-mds')
 
 def start_ceph():
+
+    hprint("Starting up ceph through ceph-init script ...")
     pdsh(get_server_nodes(), INIT_cmd + ' start')
 
 def purge_logs():
@@ -189,10 +191,19 @@ def setup_osd_fs():
     servers = cluster_config['servers']
 
     fs = cluster_config.get('fs', 'btrfs')
-    mkfs_opts = cluster_config.get('mkfs_opts', '-o noatime')
-    osds_per_node = int(cluster_config.get('osds_per_node'))
[…]

### 2013-09-06 src/cephtest.py
rados testing seems working

@@ -11,11 +11,16 @@ import sys
 from color import hprint, eprint
 
 global ceph_config, ior_config, cluster_config, mpi_config, mdtest_config, ceph_config_table
-global para_config, xfs_config, btrfs_config, ext4_config
+global para_config, xfs_config, btrfs_config, ext4_config, rados_config
 
-IOR_cmd = "/ccs/techint/home/fwang2/local/bin/IOR"
-MDTEST_cmd = "/ccs/techint/home/fwang2/local/bin/mdtest"
-INIT_cmd = "/ccs/techint/home/fwang2/local/bin/ceph-init"
+IOR_cmd         = "/ccs/techint/home/fwang2/local/bin/IOR"
+MDTEST_cmd      = "/ccs/techint/home/fwang2/local/bin/mdtest"
+INIT_cmd        = "/ccs/techint/home/fwang2/local/bin/ceph-init"
+RADOS_cmd       = "/ccs/techint/home/fwang2/local/bin/rados"
+CEPH_cmd        = "/ccs/techint/home/fwang2/local/bin/ceph"
+MKCEPHFS_cmd    = "/ccs/techint/home/fwang2/local/sbin/mkcephfs"
+MPI_cmd         = "mpirun"
+
 
 # this command requires cooporation from remote host's LD_LIBRARY_PATH
 # for example, spoon37:/root/.bashrc, I have the following:
@@ -23,14 +28,16 @@ INIT_cmd = "/ccs/techint/home/fwang2/local/bin/ceph-init"
 # export LD_LIBRARY_PATH=/ccs/techint/home/fwang2/local/lib64:/ccs/techint/home/fwang2/local/lib:$LD_LIBRARY_PATH
 # export PATH=/ccs/techint/home/fwang2/local/bin:/ccs/techint/home/fwang2/local/sbin:$PATH
 
-CEPH_cmd = "/ccs/techint/home/fwang2/local/bin/ceph"
 
-
-MKCEPHFS_cmd = "/ccs/techint/home/fwang2/local/sbin/mkcephfs"
-MPI_cmd = "mpirun"
 
 # Monitor host: spoon41
 MON_addr = "10.37.248.43:6789"
+
+def check_err(out, err):
+    if err:
+        shutdown(err)
+    else:
+        print(out)
 
 def parse_args():
     parser = argparse.ArgumentParser(description="Ceph Test Harness Program")
@@ -45,7 +52,7 @@ def parse_args():
     action.add_argument("--umount", action="store_true", help = "Umount cephfs")
[…]

### 2013-09-06 src/cephtest.py
document notes on tally rados perf #, without implementing it

@@ -349,6 +349,23 @@ def run_radosbench(out_base, ts):
                     ps.append(p)
                 for p in ps:
                     p.wait()
+
+                # tally numbers
+                # for each sub-tests, we can name it [type of test].[timestamp].csv
+                # such as rados.2013-08-3333.csv
+                # and append the result
+                #
+                # the result can be grabbed through a shell
+                #
+                # grep "^Bandwidth" * | tr -s " " | cut -f3 -d" " | awk '{s+=$1} END {print s}'
+                #
+                # we need to put more system information and running parameters in the csv of course
+                #
+                # and this file should be placed at out_dir/rados/timestamp/xxx
+                #
+                #
+
+
     hprint("RADOS bench done.")
 
 
@@ -436,7 +453,12 @@ def ceph_check_health():
             print stderr
         time.sleep(5)
 
-def ior_test():
+def run_ior(outdir, ts):
+    """
+    outdir - output data directory
+    ts - timestamp
+    """
+
     clients = cluster_config['clients'].split(',')
     servers = cluster_config['servers'].split(',')
     idx = int(cluster_config['start'])
@@ -604,7 +626,7 @@ if __name__ == "__main__":
     elif args.rados:
         run_radosbench(archive_dir, timestamp)
     elif args.ior:
-        ior_test()
+        run_ior(archive_dir, timestamp)
     elif args.mdtest:
         mdtest()
     else:

### 2013-09-06 src/mark/runtests.py

@@ -64,8 +64,7 @@ def ORNL_sudopdsh(nodes, command):
         sudocommand += "[[ `hostname -s` = %s ]]" % node
     sudocommand += "; then %s; fi" % command
 
-    #args = ['sudo', 'pdsh', '-g', 'ceph',  sudocommand]
-    args = ['pdsh', '-g', 'ceph',  sudocommand]
+    args = ['sudo', 'pdsh', '-g', 'ceph',  sudocommand]
     print sudocommand    
     return subprocess.Popen(args, stdout=subprocess.PIPE, stderr=subprocess.PIPE)
 

### 2013-09-06 src/cephtest.py
fix output file naming

@@ -344,7 +344,10 @@ def run_radosbench(out_base, ts):
                 for i in xrange(concurrent_procs):
                     out_file = '%s/output.%s' % (out_dir, i)
                     objecter_log = '%s/objecter.%s.log' % (out_dir, i)
-                    p = pdsh(clients, '%s -p rados-bench-`hostname -s`-%s %s bench %s %s %s 2> %s > %s' %
+
+                    # notice that the final out filename is composed by %s.`hostname -s`. This is because each
+                    # client node will generate multiple output files (= concurrent_procs)
+                    p = pdsh(clients, '%s -p rados-bench-`hostname -s`-%s %s bench %s %s %s 2> %s > %s.`hostname -s`' %
                             (RADOS_cmd, i, op_size_str, time, mode, concurrent_ops_str, objecter_log, out_file))
                     ps.append(p)
                 for p in ps:

### 2013-09-20 conclusion.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

@@
 
-Ceph is built on the assumption that the underlying hardware components are
-unreliable, with little or no redundancy and failure detection capability.
-This assumption is not valid for high-end HPC centers like OLCF. We have
-disabled replication for pools, haven't measured and quantified processing
-overhead, and we do not know yet if this would be significant. Investigating
-this remains as a future work.
-
-Ceph performs \textbf{metadata + data} journaling, which is fine for host
-systems that have locally attached disks. However, this presents a problem in
-DDN SFA10K-like hardware, where the backend LUNs are exposed as block devices
-through IB over SRP protocol. The journaling write requires twice the
-bandwidth compared to Lustre-like meta data-only journaling mechanism. For
-Ceph to be viable in large-scale capability HPC environments like OLCF,
-journaling operations need further design and more engineering efforts.
-
-In our earlier tests, we experienced large performance swings during different
+%Ceph is built on the assumption that the underlying hardware components are
+%unreliable, with little or no redundancy and failure detection capability.
+%This assumption is not valid for high-end HPC centers like OLCF. We have
+%disabled replication for pools, haven't measured and quantified processing
+%overhead, and we do not know yet if this would be significant. Investigating
+%this remains as a future work. 
+In our early tests, we experienced large performance swings during different
 runs, low read performance when transfer size is small, and I/O errors tend to
@@
 However, with systematic performance engineering and development efforts, we
-have seen a steady improvement through different releases. As of now, Ceph
+have seen a steady improvement through different releases. As of now, the Ceph
 system on our testbed is able to perform close to 80\% of raw hardware
 capability at RADOS level and close to 70\% at file system level (after
-accounting for journaling overheads) . This is still no comparison to Lustre
-yet, but by no means a small feat for such a \textit{young} technology. It is,
-in fact, a very respectable level of performance.
+accounting for journaling overheads) . 
+%This is still no comparison to Lustre
+%yet, but by no means a small feat for such a \textit{young} technology. It is,
+%in fact, a very respectable level of performance.
+
+Ceph is built on the assumption that the underlying hardware components are
+unreliable, with little or no redundancy and failure detection capability.
+This assumption is not valid for high-end HPC centers like OLCF.
+Ceph performs \textbf{metadata + data} journaling, which is appropriate for host
+systems that have locally attached disks rather than DDN SFA10K-like hardware,
+where the backend LUNs are exposed as block devices through IB over SRP
+protocol. The journaling write requires twice the bandwidth compared to
+Lustre-like meta data-only journaling mechanism. For Ceph to be viable in
+large-scale capability HPC environments like OLCF, journaling operations need
+to support HPC storage hardware.
 

### 2013-09-20 testbed.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

@@
 
-In the following discussion, we use ``servers'', ``osd servers'', ``server
-hosts'' interchangeably. We will emphasize with ``client'' prefix when we want
-to distinguish it from above.  All hosts  (client and servers) were configured
+%In the following discussion, we use ``servers'', ``osd servers'', ``server
+%hosts'' interchangeably. We will emphasize with ``client'' prefix when we want
+%to distinguish it from above.  
+All hosts  (client and servers) were configured
 with Redhat 6.3 and kernel version 3.5.1 initially, and later upgraded to 3.9,
@@
 
-Our testing methodology is bottom to top. We start our evaluation from the
-lowest level (i.e. block-level)  to establish a baseline performance and work
-our way up to the top (i.e. file system-level). We establish an expected
-theoretical performance of a given hardware or software layer and then compare
-that with the observed results of our experiments. Each added new layer to the
-stack introduces new bottlenecks and re-defines the expected theoretical
-performance of the overall system. We will explain each component or layer and
-its expected performance before we present our observed results.
+%Our testing methodology is bottom to top. We start our evaluation from the
+%lowest level (i.e. block-level)  to establish a baseline performance and work
+%our way up to the top (i.e. file system-level). We establish an expected
+%theoretical performance of a given hardware or software layer and then compare
+%that with the observed results of our experiments. Each added new layer to the
+%stack introduces new bottlenecks and re-defines the expected theoretical
+%performance of the overall system. We will explain each component or layer and
+%its expected performance before we present our observed results.
 
-Our tools for benchmarking and evaluating different layers also change as we
-go up in the stack.  For example, a tool perfect for assessing block-level
-performance over a single server host might be completely inadequate for
-observing parallel file system performance over multiple clients. As we
-present our evaluations, we will also introduce and explain our benchmark
-tools along the way.
+%Our tools for benchmarking and evaluating different layers also change as we
+%go up in the stack.  For example, a tool perfect for assessing block-level
+%performance over a single server host might be completely inadequate for
+%observing parallel file system performance over multiple clients. As we
+%present our evaluations, we will also introduce and explain our benchmark
+%tools along the way.

### 2013-09-20 abstract.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

@@
 
-Ceph is an open-source and emerging parallel distributed file and storage
-system technology. By design, Ceph assumes running on unreliable and commodity
-storage and network hardware and provides reliability and fault-tolerance
-through controlled object placement and data replication.
-
-We evaluated the Ceph
-technology for scientific high-performance computing (HPC) environments.  This paper
+Ceph is an emerging open-source parallel distributed file and storage
+system. By design, Ceph is designed to leverage unreliable and commodity
+storage and network hardware, and provides reliability and fault-tolerance
+via controlled object placement and data replication.  Here we evaluate Ceph
+for scientific high-performance computing (HPC) environments.  This paper
 presents our evaluation methodology, experiments, results and observations from
-mostly parallel I/O performance and scalability perspectives.  Our work made
+mostly parallel I/O performance and scalability perspectives.  Our work makes
 two unique contributions. First, our evaluation is performed under a realistic
@@
 contributions to Ceph's development and improved code quality, scalability, and
-performance. These changes should also benefit both Ceph and HPC communities at
-large. Throughout the evaluation, we observed that Ceph still is an evolving
-technology under fast-paced development and showing great promises.
+performance. These changes should benefit both Ceph and the HPC community
+at large. Throughout the evaluation, we observe that Ceph is an evolving
+technology under fast-paced development and shows great promises.
 

### 2013-09-20 baseline.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

@@
-\section{Establishing A Baseline Performance}
+\section{Establishing A Performance Baseline}
 \label{sec:baseline}
@@
 the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
-disks and 2 \textit{P} and \textit{Q} disks). In our earlier tests we observed
+disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
 that a 7.2K RPM SAS disk can perform at \textasciitilde140 MB/s for 128 kB
@@
 
-For above tests the RAID groups are exported over physical 4x IB QDR links.
-These links can provide up to 40 Gbits/s signalling rate and 32 Gbits/s actual
-data rate (reduction is due to 8/10 encoding scheme). Therefore, each IB QDR
-link can perform at 3.2 GB/s, while in practice we see around 3 GB/s as the
-best case.
+%For above tests the RAID groups are exported over physical 4x IB QDR links.
+%These links can provide up to 40 Gbits/s signalling rate and 32 Gbits/s actual
+%data rate (reduction is due to 8/10 encoding scheme). Therefore, each IB QDR
+%link can perform at 3.2 GB/s, while in practice we see around 3 GB/s as the
+%best case.
 
-As mentioned earlier, we had 280 SATA disks and 200 SAS disks. Organizing these
-into RAID 6 8+2 groups will yield 28 SATA and 20 SAS RAID 6 8+2 groups. We had
-4 server hosts in our testbed and evenly distributing these on to 4 server
-hosts translates into 7 SATA LUNs and 4 SAS LUNs per server host.
+%As mentioned earlier, we had 280 SATA disks and 200 SAS disks. Organizing these
+%into RAID 6 8+2 groups yields 28 SATA and 20 SAS RAID 6 8+2 groups. We had
+%4 server hosts in our testbed and evenly distributing these on to 4 server
+%hosts translates into 7 SATA LUNs and 4 SAS LUNs per server host.
 
-Next, we established the baseline performance for a single server host. We
-exercised all seven SATA LUNs concurrently form a single server host at the
-block-level. This resulted in an aggregate performance of roughly 2.6 GB/s.
-Repeating the same test using only four SAS LUNs yielded around 2.8 GB/s
-aggregate performance for 1 MB sequential I/O. These two numbers will be used
-as single server host aggregate baseline performance for this study. These are
-also presented in Table~\ref{tbl:block-io-baseline}.
+%Next, we established the baseline performance for a single server host. We
+%exercised all seven SATA LUNs concurrently form a single server host at the
+%block-level. This resulted in an aggregate performance of roughly 2.6 GB/s.
+%Repeating the same test using only four SAS LUNs yielded around 2.8 GB/s
+%aggregate performance for 1 MB sequential I/O. These two numbers will be used
+%as single server host aggregate baseline performance for this study. These are
+%also presented in Table~\ref{tbl:block-io-baseline}.
 
 It is worth mentioning that we used our in-house developed synthetic benchmark,
-\textit{fair-lio} for all our block-level testing.  fair-lio has better
+\textit{fair-lio} for all our block-level testing.  Fair-lio has better
 sequential I/O characteristics compared to commonly used XDD benchmark and it
@@
 When exercising all 28 SATA LUNs from all four server hosts in parallel, we
-observed an 11 GB/s aggregate performance. Same level of performance was
+observed an 11 GB/s aggregate performance. The same level of performance was
 observed using all 20 SAS LUNs from four server hosts in parallel. Comparing
@@
 
-Unfortunately there was not enough time to do more detailed analysis of the
-network performance. However, as we observed later, RADOS is performing no
-more than 8 GB/s driven by four server hosts. This confirms that we have
-provisioned enough network bandwidth. In other words, IP over IB is not a
-bottleneck in this case.
+%Unfortunately there was not enough time to do more detailed analysis of the
+%network performance. However, as we observed later, RADOS is performing no
+%more than 8 GB/s driven by four server hosts. This confirms that we have
+%provisioned enough network bandwidth. In other words, IP over IB is not a
+%bottleneck in this case.

### 2013-09-20 ceph-initial.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

@@
 
-RADOS is a reliable distributed object store, the foundational component for
-CephFS file system. There are two types of scaling tests we are interested at
-the RADOS layer:
-
-\begin{itemize}
-  \item scaling on the number of OSD servers
-  \item scaling on the number of OSDs per OSD server
-\end{itemize}
-
-Our system setup poses some limitations on the scalability tests we wanted to
-perform. In particular, we currently had four OSD servers, eight clients, and
-eleven OSD servers per client. The scaling tests, therefore, will be within
-these constraints.
+%RADOS is a reliable distributed object store, the foundational component for
+%CephFS file system. There are two types of scaling tests we are interested at
+%the RADOS layer:
+%
+%\begin{itemize}
+%  \item scaling on the number of OSD servers
+%  \item scaling on the number of OSDs per OSD server
+%\end{itemize}
+%
+%Our system setup poses some limitations on the scalability tests we wanted to
+%perform. In particular, we currently had four OSD servers, eight clients, and
+%eleven OSD servers per client. The scaling tests, therefore, will be within
+%these constraints.
 
@@
 
-During our early tests, a trend that previously had been seen became more
-apparent.  During reads, there were periods of high performance followed by
+Our early testing indicated a read performace abberation.  There were periods of high performance followed by
 periods of low performance or outright stalls that could last for up to 20
@@
 
-After running diagnostics, we observed that outstanding operations on the
-clients were not being shown as outstanding on the OSDs.  This appeared to be
-very similar to a problem Jim Schutt at Sandia National labs encountered with
-TCP autotuning in the Linux
+We observed that outstanding operations on the clients were not being shown as
+outstanding on the OSDs.  This appeared to be similar to a problem Jim Schutt
+at Sandia National labs encountered with TCP autotuning in the Linux
 kernel\cite{Jim:tcptune}.
@@
 
-Luckily, the fix was fairly straight forward by issuing the following command
-on all nodes:
+We disabled this behavior by setting 
+\url{/proc/sys/net/ipv4/tcp_moderate_rcvbuf} to 0 on all nodes, improving the Ceph read performance as
+shown in Figure~\ref{fig:rados-tcp-autotune-disabled}.
+Recent versions of Ceph work around this issue by manually controlling the TCP
+buffer size.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% REMOVED for space
+
+\begin{comment}
 
@@
 
-With this change in place, We have observed this improving the performance
-significantly on Ceph read operations. As shown in
-Figure~\ref{fig:rados-tcp-autotune-disabled}.
+\end{comment}
 
-Recent versions of Ceph work around this issue by manually controlling the TCP
-buffer size.
-
-\subsubsection{Scaling on number of OSDs per server}
+\subsubsection{Scaling OSDs per server}
 
 We also observed that using two or more client processes and many concurrent
-operations are important when performing these tests.  We tested eight client
+operations are critical to achieve high performance.  We tested eight client
 processes with 32 concurrent 4 MB objects in flight each. We created a pool
@@
 on every node before every test to ensure no data or metadata is in cache.
-All tests were run with replication set to one.
-
-In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
-from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
-We ran the test against a single client with four concurrent processes. In this
-test case, we observe that the OSD server exhibits near linear scalability up to
+All tests were run with replication set to one. Figure~\ref{fig:osd-scale}
+shows that an OSD server exhibits near linear scalability up to
 nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
@@
 provisioning more OSDs on the SFA10K backend.
+%
+%In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
+%from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
+%We ran the test against a single client with four concurrent processes. In this
+%test case, we observe that the OSD server exhibits near linear scalability up to
+%nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
+%have not reached the saturation point yet. Additional testing would require
+%provisioning more OSDs on the SFA10K backend.
 
@@
 
-\subsubsection{Scaling on number of OSD servers}
+\subsubsection{Scaling OSD servers}
 
-In this test, we exercise OSD servers from one to four, driven by four hosts
-each with four RADOS Bench process. Each additional OSD server adds eleven
-more OSDs into play.  Figure~\ref{fig:oss-scale} summarized the results.
-Comparing to Figure~\ref{fig:rados-tcp-autotune-disabled}, the read
+We measured performance at the client (using RADOS bench) for one to four OSD
+servers.  Each additional OSD server adds eleven
+more OSDs into play.  Figure~\ref{fig:oss-scale} demonstrates that read
 performance improved about 10\% given eight clients instead of four, but write
-performance is mostly flat for reason explained below. We also observe that
-Ceph exhibits linear scaling with regard to number of servers, at least in the
-given number of servers.  However, the peak performance we are seeing is about
-the half of what are expecting from the SFA10K (compare to the baseline block
-I/O performance number presented in Section~\ref{sec:block-io}).
-
-For writes, the lost performance is attributed to the way Ceph performs
-journaling: Ceph does not support meta-data only journaling, therefore every
-write is the equivalent of a double-write: once to the data device, once to
-the journaling device. This effectively cuts the observed system bandwidth in
-half. That said, it does not explain the read performance -- it is a little
-better than write, but still far from the theoretical maximum.
+performance is mostly flat.  The lost write performance compared to a single
+OSD is attributed to Ceph journaling.  Ceph does not support meta-data only
+journaling, therefore every write is the equivalent of a double-write: once to
+the data device, once to the journaling device.  It is unclear why read
+performance is so much lower than the theoretical maximum.
+%This effectively cuts the observed system bandwidth in
+%half. 
+%That said, it does not explain the read performance -- it is a little
+%better than write, but still far from the theoretical maximum.
+%Comparing to Figure~\ref{fig:rados-tcp-autotune-disabled}, the read
+%performance improved about 10\% given eight clients instead of four, but write
+%performance is mostly flat for reason explained below. We also observe that
+%Ceph exhibits linear scaling with regard to number of servers, at least in the
+%given number of servers.  However, the peak performance we are seeing is about
+%the half of what are expecting from the SFA10K (compare to the baseline block
+%I/O performance number presented in Section~\ref{sec:block-io}).
+%
+%For writes, the lost performance is attributed to the way Ceph performs
+%journaling: Ceph does not support meta-data only journaling, therefore every
+%write is the equivalent of a double-write: once to the data device, once to
+%the journaling device. This effectively cuts the observed system bandwidth in
+%half. That said, it does not explain the read performance -- it is a little
+%better than write, but still far from the theoretical maximum.
 
@@
 
-Our initial tests was less than ideal as we encountered various issues.  The
-full permutation of IOR parameters sweep were not explored due to I/O errors
-we encountered.  We were, however, able to record results in two extreme cases
-as far as transfer size is concerned: 4 KB and 4 MB, using a fixed number of
+The full permutation of IOR parameters sweep were not explored due to I/O
+errors.  We were able to record results in the I/O size boundary cases:
+4 KB and 4 MB, using a fixed number of
 OSD servers (4) and fixed block size (8 GB), the results are illustrated in
@@
 
-\subsection{Metadata Performance Evaluation}
+%% \subsection{Metadata Performance Evaluation}
 
-In our particular setup, we only had one metadata server (MDS) configured.
-Therefore, this is not a scalability test on the performance of Ceph clustered
-MDS, which would have been very interesting.  Instead, we focus on a single MDS
-performance and exercise it with up to 8 clients to observe the single MDS
-performance scaling. We used
-mdtest\footnote{\url{http://sourceforge.net/projects/mdtest/}} as our benchmark
-tool. Mdtest parameters used for this test are:
+%% In our particular setup, we only had one metadata server (MDS) configured.
+%% Therefore, this is not a scalability test on the performance of Ceph clustered
+%% MDS, which would have been very interesting.  Instead, we focus on a single MDS
+%% performance and exercise it with up to 8 clients to observe the single MDS
+%% performance scaling. We used
+%% mdtest\footnote{\url{http://sourceforge.net/projects/mdtest/}} as our benchmark
+%% tool. Mdtest parameters used for this test are:
 
-\begin{itemize}
-\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
-perform a sync operation.  This is a more realistic use case scenario than just
-open, close and unlink sequence of metadata operations.
+%% \begin{itemize}
+%% \item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
+%% perform a sync operation.  This is a more realistic use case scenario than just
+%% open, close and unlink sequence of metadata operations.
 
-\item \verb!-n 1000!: Per client file \textit{and} directory workload. For
-eight clients, the total number of files and directories in the workload is
-8,000. Since we did not specify either \verb!-D! (indicates a directory only
-workload) or \verb!-F! (indicates a file only workload), this is a mixture of
-both directory and file workloads.
+%% \item \verb!-n 1000!: Per client file \textit{and} directory workload. For
+%% eight clients, the total number of files and directories in the workload is
+%% 8,000. Since we did not specify either \verb!-D! (indicates a directory only
+%% workload) or \verb!-F! (indicates a file only workload), this is a mixture of
+%% both directory and file workloads.
 
-\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
-Lustre file system, where you can have single client multiple mounts (for
-increasing workload per client), here we just give the test an explicit home.
+%% \item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
+%% Lustre file system, where you can have single client multiple mounts (for
+%% increasing workload per client), here we just give the test an explicit home.
 
-\item \verb!-u!: without this option, we are exercising shared directory; with
-this option, we are exercising unique directories per test client processes.
+%% \item \verb!-u!: without this option, we are exercising shared directory; with
+%% this option, we are exercising unique directories per test client processes.
 
-\end{itemize}
+%% \end{itemize}
 
-Each test iterates five times and we are presenting the maximum out of all five iterations. 
-We summarize the results as follows:
+%% Each test iterates five times and we are presenting the maximum out of all five iterations. 
+%% We summarize the results as follows:
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/mdtest-fcreate}
-\caption{File creation vs.  number of clients}
-\label{fig:mdtest-fcreate}
-\end{figure}
+%% \begin{figure}[htb]
+%% \centering
+%% \includegraphics[width=3in]{data/mdtest-fcreate}
+%% \caption{File creation vs.  number of clients}
+%% \label{fig:mdtest-fcreate}
+%% \end{figure}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=3in]{data/mdtest-dcreate}
-\caption{Directory creation vs. number of clients}
-\label{fig:mdtest-dcreate}
-\end{figure}
+%% \begin{figure}[htb]
+%% \centering
+%% \includegraphics[width=3in]{data/mdtest-dcreate}
+%% \caption{Directory creation vs. number of clients}
+%% \label{fig:mdtest-dcreate}
+%% \end{figure}
 
-%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
-%directory (prefixed with d) and file (prefixed with f) operations, against the
-%number of clients. Due to the scale difference, it doesn't convey the
-%magnitude of lower numbers.
+%% %Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
+%% %directory (prefixed with d) and file (prefixed with f) operations, against the
+%% %number of clients. Due to the scale difference, it doesn't convey the
+%% %magnitude of lower numbers.
 
-\begin{itemize}
+%% \begin{itemize}
 
-\item With either shared or unique directory (\verb!-u!), stat
-operations for directories and files exhibit strong linear scaling. Same strong
-linear scaling is also observed for file read operations.
+%% \item With either shared or unique directory (\verb!-u!), stat
+%% operations for directories and files exhibit strong linear scaling. Same strong
+%% linear scaling is also observed for file read operations.
 
-\item While the other operations seems unaffected or performance remains the
-same by the number of clients, it is not so if we zoom in, see
-figures \ref{fig:mdtest-fcreate} and \ref{fig:mdtest-dcreate}:  as number of clients
-increases, we observed the contention for shared directory. The performance
-degradation amount to 50\% or more.
+%% \item While the other operations seems unaffected or performance remains the
+%% same by the number of clients, it is not so if we zoom in, see
+%% figures \ref{fig:mdtest-fcreate} and \ref{fig:mdtest-dcreate}:  as number of clients
+%% increases, we observed the contention for shared directory. The performance
+%% degradation amount to 50\% or more.
 
-\item Though the same saturation (or degradation) trend was not observed for
-file creation operation, it is likely due to lack of workload stress on MDS.
+%% \item Though the same saturation (or degradation) trend was not observed for
+%% file creation operation, it is likely due to lack of workload stress on MDS.
 
-\end{itemize}
+%% \end{itemize}
 
-The results also show that file creation rate is significantly lower than
-directory creation rate. We stipulated two contributing factors: one is the file
-creation is associated with 1 MB data write and followed by a fsync operation,
-which is a rather heavy weight operation compare to directory creation. Another
-factor is that we obtained above results while both RADOS and file
-system-level performance are not tuned for optimal, yet.
+%% The results also show that file creation rate is significantly lower than
+%% directory creation rate. We stipulated two contributing factors: one is the file
+%% creation is associated with 1 MB data write and followed by a fsync operation,
+%% which is a rather heavy weight operation compare to directory creation. Another
+%% factor is that we obtained above results while both RADOS and file
+%% system-level performance are not tuned for optimal, yet.
 
-Next, we will describe the efforts and results on performance improvement at
-both RADOS and file system-level. As consequence, we expect to see improved
-metadata performance as well.
+%% Next, we will describe the efforts and results on performance improvement at
+%% both RADOS and file system-level. As consequence, we expect to see improved
+%% metadata performance as well.

### 2013-09-20 ceph-tuning.tex
fix citation to Appendix E
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

@@
 options affect performance on the DDN platform. The result of this parameter
-probing is illustrated in Figure~\ref{fig:parametric}. Please refer to Appendix
-E for explanations of these probed parameters.
+probing is illustrated in Figure~\ref{fig:parametric}. Please refer to
+Appendix E of \cite{ceph:techreport} for explanations of these probed
+parameters.
 
@@
 
-Deeper analysis with \verb!perf! showed that there was heavy lock contention during
-parallel compaction in the Linux kernel memory manager.  This behavior was first
-observed roughly in the kernel 3.5 time frame which was the kernel
+Deeper analysis with \verb!perf! showed that there was heavy lock contention
+during parallel compaction in the Linux kernel memory manager.  This behavior
+was first observed roughly in the kernel 3.5 time frame which was the kernel
 installed on our test systems.\footnote{For more information,
 please refer to \url{http://lwn.net/Articles/517082/} and
-\url{https://patchwork.kernel.org/patch/1338691/}.}
+\url{https://patchwork.kernel.org/patch/1338691/}.}  We upgraded our test
+systems with kernel version 3.9 and performed RADOS Bench test.  The results
+were dramatic:  read performance improved from 4678 MB/s to 8643 MB/s (almost
+an 85\% improvement).  Write performance was also fractionally improved from
+4720 MB/s to 5284 MB/s 9an almost 12\% improvement).
+%extremely positive and presented in
+%Figure~\ref{fig:rados-kernel}. As can be seen, with the 3.9 kernel, while
+%there was a slight improvement on write performance, read performance improved
+%dramatically.  In addition to the kernel change, the amount of CephFS client
+%kernel read-ahead cache size was increased as well.
 
-We upgraded our test systems with kernel version 3.9 and performed RADOS Bench
-test.  The results were extremely positive and presented in
-Figure~\ref{fig:rados-kernel}. As can be seen, with the 3.9 kernel, while
-there was a slight improvement on write performance, read performance improved
-dramatically.  In addition to the kernel change, the amount of CephFS client
-kernel read-ahead cache size was increased as well.
-
-\begin{figure}[htb]
-\centering
+%\begin{figure}[htb]
+%\centering
 %\includegraphics[width=3.5in]{rados-kernel-35vs39}
-\includegraphics[width=3.5in]{rados_kernel}
-\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
-\label{fig:rados-kernel}
-\end{figure}
+%\includegraphics[width=3.5in]{rados_kernel}
+%\caption{RADOS bench: Linux kernel version 3.5 vs. 3.9}
+%\label{fig:rados-kernel}
+%\end{figure}
 
@@
 
-IOR results reflecting the read-ahead cache size change are presented in
-Figure~\ref{fig:ior-kernel-39}.
+Additionally, we increased the size of the CephFS kernel client's read-ahead
+chance.  IOR results reflecting the read-ahead cache size change are presented
+in Figure~\ref{fig:ior-kernel-39}.
 
@@
 
-\subsection{Revisiting Metadata Performance}
-
-Our previous results show that file creation rate is significantly lower than
-directory creation rate. Also, we conjectured two reasons: one is the file
-creation is associated with 1 MB data write and followed by a \verb!fsync!
-operation.  Another reason being that we obtained above results from early
-version of Ceph without all the tunings and improvement applied.
-
-Therefore, we repeated the same test on the latest CephFS 0.64. The result is
-illustrated in Figure~\ref{fig:mdtest-064-file-create}. As expected, we
-observed a significant improvement on the file creation rate. We also note
-that as number of clients increase, the file creation rate decreases rapidly,
-which suggested some form of lock contention. This presents some interesting
-issues to be investigated further.
+\subsection{Metadata Performance Tuning}
+For brevity's sake, we are omitting most of our file and directory creation
+rate results.  However, over the course of our testing we did notice that in
+CephFS 0.64 a significant improvement in the performance of file creation with
+mdtest.  Shown in Figure~\ref{fig:mdtest-064-file-create}, we note
+that as number of clients increase, the file creation rate does not scale
+linearly, which suggested some form of lock contention.  Due to the large
+differences in the initially observed performance, and the performance with
+Ceph 0.64, opportunities for file and directory create tuning may be
+substantial.
 

### 2013-09-20 introduction.tex
Brad's attempt to cut to 5 pages
So here is most of my attempt to cut this paper to 5 pages.
I amde it to about 5.7 pages.  I could go after it some more,
but this is a good first draft point to check and see if we need
to add back anything I took out.

I also added the IEEEabbrv.bib file since I couldn't build
without it.

@@
 of deploying and running very-large-scale high-performance computing (HPC)
-systems\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
-the Jaguar supercomputer up until recently, which was upgraded to the Titan
-supercomputer. In order to satisfy the I/O demand of such supercomputers (as
-well as, other OLCF computational, analysis, and visualization clusters), OLCF
+systems\footnote{\url{http://www.top500.org/site/48553}}. 
+%The facility hosted
+%the Jaguar supercomputer up until recently, which was upgraded to the Titan
+%supercomputer. 
+In order to satisfy the I/O demand of such supercomputers, OLCF
 also hosts large-scale file and storage systems. Lustre has been OLCF's choice
-as the distributed parallel file system.  The latest incarnation of such
-large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II
-is the upgrade of its predecessor, Spider, which was deployed in 2008.
-Spider II, deployed in 2013, is designed to operate at over 1 TB/s peak
-aggregate I/O throughput and has a 40 PB of raw disk capacity. As the scratch
-file system connected to a leadership computing platform at the scale of Titan,
+as the distributed parallel file system.  The latest such
+large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
+2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
+has a 40 PB of raw disk capacity. As the scratch 
+file system for Titan, a leadership computing platform,
 Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
-also recognize that there are a wide variety of scientific data and workloads
-with different performance and data access requirements (e.g., RESTful
+recognize that there are a wide variety of scientific data and emerging
+workloads with different performance and data access requirements (e.g., RESTful
 interface, S3-like API, cloud solution integration) which might not be
@@
 administrators to define flexible placement policies over a hierarchical
-cluster structure (e.g., disks, hosts, racks, rows, datacenters).  Because the
+cluster structure (e.g., disks, hosts, racks, rows, datacenters).  The
 location of objects can be calculated based on the object identifier and
 cluster layout (similar to consistent hashing~\cite{karger1997consistent}),
-there is no need for a metadata index or server for the RADOS object store.
-Further, because CRUSH provides an authoritative view of data placement,
-storage daemons can coordinate directly to handle data replications, recovery,
-or object migration in the face of failure or cluster topology changes.  A
-small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus on
+thus there is no need for a metadata index or server for the RADOS object store.
+%Further, because CRUSH provides an authoritative view of data placement,
+%storage daemons can coordinate directly to handle data replications, recovery,
+%or object migration in the face of failure or cluster topology changes.  
+A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus on
 the current cluster layout, but do not need to explicitly coordinate migration
@@
 CephFS builds a distributed cache-coherent file system on top of the object
-storage service provided by RADOS.  Files are striped over objects stored and
-replicated by RADOS, while a separate cluster of metadata servers (ceph-mds
+storage service provided by RADOS.  Files are striped across replicated
+storage objects, while a separate cluster of metadata servers (ceph-mds
 daemons) manage the file system namespace and coordinate client access to
@@
 
-Ceph metadata servers store all metadata in RADOS object, which provides a
+Ceph metadata servers store all metadata in RADOS objects, which provides a
 shared, highly-available, and reliable storage backend.  Unlike many other
@@
 
-Client hosts that mount the file system communicate with one or more metadata
-servers to traverse the namespace but perform file IO by reading and writing
+Client hosts that mount the file system communicate with metadata
+servers to traverse the namespace and perform file I/O by reading and writing
 directly to RADOS objects that contain the file data.  The metadata server
-cluster monitors the temperature of cached metadata and periodically adjusts
+cluster periodically adjusts
 the distribution of the namespace across the MDS cluster by migrating
@@
 
-As interesting and feature-rich as Ceph may be,  scalability and performance
-are our top priorities due to the unique requirements our environment.  As part
-of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
-Our goal was to investigate the feasibility of using the Ceph for future
+While we are interested in Ceph for its ability to support
+alternative workloads that are not easily accomplished with Lustre, in this
+study we are investigating the use Ceph for future
 large-scale scientific HPC storage deployments. This paper presents our
-experience, results, and observations.  While evaluating our results, please
-keep in mind that Ceph is still a relatively \textit{young} parallel file
-system and its code base is changing rapidly. In between releases, we often
-experienced different stability and performance outcomes.  We will try to make
-clear in the writing when such changes occurred.
+experience, results, and observations in measuring the scalability and
+performance of Ceph for capability workloads.  Additionally, Ceph is under
+rapid development, and in  between releases, we often
+experienced different stability and performance outcomes.  
+%We will try to make
+%clear in the writing when such changes occurred.
+%As interesting and feature-rich as Ceph may be,  scalability and performance
+%are our top priorities due to the unique requirements our environment.  As part
+%of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
+%Our goal was to investigate the feasibility of using the Ceph for future
+%large-scale scientific HPC storage deployments. This paper presents our
+%experience, results, and observations.  While evaluating our results, please
+%keep in mind that Ceph is still a relatively \textit{young} parallel file
+%system and its code base is changing rapidly. In between releases, we often
+%experienced different stability and performance outcomes.  We will try to make
+%clear in the writing when such changes occurred.
 
-This paper is organized as follows. Section~\ref{sec:testbed} gives an
-overview on our general test and evaluation methodology as well as testbed
-environment; Following it, Section~\ref{sec:baseline} establishes the baseline
-performance and expectations for all critical components on the data path;
-Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
-bottom up: from middle tier RADOS object layer to the file system-level and
-then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
-investigative and tuning effort, we compare results before and after, and how
-the process eventually bring the system performance to a respectable state.
-Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
-and future works.
+%This paper is organized as follows. Section~\ref{sec:testbed} gives an
+%overview on our general test and evaluation methodology as well as testbed
+%environment; Following it, Section~\ref{sec:baseline} establishes the baseline
+%performance and expectations for all critical components on the data path;
+%Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
+%bottom up: from middle tier RADOS object layer to the file system-level and
+%then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
+%investigative and tuning effort, we compare results before and after, and how
+%the process eventually bring the system performance to a respectable state.
+%Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
+%and future works.

### 2013-10-02 abstract.tex
cutting

@@
 storage and network hardware, and provides reliability and fault-tolerance
-via controlled object placement and data replication.  Here we evaluate Ceph
-for scientific high-performance computing (HPC) environments.  This paper
-presents our evaluation methodology, experiments, results and observations from
-mostly parallel I/O performance and scalability perspectives.  Our work makes
+via controlled object placement and data replication.  
+%Here we evaluate Ceph
+%for scientific high-performance computing (HPC) environments.  
+This paper
+presents our file and block I/O performance and scalability evaluation of Ceph for
+scientific high-performance computing (HPC) environments.
+% methodology, experiments, results and observations from
+%mostly parallel I/O performance and scalability perspectives.  
+Our work makes
 two unique contributions. First, our evaluation is performed under a realistic
@@
 performance. These changes should benefit both Ceph and the HPC community
-at large. Throughout the evaluation, we observe that Ceph is an evolving
-technology under fast-paced development and shows great promises.
+at large. 
+%Throughout the evaluation, we observe that Ceph is an evolving
+%technology under fast-paced development and shows great promises.
 

### 2013-10-02 introduction.tex
cutting

@@
 also hosts large-scale file and storage systems. Lustre has been OLCF's choice
-as the distributed parallel file system.  The latest such
-large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
-2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
-has a 40 PB of raw disk capacity. As the scratch 
-file system for Titan, a leadership computing platform,
-Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
+as the distributed parallel file system.  
+%The latest such
+%large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
+%2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
+%has a 40 PB of raw disk capacity. As the scratch 
+%file system for Titan, a leadership computing platform,
+%Spider II emphasizes \textit{capability} over \textit{capacity}. 
+However, we
 recognize that there are a wide variety of scientific data and emerging

### 2013-10-02 ceph-tuning.tex
cutting

@@
 systems with kernel version 3.9 and performed RADOS Bench test.  The results
-were dramatic:  read performance improved from 4678 MB/s to 8643 MB/s (almost
-an 85\% improvement).  Write performance was also fractionally improved from
-4720 MB/s to 5284 MB/s 9an almost 12\% improvement).
+%were dramatic:  read performance improved from 4678 MB/s to 8643 MB/s (almost
+were dramatic:  read performance improved from 4678 MB/s to 7499 MB/s 
+(a 60\% improvement).  Write performance was also fractionally improved from
+4720 MB/s to 5284 MB/s (a 12\% improvement).
 %extremely positive and presented in
@@
 Additionally, we increased the size of the CephFS kernel client's read-ahead
-chance.  IOR results reflecting the read-ahead cache size change are presented
-in Figure~\ref{fig:ior-kernel-39}.
+chance.  
+%IOR results reflecting the read-ahead cache size change are presented
+%in Figure~\ref{fig:ior-kernel-39}.
 
+\begin{comment}
 \begin{figure}[htb]
@@
 \end{figure}
+\end{comment}
 
@@
 
+\begin{comment}
 \subsection{Metadata Performance Tuning}
@@
 \end{figure}
+
+\end{comment}

### 2013-10-03 introduction.tex
using acm template now

@@
 of deploying and running very-large-scale high-performance computing (HPC)
-systems\footnote{\url{http://www.top500.org/site/48553}}. 
+systems. 
 %The facility hosted

### 2013-10-03 abstract.tex
Minor corrections

@@
 Ceph is an emerging open-source parallel distributed file and storage
-system. By design, Ceph is designed to leverage unreliable and commodity
+system. By design, Ceph leverages unreliable commodity
 storage and network hardware, and provides reliability and fault-tolerance

### 2013-10-03 baseline.tex
Minor corrections

@@
 server host connections over a 108-port Mellanox IB QDR switch), we used IP
-over IB (IPoIB) for networking\footnote{As of writing of this report, Inktank
+over IB (IPoIB) for networking\footnote{As of writing of this paper, Inktank
 is investigating using rsockets to improve performance with IB fabric}. Through

### 2013-11-05 introduction.tex
split background

@@
 
-Ceph\cite{Weil:2006:Ceph} is a distributed storage system designed for
-scalability, reliability, and performance.  The system is based on a
-distributed object storage service called RADOS (reliable autonomic distributed
-object store) that manages the distribution, replication, and migration of
-objects.  On top of that reliable storage abstraction Ceph builds a range of
-services, including a block storage abstraction (RBD, or rados block device)
-and a cache-coherent distributed file system (CephFS).
+This paper presents our findings on block I/O and file system performance of
+Ceph for scientific high-performance computing (HPC) environments. Through
+systematic experiments and tuning efforts, we observed that Ceph can perform
+close to 80\% of raw hardware bandwidth at object level and close to 70\% of
+at file system level. We also identified that Ceph's metadata 
+plus data journaling design is a weak spot for a typical
 
-Data objects are distributed across storage daemons (ceph-osd) using
-CRUSH\cite{Weil:2006:Crush}, a deterministic hashing function that allows
-administrators to define flexible placement policies over a hierarchical
-cluster structure (e.g., disks, hosts, racks, rows, datacenters).  The
-location of objects can be calculated based on the object identifier and
-cluster layout (similar to consistent hashing~\cite{karger1997consistent}),
-thus there is no need for a metadata index or server for the RADOS object store.
-%Further, because CRUSH provides an authoritative view of data placement,
-%storage daemons can coordinate directly to handle data replications, recovery,
-%or object migration in the face of failure or cluster topology changes.  
-A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus on
-the current cluster layout, but do not need to explicitly coordinate migration
-or recovery activities.
-
-CephFS builds a distributed cache-coherent file system on top of the object
-storage service provided by RADOS.  Files are striped across replicated
-storage objects, while a separate cluster of metadata servers (ceph-mds
-daemons) manage the file system namespace and coordinate client access to
-files.
-
-Ceph metadata servers store all metadata in RADOS objects, which provides a
-shared, highly-available, and reliable storage backend.  Unlike many other
-distributed file system architectures, Ceph also embeds inodes inside
-directories in the common case, allowing entire directories to read from RADOS
-into the metadata server cache or prefetched into the client cache using a
-single request.
-
-Client hosts that mount the file system communicate with metadata
-servers to traverse the namespace and perform file I/O by reading and writing
-directly to RADOS objects that contain the file data.  The metadata server
-cluster periodically adjusts
-the distribution of the namespace across the MDS cluster by migrating
-responsibility for arbitrary subtrees of the hierarchy between a dynamic pool
-of active ceph-mds daemons.  This dynamic subtree
-partitioning~\cite{Weil:2004:dynamic} strategy is both adaptive and highly
-scalable, allowing additional metadata server daemons to be added or removed
-at any time, making it ideally suited both for large-scale workloads with
-bursty workloads or general purpose clusters whose workloads grow or contract
-over time.
-
-\begin{comment}
-In comparison to other parallel file
-systems, Ceph has a number of distinctive features:
-
-\begin{itemize}
-
-\item Ceph has an intelligent and powerful data placement mechanism, known as
-  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
-  placement and layout while taking into consideration of failure domains and
-  hierarchical storage tiers.
-
-  \item From the start, Ceph's design anticipated managing meta data and the
-  name space with a cluster of meta data servers. It utilized a dynamic subtree
-  partitioning strategy to continuously adapt meta data distribution to current
-  demands.
-
-  \item Ceph's design assumes that the system is composed of unreliable
-  components; fault-detection and fault-tolerance (e.g., replication) are the
-  norm rather than the exception. This is in line with the expectations and
-  future directions of Exascale computing.
-
-  \item Ceph is built on top of a unified object management layer, RADOS. Both
-  meta data and the file data can take advantage of this uniformity. On top of
-  RADOS, Ceph build and project a host of other features such as RESTful
-  interface, S3 and Swift-compliant API, cloud integration.
-
-  \item Most of the Ceph processes reside in user-space. Generally speaking,
-this makes the system easier to debug and maintain. The client-side support has
-long been integrated into Linux mainline kernel, which eases the deployment and
-out-of-box experience.
-
-\end{itemize}
-\end{comment}
-
-While we are interested in Ceph for its ability to support
-alternative workloads that are not easily accomplished with Lustre, in this
-study we are investigating the use Ceph for future
-large-scale scientific HPC storage deployments. This paper presents our
-experience, results, and observations in measuring the scalability and
-performance of Ceph for capability workloads.  Additionally, Ceph is under
-rapid development, and in  between releases, we often
-experienced different stability and performance outcomes.  
-%We will try to make
-%clear in the writing when such changes occurred.
-%As interesting and feature-rich as Ceph may be,  scalability and performance
-%are our top priorities due to the unique requirements our environment.  As part
-%of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
-%Our goal was to investigate the feasibility of using the Ceph for future
-%large-scale scientific HPC storage deployments. This paper presents our
-%experience, results, and observations.  While evaluating our results, please
-%keep in mind that Ceph is still a relatively \textit{young} parallel file
-%system and its code base is changing rapidly. In between releases, we often
-%experienced different stability and performance outcomes.  We will try to make
-%clear in the writing when such changes occurred.
-
-%This paper is organized as follows. Section~\ref{sec:testbed} gives an
-%overview on our general test and evaluation methodology as well as testbed
-%environment; Following it, Section~\ref{sec:baseline} establishes the baseline
-%performance and expectations for all critical components on the data path;
-%Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
-%bottom up: from middle tier RADOS object layer to the file system-level and
-%then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
-%investigative and tuning effort, we compare results before and after, and how
-%the process eventually bring the system performance to a respectable state.
-%Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
-%and future works.
+This rest of the paper is organized as follows. Section~\ref{sec:testbed} gives an
+overview on our general test and evaluation methodology as well as testbed
+environment; Following it, Section~\ref{sec:baseline} establishes the baseline
+performance and expectations for all critical components on the data path;
+Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
+bottom up: from middle tier RADOS object layer to the file system-level and
+then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
+investigative and tuning effort, we compare results before and after, and how
+the process eventually bring the system performance to a respectable state.
+Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
+and future works.

### 2013-11-05 background.tex
split background

\section{Introduction}

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems. 
%The facility hosted
%the Jaguar supercomputer up until recently, which was upgraded to the Titan
%supercomputer. 
In order to satisfy the I/O demand of such supercomputers, OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  
%The latest such
%large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
%2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
%has a 40 PB of raw disk capacity. As the scratch 
%file system for Titan, a leadership computing platform,
%Spider II emphasizes \textit{capability} over \textit{capacity}. 
However, we
recognize that there are a wide variety of scientific data and emerging
workloads with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.

This paper presents our file and block I/O performance and scalability
evaluation of Ceph for scientific high-performance computing (HPC)
environments. Through systematic experiments and tuning efforts, we are able
to observe Ceph performing close to 80\% of raw hardware bandwidth at object
level and close to 70\% of at file system level.

\section{Background}

Ceph\cite{Weil:2006:Ceph} is a distributed storage system designed for
scalability, reliability, and performance.  The system is based on a
distributed object storage service called RADOS (reliable autonomic distributed
object store) that manages the distribution, replication, and migration of
objects.  On top of that reliable storage abstraction Ceph builds a range of
services, including a block storage abstraction (RBD, or rados block device)
and a cache-coherent distributed file system (CephFS).

Data objects are distributed across storage daemons (ceph-osd) using
CRUSH\cite{Weil:2006:Crush}, a deterministic hashing function that allows
administrators to define flexible placement policies over a hierarchical
cluster structure (e.g., disks, hosts, racks, rows, datacenters).  The
location of objects can be calculated based on the object identifier and
cluster layout (similar to consistent hashing~\cite{karger1997consistent}),
thus there is no need for a metadata index or server for the RADOS object store.
%Further, because CRUSH provides an authoritative view of data placement,
%storage daemons can coordinate directly to handle data replications, recovery,
%or object migration in the face of failure or cluster topology changes.  
A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus on
the current cluster layout, but do not need to explicitly coordinate migration
or recovery activities.

CephFS builds a distributed cache-coherent file system on top of the object
storage service provided by RADOS.  Files are striped across replicated
storage objects, while a separate cluster of metadata servers (ceph-mds
daemons) manage the file system namespace and coordinate client access to
files.

Ceph metadata servers store all metadata in RADOS objects, which provides a
shared, highly-available, and reliable storage backend.  Unlike many other
distributed file system architectures, Ceph also embeds inodes inside
directories in the common case, allowing entire directories to read from RADOS
into the metadata server cache or prefetched into the client cache using a
single request.

Client hosts that mount the file system communicate with metadata
servers to traverse the namespace and perform file I/O by reading and writing
directly to RADOS objects that contain the file data.  The metadata server
cluster periodically adjusts
the distribution of the namespace across the MDS cluster by migrating
responsibility for arbitrary subtrees of the hierarchy between a dynamic pool
of active ceph-mds daemons.  This dynamic subtree
partitioning~\cite{Weil:2004:dynamic} strategy is both adaptive and highly
scalable, allowing additional metadata server daemons to be added or removed
at any time, making it ideally suited both for large-scale workloads with
bursty workloads or general purpose clusters whose workloads grow or contract
over time.

\begin{comment}
In comparison to other parallel file
systems, Ceph has a number of distinctive features:

\begin{itemize}

\item Ceph has an intelligent and powerful data placement mechanism, known as
  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
  placement and layout while taking into consideration of failure domains and
  hierarchical storage tiers.

  \item From the start, Ceph's design anticipated managing meta data and the
  name space with a cluster of meta data servers. It utilized a dynamic subtree
  partitioning strategy to continuously adapt meta data distribution to current
  demands.

  \item Ceph's design assumes that the system is composed of unreliable
  components; fault-detection and fault-tolerance (e.g., replication) are the
  norm rather than the exception. This is in line with the expectations and
  future directions of Exascale computing.

  \item Ceph is built on top of a unified object management layer, RADOS. Both
  meta data and the file data can take advantage of this uniformity. On top of
  RADOS, Ceph build and project a host of other features such as RESTful
  interface, S3 and Swift-compliant API, cloud integration.

  \item Most of the Ceph processes reside in user-space. Generally speaking,
this makes the system easier to debug and maintain. The client-side support has
long been integrated into Linux mainline kernel, which eases the deployment and
out-of-box experience.

\end{itemize}
\end{comment}

While we are interested in Ceph for its ability to support
alternative workloads that are not easily accomplished with Lustre, in this
study we are investigating the use Ceph for future
large-scale scientific HPC storage deployments. This paper presents our
experience, results, and observations in measuring the scalability and
performance of Ceph for capability workloads.  Additionally, Ceph is under
rapid development, and in  between releases, we often
experienced different stability and performance outcomes.  
%We will try to make
%clear in the writing when such changes occurred.
%As interesting and feature-rich as Ceph may be,  scalability and performance
%are our top priorities due to the unique requirements our environment.  As part
%of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
%Our goal was to investigate the feasibility of using the Ceph for future
%large-scale scientific HPC storage deployments. This paper presents our
%experience, results, and observations.  While evaluating our results, please
%keep in mind that Ceph is still a relatively \textit{young} parallel file
%system and its code base is changing rapidly. In between releases, we often
%experienced different stability and performance outcomes.  We will try to make
%clear in the writing when such changes occurred.

%This paper is organized as follows. Section~\ref{sec:testbed} gives an
%overview on our general test and evaluation methodology as well as testbed
%environment; Following it, Section~\ref{sec:baseline} establishes the baseline
%performance and expectations for all critical components on the data path;
%Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
%bottom up: from middle tier RADOS object layer to the file system-level and
%then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
%investigative and tuning effort, we compare results before and after, and how
%the process eventually bring the system performance to a respectable state.
%Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
%and future works.

### 2013-11-06 report.tex
Add sponsorship info

@@
 
+\usepackage{tikz}
+
 \graphicspath{{./figs/}}
 \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+
+\title{Ceph Parallel File System Evaluation Report}
+\date{}
+\newcommand\sponsortext{%
+This research was supported by, and used the
+resources of, the Oak Ridge Leadership Computing Facility, located in the
+National Center for Computational Sciences at ORNL, which is managed by UT
+Battelle, LLC for the U.S. DOE (under the contract No. DE-AC05-00OR22725).}
+
+\newcommand\sponsornotice{%
+\begin{tikzpicture}[remember picture,overlay]
+\node[anchor=south,yshift=30pt] at (current page.south)
+{\fbox{\parbox{\dimexpr\textwidth-\fboxsep-\fboxrule\relax}{\sponsortext}}};
+\end{tikzpicture}%
+}
 
@@
 
-%\maketitle
+% \maketitle
 %\authorrunning{}
 %\titlerunning{}
+
+\sponsornotice
 

### 2013-11-06 background.tex
fixing based on various review comments

@@
-\section{Introduction}
-
-Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
-supported by, and used the resources of, the Oak Ridge Leadership Computing
-Facility, located in the National Center for Computational Sciences at ORNL,
-which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
-DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
-of deploying and running very-large-scale high-performance computing (HPC)
-systems. 
-%The facility hosted
-%the Jaguar supercomputer up until recently, which was upgraded to the Titan
-%supercomputer. 
-In order to satisfy the I/O demand of such supercomputers, OLCF
-also hosts large-scale file and storage systems. Lustre has been OLCF's choice
-as the distributed parallel file system.  
-%The latest such
-%large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
-%2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
-%has a 40 PB of raw disk capacity. As the scratch 
-%file system for Titan, a leadership computing platform,
-%Spider II emphasizes \textit{capability} over \textit{capacity}. 
-However, we
-recognize that there are a wide variety of scientific data and emerging
-workloads with different performance and data access requirements (e.g., RESTful
-interface, S3-like API, cloud solution integration) which might not be
-efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
-file and storage system technologies.
-
-This paper presents our file and block I/O performance and scalability
-evaluation of Ceph for scientific high-performance computing (HPC)
-environments. Through systematic experiments and tuning efforts, we are able
-to observe Ceph performing close to 80\% of raw hardware bandwidth at object
-level and close to 70\% of at file system level.
-
 \section{Background}
+\label{sec:background}
 
@@
 
-Data objects are distributed across storage daemons (ceph-osd) using
-CRUSH\cite{Weil:2006:Crush}, a deterministic hashing function that allows
-administrators to define flexible placement policies over a hierarchical
-cluster structure (e.g., disks, hosts, racks, rows, datacenters).  The
-location of objects can be calculated based on the object identifier and
-cluster layout (similar to consistent hashing~\cite{karger1997consistent}),
-thus there is no need for a metadata index or server for the RADOS object store.
+Data objects are distributed across Object Storage Devices (OSD), which refers
+to either physical or logical storage unit, using CRUSH\cite{Weil:2006:Crush},
+a deterministic hashing function that allows administrators to define flexible
+placement policies over a hierarchical cluster structure (e.g., disks, hosts,
+racks, rows, datacenters).  The location of objects can be calculated based on
+the object identifier and cluster layout (similar to consistent
+hashing~\cite{karger1997consistent}), thus there is no need for a metadata
+index or server for the RADOS object store.
 %Further, because CRUSH provides an authoritative view of data placement,
-%storage daemons can coordinate directly to handle data replications, recovery,
-%or object migration in the face of failure or cluster topology changes.  
-A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus on
-the current cluster layout, but do not need to explicitly coordinate migration
-or recovery activities.
+%storage daemons can coordinate directly to handle data replications,
+%recovery, or object migration in the face of failure or cluster topology
+%changes.  
+A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus
+on the current cluster layout, but do not need to explicitly coordinate
+migration or recovery activities.
 
@@
 
-While we are interested in Ceph for its ability to support
-alternative workloads that are not easily accomplished with Lustre, in this
-study we are investigating the use Ceph for future
-large-scale scientific HPC storage deployments. This paper presents our
-experience, results, and observations in measuring the scalability and
-performance of Ceph for capability workloads.  Additionally, Ceph is under
-rapid development, and in  between releases, we often
-experienced different stability and performance outcomes.  
+While we are interested in Ceph for its ability to support alternative
+workloads that are not easily accomplished with Lustre, in this study we are
+investigating the use Ceph for future large-scale scientific HPC storage
+deployments. This paper presents our experience, results, and observations in
+measuring the scalability and performance of Ceph.
+
+%Additionally, Ceph is under
+%rapid development, and in between releases, we often
+%experienced different stability and performance outcomes.  
 %We will try to make

### 2013-11-06 ceph-tuning.tex
fixing based on various review comments

@@
-\section{Further Optimization and Improvements}
+\section{Further Optimization \\and Improvements}
 \label{sec:ceph-tuning}
@@
 \centering
-\includegraphics[width=3.5in]{parametric}
+\includegraphics[width=3.5in]{para2}
+%\includegraphics[width=3.5in]{parametric}
 \caption{Evaluating parameter impact through sweeping test}
@@
 After the initial test results, we tried various combinations of tweaks
-including changing the number of filestore op threads, putting all of the
+including: changing the number of filestore op threads, putting all of the
 journals on the same disks as the data, doubling the OSD count, and upgrading
@@
 \texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
-included as of the Ceph Cuttlefish release, v0.61).  The two biggest
-improvements resulted from disabling CRC32c checksums and increasing the OSD
-count on the server.  With these changes, we are seeing better results.
+included as of the Ceph Cuttlefish release, v0.61).
+
+%The two biggest
+%improvements resulted from disabling CRC32c checksums and increasing the OSD
+%count on the server.  With these changes, we are seeing better results.
 
@@
 Appendix E of \cite{ceph:techreport} for explanations of these probed
-parameters.
+parameters. In this figure, the default is where we started with. Reads
+benefit from increasing the \verb!osd_op_threads! (4 and 8), with 7.3\% and
+9\% improvement respectively. For writes, the substantial boost comes with
+\verb!journal_aio! true and \verb!big_bytes!, with 11.5\% and 16.3\%
+improvement respectively. Other probed parameters (not shown on this figure)
+doesn't bear tangible impacts.
 
-As a result of this testing, we improved performance slightly by
-increasing the size of various Ceph buffers and queues, enabling AIO journals,
-and increasing the number of OSD op threads.
+%As a result of this testing, we improved performance slightly by
+%increasing the size of various Ceph buffers and queues, enabling AIO journals,
+%and increasing the number of OSD op threads.
 
@@
 %\includegraphics[width=3.5in]{ior-client-no-crc32}
-\includegraphics[width=3.5in]{ior_no_crc}
-\caption{IOR test with disabling client-side CRC32}
+%\includegraphics[width=3.5in]{ior_no_crc}
+\includegraphics[width=3.5in]{crc32}
+\caption{Impact of Disabling CRC32}
 \label{fig:ior-no-client-crc32}
@@
 Additionally, we increased the size of the CephFS kernel client's read-ahead
-chance.  
-%IOR results reflecting the read-ahead cache size change are presented
-%in Figure~\ref{fig:ior-kernel-39}.
+cache.  
+%IOR results reflecting the read-ahead cache size change are presented in
+%Figure~\ref{fig:ior-kernel-39}.
 

### 2013-11-06 introduction.tex
fixing based on various review comments

@@
 close to 80\% of raw hardware bandwidth at object level and close to 70\% of
-at file system level. We also identified that Ceph's metadata 
-plus data journaling design is a weak spot for a typical
+at file system level. We also identified that Ceph's metadata plus data
+journaling design is a weak spot as far as our particular storage
+infrastructure is concerned.
 
-This rest of the paper is organized as follows. Section~\ref{sec:testbed} gives an
-overview on our general test and evaluation methodology as well as testbed
-environment; Following it, Section~\ref{sec:baseline} establishes the baseline
-performance and expectations for all critical components on the data path;
+This rest of the paper is organized as follows. Section~\ref{sec:background}
+provides an overview to Ceph and its architectural components;
+Section~\ref{sec:testbed} gives an overview on our general test and evaluation
+methodology as well as testbed environment; Following it,
+Section~\ref{sec:baseline} establishes the baseline performance and
+expectations for all critical components on the data path;
 Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues

### 2013-11-06 testbed.tex
cutting
fixing based on various review comments

--- 2013-09-05 testbed.tex
@@
 setup is adequate to drive the SFA10K at its maximum theoretical throughput
-(roughly 12 GB/s). Server hosts and SFA10K connection diagram is illustrated in
-Figure~\ref{fig:ddn-sfa10k}.
+(roughly 12 GB/s). 
+%Server hosts and SFA10K connection diagram is illustrated in
+%Figure~\ref{fig:ddn-sfa10k}.
 
+\begin{comment}
 \begin{figure}[htb]
@@
 
-Our tools for benchmarking and evaluating different layers also change as we
-go up in the stack.  For example, a tool perfect for assessing block-level
-performance over a single server host might be completely inadequate for
-observing parallel file system performance over multiple clients. As we
-present our evaluations, we will also introduce and explain our benchmark
-tools along the way.
+%Our tools for benchmarking and evaluating different layers also change as we
+%go up in the stack.  For example, a tool perfect for assessing block-level
+%performance over a single server host might be completely inadequate for
+%observing parallel file system performance over multiple clients. As we
+%present our evaluations, we will also introduce and explain our benchmark
+%tools along the way.

### 2013-11-06 ceph-initial.tex
cutting
more fixes based on the reviewer's comment

@@
 
-Our early testing indicated a read performace abberation.  There were periods of high performance followed by
-periods of low performance or outright stalls that could last for up to 20
-seconds at a time.  RADOS bench recorded poor read performance across
-different backend file systems, as shown in
-Figure~\ref{fig:rados-tcp-autotune}.
+Our early testing indicated a read performace abberation.  There were periods
+of high performance followed by periods of low performance or outright stalls
+that could last for up to 20 seconds at a time.  RADOS bench recorded poor
+read performance across different backend file systems, as shown in
+Figure~\ref{fig:rados-tcp-autotune}.\footnote{Although we conducted this
+particular experiment with three different flavors of local file system, with
+BTRFS the best performer, Inktank however doesn't think BTRFS is
+production-ready yet. So when not explicitly stated, the follow-on experiments
+use XFS by default.}
 
@@
 at Sandia National labs encountered with TCP autotuning in the Linux
-kernel\cite{Jim:tcptune}.
-TCP auto tuning enables TCP window scaling by default and automatically adjusts
-the TCP receive window for each connection based on link conditions such as
-bandwidth delay product.
+kernel\cite{Jim:tcptune}. TCP auto tuning enables TCP window scaling by
+default and automatically adjusts the TCP receive window for each connection
+based on link conditions such as bandwidth delay product.
 
@@
 We measured performance at the client (using RADOS bench) for one to four OSD
-servers.  Each additional OSD server adds eleven
-more OSDs into play.  Figure~\ref{fig:oss-scale} demonstrates that read
-performance improved about 10\% given eight clients instead of four, but write
-performance is mostly flat.  The lost write performance compared to a single
-OSD is attributed to Ceph journaling.  Ceph does not support meta-data only
-journaling, therefore every write is the equivalent of a double-write: once to
-the data device, once to the journaling device.  It is unclear why read
-performance is so much lower than the theoretical maximum.
+servers. Each additional OSD server adds eleven more OSDs into play. Based on
+Figure~\ref{fig:osd-scale}, the perfect scaling projects the aggregated read
+with 4 OSSs should be at 6616 MB/s and write at 5640 MB/s.
+Figure~\ref{fig:oss-scale} demonstrates that both read and write
+\textit{scales} with increasing number of OSSs, but at a loss of 13.6\% and
+16.0\% respectively. We will discuss the improvement to this result through
+parameter probing.
+
+%Figure~\ref{fig:oss-scale} demonstrates that read
+%performance improved about 10\% given eight clients instead of four, but write
+%performance is mostly flat.  The lost write performance compared to a single
+%OSD is attributed to Ceph journaling.  Ceph does not support meta-data only
+%journaling, therefore every write is the equivalent of a double-write: once to
+%the data device, once to the journaling device.  It is unclear why read
+%performance is so much lower than the theoretical maximum.
+
 %This effectively cuts the observed system bandwidth in
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 
 \centerline{\subfloat[4 KB transfer size]
-{\includegraphics[width=3in]{data/ior_4k}
+%{\includegraphics[width=3in]{data/ior_4k}
+{\includegraphics[width=1.7in]{data/ior_4k}
 \label{fig:ior4k}}
@@
 \subfloat[4 MB transfer size]
-{\includegraphics[width=3in]{data/ior_4m}
+%{\includegraphics[width=3in]{data/ior_4m}
+{\includegraphics[width=1.7in]{data/ior_4m}
 \label{fig:ior4m}}
@@
 
-\end{figure*}
+\end{figure}
 

### 2013-11-06 ceph-tuning.tex
more fixes based on the reviewer's comment

@@
 MB.  These results are illustrated in Figure~\ref{fig:ior-064}, respectively.
-As expected, we saw saw  improved read and write performance. These new read
+As expected, we saw both improved read and write performance. These new read
 and write performance are in line with observed RADOS bench performance.
@@
 
-Throughout our IOR testing, we observed that the average write throughput is
-lower than the maximum.  This behavior was observed during other tests as well,
-indicating that we may have periods of time where write throughput is
-temporarily degrading.  Despite these issues, performance generally seems to be
-improving with respect to increasing number of clients.  Writes seem to be
-topping out at around 5.2 GB/s (which is roughly what we would expect due to
-journalling effectively halving the write performance).  Reads seem to be
-topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
-would continue scaling with more clients and get closer to ~8 GB/s we observed 
-with RADOS Bench.
+%Throughout our IOR testing, we observed that the average write throughput is
+%lower than the maximum.  
+% This behavior was observed during other tests as well,
+%indicating that we may have periods of time where write throughput is
+%temporarily degrading.  Despite these issues, performance generally seems to be
+%improving with respect to increasing number of clients.
+
+Writes seem to be topping out at around 5.2 GB/s (which is roughly what we
+would expect due to journaling effectively halving the write performance).
+Reads seem to be topping out anywhere from 5.6-7 GB/s, however it is unclear
+if read performance would continue scaling with more clients and get closer to
+8 GB/s we observed with RADOS Bench.
 

### 2013-11-06 baseline.tex
fixing based on various review comments
more fixes based on the reviewer's comment

@@
-\section{Establishing A Performance Baseline}
+\section{Establishing A \\Performance Baseline}
 \label{sec:baseline}
@@
 disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
-that a 7.2K RPM SAS disk can perform at \textasciitilde140 MB/s for 128 kB
-sequential I/O requests and a 7.2K RPM SATA disk can do \textasciitilde36 MB/s.
+that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
+sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
 For these tests, all disk caches were turned off. Therefore, in 8 data disk
 RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
-the request) the expected aggregate performance would be \textasciitilde1.12
-GB/s for a SAS RAID group and \textasciitilde288 MB/s for a SATA RAID group, if
+the request) the aggregate performance is about 1.12
+GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
 there are no caches along the I/O path.  With the caches turned on, especially

### 2013-11-07 baseline.tex
shrink Section 3 and 4.1 to fit 5 pages

@@
 the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
-disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
-that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
-sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
-For these tests, all disk caches were turned off. Therefore, in 8 data disk
-RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
-the request) the aggregate performance is about 1.12
-GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
-there are no caches along the I/O path.  With the caches turned on, especially
-the write-back cache on the DDN RAID controller, we observe a significant
-performance improvement. In our day-to-day HPC operations we run our storage
+disks and 2 \textit{P} and \textit{Q} disks).
+
+%In prior tests we observed
+%that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
+%sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
+%For these tests, all disk caches were turned off. Therefore, in 8 data disk
+%RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
+%the request) the aggregate performance is about 1.12
+%GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
+%there are no caches along the I/O path.  With the caches turned on, especially
+%the write-back cache on the DDN RAID controller, we observe a significant
+%performance improvement.
+
+In our day-to-day HPC operations, we run our storage
 systems with write-back cache turned on on RAID controllers, if and only if,
 there is a method of cache-mirroring between the two active-active RAID
-controllers. With the write-back cache on we observe \textasciitilde1.4 GB/s
-per RAID 6 8+2 SAS group and  \textasciitilde955 MB/s per RAID 6 8+2 SATA
+controllers. With the write-back cache on we observe \string~1.4 GB/s
+per RAID 6 8+2 SAS group and  \string~955 MB/s per RAID 6 8+2 SATA
 group, for 1 MB sequential I/O.  These two performance numbers will be used as

### 2013-11-07 testbed.tex
shrink Section 3 and 4.1 to fit 5 pages

@@
 Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
-10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
-has two SAS links per controller (four in total). The SATA and SAS disks in our
-testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
-disks per tray). Each SFA10K RAID controller has two RAID processors and each
-RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
-groups by the RAID processors (software RAID) and then exported to connected
-server hosts over the IB connections. Since each DDN SFA10K controller is a
+10-tray configuration.
+%Each DDN SA4601 disk tray can host up to 60 disks and
+%has two SAS links per controller (four in total). The SATA and SAS disks in our
+%testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
+%disks per tray). 
+%Each SFA10K RAID controller has two RAID processors and each
+%RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
+%groups by the RAID processors (software RAID) and then exported to connected
+%server hosts over the IB connections. 
+Since each DDN SFA10K controller is a
 stand-alone computer system running Linux, CPU and memory affinity while

### 2013-11-07 background.tex
add ack, paper, background

@@
 objects.  On top of that reliable storage abstraction Ceph builds a range of
-services, including a block storage abstraction (RBD, or rados block device)
+services, including a block storage abstraction (RBD, or Rados Block Device)
 and a cache-coherent distributed file system (CephFS).
@@
 Data objects are distributed across Object Storage Devices (OSD), which refers
-to either physical or logical storage unit, using CRUSH\cite{Weil:2006:Crush},
+to either physical or logical storage units, using CRUSH\cite{Weil:2006:Crush},
 a deterministic hashing function that allows administrators to define flexible
@@
 workloads that are not easily accomplished with Lustre, in this study we are
-investigating the use Ceph for future large-scale scientific HPC storage
-deployments. This paper presents our experience, results, and observations in
-measuring the scalability and performance of Ceph.
+investigating the use of Ceph for future large-scale scientific HPC storage
+deployments.
+
+%This paper presents our experience, results, and observations in
+%measuring the scalability and performance of Ceph.
 

### 2013-11-07 testbed.tex
add testbed

@@
 
-We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
+We used a Data Direct Networks (DDN) SFA10K as the storage backend for this
 evaluation. SFA10K organizes disks into various RAID levels by two
-active-active RAID controllers. Exported RAID groups (LUNs) by these
-controllers are driven by four server hosts (oss-[1-4]).  Each server host has
-two InfiniBand (IB) QDR connections to the storage backend.  We used a single
+active-active RAID controllers. In our testbed, exported RAID groups (LUNs) 
+are driven by four server hosts (oss-[1-4]).  Each server host has
+two InfiniBand (IB) QDR connections to SFA10K.  We used a single
 dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
@@
 
-Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
-10-tray configuration.
-%Each DDN SA4601 disk tray can host up to 60 disks and
-%has two SAS links per controller (four in total). The SATA and SAS disks in our
-%testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
+Our SFA10K system consists of 200 SAS drives and 280 SATA drives.
+% hosted in a
+%10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
+%has two SAS links per controller (four in total). 
+The SATA and SAS disks in our
+testbed are distributed evenly over the SFA10K.
+%ten SA4601 disk trays (20 SAS and 28 SATA
 %disks per tray). 
-%Each SFA10K RAID controller has two RAID processors and each
-%RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
-%groups by the RAID processors (software RAID) and then exported to connected
-%server hosts over the IB connections. 
-Since each DDN SFA10K controller is a
-stand-alone computer system running Linux, CPU and memory affinity while
-organizing disks into RAID groups and exporting them is crucial for obtaining
-top performance out of an SFA10K system.
+Each SFA10K controller has two RAID processors and each
+RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
+groups by the RAID processors and then exported to connected
+server hosts.
+%over the IB connections. 
+%Since each SFA10K controller is a
+%stand-alone computer system running Linux, CPU and memory affinity while
+%organizing disks into RAID groups and exporting them is crucial for obtaining
+%top performance out of an SFA10K system.
 
@@
 Our testing methodology is bottom to top. We start our evaluation from the
-lowest level (i.e. block-level)  to establish a baseline performance and work
-our way up to the top (i.e. file system-level). We establish an expected
+block-level to establish a baseline performance and work
+our way up to the file system-level. We establish an expected
 theoretical performance of a given hardware or software layer and then compare
@@
 stack introduces new bottlenecks and re-defines the expected theoretical
-performance of the overall system. We will explain each component or layer and
-its expected performance before we present our observed results.
+performance of the overall system. 
+%We will explain each component or layer and
+%its expected performance before we present our observed results.
 

### 2013-11-07 conclusion.tex
add intro

@@
 have seen a steady improvement through different releases. As of now, the Ceph
-system on our testbed is able to perform close to 80\% of raw hardware
-capability at RADOS level and close to 70\% at file system level (after
+system on our testbed is able to perform close to 70\% of raw hardware
+capability at RADOS level and close to 62\% at file system level (after
 accounting for journaling overheads) . 

### 2013-11-07 introduction.tex
add intro

@@
 also hosts large-scale file and storage systems. Lustre has been OLCF's choice
-as the distributed parallel file system.  
+as the distributed parallel file system for scratch I/O. 
 %The latest such
@@
 However, we
-recognize that there are a wide variety of scientific data and emerging
+recognize that there are a wide variety of scientific 
+%data and 
+%emerging
 workloads with different performance and data access requirements (e.g., RESTful
 interface, S3-like API, cloud solution integration) which might not be
-efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
-file and storage system technologies.
+efficiently serviced by Lustre. 
+%OLCF is constantly evaluating new and emerging
+%file and storage system technologies.
 
-This paper presents our findings on block I/O and file system performance of
-Ceph for scientific high-performance computing (HPC) environments. Through
-systematic experiments and tuning efforts, we observed that Ceph can perform
-close to 80\% of raw hardware bandwidth at object level and close to 70\% of
-at file system level. We also identified that Ceph's metadata plus data
-journaling design is a weak spot as far as our particular storage
+%\textit{FEIYI: Are the 80\% and 70\% numbers still valid?}
+This paper presents our evaluation and findings on block I/O and file system
+performance of Ceph for scientific HPC environments. Through systematic
+experiments and tuning efforts, we observed that Ceph can perform close to
+70\% of raw hardware bandwidth at object level and about 62\% of at file
+system level. We also identified that Ceph's metadata plus data journaling
+design is currently a weak spot as far as our particular storage
 infrastructure is concerned.

### 2013-11-11 introduction.tex
minor fixes for final touch

@@
 Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
-bottom up: from middle tier RADOS object layer to the file system-level and
-then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
-investigative and tuning effort, we compare results before and after, and how
-the process eventually bring the system performance to a respectable state.
-Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
-and future works.
+bottom up: from middle tier RADOS object layer to the file system-level
+performance. In Section~\ref{sec:ceph-tuning} we highlight the investigative
+and tuning effort, we compare results before and after, and how the process
+eventually bring the system performance to a respectable state. Finally,
+Section~\ref{sec:conclusion} summarizes our findings, observations, and future
+works.

### 2013-11-11 testbed.tex
minor fixes for final touch

@@
 active-active RAID controllers. In our testbed, exported RAID groups (LUNs)
-are driven by four server hosts (oss-[1-4]).  Each server host has
-two InfiniBand (IB) QDR connections to SFA10K.  We used a single
-dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
-setup is adequate to drive the SFA10K at its maximum theoretical throughput
-(roughly 12 GB/s). 
+are driven by four server hosts (oss-[1-4]).  Each server host has two
+InfiniBand (IB) QDR connections (supported by a dual-port Mellanox ConnectX IB
+card) to SFA10K. By our calculation, this setup is adequate to drive the
+SFA10K at its maximum theoretical throughput (roughly 12 GB/s). 
 %Server hosts and SFA10K connection diagram is illustrated in
@@
 
-Our SFA10K system consists of 200 SAS drives and 280 SATA drives.
-% hosted in a
-%10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
-%has two SAS links per controller (four in total). 
-The SATA and SAS disks in our
-testbed are distributed evenly over the SFA10K.
-%ten SA4601 disk trays (20 SAS and 28 SATA
-%disks per tray). 
-Each SFA10K controller has two RAID processors and each
-RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
-groups by the RAID processors and then exported to connected
-server hosts.
-%over the IB connections. 
-%Since each SFA10K controller is a
-%stand-alone computer system running Linux, CPU and memory affinity while
-%organizing disks into RAID groups and exporting them is crucial for obtaining
-%top performance out of an SFA10K system.
+Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
+10-tray configuration. 
+%Each DDN SA4601 disk tray can host up to 60 disks and has two SAS links per
+%controller (four in total). 
+The SATA and SAS disks in our testbed are distributed evenly over the SFA10K.
+%ten SA4601 disk trays (20 SAS and 28 SATA disks per tray). 
+Each SFA10K controller has two RAID processors and each RAID processor hosts a
+dual-port IB QDR card. The disks are organized into RAID groups by the RAID
+processors and then exported to connected server hosts.
+%over the IB connections. Since each SFA10K controller is a stand-alone
+%computer system running Linux, CPU and memory affinity while organizing disks
+%into RAID groups and exporting them is crucial for obtaining top performance
+%out of an SFA10K system.
 

### 2013-11-11 baseline.tex
minor fix
minor fixes for final touch

--- 2013-11-06 baseline.tex
@@
 the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
-disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
+disks and 2 \textit{P} and \textit{Q} disks).
+
+In prior tests we observed
 that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
@@
 the write-back cache on the DDN RAID controller, we observe a significant
-performance improvement. In our day-to-day HPC operations we run our storage
+performance improvement.
+
+In our day-to-day HPC operations, we run our storage
 systems with write-back cache turned on on RAID controllers, if and only if,
 there is a method of cache-mirroring between the two active-active RAID
-controllers. With the write-back cache on we observe \textasciitilde1.4 GB/s
-per RAID 6 8+2 SAS group and  \textasciitilde955 MB/s per RAID 6 8+2 SATA
+controllers. With the write-back cache on we observe \string~1.4 GB/s
+per RAID 6 8+2 SAS group and  \string~955 MB/s per RAID 6 8+2 SATA
 group, for 1 MB sequential I/O.  These two performance numbers will be used as
@@
 this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
-MB/s/disk. As can be seen, SATA RAID groups benefit from caching more than SAS
-groups.
+MB/s/disk.
+
+%As can be seen, SATA RAID groups benefit from caching more than SAS
+%groups.
 
